---
title: "EIP Service Center"
description: |
  This page shows data regarding the CRC screening efforts for EIP.
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}

rm(list=ls(all=T))

library(tidyverse)
library(ggplot2)
library(gt)
library(plotly)
library(reactable)


# EIP-CRC Screening Data

crc <- read.csv('M:/EIP Data/EIP-CRC Screening/Original Data/EIP CRC Screening Data 20230620_1330.csv')
dim(crc)
head(crc)

```


```{r, include=FALSE}

# EIP-CRC Screening started 5/3/2023
summary(crc$datetime)
crc$datetime <- as.Date(crc$datetime, format = '%m/%d/%Y')
summary(crc$datetime)
crc <- crc[which(crc$datetime >= '2023-05-03'), ]
dim(crc)
summary(crc$datetime)

total_screened <- nrow(crc)
total_screened


table(crc$pt_willing)
crc_excluded_screen <- select(crc, record_id, pt_willing)
crc_excluded_screen <- crc_excluded_screen[which(crc_excluded_screen$pt_willing == 0), ]
crc_excluded_screen <- nrow(crc_excluded_screen)
crc_excluded_screen

dim(crc)
crc <- crc[which(crc$pt_willing != 0), ]
dim(crc)


total_eip_eligible <- select(crc, record_id, age)
total_eip_eligible <- total_eip_eligible[which(total_eip_eligible$age >= 15), ]
table(total_eip_eligible$age)
dim(total_eip_eligible)
total_eip_eligible <- nrow(total_eip_eligible)
total_eip_eligible


total_eip_eligible_percent <- (total_eip_eligible/total_screened)*100
total_eip_eligible_percent <- signif(total_eip_eligible_percent, digits = 3)
total_eip_eligible_percent


table(crc$eip)
total_eip_screened <- select(crc, record_id, eip)
total_eip_screened <- total_eip_screened[which(total_eip_screened$eip == 1), ]
dim(total_eip_screened)
total_eip_screened <- nrow(total_eip_screened)
total_eip_screened


total_eip_eligible_screened <- (total_eip_screened/total_eip_eligible)*100
total_eip_eligible_screened <- signif(total_eip_eligible_screened, digits = 3)
total_eip_eligible_screened


daily_crc_screen <- select(crc, datetime, record_id, eip)
head(daily_crc_screen)
daily_crc_screen$crc_screen <- 1
daily_crc_screen <- select(daily_crc_screen, -record_id)
head(daily_crc_screen)

daily_screening <- aggregate(x = daily_crc_screen[c("eip","crc_screen")],
                             FUN = sum,
                             by = list(Date = daily_crc_screen$datetime))
daily_screening$eip[is.na(daily_screening$eip)] <- 0
daily_screening$crc_screen[is.na(daily_screening$crc_screen)] <- 0
head(daily_screening)
daily_screening


crc <- select(crc, -pt_location, -pt_willing, -abbott_istat, -astral, -boost, -brain_pulse2,
              -cgwell, -endolow, -fastest, -headsmartii_v2, -icecap, -istat, -most, -platinum,
              -portola, -rnaseq, -sensecan, -sense5, -siemenspoc, -reset, -restore1,
              -ed_general_screen_complete, -eip_provider_name,
              -eip_service_center_screening_complete)
head(crc)
table(crc$eip)
crc <- crc[which(crc$eip == 1), ]
dim(crc)




# Defining sex/gender

table(crc$sex)
crc$sex[crc$sex == 0] <- 'Male'
crc$sex[crc$sex == 1] <- 'Female'
table(crc$sex)

table(crc$sex, crc$gender)
crc$gender[crc$gender == 0 & crc$sex == 'Male'] <- 'Male'
crc$gender[crc$gender == 1 & crc$sex == 'Male'] <- 'Transgender/Nonbinary'
crc$gender[crc$gender == 0 & crc$sex == 'Female'] <- 'Transgender/Nonbinary'
crc$gender[crc$gender == 1 & crc$sex == 'Female'] <- 'Female'
crc$gender[crc$gender == 2] <- 'Transgender/Nonbinary'
table(crc$sex, crc$gender)




# Defining Race

table(crc$race___1)
White <- crc[which(crc$race___1 == 1), ]
dim(White)
White <- select(White, record_id)
White$White <- 1
table(White$White)
White <- distinct(White)
dim(White)
head(White)

table(crc$race___2)
Black <- crc[which(crc$race___2 == 1), ]
dim(Black)
Black <- select(Black, record_id)
Black$Black <- 1
table(Black$Black)
Black <- distinct(Black)
dim(Black)
head(Black)

table(crc$race___3)
AmIn <- crc[which(crc$race___3 == 1), ]
dim(AmIn)
AmIn <- select(AmIn, record_id)
AmIn$AmIn <- 1
table(AmIn$AmIn)
AmIn <- distinct(AmIn)
dim(AmIn)
head(AmIn)

table(crc$race___4)
Asian <- crc[which(crc$race___4 == 1), ]
dim(Asian)
Asian <- select(Asian, record_id)
Asian$Asian <- 1
table(Asian$Asian)
Asian <- distinct(Asian)
dim(Asian)
head(Asian)

table(crc$race___5)
NHPI <- crc[which(crc$race___5 == 1), ]
dim(NHPI)
NHPI <- select(NHPI, record_id)
NHPI$NHPI <- 1
table(NHPI$NHPI)
NHPI <- distinct(NHPI)
dim(NHPI)
head(NHPI)

table(crc$race___6)
RaceOther <- crc[which(crc$race___6 == 1), ]
dim(RaceOther)
RaceOther <- select(RaceOther, record_id)
RaceOther$RaceOther <- 1
table(RaceOther$RaceOther)
RaceOther <- distinct(RaceOther)
dim(RaceOther)
head(RaceOther)

table(crc$race___9)
Multi <- crc[which(crc$race___9 == 1), ]
dim(Multi)
Multi <- select(Multi, record_id)
Multi$Multi <- 1
table(Multi$Multi)
Multi <- distinct(Multi)
dim(Multi)
head(Multi)

table(crc$race___10)
Hisp <- crc[which(crc$race___10 == 1), ]
dim(Hisp)
Hisp <- select(Hisp, record_id)
Hisp$Hisp <- 1
table(Hisp$Hisp)
Hisp <- distinct(Hisp)
dim(Hisp)
head(Hisp)

table(crc$race___7)
table(crc$race___8)
RaceUnk <- crc[which(crc$race___7 == 1 | crc$race___8 == 1), ]
dim(RaceUnk)
RaceUnk <- select(RaceUnk, record_id)
RaceUnk$RaceUnk <- 1
table(RaceUnk$RaceUnk)
RaceUnk <- distinct(RaceUnk)
dim(RaceUnk)
head(RaceUnk)




race <- select(crc, record_id)
race <- distinct(race)
dim(race)


dim(race)
race <- merge(race, White, by = 'record_id', all.x = T)
race <- merge(race, Black, by = 'record_id', all.x = T)
race <- merge(race, AmIn, by = 'record_id', all.x = T)
race <- merge(race, Asian, by = 'record_id', all.x = T)
race <- merge(race, NHPI, by = 'record_id', all.x = T)
race <- merge(race, RaceOther, by = 'record_id', all.x = T)
race <- merge(race, Multi, by = 'record_id', all.x = T)
race <- merge(race, Hisp, by = 'record_id', all.x = T)
race <- merge(race, RaceUnk, by = 'record_id', all.x = T)
dim(race)
head(race)
table(race$White)

race$White[is.na(race$White)] <- 0
race$Black[is.na(race$Black)] <- 0
race$AmIn[is.na(race$AmIn)] <- 0
race$Asian[is.na(race$Asian)] <- 0
race$NHPI[is.na(race$NHPI)] <- 0
race$RaceOther[is.na(race$RaceOther)] <- 0
race$Multi[is.na(race$Multi)] <- 0
race$Hisp[is.na(race$Hisp)] <- 0
race$RaceUnk[is.na(race$RaceUnk)] <- 0

race$RaceNumber <- race$White + race$Black + race$AmIn + race$Asian + race$NHPI + race$RaceOther + race$Multi + race$Hisp + race$RaceUnk
table(race$RaceNumber)
head(race)

race$race[race$RaceNumber == 1 & race$White == 1] <- 'White or Caucasian'
race$race[race$RaceNumber == 1 & race$Black == 1] <- 'Black or African American'
race$race[race$RaceNumber == 1 & race$AmIn == 1] <- 'American Indian or Alaska Native'
race$race[race$RaceNumber == 1 & race$Asian == 1] <- 'Asian'
race$race[race$RaceNumber == 1 & race$NHPI == 1] <- 'Native Hawaiian or Other Pacific Islander'
race$race[race$RaceNumber == 1 & race$RaceOther == 1] <- 'Other'
race$race[race$RaceNumber == 1 & race$Hisp == 1] <- 'Hispanic'
race$race[race$Multi == 1 | (race$RaceNumber > 1)] <- 'Biracial/Multiracial'
race$race[race$RaceNumber == 0 | is.na(race$RaceNumber) | race$RaceUnk == 1] <- 'Unknown'
table(race$race)

dim(crc)
dim(race)
crc <- merge(crc, race, by = 'record_id', all.x = T)
dim(crc)
table(crc$race)


table(crc$race, crc$ethnicity)
crc$race[crc$race == 'White or Caucasian' & crc$ethnicity == 1] <- 'Biracial/Multiracial'
crc$race[crc$race == 'Black or African American' & crc$ethnicity == 1] <- 'Biracial/Multiracial'
crc$race[crc$race == 'American Indian or Alaska Native' & crc$ethnicity == 1] <- 'Biracial/Multiracial'
crc$race[crc$race == 'Asian' & crc$ethnicity == 1] <- 'Biracial/Multiracial'
crc$race[crc$race == 'Native Hawaiian or Other Pacific Islander' & crc$ethnicity == 1] <- 'Biracial/Multiracial'
crc$race[crc$race == 'Other' & crc$ethnicity == 1] <- 'Biracial/Multiracial'
crc$race[crc$race == 'Biracial/Multiracial' & crc$ethnicity == 1] <- 'Biracial/Multiracial'
crc$race[crc$race == 'Unknown' & crc$ethnicity == 1] <- 'Hispanic'

table(crc$race, crc$ethnicity)

head(crc)
crc <- select(crc, -race___3, -race___4, -race___2, -race___10, -race___9, -race___5, -race___6,
              -race___7, -race___8, -race___1, -ethnicity, -RaceUnk, -RaceNumber, -White, -Black,
              -AmIn, -Asian, -NHPI, -RaceOther, -Multi, -Hisp)
head(crc)
dim(crc)



# Creating a patient list

patients <- select(crc, mrn)
dim(patients)
patients <- distinct(patients)
dim(patients)
head(patients)



age <- select(crc, mrn, age)
dim(age)
age <- distinct(age)
dim(age)
age <- age[order(age$mrn),]
age$dup <- duplicated(age$mrn)
age <- age[which(age$dup == F), ]
dim(age)
age <- select(age, -dup)
dim(age)

dim(patients)
dim(age)
patients <- merge(patients, age, by = 'mrn', all.x = T)
dim(patients)
head(patients)



sex <- select(crc, mrn, sex)
dim(sex)
sex <- distinct(sex)
dim(sex)
sex <- sex[order(sex$mrn),]
sex$dup <- duplicated(sex$mrn)
sex <- sex[which(sex$dup == F), ]
dim(sex)
sex <- select(sex, -dup)
dim(sex)

dim(patients)
dim(sex)
patients <- merge(patients, sex, by = 'mrn', all.x = T)
dim(patients)
head(patients)



gender <- select(crc, mrn, gender)
dim(gender)
gender <- distinct(gender)
dim(gender)
gender <- gender[order(gender$mrn),]
gender$dup <- duplicated(gender$mrn)
gender <- gender[which(gender$dup == F), ]
dim(gender)
gender <- select(gender, -dup)
dim(gender)

dim(patients)
dim(gender)
patients <- merge(patients, gender, by = 'mrn', all.x = T)
dim(patients)
head(patients)



race <- select(crc, mrn, race)
dim(race)
race <- distinct(race)
dim(race)
race <- race[order(race$mrn),]
race$dup <- duplicated(race$mrn)
race <- race[which(race$dup == F), ]
dim(race)
race <- select(race, -dup)
dim(race)

dim(patients)
dim(race)
patients <- merge(patients, race, by = 'mrn', all.x = T)
dim(patients)
head(patients)




# Creating Encounter/Screening Data

head(crc)
enc <- select(crc, -chief_comp, -eip, -eip_start, -eip_calc, -eip_eligible, -eip_complete_step3,
              -eip_complete_time1, -epi_sign1, -eip_id1, -csn)
head(enc)
dim(enc)

dim(enc)
total_eip_eligible_age <- nrow(enc)
total_eip_eligible_age
total_screened
eligible_screened_percent <- ((nrow(enc))/total_screened)*100
eligible_screened_percent <- signif(eligible_screened_percent, digits = 2)
eligible_screened_percent

summary(enc$datetime)
enc$enc_date <- as.Date(enc$datetime, format = '%m/%d/%Y')
summary(enc$enc_date)
enc <- select(enc, -datetime)


table(enc$sex_assault)
enc$sex_assault <- as.numeric(enc$sex_assault)
total_sex_assault <- sum(enc$sex_assault, na.rm = TRUE)
total_sex_assault
total_sex_assault[is.na(total_sex_assault)] <- 0
total_sex_assault
total_sex_assault_percent <- (total_sex_assault/total_eip_eligible_age)*100
total_sex_assault_percent <- signif(total_sex_assault_percent, digits = 2)
total_sex_assault_percent


table(enc$overdose)
enc$overdose <- as.numeric(enc$overdose)
total_overdose <- sum(enc$overdose, na.rm = TRUE)
total_overdose
total_overdose[is.na(total_overdose)] <- 0
total_overdose
total_overdose_percent <- (total_overdose/total_eip_eligible_age)*100
total_overdose_percent <- signif(total_overdose_percent, digits = 2)
total_overdose_percent


table(enc$opiates)
enc$opiates <- as.numeric(enc$opiates)
total_opiates <- sum(enc$opiates, na.rm = TRUE)
total_opiates
total_opiates[is.na(total_opiates)] <- 0
total_opiates
total_opiates_percent <- (total_opiates/total_eip_eligible_age)*100
total_opiates_percent <- signif(total_opiates_percent, digits = 2)
total_opiates_percent


table(enc$preg)
enc$preg <- as.numeric(enc$preg)
total_preg <- sum(enc$preg, na.rm = TRUE)
total_preg
total_preg[is.na(total_preg)] <- 0
total_preg
total_preg_percent <- (total_preg/total_eip_eligible_age)*100
total_preg_percent <- signif(total_preg_percent, digits = 2)
total_preg_percent


table(enc$hiv)
enc$hiv <- as.numeric(enc$hiv)
total_hiv <- sum(enc$hiv, na.rm = TRUE)
total_hiv
total_hiv[is.na(total_hiv)] <- 0
total_hiv
total_hiv_percent <- (total_hiv/total_eip_eligible_age)*100
total_hiv_percent <- signif(total_hiv_percent, digits = 2)
total_hiv_percent


table(enc$idc)
enc$idc <- as.numeric(enc$idc)
total_idc <- sum(enc$idc, na.rm = TRUE)
total_idc
total_idc[is.na(total_idc)] <- 0
total_idc
total_idc_percent <- (total_idc/total_hiv)*100
total_idc_percent <- signif(total_idc_percent, digits = 2)
total_idc_percent


table(enc$pwid)
enc$pwid <- as.numeric(enc$pwid)
total_pwid <- sum(enc$pwid, na.rm = TRUE)
total_pwid
total_pwid[is.na(total_pwid)] <- 0
total_pwid
total_pwid_percent <- (total_pwid/total_eip_eligible_age)*100
total_pwid_percent <- signif(total_pwid_percent, digits = 2)
total_pwid_percent


table(enc$sti)
enc$sti <- as.numeric(enc$sti)
total_sti <- sum(enc$sti, na.rm = TRUE)
total_sti
total_sti[is.na(total_sti)] <- 0
total_sti
total_sti_percent <- (total_sti/total_eip_eligible_age)*100
total_sti_percent <- signif(total_sti_percent, digits = 2)
total_sti_percent


table(enc$sti_syph)
enc$sti_syph <- as.numeric(enc$sti_syph)
total_sti_syph <- sum(enc$sti_syph, na.rm = TRUE)
total_sti_syph
total_sti_syph[is.na(total_sti_syph)] <- 0
total_sti_syph
total_sti_syph_percent <- (total_sti_syph/total_eip_eligible_age)*100
total_sti_syph_percent <- signif(total_sti_syph_percent, digits = 2)
total_sti_syph_percent


table(enc$homeless)
enc$homeless <- as.numeric(enc$homeless)
total_homeless <- sum(enc$homeless, na.rm = TRUE)
total_homeless
total_homeless[is.na(total_homeless)] <- 0
total_homeless
total_homeless_percent <- (total_homeless/total_eip_eligible_age)*100
total_homeless_percent <- signif(total_homeless_percent, digits = 2)
total_homeless_percent


table(enc$hiv_test)
enc$hiv_test <- as.numeric(enc$hiv_test)
enc$risk_group[enc$aa_male_calc == 1 | enc$woc_calc == 1 | enc$trans_calc == 1] <- 1
total_risk_group <- sum(enc$risk_group, na.rm = TRUE)
total_risk_group
total_risk_group_percent <- (total_risk_group/total_eip_eligible_age)*100
total_risk_group_percent <- signif(total_risk_group_percent, digits = 2)
total_risk_group_percent

table(enc$risk_group, enc$hiv_test)
enc$risk_group_not_tested[enc$risk_group == 1 & enc$hiv_test == 1] <- 1
total_risk_group_not_tested <- sum(enc$risk_group_not_tested, na.rm = TRUE)
total_risk_group_not_tested
total_risk_group_not_tested[is.na(total_risk_group_not_tested)] <- 0
total_risk_group_not_tested
total_risk_group_not_tested_percent <- (total_risk_group_not_tested/total_risk_group)*100
total_risk_group_not_tested_percent <- signif(total_risk_group_not_tested_percent, digits = 2)
total_risk_group_not_tested_percent


table(crc$approach_calc)
eip_approach_eligible <- sum(crc$approach_calc, na.rm = TRUE)
eip_approach_eligible
eip_approach_eligible_percent <- (eip_approach_eligible/total_eip_eligible_age)*100
eip_approach_eligible_percent <- signif(eip_approach_eligible_percent, digits = 2)
eip_approach_eligible_percent


table(crc$eip_crc_offer_outcome)
crc$consented[crc$eip_crc_offer_outcome == 1] <- 1
table(crc$consented)
consented <- sum(crc$consented, na.rm = TRUE)
consented
consented_percent <- (consented/eip_approach_eligible)*100
consented_percent <- signif(consented_percent, digits = 2)
consented_percent

```

The EIP Service Center started on **May 3rd, 2023**.

In order to fit with their ED General Screening process, the CRCs select the EIP Service Center screening protocol when the patient is at least 15 years or older. The table below shows the total number of screens that have occurred since the start of the EIP Service Center (*based on number of entries into the ED General Screen*), as well as the total number of patients that were eligible for the EIP Service Center screening protocol based on their age (*15 years or older*). The percentage of the total screened who are eligible for the EIP Service Center is presented in the table. Finally, the table shows the total number that were marked for the EIP Service Center, and the percentage of the total eligible based on their age.

```{r}

crc_screening_tbl <- data.frame(matrix(ncol = 5, nrow = 0))
colnames(crc_screening_tbl) <- c('Total Screened', 'Total EIP Eligible', '% EIP Eligible', 'Total EIP Screened', '% EIP Eligible Screened')
crc_screening_tbl[nrow(crc_screening_tbl) + 1,] <- list(total_screened, total_eip_eligible, total_eip_eligible_percent, total_eip_screened, total_eip_eligible_screened)
reactable(crc_screening_tbl)

```


*Screening encounters are excluded from the total eligible for the EIP Service Center if they were unwilling to answer questions during the ED General Screen. The total number of encounters where the patient was unwilling to answer questions at this stage was **`r crc_excluded_screen`**, and thus excluded from the total number eligible for the EIP Service Center.*

Total numbers are tracked daily for all ED General Screening done by the CRCs, as well as the daily numbers for those that are marked for the EIP Service Center Screen. The following two graphs show these daily numbers. The first graph and subsequent table shows the daily count of the number of screening encounters done by the CRCs, and the number of screening encounters where the patient was marked as eligible for the EIP Service Center.


```{r}

daily_screening_plot <- ggplot(daily_screening, aes(x = Date)) +
  geom_line(aes(y = crc_screen), color = "darkblue") +
  geom_line(aes(y = eip), color = "lightblue") +
  ylab("Count") +
  ggtitle("Daily Screening")

ggplotly(daily_screening_plot)


daily_screening_table <- select(daily_screening, Date, crc_screen, eip)
daily_screening_table$percent <- (daily_screening_table$eip/daily_screening_table$crc_screen)*100
daily_screening_table$percent <- signif(daily_screening_table$percent, digits = 0)
colnames(daily_screening_table)[2] <- 'CRC Screens'
colnames(daily_screening_table)[3] <- 'EIP Service Center'
colnames(daily_screening_table)[4] <- 'Percent (%)'
reactable(daily_screening_table,
          showPageSizeOptions = TRUE,
          pageSizeOptions = c(10, 15, 31),
          defaultPageSize = 10)


```


The following graph shows the daily percentage of the total eligible for the EIP Service Center based on age that are marked for the EIP Service Center on the ED General Screen.


```{r}

colnames(daily_screening_table)[4] <- 'eip_screened_percent'
daily_screening_percent_plot <- ggplot(daily_screening_table, aes(x = Date)) +
  geom_line(aes(y = eip_screened_percent), color = "orange") +
  ylab("% EIP Screened") +
  ggtitle("Daily % EIP Screened")

ggplotly(daily_screening_percent_plot)

```


The CRCs continue with the EIP-specific EPIC pre-screen, looking for various criteria that would indicate that the CRC could approach the patient to gather more information regarding risk and need for EIP action. The graph below shows the number of screens that met the various criteria, and the percentage of the total eligible based on age.

```{r}

graph1 <- data.frame(Criteria = c('Sexual Assault', 'Overdose', 'Illicit Opiate Use', 'Risk group w/o test', 'HIV+', 'HIV+ not in care', 'PWID', 'STI+ past yr', 'Syphilis+ past yr', 'Homeless', 'Pregnant'),
                     Count = c(total_sex_assault, total_overdose, total_opiates, total_risk_group_not_tested, total_hiv, total_idc, total_pwid, total_sti, total_sti_syph, total_homeless, total_preg))

p <- ggplot(data = graph1, aes(x = Criteria, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  geom_text(aes(label = Count), vjust = -0.3, size = 3.5) +
  theme_minimal()
p + theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

*The risk groups that the CRCs are looking for during their Epic pre-screen include: African-American males between the ages of 15-29, Women of Color (WOC), and individuals who identify within the transgender or non-binary community.*


The percentages shown in the table below are the percent of the total marked for EIP screening based on age (*not all eligible to be screened*). The only exceptions are the percentage of those HIV+ not in care (*which is a percentage of the total identified as HIV+*), and the percentage of those positive for Syphilis in the past year (*which is a percentage of the total with a STI in the past year*).

```{r, layout="l-page"}

table2 <- data.frame(matrix(ncol = 11, nrow = 0))
colnames(table2) <- c('Sexual Assault', 'Overdose', 'Illicit Opiate Use', 'Risk group w/o test', 'HIV+', 'HIV+ not in care', 'PWID', 'STI+ past yr', 'Syphilis+ past yr', 'Homeless', 'Pregnant')
table2[nrow(table2) + 1,] <- list(total_sex_assault_percent, total_overdose_percent, total_opiates_percent, total_risk_group_not_tested_percent, total_hiv_percent, total_idc_percent, total_pwid_percent, total_sti_percent, total_sti_syph_percent, total_homeless_percent, total_preg_percent)
reactable(table2)

```

This table shows the total number of screening encounters where the patient met at least one criteria for approach by the CRC, and the percent of the total eligible for the EIP Service Center screening based on age. Also shown are the total number of encounters where the patient was approached and consented to discussing additional risk questions, as well as the percentage of the total eligible for approach.

```{r}

table3 <- data.frame(matrix(ncol = 4, nrow = 0))
colnames(table3) <- c('Total Eligible for Approach', '% Eligible', 'Total Consented', '% Consented')
table3[nrow(table3) + 1,] <- list(eip_approach_eligible, eip_approach_eligible_percent, consented, consented_percent)
table3 %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
  )

```
