---
title: "EIP Service Center"
description: |
  This page shows data regarding the CRC screening efforts for EIP.
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}

rm(list=ls(all=T))

library(tidyverse)
library(ggplot2)
library(gt)
library(plotly)
library(reactable)


# EIP-CRC Screening Data

crc <- read.csv('M:/EIP Data/EIP-CRC Screening/Original Data/EIP CRC Screening Data 20230626_1307.csv')
dim(crc)
head(crc)

```


```{r, include=FALSE}

# EIP-CRC Screening started 5/3/2023
summary(crc$datetime)
crc$datetime <- as.Date(crc$datetime, format = '%m/%d/%Y')
summary(crc$datetime)
crc <- crc[which(crc$datetime >= '2023-05-03'), ]
dim(crc)
summary(crc$datetime)


total_screened <- nrow(crc)
total_screened


table(crc$pt_willing)
crc_excluded_screen <- select(crc, record_id, pt_willing)
crc_excluded_screen <- crc_excluded_screen[which(crc_excluded_screen$pt_willing == 0), ]
crc_excluded_screen <- nrow(crc_excluded_screen)
crc_excluded_screen

dim(crc)
crc <- crc[which(crc$pt_willing != 0), ]
dim(crc)


total_eip_eligible <- select(crc, record_id, age)
total_eip_eligible <- total_eip_eligible[which(total_eip_eligible$age >= 15), ]
table(total_eip_eligible$age)
dim(total_eip_eligible)
total_eip_eligible <- nrow(total_eip_eligible)
total_eip_eligible


total_eip_eligible_percent <- (total_eip_eligible/total_screened)*100
total_eip_eligible_percent <- signif(total_eip_eligible_percent, digits = 3)
total_eip_eligible_percent


table(crc$eip)
total_eip_screened <- select(crc, record_id, eip)
total_eip_screened <- total_eip_screened[which(total_eip_screened$eip == 1), ]
dim(total_eip_screened)
total_eip_screened <- nrow(total_eip_screened)
total_eip_screened


total_eip_eligible_screened <- (total_eip_screened/total_eip_eligible)*100
total_eip_eligible_screened <- signif(total_eip_eligible_screened, digits = 3)
total_eip_eligible_screened


daily_crc_screen <- select(crc, datetime, record_id, eip)
head(daily_crc_screen)
daily_crc_screen$crc_screen <- 1
daily_crc_screen <- select(daily_crc_screen, -record_id)
head(daily_crc_screen)

daily_screening <- aggregate(x = daily_crc_screen[c("eip","crc_screen")],
                             FUN = sum,
                             by = list(Date = daily_crc_screen$datetime))
daily_screening$eip[is.na(daily_screening$eip)] <- 0
daily_screening$crc_screen[is.na(daily_screening$crc_screen)] <- 0
head(daily_screening)
daily_screening


crc <- select(crc, -pt_location, -pt_willing, -abbott_istat, -astral, -boost, -brain_pulse2,
              -cgwell, -endolow, -fastest, -headsmartii_v2, -icecap, -istat, -most, -platinum,
              -portola, -rnaseq, -sensecan, -sense5, -siemenspoc, -reset, -restore1,
              -ed_general_screen_complete, -eip_provider_name,
              -eip_service_center_screening_complete)
head(crc)





# Defining sex/gender

table(crc$sex)
crc$sex[crc$sex == 0] <- 'Male'
crc$sex[crc$sex == 1] <- 'Female'
table(crc$sex)

table(crc$sex, crc$gender)
crc$gender[crc$gender == 0 & crc$sex == 'Male'] <- 'Male'
crc$gender[crc$gender == 1 & crc$sex == 'Male'] <- 'Transgender/Nonbinary'
crc$gender[crc$gender == 0 & crc$sex == 'Female'] <- 'Transgender/Nonbinary'
crc$gender[crc$gender == 1 & crc$sex == 'Female'] <- 'Female'
crc$gender[crc$gender == 2] <- 'Transgender/Nonbinary'
table(crc$sex, crc$gender)




# Defining Race

table(crc$race___1)
White <- crc[which(crc$race___1 == 1), ]
dim(White)
White <- select(White, record_id)
White$White <- 1
table(White$White)
White <- distinct(White)
dim(White)
head(White)

table(crc$race___2)
Black <- crc[which(crc$race___2 == 1), ]
dim(Black)
Black <- select(Black, record_id)
Black$Black <- 1
table(Black$Black)
Black <- distinct(Black)
dim(Black)
head(Black)

table(crc$race___3)
AmIn <- crc[which(crc$race___3 == 1), ]
dim(AmIn)
AmIn <- select(AmIn, record_id)
AmIn$AmIn <- 1
table(AmIn$AmIn)
AmIn <- distinct(AmIn)
dim(AmIn)
head(AmIn)

table(crc$race___4)
Asian <- crc[which(crc$race___4 == 1), ]
dim(Asian)
Asian <- select(Asian, record_id)
Asian$Asian <- 1
table(Asian$Asian)
Asian <- distinct(Asian)
dim(Asian)
head(Asian)

table(crc$race___5)
NHPI <- crc[which(crc$race___5 == 1), ]
dim(NHPI)
NHPI <- select(NHPI, record_id)
NHPI$NHPI <- 1
table(NHPI$NHPI)
NHPI <- distinct(NHPI)
dim(NHPI)
head(NHPI)

table(crc$race___6)
RaceOther <- crc[which(crc$race___6 == 1), ]
dim(RaceOther)
RaceOther <- select(RaceOther, record_id)
RaceOther$RaceOther <- 1
table(RaceOther$RaceOther)
RaceOther <- distinct(RaceOther)
dim(RaceOther)
head(RaceOther)

table(crc$race___9)
Multi <- crc[which(crc$race___9 == 1), ]
dim(Multi)
Multi <- select(Multi, record_id)
Multi$Multi <- 1
table(Multi$Multi)
Multi <- distinct(Multi)
dim(Multi)
head(Multi)

table(crc$race___10)
Hisp <- crc[which(crc$race___10 == 1), ]
dim(Hisp)
Hisp <- select(Hisp, record_id)
Hisp$Hisp <- 1
table(Hisp$Hisp)
Hisp <- distinct(Hisp)
dim(Hisp)
head(Hisp)

table(crc$race___7)
table(crc$race___8)
RaceUnk <- crc[which(crc$race___7 == 1 | crc$race___8 == 1), ]
dim(RaceUnk)
RaceUnk <- select(RaceUnk, record_id)
RaceUnk$RaceUnk <- 1
table(RaceUnk$RaceUnk)
RaceUnk <- distinct(RaceUnk)
dim(RaceUnk)
head(RaceUnk)




race <- select(crc, record_id)
race <- distinct(race)
dim(race)


dim(race)
race <- merge(race, White, by = 'record_id', all.x = T)
race <- merge(race, Black, by = 'record_id', all.x = T)
race <- merge(race, AmIn, by = 'record_id', all.x = T)
race <- merge(race, Asian, by = 'record_id', all.x = T)
race <- merge(race, NHPI, by = 'record_id', all.x = T)
race <- merge(race, RaceOther, by = 'record_id', all.x = T)
race <- merge(race, Multi, by = 'record_id', all.x = T)
race <- merge(race, Hisp, by = 'record_id', all.x = T)
race <- merge(race, RaceUnk, by = 'record_id', all.x = T)
dim(race)
head(race)
table(race$White)

race$White[is.na(race$White)] <- 0
race$Black[is.na(race$Black)] <- 0
race$AmIn[is.na(race$AmIn)] <- 0
race$Asian[is.na(race$Asian)] <- 0
race$NHPI[is.na(race$NHPI)] <- 0
race$RaceOther[is.na(race$RaceOther)] <- 0
race$Multi[is.na(race$Multi)] <- 0
race$Hisp[is.na(race$Hisp)] <- 0
race$RaceUnk[is.na(race$RaceUnk)] <- 0

race$RaceNumber <- race$White + race$Black + race$AmIn + race$Asian + race$NHPI + race$RaceOther + race$Multi + race$Hisp + race$RaceUnk
table(race$RaceNumber)
head(race)

race$race[race$RaceNumber == 1 & race$White == 1] <- 'White or Caucasian'
race$race[race$RaceNumber == 1 & race$Black == 1] <- 'Black or African American'
race$race[race$RaceNumber == 1 & race$AmIn == 1] <- 'American Indian or Alaska Native'
race$race[race$RaceNumber == 1 & race$Asian == 1] <- 'Asian'
race$race[race$RaceNumber == 1 & race$NHPI == 1] <- 'Native Hawaiian or Other Pacific Islander'
race$race[race$RaceNumber == 1 & race$RaceOther == 1] <- 'Other'
race$race[race$RaceNumber == 1 & race$Hisp == 1] <- 'Hispanic'
race$race[race$Multi == 1 | (race$RaceNumber > 1)] <- 'Biracial/Multiracial'
race$race[race$RaceNumber == 0 | is.na(race$RaceNumber) | race$RaceUnk == 1] <- 'Unknown'
table(race$race)

dim(crc)
dim(race)
crc <- merge(crc, race, by = 'record_id', all.x = T)
dim(crc)
table(crc$race)


table(crc$race, crc$ethnicity)
crc$race[crc$race == 'White or Caucasian' & crc$ethnicity == 1] <- 'Biracial/Multiracial'
crc$race[crc$race == 'Black or African American' & crc$ethnicity == 1] <- 'Biracial/Multiracial'
crc$race[crc$race == 'American Indian or Alaska Native' & crc$ethnicity == 1] <- 'Biracial/Multiracial'
crc$race[crc$race == 'Asian' & crc$ethnicity == 1] <- 'Biracial/Multiracial'
crc$race[crc$race == 'Native Hawaiian or Other Pacific Islander' & crc$ethnicity == 1] <- 'Biracial/Multiracial'
crc$race[crc$race == 'Other' & crc$ethnicity == 1] <- 'Biracial/Multiracial'
crc$race[crc$race == 'Biracial/Multiracial' & crc$ethnicity == 1] <- 'Biracial/Multiracial'
crc$race[crc$race == 'Unknown' & crc$ethnicity == 1] <- 'Hispanic'

table(crc$race, crc$ethnicity)

head(crc)
crc <- select(crc, -race___3, -race___4, -race___2, -race___10, -race___9, -race___5, -race___6,
              -race___7, -race___8, -race___1, -ethnicity, -RaceUnk, -RaceNumber, -White, -Black,
              -AmIn, -Asian, -NHPI, -RaceOther, -Multi, -Hisp)
head(crc)
dim(crc)



# Defining risk groups

table(crc$aa_male_calc)
crc_risk_aa_males <- select(crc, record_id, aa_male_calc)
crc_risk_aa_males <- crc[which(crc$aa_male_calc == 1), ]
crc_risk_aa_males <- nrow(crc_risk_aa_males)
crc_risk_aa_males
crc_risk_aa_males_percent <- (crc_risk_aa_males/total_eip_eligible)*100
crc_risk_aa_males_percent <- signif(crc_risk_aa_males_percent, digits = 2)
crc_risk_aa_males_percent

table(crc$woc_calc)
crc_risk_woc <- select(crc, record_id, woc_calc)
crc_risk_woc <- crc[which(crc$woc_calc == 1), ]
crc_risk_woc <- nrow(crc_risk_woc)
crc_risk_woc
crc_risk_woc_percent <- (crc_risk_woc/total_eip_eligible)*100
crc_risk_woc_percent <- signif(crc_risk_woc_percent, digits = 2)
crc_risk_woc_percent

table(crc$trans_calc)
crc_risk_trans <- select(crc, record_id, trans_calc)
crc_risk_trans <- crc[which(crc$trans_calc == 1), ]
crc_risk_trans <- nrow(crc_risk_trans)
crc_risk_trans
crc_risk_trans_percent <- (crc_risk_trans/total_eip_eligible)*100
crc_risk_trans_percent <- signif(crc_risk_trans_percent, digits = 2)
crc_risk_trans_percent



########################################################################################################
# Creating a patient list (only those with EIP screen)

table(crc$eip)
patients <- select(crc, mrn, eip)
dim(patients)
patients <- patients[which(patients$eip == 1), ]
patients <- select(patients, -eip)
dim(patients)
patients <- distinct(patients)
dim(patients)
head(patients)



age <- select(crc, mrn, age)
dim(age)
age <- distinct(age)
dim(age)
age <- age[order(age$mrn),]
age$dup <- duplicated(age$mrn)
age <- age[which(age$dup == F), ]
dim(age)
age <- select(age, -dup)
dim(age)

dim(patients)
dim(age)
patients <- merge(patients, age, by = 'mrn', all.x = T)
dim(patients)
head(patients)



sex <- select(crc, mrn, sex)
dim(sex)
sex <- distinct(sex)
dim(sex)
sex <- sex[order(sex$mrn),]
sex$dup <- duplicated(sex$mrn)
sex <- sex[which(sex$dup == F), ]
dim(sex)
sex <- select(sex, -dup)
dim(sex)

dim(patients)
dim(sex)
patients <- merge(patients, sex, by = 'mrn', all.x = T)
dim(patients)
head(patients)



gender <- select(crc, mrn, gender)
dim(gender)
gender <- distinct(gender)
dim(gender)
gender <- gender[order(gender$mrn),]
gender$dup <- duplicated(gender$mrn)
gender <- gender[which(gender$dup == F), ]
dim(gender)
gender <- select(gender, -dup)
dim(gender)

dim(patients)
dim(gender)
patients <- merge(patients, gender, by = 'mrn', all.x = T)
dim(patients)
head(patients)



race <- select(crc, mrn, race)
dim(race)
race <- distinct(race)
dim(race)
race <- race[order(race$mrn),]
race$dup <- duplicated(race$mrn)
race <- race[which(race$dup == F), ]
dim(race)
race <- select(race, -dup)
dim(race)

dim(patients)
dim(race)
patients <- merge(patients, race, by = 'mrn', all.x = T)
dim(patients)
head(patients)




# Creating Encounter/Screening Data

head(crc)
table(crc$eip)
enc <- select(crc, -chief_comp, -eip_start, -eip_calc, -eip_eligible, -eip_complete_step3,
              -eip_complete_time1, -epi_sign1, -eip_id1, -csn)
enc <- enc[which(enc$eip == 1), ]
dim(enc)
head(enc)


summary(enc$datetime)
enc$enc_date <- as.Date(enc$datetime, format = '%m/%d/%Y')
summary(enc$enc_date)
enc <- select(enc, -datetime)


table(enc$sex_assault)
enc$sex_assault <- as.numeric(enc$sex_assault)
total_sex_assault <- sum(enc$sex_assault, na.rm = TRUE)
total_sex_assault
total_sex_assault[is.na(total_sex_assault)] <- 0
total_sex_assault
total_sex_assault_percent <- (total_sex_assault/total_eip_screened)*100
total_sex_assault_percent <- signif(total_sex_assault_percent, digits = 2)
total_sex_assault_percent


table(enc$overdose)
enc$overdose <- as.numeric(enc$overdose)
total_overdose <- sum(enc$overdose, na.rm = TRUE)
total_overdose
total_overdose[is.na(total_overdose)] <- 0
total_overdose
total_overdose_percent <- (total_overdose/total_eip_screened)*100
total_overdose_percent <- signif(total_overdose_percent, digits = 2)
total_overdose_percent


table(enc$opiates)
enc$opiates <- as.numeric(enc$opiates)
total_opiates <- sum(enc$opiates, na.rm = TRUE)
total_opiates
total_opiates[is.na(total_opiates)] <- 0
total_opiates
total_opiates_percent <- (total_opiates/total_eip_screened)*100
total_opiates_percent <- signif(total_opiates_percent, digits = 2)
total_opiates_percent


table(enc$preg)
enc$preg <- as.numeric(enc$preg)
total_preg <- sum(enc$preg, na.rm = TRUE)
total_preg
total_preg[is.na(total_preg)] <- 0
total_preg
total_preg_percent <- (total_preg/total_eip_screened)*100
total_preg_percent <- signif(total_preg_percent, digits = 2)
total_preg_percent


table(enc$hiv)
enc$hiv <- as.numeric(enc$hiv)
total_hiv <- sum(enc$hiv, na.rm = TRUE)
total_hiv
total_hiv[is.na(total_hiv)] <- 0
total_hiv
total_hiv_percent <- (total_hiv/total_eip_screened)*100
total_hiv_percent <- signif(total_hiv_percent, digits = 2)
total_hiv_percent


table(enc$idc)
enc$idc <- as.numeric(enc$idc)
total_idc <- sum(enc$idc, na.rm = TRUE)
total_idc
total_idc[is.na(total_idc)] <- 0
total_idc
total_idc_percent <- (total_idc/total_hiv)*100
total_idc_percent <- signif(total_idc_percent, digits = 2)
total_idc_percent


table(enc$pwid)
enc$pwid <- as.numeric(enc$pwid)
total_pwid <- sum(enc$pwid, na.rm = TRUE)
total_pwid
total_pwid[is.na(total_pwid)] <- 0
total_pwid
total_pwid_percent <- (total_pwid/total_eip_screened)*100
total_pwid_percent <- signif(total_pwid_percent, digits = 2)
total_pwid_percent


table(enc$sti)
enc$sti <- as.numeric(enc$sti)
total_sti <- sum(enc$sti, na.rm = TRUE)
total_sti
total_sti[is.na(total_sti)] <- 0
total_sti
total_sti_percent <- (total_sti/total_eip_screened)*100
total_sti_percent <- signif(total_sti_percent, digits = 2)
total_sti_percent


table(enc$sti_syph)
enc$sti_syph <- as.numeric(enc$sti_syph)
total_sti_syph <- sum(enc$sti_syph, na.rm = TRUE)
total_sti_syph
total_sti_syph[is.na(total_sti_syph)] <- 0
total_sti_syph
total_sti_syph_percent <- (total_sti_syph/total_eip_screened)*100
total_sti_syph_percent <- signif(total_sti_syph_percent, digits = 2)
total_sti_syph_percent


table(enc$homeless)
enc$homeless <- as.numeric(enc$homeless)
total_homeless <- sum(enc$homeless, na.rm = TRUE)
total_homeless
total_homeless[is.na(total_homeless)] <- 0
total_homeless
total_homeless_percent <- (total_homeless/total_eip_screened)*100
total_homeless_percent <- signif(total_homeless_percent, digits = 2)
total_homeless_percent


table(enc$hiv_test)
enc$hiv_test <- as.numeric(enc$hiv_test)
enc$risk_group[enc$aa_male_calc == 1 | enc$woc_calc == 1 | enc$trans_calc == 1] <- 1
total_risk_group <- sum(enc$risk_group, na.rm = TRUE)
total_risk_group
total_risk_group_percent <- (total_risk_group/total_eip_screened)*100
total_risk_group_percent <- signif(total_risk_group_percent, digits = 2)
total_risk_group_percent


table(enc$risk_group, enc$hiv_test)
enc$risk_group_not_tested[enc$risk_group == 1 & enc$hiv_test == 1] <- 1
total_risk_group_not_tested <- sum(enc$risk_group_not_tested, na.rm = TRUE)
total_risk_group_not_tested
total_risk_group_not_tested[is.na(total_risk_group_not_tested)] <- 0
total_risk_group_not_tested
total_risk_group_not_tested_percent <- (total_risk_group_not_tested/total_risk_group)*100
total_risk_group_not_tested_percent <- signif(total_risk_group_not_tested_percent, digits = 2)
total_risk_group_not_tested_percent
total_risk_group_no_test_percent <- (total_risk_group_not_tested/total_eip_screened)*100
total_risk_group_no_test_percent <- signif(total_risk_group_no_test_percent, digits = 2)
total_risk_group_no_test_percent


table(crc$approach_calc)
eip_approach_eligible <- sum(crc$approach_calc, na.rm = TRUE)
eip_approach_eligible
eip_approach_eligible_percent <- (eip_approach_eligible/total_eip_screened)*100
eip_approach_eligible_percent <- signif(eip_approach_eligible_percent, digits = 2)
eip_approach_eligible_percent


table(crc$eip_crc_offer_outcome)
crc$consented[crc$eip_crc_offer_outcome == 1] <- 1
table(crc$consented)
consented <- sum(crc$consented, na.rm = TRUE)
consented
consented_percent <- (consented/eip_approach_eligible)*100
consented_percent <- signif(consented_percent, digits = 2)
consented_percent

```


The EIP Service Center started on **May 3rd, 2023**.

In order to fit with the ED General Screening process, the CRCs select the EIP Service Center screening protocol when the patient is *at least 15 years or older*. The table below shows the total number of screens that have occurred since the start of the EIP Service Center (*based on the number of entries into the ED General Screen database*), as well as the total number of patients that were eligible for the EIP Service Center screening protocol based on their age (*15 years or older*). The percentage of the total screened who are eligible for the EIP Service Center based on age is presented in the table. The table also shows the total number that were selected for the EIP Service Center (*by selecting the EIP Service Center protocol on the ED General Screen*), and the percentage selected for the EIP Service Center from the total number eligible during screening.


```{r}

crc_screening_tbl <- data.frame(matrix(ncol = 5, nrow = 0))
colnames(crc_screening_tbl) <- c('Total Screened', 'Total EIP Eligible', '% EIP Eligible', 'Total EIP Screened', '% EIP Eligible Screened')
crc_screening_tbl[nrow(crc_screening_tbl) + 1,] <- list(total_screened, total_eip_eligible, total_eip_eligible_percent, total_eip_screened, total_eip_eligible_screened)
reactable(crc_screening_tbl)

```


*Screening encounters are excluded from the total eligible for the EIP Service Center if they were unwilling to answer questions during the ED General Screen. The total number of encounters where the patient was unwilling to answer questions at this stage was **`r crc_excluded_screen`**, and thus excluded from the total number eligible for the EIP Service Center.*

Total numbers are tracked daily for all ED General Screening encounters done by the CRCs, as well as the daily numbers for those that are selected for the EIP Service Center protocol. The following two graphs show these daily numbers. The first graph (and subsequent table) shows the daily count of the number of screening encounters done by the CRCs, and the number of screening encounters where the patient was selected for the EIP Service Center.


```{r}

daily_screening_plot <- ggplot(daily_screening, aes(x = Date)) +
  geom_line(aes(y = crc_screen), color = "darkblue") +
  geom_line(aes(y = eip), color = "lightblue") +
  ylab("Count") +
  ggtitle("Daily Screening")

ggplotly(daily_screening_plot)


daily_screening_table <- select(daily_screening, Date, crc_screen, eip)
daily_screening_table$percent <- (daily_screening_table$eip/daily_screening_table$crc_screen)*100
daily_screening_table$percent <- signif(daily_screening_table$percent, digits = 0)
colnames(daily_screening_table)[2] <- 'CRC Screens'
colnames(daily_screening_table)[3] <- 'EIP Service Center'
colnames(daily_screening_table)[4] <- 'Percent (%)'
reactable(daily_screening_table,
          showPageSizeOptions = TRUE,
          pageSizeOptions = c(10, 15, 31),
          defaultPageSize = 10)


```


This second graph shows the daily percentage of those selected for the EIP Service Center protocol out of the total encounters the CRCs had with the ED General Screen (n = `r total_screened`). The blue line shows the average percentage of those eligible for the EIP Service Center selected on the ED General Screen since the start of the EIP Service Center.


```{r}

colnames(daily_screening_table)[4] <- 'eip_screened_percent'
daily_screening_percent_plot <- ggplot(daily_screening_table, aes(x = Date)) +
  geom_line(aes(y = eip_screened_percent), color = "orange") +
  ylab("% EIP Screened") +
  ggtitle("Daily % EIP Screened") +
  geom_hline(yintercept = total_eip_eligible_screened, color="blue")

ggplotly(daily_screening_percent_plot)

```


Once the individual is selected for the EIP Service Center on the ED General Screen, the CRCs continue with the EIP-specific EPIC pre-screen. This EPIC pre-screen has the CRC looking for various criteria within the electronic health record (EHR) that would indicate that they could approach the patient to gather more information regarding risk and need for EIP action. The bar graph below shows the number of screens where the individual met each of the various criteria.


```{r}

graph1 <- data.frame(Criteria = c('Sexual Assault', 'Overdose', 'Illicit Opiate Use', 'Risk group w/o test', 'HIV+', 'HIV+ not in care', 'PWID', 'STI+ past yr', 'Syphilis+ past yr', 'Homeless', 'Pregnant'),
                     Count = c(total_sex_assault, total_overdose, total_opiates, total_risk_group_not_tested, total_hiv, total_idc, total_pwid, total_sti, total_sti_syph, total_homeless, total_preg))

p <- ggplot(data = graph1, aes(x = Criteria, y = Count)) +
  geom_bar(stat="identity", fill="steelblue")+
  geom_text(aes(label = Count), vjust = -0.3, size = 3.5) +
  theme_minimal()
p + theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


The population groups at risk that the CRCs are looking for during their EPIC pre-screen include: African-American males between the ages of 15-29, Women of Color (WOC), and individuals who identify within the transgender or non-binary community. If someone belonging to any of these populations groups have no evidence of a HIV test within the past year, they are of eligible for CRC approach (i.e. Risk group w/o test). There were a total number of `r total_risk_group` encounters where the EIP Service Center was selected where the individual fit within one of these population groups (`r total_risk_group`/`r total_eip_screened`, `r total_risk_group_percent`%). Out of those, there were `r total_risk_group_not_tested` encounters where the individual had no evidence of a HIV test within the past year (`r total_risk_group_not_tested`/`r total_risk_group`, `r total_risk_group_not_tested_percent`%).

The bar chart below shows the total number of encounters where the individual falls within these population groups. This counts all individuals within these population groups, not solely those without HIV testing in the past year. Their demographics are determined during the ED General Screen, and thus are based on the total screens done by the CRCs. The blue labels on the end of each bar in the chart shows the percentage of the total that were screened and eligible for the EIP Service Center (based on age) during the ED General Screen (n = `r total_eip_eligible`).


```{r}
crc_risk_group_table <- data.frame(matrix(ncol = 3, nrow = 0))
colnames(crc_risk_group_table) <- c('risk_group', 'number', 'percent')
crc_risk_group_table[nrow(crc_risk_group_table) + 1,] <- list('African American male age 15-29', crc_risk_aa_males, crc_risk_aa_males_percent)
crc_risk_group_table[nrow(crc_risk_group_table) + 1,] <- list('Women of Color (WOC)', crc_risk_woc, crc_risk_woc_percent)
crc_risk_group_table[nrow(crc_risk_group_table) + 1,] <- list('Transgender/Nonbinary Individuals', crc_risk_trans, crc_risk_trans_percent)


crc_risk_group_table$risk_group = with(crc_risk_group_table, reorder(risk_group, number))
crc_risk_group_table <- crc_risk_group_table %>%
  mutate(x = fct_reorder(risk_group, number)) %>%
  ggplot( aes(x=risk_group, y=number)) +
  geom_bar(stat="identity", fill="#f68060", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  ylab("Count") +
  theme_bw() +
  geom_text(aes(label = percent), nudge_y = 50, size = 3, color = 'blue')
ggplotly(crc_risk_group_table)

```


The lollipop chart below shows the percentage for each risk group determined by the CRC during the EIP EPIC pre-screen. The denominator for these percentages are the total number of encounters selected for the EIP Service Center protocol (n = `r total_eip_screened`).


```{r}

crc_risk_table <- data.frame(matrix(ncol = 2, nrow = 0))
colnames(crc_risk_table) <- c('risk', 'percent')
crc_risk_table[nrow(crc_risk_table) + 1,] <- list('HIV+', total_hiv_percent)
#crc_risk_table[nrow(crc_risk_table) + 1,] <- list('HIV+ not in care', total_idc_percent)
crc_risk_table[nrow(crc_risk_table) + 1,] <- list('Homeless', total_homeless_percent)
crc_risk_table[nrow(crc_risk_table) + 1,] <- list('Illicit Opiate Use', total_opiates_percent)
crc_risk_table[nrow(crc_risk_table) + 1,] <- list('Overdose', total_overdose_percent)
crc_risk_table[nrow(crc_risk_table) + 1,] <- list('Pregnant', total_preg_percent)
crc_risk_table[nrow(crc_risk_table) + 1,] <- list('PWID', total_pwid_percent)
crc_risk_table[nrow(crc_risk_table) + 1,] <- list('Risk group w/o test', total_risk_group_no_test_percent)
crc_risk_table[nrow(crc_risk_table) + 1,] <- list('Sexual Assault', total_sex_assault_percent)
crc_risk_table[nrow(crc_risk_table) + 1,] <- list('STI+ past yr', total_sti_percent)
#crc_risk_table[nrow(crc_risk_table) + 1,] <- list('Syph+ past yr', total_sti_syph_percent)


crc_risk_table$risk = with(crc_risk_table, reorder(risk, percent))
ggplot(crc_risk_table, aes(x=risk, y=percent, label=percent)) +
  geom_segment(aes(x=risk, xend=risk, y=0, yend=percent), color="steelblue") +
  geom_point(color="skyblue", size=4, alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(panel.grid.major.y = element_blank(),
        panel.border = element_blank(),
        axis.ticks.y = element_blank()) +
  geom_text(nudge_y = 1, size = 3) +
  xlab('Risk Group') +
  ylab('Percent')

```


The only exceptions are the percent of those who are HIV+ but not currently in care (*or at least no evidence of care*) and those that had syphilis in the past year, and are thus *excluded* from this graph. The percentage of those who are HIV+ and not in care is based on the total that were identified as living with HIV. The percentage of those who were positive for HIV, but did not appear to be in care was **`r total_idc_percent`%**. The percentage of those who had syphilis in the past year are based on the total that were identified as having any STI in the past year. The percentage of those who were positive for syphilis in the past year was **`r total_sti_syph_percent`%**.


Once the CRC completes the EIP EPIC pre-screen and identifies individuals to approach based on those risk groups or populations of interest, they determine whether the patient is willing to continue the discussion about their associated risks. This table shows the total number of those screened for the EIP Service Center (*selected on the ED General Screen*), and the total number of encounters where the patient met *at least* one criteria for approach, and the percent of the total selected for the EIP Service Center screening. Also shown are the total number of encounters where the patient was approached and consented to discussing additional EIP risk questions, as well as the percentage of the total eligible for approach that consented to continuing the conversation.


```{r}

table3 <- data.frame(matrix(ncol = 5, nrow = 0))
colnames(table3) <- c('Total EIP Screened', 'Total Eligible for Approach', '% Eligible', 'Total Consented', '% Consented')
table3[nrow(table3) + 1,] <- list(total_eip_screened, eip_approach_eligible, eip_approach_eligible_percent, consented, consented_percent)
reactable(table3)


```


Upon verbal consent for continuing the conversation, there are several assessment questions that the CRCs discuss with the individual to evaluate their situation beyond what is evident within EPIC.


**Add assessment question data**









