---
title: "EHE Deliverables (2024/2025)"
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r Data, include=FALSE}

rm(list=ls(all=T))

library(dplyr)
library(tidyverse)
library(lubridate)
library(plotly)
library(ggplot2)
library(reactable)
library(htmltools)
library(lubridate)
library(hrbrthemes)
library(gt)
library(janitor)
library(scales)
library(apyramid)
library(kableExtra)
library(knitr)
library(zoo)

### EIP Database Data
# 2024
eip24 <- read.csv('M:/EIP Data/EIP Database/REDCap 2024/EIP Database Data 20241021_0938.csv')
dim(eip24)
summary(eip24$record_id)
eip24$record_id <- paste(eip24$record_id, "_24", sep = "")
summary(eip24$record_id)

```

```{r Patient Data to Encounter, include=FALSE}

### Person-level data is only visit_001_arm_1, use to match to encounters

# 2024
table(eip24$redcap_event_name)
person <- eip24[which(eip24$redcap_event_name == 'visit_001_arm_1'), ]
dim(person)

person <- select(person, record_id, mrn, dob, 
                 race___1, race___2, race___3, race___4, race___5, race___6, ethnicity,
                 sex_raised, sex_selfdefined, insurance, address_county,
                 address_zip_code,
                 followup_date1, followup_date2, followup_date3, followup_date4,
                 followup_date5, followup_date6, followup_date7, followup_date8,
                 followup_date9, followup_date10, followup_date11, followup_date12,
                 followup_date13, followup_date14, followup_date15, followup_date16,
                 followup_date17, followup_date18, followup_date19, followup_date20,
                 followup_date21, followup_date22, followup_date23, followup_date24,
                 followup_date25, followup_date26, followup_date27, followup_date28,
                 followup_date29, followup_date30, followup_date31, followup_date32,
                 followup_date33, followup_date34, followup_date35, followup_date36,
                 followup_date37, followup_date38, followup_date39, followup_date40,
                 followup_date41, followup_date42, followup_date43, followup_date44,
                 followup_date45, followup_date46, followup_date47, followup_date48,
                 followup_date49, followup_date50, followup_counselor1, followup_counselor2,
                 followup_counselor3, followup_counselor4, followup_counselor5,
                 followup_counselor6, followup_counselor7, followup_counselor8,
                 followup_counselor9, followup_counselor10, followup_counselor11,
                 followup_counselor12, followup_counselor13, followup_counselor14,
                 followup_counselor15, followup_counselor16, followup_counselor17,
                 followup_counselor18, followup_counselor19, followup_counselor20,
                 followup_counselor21, followup_counselor22, followup_counselor23,
                 followup_counselor24, followup_counselor25, followup_counselor26,
                 followup_counselor27, followup_counselor28, followup_counselor29,
                 followup_counselor30, followup_counselor31, followup_counselor32,
                 followup_counselor33, followup_counselor34, followup_counselor35,
                 followup_counselor36, followup_counselor37, followup_counselor38,
                 followup_counselor39, followup_counselor40, followup_counselor41,
                 followup_counselor42, followup_counselor43, followup_counselor44,
                 followup_counselor45, followup_counselor46, followup_counselor47,
                 followup_counselor48, followup_counselor49, followup_counselor50,
                 ltc_service1___8, ltc_service2___8,
                 ltc_service3___8, ltc_service4___8, ltc_service5___8,
                 ltc_service6___8, ltc_service7___8, ltc_service8___8,
                 ltc_service9___8, ltc_service10___8, ltc_service11___8,
                 ltc_service12___8, ltc_service13___8, ltc_service14___8,
                 ltc_service15___8, ltc_service16___8, ltc_service17___8,
                 ltc_service18___8, ltc_service19___8, ltc_service20___8,
                 ltc_service21___8, ltc_service22___8, ltc_service23___8,
                 ltc_service24___8, ltc_service25___8, ltc_service26___8,
                 ltc_service27___8, ltc_service28___8, ltc_service29___8,
                 ltc_service30___8, ltc_service31___8, ltc_service32___8,
                 ltc_service33___8, ltc_service34___8, ltc_service35___8,
                 ltc_service36___8, ltc_service37___8, ltc_service38___8,
                 ltc_service39___8, ltc_service40___8, ltc_service41___8,
                 ltc_service42___8, ltc_service43___8, ltc_service44___8,
                 ltc_service45___8, ltc_service46___8, ltc_service47___8,
                 ltc_service48___8, ltc_service49___8, ltc_service50___8,
                 naccho_contact_day1, naccho_contact_day2,
                 naccho_contact_day3, naccho_contact_day4, naccho_contact_day5,
                 naccho_contact_day6, naccho_contact_day7, naccho_contact_day8,
                 naccho_contact_day9, naccho_contact_day10, naccho_contact_day11,
                 naccho_contact_day12, naccho_contact_day13, naccho_contact_day14,
                 naccho_contact_day15, naccho_contact_day16, naccho_contact_day17,
                 naccho_contact_day18, naccho_contact_day19, naccho_contact_day20,
                 naccho_contact_day21, naccho_contact_day22, naccho_contact_day23,
                 naccho_contact_day24, naccho_contact_day25, naccho_contact_day26,
                 naccho_contact_day27, naccho_contact_day28, naccho_contact_day29,
                 naccho_contact_day30, naccho_contact_day31, naccho_contact_day32,
                 naccho_contact_day33, naccho_contact_day34, naccho_contact_day35,
                 naccho_contact_day36, naccho_contact_day37, naccho_contact_day38,
                 naccho_contact_day39, naccho_contact_day40, naccho_contact_day41,
                 naccho_contact_day42, naccho_contact_day43, naccho_contact_day44,
                 naccho_contact_day45, naccho_contact_day46, naccho_contact_day47,
                 naccho_contact_day48, naccho_contact_day49, naccho_contact_day50,
                 naccho_contact_confirm_tx1, naccho_contact_confirm_tx2,
                 naccho_contact_confirm_tx3, naccho_contact_confirm_tx4, naccho_contact_confirm_tx5,
                 naccho_contact_confirm_tx6, naccho_contact_confirm_tx7, naccho_contact_confirm_tx8,
                 naccho_contact_confirm_tx9, naccho_contact_confirm_tx10, naccho_contact_confirm_tx11,
                 naccho_contact_confirm_tx12, naccho_contact_confirm_tx13, naccho_contact_confirm_tx14,
                 naccho_contact_confirm_tx15, naccho_contact_confirm_tx16, naccho_contact_confirm_tx17,
                 naccho_contact_confirm_tx18, naccho_contact_confirm_tx19, naccho_contact_confirm_tx20,
                 naccho_contact_confirm_tx21, naccho_contact_confirm_tx22, naccho_contact_confirm_tx23,
                 naccho_contact_confirm_tx24, naccho_contact_confirm_tx25, naccho_contact_confirm_tx26,
                 naccho_contact_confirm_tx27, naccho_contact_confirm_tx28, naccho_contact_confirm_tx29,
                 naccho_contact_confirm_tx30, naccho_contact_confirm_tx31, naccho_contact_confirm_tx32,
                 naccho_contact_confirm_tx33, naccho_contact_confirm_tx34, naccho_contact_confirm_tx35,
                 naccho_contact_confirm_tx36, naccho_contact_confirm_tx37, naccho_contact_confirm_tx38,
                 naccho_contact_confirm_tx39, naccho_contact_confirm_tx40, naccho_contact_confirm_tx41,
                 naccho_contact_confirm_tx42, naccho_contact_confirm_tx43, naccho_contact_confirm_tx44,
                 naccho_contact_confirm_tx45, naccho_contact_confirm_tx46, naccho_contact_confirm_tx47,
                 naccho_contact_confirm_tx48, naccho_contact_confirm_tx49, naccho_contact_confirm_tx50,
                 who_initiated_contact1, who_initiated_contact2, who_initiated_contact3, who_initiated_contact4, who_initiated_contact5,
                 who_initiated_contact6, who_initiated_contact7, who_initiated_contact8, who_initiated_contact9, who_initiated_contact10,
                 who_initiated_contact11, who_initiated_contact12, who_initiated_contact13, who_initiated_contact14,
                 who_initiated_contact15, who_initiated_contact16, who_initiated_contact17, who_initiated_contact18,
                 who_initiated_contact19, who_initiated_contact20, who_initiated_contact21, who_initiated_contact22,
                 who_initiated_contact23, who_initiated_contact24, who_initiated_contact25, who_initiated_contact26,
                 who_initiated_contact27, who_initiated_contact28, who_initiated_contact29, who_initiated_contact30,
                 who_initiated_contact31, who_initiated_contact32, who_initiated_contact33, who_initiated_contact34,
                 who_initiated_contact35, who_initiated_contact36, who_initiated_contact37, who_initiated_contact38,
                 who_initiated_contact39, who_initiated_contact40, who_initiated_contact41, who_initiated_contact42,
                 who_initiated_contact43, who_initiated_contact44, who_initiated_contact45, who_initiated_contact46,
                 who_initiated_contact47, who_initiated_contact48, who_initiated_contact49, who_initiated_contact50,
                 contact_with1, contact_with2, contact_with3, contact_with4, contact_with5,
                 contact_with6, contact_with7, contact_with8, contact_with9, contact_with10,
                 contact_with11, contact_with12, contact_with13, contact_with14,
                 contact_with15, contact_with16, contact_with17, contact_with18,
                 contact_with19, contact_with20, contact_with21, contact_with22,
                 contact_with23, contact_with24, contact_with25, contact_with26,
                 contact_with27, contact_with28, contact_with29, contact_with30,
                 contact_with31, contact_with32, contact_with33, contact_with34,
                 contact_with35, contact_with36, contact_with37, contact_with38,
                 contact_with39, contact_with40, contact_with41, contact_with42,
                 contact_with43, contact_with44, contact_with45, contact_with46,
                 contact_with47, contact_with48, contact_with49, contact_with50,
                 ltc_contact1, ltc_contact2, ltc_contact3, ltc_contact4, ltc_contact5,
                 ltc_contact6, ltc_contact7, ltc_contact8, ltc_contact9, ltc_contact10,
                 ltc_contact11, ltc_contact12, ltc_contact13, ltc_contact14, ltc_contact15,
                 ltc_contact16, ltc_contact17, ltc_contact18, ltc_contact19, ltc_contact20,
                 ltc_contact21, ltc_contact22, ltc_contact23, ltc_contact24, ltc_contact25,
                 ltc_contact26, ltc_contact27, ltc_contact28, ltc_contact29, ltc_contact30,
                 ltc_contact31, ltc_contact32, ltc_contact33, ltc_contact34, ltc_contact35,
                 ltc_contact36, ltc_contact37, ltc_contact38, ltc_contact39, ltc_contact40,
                 ltc_contact41, ltc_contact42, ltc_contact43, ltc_contact44, ltc_contact45,
                 ltc_contact46, ltc_contact47, ltc_contact48, ltc_contact49, ltc_contact50,
                 no_contact_reason1, no_contact_reason2, no_contact_reason3, no_contact_reason4, no_contact_reason5,
                 no_contact_reason6, no_contact_reason7, no_contact_reason8, no_contact_reason9, no_contact_reason10,
                 no_contact_reason11, no_contact_reason12, no_contact_reason13, no_contact_reason14,
                 no_contact_reason15, no_contact_reason16, no_contact_reason17, no_contact_reason18,
                 no_contact_reason19, no_contact_reason20, no_contact_reason21, no_contact_reason22,
                 no_contact_reason23, no_contact_reason24, no_contact_reason25, no_contact_reason26,
                 no_contact_reason27, no_contact_reason28, no_contact_reason29, no_contact_reason30,
                 no_contact_reason31, no_contact_reason32, no_contact_reason33, no_contact_reason34,
                 no_contact_reason35, no_contact_reason36, no_contact_reason37, no_contact_reason38,
                 no_contact_reason39, no_contact_reason40, no_contact_reason41, no_contact_reason42,
                 no_contact_reason43, no_contact_reason44, no_contact_reason45, no_contact_reason46,
                 no_contact_reason47, no_contact_reason48, no_contact_reason49, no_contact_reason50)
dim(person)

eip24 <- select(eip24, -mrn, -dob, 
               -race___1, -race___2, -race___3, -race___4, -race___5, 
               -race___6, -ethnicity,
               -sex_raised, -sex_selfdefined, -insurance, -address_county,
               -address_zip_code,
               -followup_date1, -followup_date2, -followup_date3, -followup_date4,
               -followup_date5, -followup_date6, -followup_date7, -followup_date8,
               -followup_date9, -followup_date10, -followup_date11, -followup_date12,
               -followup_date13, -followup_date14, -followup_date15, -followup_date16,
               -followup_date17, -followup_date18, -followup_date19, -followup_date20,
               -followup_date21, -followup_date22, -followup_date23, -followup_date24,
               -followup_date25, -followup_date26, -followup_date27, -followup_date28,
               -followup_date29, -followup_date30, -followup_date31, -followup_date32,
               -followup_date33, -followup_date34, -followup_date35, -followup_date36,
               -followup_date37, -followup_date38, -followup_date39, -followup_date40,
               -followup_date41, -followup_date42, -followup_date43, -followup_date44,
               -followup_date45, -followup_date46, -followup_date47, -followup_date48,
               -followup_date49, -followup_date50, -followup_counselor1, -followup_counselor2,
               -followup_counselor3, -followup_counselor4, -followup_counselor5,
               -followup_counselor6, -followup_counselor7, -followup_counselor8,
               -followup_counselor9, -followup_counselor10, -followup_counselor11,
               -followup_counselor12, -followup_counselor13, -followup_counselor14,
               -followup_counselor15, -followup_counselor16, -followup_counselor17,
               -followup_counselor18, -followup_counselor19, -followup_counselor20,
               -followup_counselor21, -followup_counselor22, -followup_counselor23,
               -followup_counselor24, -followup_counselor25, -followup_counselor26,
               -followup_counselor27, -followup_counselor28, -followup_counselor29,
               -followup_counselor30, -followup_counselor31, -followup_counselor32,
               -followup_counselor33, -followup_counselor34, -followup_counselor35,
               -followup_counselor36, -followup_counselor37, -followup_counselor38,
               -followup_counselor39, -followup_counselor40, -followup_counselor41,
               -followup_counselor42, -followup_counselor43, -followup_counselor44,
               -followup_counselor45, -followup_counselor46, -followup_counselor47,
               -followup_counselor48, -followup_counselor49, -followup_counselor50,
               -ltc_service1___8, -ltc_service2___8,
               -ltc_service3___8, -ltc_service4___8, -ltc_service5___8,
               -ltc_service6___8, -ltc_service7___8, -ltc_service8___8,
               -ltc_service9___8, -ltc_service10___8, -ltc_service11___8,
               -ltc_service12___8, -ltc_service13___8, -ltc_service14___8,
               -ltc_service15___8, -ltc_service16___8, -ltc_service17___8,
               -ltc_service18___8, -ltc_service19___8, -ltc_service20___8,
               -ltc_service21___8, -ltc_service22___8, -ltc_service23___8,
               -ltc_service24___8, -ltc_service25___8, -ltc_service26___8,
               -ltc_service27___8, -ltc_service28___8, -ltc_service29___8,
               -ltc_service30___8, -ltc_service31___8, -ltc_service32___8,
               -ltc_service33___8, -ltc_service34___8, -ltc_service35___8,
               -ltc_service36___8, -ltc_service37___8, -ltc_service38___8,
               -ltc_service39___8, -ltc_service40___8, -ltc_service41___8,
               -ltc_service42___8, -ltc_service43___8, -ltc_service44___8,
               -ltc_service45___8, -ltc_service46___8, -ltc_service47___8,
               -ltc_service48___8, -ltc_service49___8, -ltc_service50___8,
               -naccho_contact_day1, -naccho_contact_day2,
               -naccho_contact_day3, -naccho_contact_day4, -naccho_contact_day5,
               -naccho_contact_day6, -naccho_contact_day7, -naccho_contact_day8,
               -naccho_contact_day9, -naccho_contact_day10, -naccho_contact_day11,
               -naccho_contact_day12, -naccho_contact_day13, -naccho_contact_day14,
               -naccho_contact_day15, -naccho_contact_day16, -naccho_contact_day17,
               -naccho_contact_day18, -naccho_contact_day19, -naccho_contact_day20,
               -naccho_contact_day21, -naccho_contact_day22, -naccho_contact_day23,
               -naccho_contact_day24, -naccho_contact_day25, -naccho_contact_day26,
               -naccho_contact_day27, -naccho_contact_day28, -naccho_contact_day29,
               -naccho_contact_day30, -naccho_contact_day31, -naccho_contact_day32,
               -naccho_contact_day33, -naccho_contact_day34, -naccho_contact_day35,
               -naccho_contact_day36, -naccho_contact_day37, -naccho_contact_day38,
               -naccho_contact_day39, -naccho_contact_day40, -naccho_contact_day41,
               -naccho_contact_day42, -naccho_contact_day43, -naccho_contact_day44,
               -naccho_contact_day45, -naccho_contact_day46, -naccho_contact_day47,
               -naccho_contact_day48, -naccho_contact_day49, -naccho_contact_day50,
               -naccho_contact_confirm_tx1, -naccho_contact_confirm_tx2,
               -naccho_contact_confirm_tx3, -naccho_contact_confirm_tx4, -naccho_contact_confirm_tx5,
               -naccho_contact_confirm_tx6, -naccho_contact_confirm_tx7, -naccho_contact_confirm_tx8,
               -naccho_contact_confirm_tx9, -naccho_contact_confirm_tx10, -naccho_contact_confirm_tx11,
               -naccho_contact_confirm_tx12, -naccho_contact_confirm_tx13, -naccho_contact_confirm_tx14,
               -naccho_contact_confirm_tx15, -naccho_contact_confirm_tx16, -naccho_contact_confirm_tx17,
               -naccho_contact_confirm_tx18, -naccho_contact_confirm_tx19, -naccho_contact_confirm_tx20,
               -naccho_contact_confirm_tx21, -naccho_contact_confirm_tx22, -naccho_contact_confirm_tx23,
               -naccho_contact_confirm_tx24, -naccho_contact_confirm_tx25, -naccho_contact_confirm_tx26,
               -naccho_contact_confirm_tx27, -naccho_contact_confirm_tx28, -naccho_contact_confirm_tx29,
               -naccho_contact_confirm_tx30, -naccho_contact_confirm_tx31, -naccho_contact_confirm_tx32,
               -naccho_contact_confirm_tx33, -naccho_contact_confirm_tx34, -naccho_contact_confirm_tx35,
               -naccho_contact_confirm_tx36, -naccho_contact_confirm_tx37, -naccho_contact_confirm_tx38,
               -naccho_contact_confirm_tx39, -naccho_contact_confirm_tx40, -naccho_contact_confirm_tx41,
               -naccho_contact_confirm_tx42, -naccho_contact_confirm_tx43, -naccho_contact_confirm_tx44,
               -naccho_contact_confirm_tx45, -naccho_contact_confirm_tx46, -naccho_contact_confirm_tx47,
               -naccho_contact_confirm_tx48, -naccho_contact_confirm_tx49, -naccho_contact_confirm_tx50,
               -who_initiated_contact1, -who_initiated_contact2, -who_initiated_contact3, -who_initiated_contact4, -who_initiated_contact5,
               -who_initiated_contact6, -who_initiated_contact7, -who_initiated_contact8, -who_initiated_contact9, -who_initiated_contact10,
               -who_initiated_contact11, -who_initiated_contact12, -who_initiated_contact13, -who_initiated_contact14,
               -who_initiated_contact15, -who_initiated_contact16, -who_initiated_contact17, -who_initiated_contact18,
               -who_initiated_contact19, -who_initiated_contact20, -who_initiated_contact21, -who_initiated_contact22,
               -who_initiated_contact23, -who_initiated_contact24, -who_initiated_contact25, -who_initiated_contact26,
               -who_initiated_contact27, -who_initiated_contact28, -who_initiated_contact29, -who_initiated_contact30,
               -who_initiated_contact31, -who_initiated_contact32, -who_initiated_contact33, -who_initiated_contact34,
               -who_initiated_contact35, -who_initiated_contact36, -who_initiated_contact37, -who_initiated_contact38,
               -who_initiated_contact39, -who_initiated_contact40, -who_initiated_contact41, -who_initiated_contact42,
               -who_initiated_contact43, -who_initiated_contact44, -who_initiated_contact45, -who_initiated_contact46,
               -who_initiated_contact47, -who_initiated_contact48, -who_initiated_contact49, -who_initiated_contact50,
               -contact_with1, -contact_with2, -contact_with3, -contact_with4, -contact_with5,
               -contact_with6, -contact_with7, -contact_with8, -contact_with9, -contact_with10,
               -contact_with11, -contact_with12, -contact_with13, -contact_with14,
               -contact_with15, -contact_with16, -contact_with17, -contact_with18,
               -contact_with19, -contact_with20, -contact_with21, -contact_with22,
               -contact_with23, -contact_with24, -contact_with25, -contact_with26,
               -contact_with27, -contact_with28, -contact_with29, -contact_with30,
               -contact_with31, -contact_with32, -contact_with33, -contact_with34,
               -contact_with35, -contact_with36, -contact_with37, -contact_with38,
               -contact_with39, -contact_with40, -contact_with41, -contact_with42,
               -contact_with43, -contact_with44, -contact_with45, -contact_with46,
               -contact_with47, -contact_with48, -contact_with49, -contact_with50,
               -ltc_contact1, -ltc_contact2, -ltc_contact3, -ltc_contact4, -ltc_contact5,
               -ltc_contact6, -ltc_contact7, -ltc_contact8, -ltc_contact9, -ltc_contact10,
               -ltc_contact11, -ltc_contact12, -ltc_contact13, -ltc_contact14, -ltc_contact15,
               -ltc_contact16, -ltc_contact17, -ltc_contact18, -ltc_contact19, -ltc_contact20,
               -ltc_contact21, -ltc_contact22, -ltc_contact23, -ltc_contact24, -ltc_contact25,
               -ltc_contact26, -ltc_contact27, -ltc_contact28, -ltc_contact29, -ltc_contact30,
               -ltc_contact31, -ltc_contact32, -ltc_contact33, -ltc_contact34, -ltc_contact35,
               -ltc_contact36, -ltc_contact37, -ltc_contact38, -ltc_contact39, -ltc_contact40,
               -ltc_contact41, -ltc_contact42, -ltc_contact43, -ltc_contact44, -ltc_contact45,
               -ltc_contact46, -ltc_contact47, -ltc_contact48, -ltc_contact49, -ltc_contact50,
               -no_contact_reason1, -no_contact_reason2, -no_contact_reason3, -no_contact_reason4, -no_contact_reason5,
               -no_contact_reason6, -no_contact_reason7, -no_contact_reason8, -no_contact_reason9, -no_contact_reason10,
               -no_contact_reason11, -no_contact_reason12, -no_contact_reason13, -no_contact_reason14,
               -no_contact_reason15, -no_contact_reason16, -no_contact_reason17, -no_contact_reason18,
               -no_contact_reason19, -no_contact_reason20, -no_contact_reason21, -no_contact_reason22,
               -no_contact_reason23, -no_contact_reason24, -no_contact_reason25, -no_contact_reason26,
               -no_contact_reason27, -no_contact_reason28, -no_contact_reason29, -no_contact_reason30,
               -no_contact_reason31, -no_contact_reason32, -no_contact_reason33, -no_contact_reason34,
               -no_contact_reason35, -no_contact_reason36, -no_contact_reason37, -no_contact_reason38,
               -no_contact_reason39, -no_contact_reason40, -no_contact_reason41, -no_contact_reason42,
               -no_contact_reason43, -no_contact_reason44, -no_contact_reason45, -no_contact_reason46,
               -no_contact_reason47, -no_contact_reason48, -no_contact_reason49, -no_contact_reason50)

# Merge person dataset with full eip24 dataset

dim(eip24)
dim(person)
eip24 <- merge(eip24, person, by='record_id', all.x=T)
dim(eip24)
eip24 <- distinct(eip24)
dim(eip24)

```

``` {r Combining Datasets, include=FALSE}

### Combine 2023/2024 Data

eip <- eip24
dim(eip)

```

``` {r Patient Information, include=FALSE}

# Formatting variables

summary(eip$enc_date)
eip$enc_date <- as.Date(eip$enc_date, format='%m/%d/%Y')
summary(eip$enc_date)

summary(eip$dob)
eip$dob <- as.Date(eip$dob, format='%m/%d/%Y')
summary(eip$dob)


table(eip$race___1)
White <- eip[which(eip$race___1 == '1'), ]
dim(White)
White <- select(White, record_id)
White$White <- 1
table(White$White)
White <- distinct(White)
dim(White)
head(White)

table(eip$race___2)
Black <- eip[which(eip$race___2 == '1'), ]
dim(Black)
Black <- select(Black, record_id)
Black$Black <- 1
table(Black$Black)
Black <- distinct(Black)
dim(Black)
head(Black)

table(eip$race___3)
Asian <- eip[which(eip$race___3 == '1'), ]
dim(Asian)
Asian <- select(Asian, record_id)
Asian$Asian <- 1
table(Asian$Asian)
Asian <- distinct(Asian)
dim(Asian)
head(Asian)

table(eip$race___4)
AmIn <- eip[which(eip$race___4 == '1'), ]
dim(AmIn)
AmIn <- select(AmIn, record_id)
AmIn$AmIn <- 1
table(AmIn$AmIn)
AmIn <- distinct(AmIn)
dim(AmIn)
head(AmIn)

table(eip$race___5)
RaceOther <- eip[which(eip$race___5 == '1'), ]
dim(RaceOther)
RaceOther <- select(RaceOther, record_id)
RaceOther$RaceOther <- 1
table(RaceOther$RaceOther)
RaceOther <- distinct(RaceOther)
dim(RaceOther)
head(RaceOther)

table(eip$race___6)
RaceUnk <- eip[which(eip$race___6 == '1'), ]
dim(RaceUnk)
RaceUnk <- select(RaceUnk, record_id)
RaceUnk$RaceUnk <- 1
table(RaceUnk$RaceUnk)
RaceUnk <- distinct(RaceUnk)
dim(RaceUnk)
head(RaceUnk)

table(eip$ethnicity)
RaceHisp <- eip[which(eip$ethnicity == 1), ]
dim(RaceHisp)
RaceHisp <- select(RaceHisp, record_id)
RaceHisp$RaceHisp <- 1
table(RaceHisp$RaceHisp)
RaceHisp <- distinct(RaceHisp)
dim(RaceHisp)
head(RaceHisp)


race <- select(eip, record_id)
race <- distinct(race)
dim(race)


dim(race)
race <- merge(race, White, by = 'record_id', all.x = T)
race <- merge(race, Black, by = 'record_id', all.x = T)
race <- merge(race, Asian, by = 'record_id', all.x = T)
race <- merge(race, AmIn, by = 'record_id', all.x = T)
race <- merge(race, RaceOther, by = 'record_id', all.x = T)
race <- merge(race, RaceUnk, by = 'record_id', all.x = T)
race <- merge(race, RaceHisp, by = 'record_id', all.x = T)
dim(race)
head(race)

race$White[is.na(race$White)] <- 0
race$Black[is.na(race$Black)] <- 0
race$Asian[is.na(race$Asian)] <- 0
race$AmIn[is.na(race$AmIn)] <- 0
race$RaceOther[is.na(race$RaceOther)] <- 0
race$RaceUnk[is.na(race$RaceUnk)] <- 0
race$RaceHisp[is.na(race$RaceHisp)] <- 0

race$RaceNumber <- race$White + race$Black + race$Asian + race$AmIn + race$RaceOther + race$RaceUnk + race$RaceHisp
table(race$RaceNumber)
head(race)

race$race[race$RaceNumber == 1 & race$Black == 1] <- 'Black/African American'
race$race[race$RaceNumber == 1 & race$White == 1] <- 'White'
race$race[race$RaceNumber == 1 & race$Asian == 1] <- 'Asian/Pacific Islander'
race$race[race$RaceNumber == 1 & race$AmIn == 1] <- 'American Indian/Alaska native'
race$race[race$RaceNumber == 1 & race$RaceOther == 1] <- 'Other'
race$race[(race$RaceNumber == 1 & race$RaceHisp == 1) |
            (race$RaceNumber > 1 & race$RaceHisp == 1)] <- 'Hispanic/Latinx'
race$race[race$RaceNumber > 1 & race$RaceHisp != 1] <- 'Biracial/Multiracial'
race$race[race$RaceNumber == 0 | is.na(race$RaceNumber) | race$RaceUnk == 1] <- 'Unknown'
table(race$race)

dim(eip)
dim(race)
eip <- merge(eip, race, by = 'record_id', all.x = T)
dim(eip)
table(eip$race)




table(eip$sex_raised)
eip$sex[eip$sex_raised == 1] <- 'Male'
eip$sex[eip$sex_raised == 2] <- 'Female'
eip$sex[eip$sex_raised == 3 | is.na(eip$sex_raised) | eip$sex_raised == ''] <- 'Unknown/Unassigned'
table(eip$sex)



table(eip$sex_raised, eip$sex_selfdefined)
eip$gender[eip$sex_raised == 1 & eip$sex_selfdefined == 1] <- 'Male'
eip$gender[eip$sex_raised == 2 & eip$sex_selfdefined == 2] <- 'Female'
eip$gender[(eip$sex_raised == 1 & eip$sex_selfdefined == 2) |
             (eip$sex_raised == 2 & eip$sex_selfdefined == 1) |
             (eip$sex_raised == 1 & eip$sex_selfdefined == 3) |
             (eip$sex_raised == 2 & eip$sex_selfdefined == 3)] <- 'Transgender/Nonbinary'
eip$gender[(eip$sex_raised == 3 & eip$sex_selfdefined == 3) |
             is.na(eip$sex_raised) | is.na(eip$sex_selfdefined)] <- 'Unknown'
table(eip$gender)


table(eip$insurance)
eip$insurance[eip$insurance == 1] <- 'None'
eip$insurance[eip$insurance == 2] <- 'UC Health (Levy)'
eip$insurance[eip$insurance == 3] <- 'Medicaid'
eip$insurance[eip$insurance == 4] <- 'Medicare'
eip$insurance[eip$insurance == 5] <- 'Military/VA'
eip$insurance[eip$insurance == 6] <- 'Private'
eip$insurance[eip$insurance == 7] <- 'Dual Medicaid/Medicare'
eip$insurance[is.na(eip$insurance)] <- 'Unknown'
table(eip$insurance)



# Populations of Interest
### WOC, Youth (18-29), MSM, IDU, HRHS, PLWHA

table(eip$race, eip$gender)
eip$WOC[(eip$race != 'White' & eip$race != 'Unknown') & eip$gender == 'Female'] <- 1
table(eip$WOC)


table(eip$age)
eip$Youth[eip$age >= 13 & eip$age <= 29] <- 1
table(eip$Youth)


eip$MSM[eip$gender == 'Male' & ((eip$sex_orientation == '2' | eip$sex_orientation == '4') |
                                  (eip$sex_w_man___1 == '1' | eip$sex_w_man___2 == '1' |
                                     eip$sex_w_man___3 == '1') |
                                  (eip$sex_w_ftm___1 == '1' | eip$sex_w_ftm___2 == '1' |
                                     eip$sex_w_ftm___3 == '1') |
                                  (eip$sex_msm___1 == '1' | eip$sex_msm___2 == '1' |
                                     eip$sex_msm___3 == '1') |
                                  (eip$hiv_dx_risks___2 == '1'))] <- 1
table(eip$MSM)


eip$IDU[eip$idu_calc == 1 | eip$hiv_dx_risks___3 == '1'] <- 1
table(eip$IDU)


# For HRHS, all sexual behavior is within the previous 12 months
### Heterosexual males that have unprotected sex with women
### Heterosexual women that have unprotected sex with men
### Heterosexual women that have sex with MSM
### Heterosexual men/women that have sex with IDU
### Heterosexual men/women that have sex with HIV+ partner
### Heterosexual men/women that exchange money/drugs for sex
### Heterosexual men/women that have sex with STD+ partner
### Heterosexual men/women that have more than 3 partners

eip$Hetero[(eip$gender == 'Male' & (eip$sex_w_woman___1 == '1' |
                                      eip$sex_w_woman___2 == '1' |
                                      eip$sex_w_woman___3 == '1' |
                                      eip$sex_orientation == '1')) |
             (eip$gender == 'Female' & (eip$sex_w_man___1 == '1' |
                                          eip$sex_w_man___2 == '1' |
                                          eip$sex_w_man___3 == '1' |
                                          eip$sex_orientation == '1'))] <- 1
table(eip$Hetero)


eip$HRHS[((eip$Hetero == 1) & ((((eip$sex_w_woman___6 == '1' | eip$sex_w_woman___7 == '1') |
                                   (is.na(eip$sex_w_woman___6) & is.na(eip$sex_w_woman___7) &
                                      is.na(eip$sex_w_woman___8)))) | (((eip$sex_w_man___6 == '1' |
                                                                           eip$sex_w_man___7 == '1') |
                                                                          (is.na(eip$sex_w_man___6) &
                                                                             is.na(eip$sex_w_man___7) &
                                                                             is.na(eip$sex_w_man___8)))) |
                                 (eip$sex_msm___1 == '1' | eip$sex_msm___2 == '1' | eip$sex_msm___3 == '1') |
                                 (eip$sex_idu___1 == '1' | eip$sex_idu___2 == '1' | eip$sex_idu___3 == '1') |
                                 (eip$sex_hiv_pos___1 == '1' | eip$sex_hiv_pos___2 == '1' |
                                    eip$sex_hiv_pos___3 == '1') | (eip$sex_receivemoney___1 == '1' |
                                                                     eip$sex_receivemoney___2 == '1' |
                                                                     eip$sex_receivemoney___3 == '1' |
                                                                     eip$sex_receivedrugs___1 == '1' |
                                                                     eip$sex_receivedrugs___2 == '1' |
                                                                     eip$sex_receivedrugs___3 == '1' |
                                                                     eip$sex_paymoney___1 == '1' |
                                                                     eip$sex_paymoney___2 == '1' |
                                                                     eip$sex_paymoney___3 == '1' |
                                                                     eip$sex_paydrugs___1 == '1' |
                                                                     eip$sex_paydrugs___2 == '1' |
                                                                     eip$sex_paydrugs___3 == '1')  |
                                 (eip$sex_sti_pos___1 == '1' | eip$sex_sti_pos___2 == '1' |
                                    eip$sex_sti_pos___3 == '1') | (eip$sex_partners_past_year >= 3))) |
           (eip$hiv_dx_risks___1 == '1')] <- 1
table(eip$HRHS)




# Appalachian

eip$appalachian_pt[eip$address_zip_code == 43006 | eip$address_zip_code == 43056 |
                     eip$address_zip_code == 43076 | eip$address_zip_code == 43101 |
                     eip$address_zip_code == 43102 | eip$address_zip_code == 43107 |
                     eip$address_zip_code == 43111 | eip$address_zip_code == 43115 |
                     eip$address_zip_code == 43127 | eip$address_zip_code == 43135 |
                     eip$address_zip_code == 43138 | eip$address_zip_code == 43144 |
                     eip$address_zip_code == 43148 | eip$address_zip_code == 43149 |
                     eip$address_zip_code == 43150 | eip$address_zip_code == 43152 |
                     eip$address_zip_code == 43155 | eip$address_zip_code == 43158 |
                     eip$address_zip_code == 43160 | eip$address_zip_code == 43164 |
                     eip$address_zip_code == 43701 | eip$address_zip_code == 43702 |
                     eip$address_zip_code == 43711 | eip$address_zip_code == 43713 |
                     eip$address_zip_code == 43716 | eip$address_zip_code == 43717 |
                     eip$address_zip_code == 43718 | eip$address_zip_code == 43719 |
                     eip$address_zip_code == 43720 | eip$address_zip_code == 43722 |
                     eip$address_zip_code == 43723 | eip$address_zip_code == 43724 |
                     eip$address_zip_code == 43725 | eip$address_zip_code == 43727 |
                     eip$address_zip_code == 43728 | eip$address_zip_code == 43730 |
                     eip$address_zip_code == 43731 | eip$address_zip_code == 43732 |
                     eip$address_zip_code == 43733 | eip$address_zip_code == 43734 |
                     eip$address_zip_code == 43735 | eip$address_zip_code == 43736 |
                     eip$address_zip_code == 43738 | eip$address_zip_code == 43739 |
                     eip$address_zip_code == 43746 | eip$address_zip_code == 43747 |
                     eip$address_zip_code == 43748 | eip$address_zip_code == 43749 |
                     eip$address_zip_code == 43750 | eip$address_zip_code == 43752 |
                     eip$address_zip_code == 43754 | eip$address_zip_code == 43755 |
                     eip$address_zip_code == 43756 | eip$address_zip_code == 43757 |
                     eip$address_zip_code == 43758 | eip$address_zip_code == 43759 |
                     eip$address_zip_code == 43760 | eip$address_zip_code == 43761 |
                     eip$address_zip_code == 43762 | eip$address_zip_code == 43764 |
                     eip$address_zip_code == 43766 | eip$address_zip_code == 43767 |
                     eip$address_zip_code == 43768 | eip$address_zip_code == 43771 |
                     eip$address_zip_code == 43772 | eip$address_zip_code == 43773 |
                     eip$address_zip_code == 43777 | eip$address_zip_code == 43778 |
                     eip$address_zip_code == 43779 | eip$address_zip_code == 43780 |
                     eip$address_zip_code == 43782 | eip$address_zip_code == 43783 |
                     eip$address_zip_code == 43786 | eip$address_zip_code == 43787 |
                     eip$address_zip_code == 43788 | eip$address_zip_code == 43791 |
                     eip$address_zip_code == 43793 | eip$address_zip_code == 43802 |
                     eip$address_zip_code == 43803 | eip$address_zip_code == 43804 |
                     eip$address_zip_code == 43805 | eip$address_zip_code == 43811 |
                     eip$address_zip_code == 43812 | eip$address_zip_code == 43821 |
                     eip$address_zip_code == 43822 | eip$address_zip_code == 43824 |
                     eip$address_zip_code == 43828 | eip$address_zip_code == 43830 |
                     eip$address_zip_code == 43832 | eip$address_zip_code == 43836 |
                     eip$address_zip_code == 43837 | eip$address_zip_code == 43840 |
                     eip$address_zip_code == 43842 | eip$address_zip_code == 43843 |
                     eip$address_zip_code == 43844 | eip$address_zip_code == 43845 |
                     eip$address_zip_code == 43901 | eip$address_zip_code == 43902 |
                     eip$address_zip_code == 43903 | eip$address_zip_code == 43905 |
                     eip$address_zip_code == 43906 | eip$address_zip_code == 43907 |
                     eip$address_zip_code == 43908 | eip$address_zip_code == 43909 |
                     eip$address_zip_code == 43910 | eip$address_zip_code == 43912 |
                     eip$address_zip_code == 43913 | eip$address_zip_code == 43914 |
                     eip$address_zip_code == 43915 | eip$address_zip_code == 43916 |
                     eip$address_zip_code == 43917 | eip$address_zip_code == 43920 |
                     eip$address_zip_code == 43925 | eip$address_zip_code == 43926 |
                     eip$address_zip_code == 43927 | eip$address_zip_code == 43928 |
                     eip$address_zip_code == 43930 | eip$address_zip_code == 43931 |
                     eip$address_zip_code == 43932 | eip$address_zip_code == 43933 |
                     eip$address_zip_code == 43934 | eip$address_zip_code == 43935 |
                     eip$address_zip_code == 43937 | eip$address_zip_code == 43938 |
                     eip$address_zip_code == 43939 | eip$address_zip_code == 43940 |
                     eip$address_zip_code == 43941 | eip$address_zip_code == 43942 |
                     eip$address_zip_code == 43943 | eip$address_zip_code == 43944 |
                     eip$address_zip_code == 43945 | eip$address_zip_code == 43946 |
                     eip$address_zip_code == 43947 | eip$address_zip_code == 43948 |
                     eip$address_zip_code == 43950 | eip$address_zip_code == 43951 |
                     eip$address_zip_code == 43952 | eip$address_zip_code == 43953 |
                     eip$address_zip_code == 43961 | eip$address_zip_code == 43962 |
                     eip$address_zip_code == 43963 | eip$address_zip_code == 43964 |
                     eip$address_zip_code == 43967 | eip$address_zip_code == 43968 |
                     eip$address_zip_code == 43970 | eip$address_zip_code == 43971 |
                     eip$address_zip_code == 43972 | eip$address_zip_code == 43973 |
                     eip$address_zip_code == 43974 | eip$address_zip_code == 43976 |
                     eip$address_zip_code == 43977 | eip$address_zip_code == 43981 |
                     eip$address_zip_code == 43983 | eip$address_zip_code == 43984 |
                     eip$address_zip_code == 43985 | eip$address_zip_code == 43986 |
                     eip$address_zip_code == 43988 | eip$address_zip_code == 44003 |
                     eip$address_zip_code == 44004 | eip$address_zip_code == 44005 |
                     eip$address_zip_code == 44010 | eip$address_zip_code == 44030 |
                     eip$address_zip_code == 44032 | eip$address_zip_code == 44041 |
                     eip$address_zip_code == 44046 | eip$address_zip_code == 44047 |
                     eip$address_zip_code == 44048 | eip$address_zip_code == 44057 |
                     eip$address_zip_code == 44062 | eip$address_zip_code == 44064 |
                     eip$address_zip_code == 44068 | eip$address_zip_code == 44076 |
                     eip$address_zip_code == 44082 | eip$address_zip_code == 44084 |
                     eip$address_zip_code == 44085 | eip$address_zip_code == 44086 |
                     eip$address_zip_code == 44088 | eip$address_zip_code == 44093 |
                     eip$address_zip_code == 44099 | eip$address_zip_code == 44231 |
                     eip$address_zip_code == 44288 | eip$address_zip_code == 44401 |
                     eip$address_zip_code == 44402 | eip$address_zip_code == 44403 |
                     eip$address_zip_code == 44404 | eip$address_zip_code == 44405 |
                     eip$address_zip_code == 44406 | eip$address_zip_code == 44408 |
                     eip$address_zip_code == 44410 | eip$address_zip_code == 44411 |
                     eip$address_zip_code == 44412 | eip$address_zip_code == 44413 |
                     eip$address_zip_code == 44415 | eip$address_zip_code == 44416 |
                     eip$address_zip_code == 44417 | eip$address_zip_code == 44418 |
                     eip$address_zip_code == 44420 | eip$address_zip_code == 44422 |
                     eip$address_zip_code == 44423 | eip$address_zip_code == 44424 |
                     eip$address_zip_code == 44425 | eip$address_zip_code == 44427 |
                     eip$address_zip_code == 44428 | eip$address_zip_code == 44429 |
                     eip$address_zip_code == 44430 | eip$address_zip_code == 44431 |
                     eip$address_zip_code == 44432 | eip$address_zip_code == 44436 |
                     eip$address_zip_code == 44437 | eip$address_zip_code == 44438 |
                     eip$address_zip_code == 44439 | eip$address_zip_code == 44440 |
                     eip$address_zip_code == 44441 | eip$address_zip_code == 44442 |
                     eip$address_zip_code == 44443 | eip$address_zip_code == 44444 |
                     eip$address_zip_code == 44445 | eip$address_zip_code == 44446 |
                     eip$address_zip_code == 44449 | eip$address_zip_code == 44450 |
                     eip$address_zip_code == 44451 | eip$address_zip_code == 44452 |
                     eip$address_zip_code == 44453 | eip$address_zip_code == 44454 |
                     eip$address_zip_code == 44455 | eip$address_zip_code == 44460 |
                     eip$address_zip_code == 44470 | eip$address_zip_code == 44471 |
                     eip$address_zip_code == 44473 | eip$address_zip_code == 44481 |
                     eip$address_zip_code == 44482 | eip$address_zip_code == 44483 |
                     eip$address_zip_code == 44484 | eip$address_zip_code == 44485 |
                     eip$address_zip_code == 44486 | eip$address_zip_code == 44490 |
                     eip$address_zip_code == 44491 | eip$address_zip_code == 44492 |
                     eip$address_zip_code == 44493 | eip$address_zip_code == 44501 |
                     eip$address_zip_code == 44502 | eip$address_zip_code == 44503 |
                     eip$address_zip_code == 44504 | eip$address_zip_code == 44505 |
                     eip$address_zip_code == 44506 | eip$address_zip_code == 44507 |
                     eip$address_zip_code == 44509 | eip$address_zip_code == 44510 |
                     eip$address_zip_code == 44511 | eip$address_zip_code == 44512 |
                     eip$address_zip_code == 44513 | eip$address_zip_code == 44514 |
                     eip$address_zip_code == 44515 | eip$address_zip_code == 44555 |
                     eip$address_zip_code == 44601 | eip$address_zip_code == 44607 |
                     eip$address_zip_code == 44608 | eip$address_zip_code == 44609 |
                     eip$address_zip_code == 44610 | eip$address_zip_code == 44611 |
                     eip$address_zip_code == 44612 | eip$address_zip_code == 44615 |
                     eip$address_zip_code == 44617 | eip$address_zip_code == 44619 |
                     eip$address_zip_code == 44620 | eip$address_zip_code == 44621 |
                     eip$address_zip_code == 44622 | eip$address_zip_code == 44624 |
                     eip$address_zip_code == 44625 | eip$address_zip_code == 44626 |
                     eip$address_zip_code == 44627 | eip$address_zip_code == 44628 |
                     eip$address_zip_code == 44629 | eip$address_zip_code == 44633 |
                     eip$address_zip_code == 44634 | eip$address_zip_code == 44637 |
                     eip$address_zip_code == 44638 | eip$address_zip_code == 44639 |
                     eip$address_zip_code == 44643 | eip$address_zip_code == 44644 |
                     eip$address_zip_code == 44651 | eip$address_zip_code == 44653 |
                     eip$address_zip_code == 44654 | eip$address_zip_code == 44656 |
                     eip$address_zip_code == 44657 | eip$address_zip_code == 44660 |
                     eip$address_zip_code == 44661 | eip$address_zip_code == 44663 |
                     eip$address_zip_code == 44665 | eip$address_zip_code == 44671 |
                     eip$address_zip_code == 44672 | eip$address_zip_code == 44675 |
                     eip$address_zip_code == 44676 | eip$address_zip_code == 44678 |
                     eip$address_zip_code == 44679 | eip$address_zip_code == 44680 |
                     eip$address_zip_code == 44681 | eip$address_zip_code == 44682 |
                     eip$address_zip_code == 44683 | eip$address_zip_code == 44687 |
                     eip$address_zip_code == 44688 | eip$address_zip_code == 44689 |
                     eip$address_zip_code == 44690 | eip$address_zip_code == 44693 |
                     eip$address_zip_code == 44695 | eip$address_zip_code == 44697 |
                     eip$address_zip_code == 44699 | eip$address_zip_code == 44730 |
                     eip$address_zip_code == 44842 | eip$address_zip_code == 45101 |
                     eip$address_zip_code == 45102 | eip$address_zip_code == 45103 |
                     eip$address_zip_code == 45105 | eip$address_zip_code == 45106 |
                     eip$address_zip_code == 45107 | eip$address_zip_code == 45112 |
                     eip$address_zip_code == 45115 | eip$address_zip_code == 45118 |
                     eip$address_zip_code == 45119 | eip$address_zip_code == 45120 |
                     eip$address_zip_code == 45121 | eip$address_zip_code == 45122 |
                     eip$address_zip_code == 45123 | eip$address_zip_code == 45130 |
                     eip$address_zip_code == 45131 | eip$address_zip_code == 45132 |
                     eip$address_zip_code == 45133 | eip$address_zip_code == 45135 |
                     eip$address_zip_code == 45140 | eip$address_zip_code == 45142 |
                     eip$address_zip_code == 45144 | eip$address_zip_code == 45147 |
                     eip$address_zip_code == 45148 | eip$address_zip_code == 45150 |
                     eip$address_zip_code == 45153 | eip$address_zip_code == 45154 |
                     eip$address_zip_code == 45155 | eip$address_zip_code == 45156 |
                     eip$address_zip_code == 45157 | eip$address_zip_code == 45158 |
                     eip$address_zip_code == 45159 | eip$address_zip_code == 45160 |
                     eip$address_zip_code == 45162 | eip$address_zip_code == 45167 |
                     eip$address_zip_code == 45168 | eip$address_zip_code == 45171 |
                     eip$address_zip_code == 45172 | eip$address_zip_code == 45176 |
                     eip$address_zip_code == 45244 | eip$address_zip_code == 45245 |
                     eip$address_zip_code == 45255 | eip$address_zip_code == 45601 |
                     eip$address_zip_code == 45612 | eip$address_zip_code == 45613 |
                     eip$address_zip_code == 45614 | eip$address_zip_code == 45616 |
                     eip$address_zip_code == 45617 | eip$address_zip_code == 45618 |
                     eip$address_zip_code == 45619 | eip$address_zip_code == 45620 |
                     eip$address_zip_code == 45621 | eip$address_zip_code == 45622 |
                     eip$address_zip_code == 45623 | eip$address_zip_code == 45624 |
                     eip$address_zip_code == 45628 | eip$address_zip_code == 45629 |
                     eip$address_zip_code == 45630 | eip$address_zip_code == 45631 |
                     eip$address_zip_code == 45633 | eip$address_zip_code == 45634 |
                     eip$address_zip_code == 45636 | eip$address_zip_code == 45638 |
                     eip$address_zip_code == 45640 | eip$address_zip_code == 45642 |
                     eip$address_zip_code == 45643 | eip$address_zip_code == 45644 |
                     eip$address_zip_code == 45645 | eip$address_zip_code == 45646 |
                     eip$address_zip_code == 45647 | eip$address_zip_code == 45648 |
                     eip$address_zip_code == 45650 | eip$address_zip_code == 45651 |
                     eip$address_zip_code == 45652 | eip$address_zip_code == 45653 |
                     eip$address_zip_code == 45654 | eip$address_zip_code == 45656 |
                     eip$address_zip_code == 45657 | eip$address_zip_code == 45658 |
                     eip$address_zip_code == 45659 | eip$address_zip_code == 45660 |
                     eip$address_zip_code == 45661 | eip$address_zip_code == 45662 |
                     eip$address_zip_code == 45663 | eip$address_zip_code == 45669 |
                     eip$address_zip_code == 45671 | eip$address_zip_code == 45672 |
                     eip$address_zip_code == 45673 | eip$address_zip_code == 45674 |
                     eip$address_zip_code == 45675 | eip$address_zip_code == 45677 |
                     eip$address_zip_code == 45678 | eip$address_zip_code == 45679 |
                     eip$address_zip_code == 45680 | eip$address_zip_code == 45681 |
                     eip$address_zip_code == 45682 | eip$address_zip_code == 45683 |
                     eip$address_zip_code == 45684 | eip$address_zip_code == 45685 |
                     eip$address_zip_code == 45686 | eip$address_zip_code == 45687 |
                     eip$address_zip_code == 45688 | eip$address_zip_code == 45690 |
                     eip$address_zip_code == 45692 | eip$address_zip_code == 45693 |
                     eip$address_zip_code == 45694 | eip$address_zip_code == 45695 |
                     eip$address_zip_code == 45696 | eip$address_zip_code == 45697 |
                     eip$address_zip_code == 45698 | eip$address_zip_code == 45699 |
                     eip$address_zip_code == 45701 | eip$address_zip_code == 45710 |
                     eip$address_zip_code == 45711 | eip$address_zip_code == 45712 |
                     eip$address_zip_code == 45713 | eip$address_zip_code == 45714 |
                     eip$address_zip_code == 45715 | eip$address_zip_code == 45716 |
                     eip$address_zip_code == 45717 | eip$address_zip_code == 45719 |
                     eip$address_zip_code == 45720 | eip$address_zip_code == 45721 |
                     eip$address_zip_code == 45723 | eip$address_zip_code == 45724 |
                     eip$address_zip_code == 45727 | eip$address_zip_code == 45729 |
                     eip$address_zip_code == 45732 | eip$address_zip_code == 45734 |
                     eip$address_zip_code == 45735 | eip$address_zip_code == 45739 |
                     eip$address_zip_code == 45740 | eip$address_zip_code == 45741 |
                     eip$address_zip_code == 45742 | eip$address_zip_code == 45743 |
                     eip$address_zip_code == 45744 | eip$address_zip_code == 45745 |
                     eip$address_zip_code == 45746 | eip$address_zip_code == 45750 |
                     eip$address_zip_code == 45760 | eip$address_zip_code == 45761 |
                     eip$address_zip_code == 45764 | eip$address_zip_code == 45766 |
                     eip$address_zip_code == 45767 | eip$address_zip_code == 45768 |
                     eip$address_zip_code == 45769 | eip$address_zip_code == 45770 |
                     eip$address_zip_code == 45771 | eip$address_zip_code == 45772 |
                     eip$address_zip_code == 45773 | eip$address_zip_code == 45775 |
                     eip$address_zip_code == 45776 | eip$address_zip_code == 45777 |
                     eip$address_zip_code == 45778 | eip$address_zip_code == 45779 |
                     eip$address_zip_code == 45780 | eip$address_zip_code == 45782 |
                     eip$address_zip_code == 45783 | eip$address_zip_code == 45784 |
                     eip$address_zip_code == 45786 | eip$address_zip_code == 45787 |
                     eip$address_zip_code == 45788 | eip$address_zip_code == 45789 |
                     (eip$appalachian == 1 | eip$appalachian_family == 1)] <- 1
table(eip$appalachian_pt)



# EIP unique patients
dim(eip)
eip_pts <- select(eip, record_id)
dim(eip_pts)
eip_pts <- distinct(eip_pts)
dim(eip_pts)

eip_patients <- nrow(eip_pts)
eip_patients



# PLWHA
eip$plwha[(eip$history_hiv_test_result == 1 |
             eip$reason_for_offer_category_hiv_test == 7 |
             eip$reason_for_offer_category_hiv_test == 8 |
             eip$offer_outcome_declined_hiv___21 == 1 |
             eip$offer_outcome_declined_hiv_2___21 == 1 |
             eip$offer_outcome_declined_hiv_3___21 == 1 |
             eip$final_test_status_hiv == 1 |
             eip$diagnosis_hiv == 1 |
             eip$diagnosis_hiv == 2)] <- 1
table(eip$plwha)


table(eip$plwha)
plwha <- eip[which(eip$plwha == 1), ]
dim(plwha)
plwha <- nrow(plwha)
plwha



# Formatting contact note dates
eip$followup_date1 <- as.Date(eip$followup_date1, format = '%m/%d/%Y')
eip$followup_date2 <- as.Date(eip$followup_date2, format = '%m/%d/%Y')
eip$followup_date3 <- as.Date(eip$followup_date3, format = '%m/%d/%Y')
eip$followup_date4 <- as.Date(eip$followup_date4, format = '%m/%d/%Y')
eip$followup_date5 <- as.Date(eip$followup_date5, format = '%m/%d/%Y')
eip$followup_date6 <- as.Date(eip$followup_date6, format = '%m/%d/%Y')
eip$followup_date7 <- as.Date(eip$followup_date7, format = '%m/%d/%Y')
eip$followup_date8 <- as.Date(eip$followup_date8, format = '%m/%d/%Y')
eip$followup_date9 <- as.Date(eip$followup_date9, format = '%m/%d/%Y')
eip$followup_date10 <- as.Date(eip$followup_date10, format = '%m/%d/%Y')
eip$followup_date11 <- as.Date(eip$followup_date11, format = '%m/%d/%Y')
eip$followup_date12 <- as.Date(eip$followup_date12, format = '%m/%d/%Y')
eip$followup_date13 <- as.Date(eip$followup_date13, format = '%m/%d/%Y')
eip$followup_date14 <- as.Date(eip$followup_date14, format = '%m/%d/%Y')
eip$followup_date15 <- as.Date(eip$followup_date15, format = '%m/%d/%Y')
eip$followup_date16 <- as.Date(eip$followup_date16, format = '%m/%d/%Y')
eip$followup_date17 <- as.Date(eip$followup_date17, format = '%m/%d/%Y')
eip$followup_date18 <- as.Date(eip$followup_date18, format = '%m/%d/%Y')
eip$followup_date19 <- as.Date(eip$followup_date19, format = '%m/%d/%Y')
eip$followup_date20 <- as.Date(eip$followup_date20, format = '%m/%d/%Y')
eip$followup_date21 <- as.Date(eip$followup_date21, format = '%m/%d/%Y')
eip$followup_date22 <- as.Date(eip$followup_date22, format = '%m/%d/%Y')
eip$followup_date23 <- as.Date(eip$followup_date23, format = '%m/%d/%Y')
eip$followup_date24 <- as.Date(eip$followup_date24, format = '%m/%d/%Y')
eip$followup_date25 <- as.Date(eip$followup_date25, format = '%m/%d/%Y')
eip$followup_date26 <- as.Date(eip$followup_date26, format = '%m/%d/%Y')
eip$followup_date27 <- as.Date(eip$followup_date27, format = '%m/%d/%Y')
eip$followup_date28 <- as.Date(eip$followup_date28, format = '%m/%d/%Y')
eip$followup_date29 <- as.Date(eip$followup_date29, format = '%m/%d/%Y')
eip$followup_date30 <- as.Date(eip$followup_date30, format = '%m/%d/%Y')
eip$followup_date31 <- as.Date(eip$followup_date31, format = '%m/%d/%Y')
eip$followup_date32 <- as.Date(eip$followup_date32, format = '%m/%d/%Y')
eip$followup_date33 <- as.Date(eip$followup_date33, format = '%m/%d/%Y')
eip$followup_date34 <- as.Date(eip$followup_date34, format = '%m/%d/%Y')
eip$followup_date35 <- as.Date(eip$followup_date35, format = '%m/%d/%Y')
eip$followup_date36 <- as.Date(eip$followup_date36, format = '%m/%d/%Y')
eip$followup_date37 <- as.Date(eip$followup_date37, format = '%m/%d/%Y')
eip$followup_date38 <- as.Date(eip$followup_date38, format = '%m/%d/%Y')
eip$followup_date39 <- as.Date(eip$followup_date39, format = '%m/%d/%Y')
eip$followup_date40 <- as.Date(eip$followup_date40, format = '%m/%d/%Y')
eip$followup_date41 <- as.Date(eip$followup_date41, format = '%m/%d/%Y')
eip$followup_date42 <- as.Date(eip$followup_date42, format = '%m/%d/%Y')
eip$followup_date43 <- as.Date(eip$followup_date43, format = '%m/%d/%Y')
eip$followup_date44 <- as.Date(eip$followup_date44, format = '%m/%d/%Y')
eip$followup_date45 <- as.Date(eip$followup_date45, format = '%m/%d/%Y')
eip$followup_date46 <- as.Date(eip$followup_date46, format = '%m/%d/%Y')
eip$followup_date47 <- as.Date(eip$followup_date47, format = '%m/%d/%Y')
eip$followup_date48 <- as.Date(eip$followup_date48, format = '%m/%d/%Y')
eip$followup_date49 <- as.Date(eip$followup_date49, format = '%m/%d/%Y')
eip$followup_date50 <- as.Date(eip$followup_date50, format = '%m/%d/%Y')


# Formatting timeframe between encounter date and contact note
eip$datediff1 <- as.numeric(interval(eip$enc_date, eip$followup_date1)/ddays(1))
eip$datediff2 <- as.numeric(interval(eip$enc_date, eip$followup_date2)/ddays(1))
eip$datediff3 <- as.numeric(interval(eip$enc_date, eip$followup_date3)/ddays(1))
eip$datediff4 <- as.numeric(interval(eip$enc_date, eip$followup_date4)/ddays(1))
eip$datediff5 <- as.numeric(interval(eip$enc_date, eip$followup_date5)/ddays(1))
eip$datediff6 <- as.numeric(interval(eip$enc_date, eip$followup_date6)/ddays(1))
eip$datediff7 <- as.numeric(interval(eip$enc_date, eip$followup_date7)/ddays(1))
eip$datediff8 <- as.numeric(interval(eip$enc_date, eip$followup_date8)/ddays(1))
eip$datediff9 <- as.numeric(interval(eip$enc_date, eip$followup_date9)/ddays(1))
eip$datediff10 <- as.numeric(interval(eip$enc_date, eip$followup_date10)/ddays(1))
eip$datediff11 <- as.numeric(interval(eip$enc_date, eip$followup_date11)/ddays(1))
eip$datediff12 <- as.numeric(interval(eip$enc_date, eip$followup_date12)/ddays(1))
eip$datediff13 <- as.numeric(interval(eip$enc_date, eip$followup_date13)/ddays(1))
eip$datediff14 <- as.numeric(interval(eip$enc_date, eip$followup_date14)/ddays(1))
eip$datediff15 <- as.numeric(interval(eip$enc_date, eip$followup_date15)/ddays(1))
eip$datediff16 <- as.numeric(interval(eip$enc_date, eip$followup_date16)/ddays(1))
eip$datediff17 <- as.numeric(interval(eip$enc_date, eip$followup_date17)/ddays(1))
eip$datediff18 <- as.numeric(interval(eip$enc_date, eip$followup_date18)/ddays(1))
eip$datediff19 <- as.numeric(interval(eip$enc_date, eip$followup_date19)/ddays(1))
eip$datediff20 <- as.numeric(interval(eip$enc_date, eip$followup_date20)/ddays(1))
eip$datediff21 <- as.numeric(interval(eip$enc_date, eip$followup_date21)/ddays(1))
eip$datediff22 <- as.numeric(interval(eip$enc_date, eip$followup_date22)/ddays(1))
eip$datediff23 <- as.numeric(interval(eip$enc_date, eip$followup_date23)/ddays(1))
eip$datediff24 <- as.numeric(interval(eip$enc_date, eip$followup_date24)/ddays(1))
eip$datediff25 <- as.numeric(interval(eip$enc_date, eip$followup_date25)/ddays(1))
eip$datediff26 <- as.numeric(interval(eip$enc_date, eip$followup_date26)/ddays(1))
eip$datediff27 <- as.numeric(interval(eip$enc_date, eip$followup_date27)/ddays(1))
eip$datediff28 <- as.numeric(interval(eip$enc_date, eip$followup_date28)/ddays(1))
eip$datediff29 <- as.numeric(interval(eip$enc_date, eip$followup_date29)/ddays(1))
eip$datediff30 <- as.numeric(interval(eip$enc_date, eip$followup_date30)/ddays(1))
eip$datediff31 <- as.numeric(interval(eip$enc_date, eip$followup_date31)/ddays(1))
eip$datediff32 <- as.numeric(interval(eip$enc_date, eip$followup_date32)/ddays(1))
eip$datediff33 <- as.numeric(interval(eip$enc_date, eip$followup_date33)/ddays(1))
eip$datediff34 <- as.numeric(interval(eip$enc_date, eip$followup_date34)/ddays(1))
eip$datediff35 <- as.numeric(interval(eip$enc_date, eip$followup_date35)/ddays(1))
eip$datediff36 <- as.numeric(interval(eip$enc_date, eip$followup_date36)/ddays(1))
eip$datediff37 <- as.numeric(interval(eip$enc_date, eip$followup_date37)/ddays(1))
eip$datediff38 <- as.numeric(interval(eip$enc_date, eip$followup_date38)/ddays(1))
eip$datediff39 <- as.numeric(interval(eip$enc_date, eip$followup_date39)/ddays(1))
eip$datediff40 <- as.numeric(interval(eip$enc_date, eip$followup_date40)/ddays(1))
eip$datediff41 <- as.numeric(interval(eip$enc_date, eip$followup_date41)/ddays(1))
eip$datediff42 <- as.numeric(interval(eip$enc_date, eip$followup_date42)/ddays(1))
eip$datediff43 <- as.numeric(interval(eip$enc_date, eip$followup_date43)/ddays(1))
eip$datediff44 <- as.numeric(interval(eip$enc_date, eip$followup_date44)/ddays(1))
eip$datediff45 <- as.numeric(interval(eip$enc_date, eip$followup_date45)/ddays(1))
eip$datediff46 <- as.numeric(interval(eip$enc_date, eip$followup_date46)/ddays(1))
eip$datediff47 <- as.numeric(interval(eip$enc_date, eip$followup_date47)/ddays(1))
eip$datediff48 <- as.numeric(interval(eip$enc_date, eip$followup_date48)/ddays(1))
eip$datediff49 <- as.numeric(interval(eip$enc_date, eip$followup_date49)/ddays(1))
eip$datediff50 <- as.numeric(interval(eip$enc_date, eip$followup_date50)/ddays(1))

```

```{r EHE, include=FALSE}

###############################################################################################################
########################################  Creating EHE Dataset  ########################################
###############################################################################################################

summary(eip$enc_date)
ehe <- eip[which(eip$enc_date >= '2024-08-01' & eip$enc_date <= '2025-05-31'), ]
summary(ehe$enc_date)


################################################  EHE Metrics  ################################################

table(ehe$ehe_calc)
ehe_tests <- ehe[which(ehe$ehe_calc == 1), ]
ehe_tests <- nrow(ehe_tests)
ehe_tests

table(ehe$ehe_calc, ehe$final_test_status_hiv)
ehe_positive <- ehe[which(ehe$ehe_calc == 1 & ehe$final_test_status_hiv == 1), ]
ehe_positive <- nrow(ehe_positive)
ehe_positive

table(ehe$ehe_calc, ehe$final_test_status_hiv, ehe$diagnosis_hiv)
ehe_new_positive <- ehe[which(ehe$ehe_calc == 1 & ehe$final_test_status_hiv == 1 & ehe$diagnosis_hiv == 1), ]
ehe_new_positive <- nrow(ehe_new_positive)
ehe_new_positive

ehe_new_positive_deliverable_percent <- percent(ehe_new_positive/3, accuracy = 0.1)
ehe_new_positive_deliverable_percent

ehe_positivity_rate <- percent(ehe_new_positive/ehe_tests, accuracy = 0.01)
ehe_positivity_rate


# Monthly EHE Testing
monthly_ehe_testing <- select(ehe, enc_date, ehe_calc)
monthly_ehe_testing <- monthly_ehe_testing[which(monthly_ehe_testing$ehe_calc == 1), ]
head(monthly_ehe_testing)
colnames(monthly_ehe_testing)[2] <- 'ehe_tests'
monthly_ehe_testing$ehe_tests[is.na(monthly_ehe_testing$ehe_tests)] <- 0
head(monthly_ehe_testing)

monthly_ehe_testing$Date <- as.Date(monthly_ehe_testing$enc_date, format="%d/%m/%Y")
head(monthly_ehe_testing)

monthly_ehe_tests <- aggregate(ehe_tests ~ as.yearmon(Date),
                               monthly_ehe_testing,
                               FUN = sum)
monthly_ehe_tests$Date <- as.Date(as.yearmon(monthly_ehe_tests$`as.yearmon(Date)`))
head(monthly_ehe_tests)
monthly_ehe_tests


# MSM

table(ehe$MSM, ehe$offer_outcome_risks)
ehe_msm_assessed <- ehe[which(ehe$offer_outcome_risks == 1 & ehe$MSM == 1), ]
ehe_msm_assessed <- nrow(ehe_msm_assessed)
ehe_msm_assessed

ehe_msm_assessed_deliverable <- 80
ehe_msm_assessed_deliverable_percent <- percent(ehe_msm_assessed/ehe_msm_assessed_deliverable, accuracy = 0.1)
ehe_msm_assessed_deliverable_percent



table(ehe$ehe_calc, ehe$MSM)
ehe_msm_tested <- ehe[which(ehe$ehe_calc == 1 & ehe$MSM == 1), ]
ehe_msm_tested <- nrow(ehe_msm_tested)
ehe_msm_tested

ehe_msm_tested_deliverable <- 30
ehe_msm_tested_deliverable_percent <- percent(ehe_msm_tested/ehe_msm_tested_deliverable, accuracy = 0.1)
ehe_msm_tested_deliverable_percent



table(ehe$ehe_calc, ehe$diagnosis_hiv, ehe$MSM)
ehe_msm_new_positive <- ehe[which(ehe$ehe_calc == 1 & ehe$MSM == 1 & ehe$diagnosis_hiv == 1), ]
ehe_msm_new_positive <- nrow(ehe_msm_new_positive)
ehe_msm_new_positive

ehe_msm_new_positive_deliverable <- 3
ehe_msm_new_positive_deliverable_percent <- percent(ehe_msm_new_positive/ehe_msm_new_positive_deliverable, accuracy = 0.1)
ehe_msm_new_positive_deliverable_percent



table(ehe$ehe_calc, ehe$enc_location, ehe$MSM)
ehe_msm_ucmc_test <- ehe[which(ehe$ehe_calc == 1 & ehe$MSM == 1 & ehe$enc_location == 5), ]
ehe_msm_ucmc_test <- nrow(ehe_msm_ucmc_test)
ehe_msm_ucmc_test

ehe_msm_ucmc_test_deliverable <- 5
ehe_msm_ucmc_test_deliverable_percent <- percent(ehe_msm_ucmc_test/ehe_msm_ucmc_test_deliverable, accuracy = 0.1)
ehe_msm_ucmc_test_deliverable_percent



table(ehe$ehe_calc, ehe$enc_location, ehe$MSM)
ehe_msm_wch_test <- ehe[which(ehe$ehe_calc == 1 & ehe$MSM == 1 &  ehe$enc_location == 1), ]
ehe_msm_wch_test <- nrow(ehe_msm_wch_test)
ehe_msm_wch_test

ehe_msm_wch_test_deliverable <- 5
ehe_msm_wch_test_deliverable_percent <- percent(ehe_msm_wch_test/ehe_msm_wch_test_deliverable, accuracy = 0.1)
ehe_msm_wch_test_deliverable_percent



table(ehe$ehe_calc, ehe$enc_location, ehe$MSM)
ehe_msm_comm_test <- ehe[which(ehe$ehe_calc == 1 & ehe$MSM == 1 & 
                                 (ehe$enc_location != 1 & ehe$enc_location != 5)), ]
ehe_msm_comm_test <- nrow(ehe_msm_comm_test)
ehe_msm_comm_test

ehe_msm_comm_test_deliverable <- 20
ehe_msm_comm_test_deliverable_percent <- percent(ehe_msm_comm_test/ehe_msm_comm_test_deliverable, accuracy = 0.1)
ehe_msm_comm_test_deliverable_percent



table(ehe$ehe_calc, ehe$MSM, ehe$Youth)
ehe_msm_youth_tested <- ehe[which(ehe$ehe_calc == 1 & ehe$MSM == 1 & ehe$Youth == 1), ]
ehe_msm_youth_tested <- nrow(ehe_msm_youth_tested)
ehe_msm_youth_tested

ehe_msm_youth_tested_deliverable <- 10
ehe_msm_youth_tested_deliverable_percent <- percent(ehe_msm_youth_tested/ehe_msm_youth_tested_deliverable, accuracy = 0.1)
ehe_msm_youth_tested_deliverable_percent



table(ehe$ehe_calc, ehe$MSM, ehe$IDU)
ehe_msm_idu_tested <- ehe[which(ehe$ehe_calc == 1 & ehe$MSM == 1 & ehe$IDU == 1), ]
ehe_msm_idu_tested <- nrow(ehe_msm_idu_tested)
ehe_msm_idu_tested

ehe_msm_idu_tested_deliverable <- 10
ehe_msm_idu_tested_deliverable_percent <- percent(ehe_msm_idu_tested/ehe_msm_idu_tested_deliverable, accuracy = 0.1)
ehe_msm_idu_tested_deliverable_percent



# HRHS

table(ehe$offer_outcome_risks, ehe$HRHS)
ehe_hrhs_assessed <- ehe[which(ehe$HRHS == 1 & ehe$offer_outcome_risks == 1), ]
ehe_hrhs_assessed <- nrow(ehe_hrhs_assessed)
ehe_hrhs_assessed

ehe_hrhs_assessed_deliverable <- 550
ehe_hrhs_assessed_deliverable_percent <- percent(ehe_hrhs_assessed/ehe_hrhs_assessed_deliverable, accuracy = 0.1)
ehe_hrhs_assessed_deliverable_percent



table(ehe$enc_location, ehe$HRHS)
ehe_hrhs_ucmc_assessed <- ehe[which(ehe$HRHS == 1 & ehe$offer_outcome_risks == 1 & ehe$enc_location == 5), ]
ehe_hrhs_ucmc_assessed <- nrow(ehe_hrhs_ucmc_assessed)
ehe_hrhs_ucmc_assessed

ehe_hrhs_ucmc_assessed_deliverable <- 400
ehe_hrhs_ucmc_assessed_deliverable_percent <- percent(ehe_hrhs_ucmc_assessed/ehe_hrhs_ucmc_assessed_deliverable, accuracy = 0.1)
ehe_hrhs_ucmc_assessed_deliverable_percent



table(ehe$enc_location, ehe$HRHS)
ehe_hrhs_wch_assessed <- ehe[which(ehe$HRHS == 1 & ehe$offer_outcome_risks == 1 & ehe$enc_location == 1), ]
ehe_hrhs_wch_assessed <- nrow(ehe_hrhs_wch_assessed)
ehe_hrhs_wch_assessed

ehe_hrhs_wch_assessed_deliverable <- 50
ehe_hrhs_wch_assessed_deliverable_percent <- percent(ehe_hrhs_wch_assessed/ehe_hrhs_wch_assessed_deliverable, accuracy = 0.1)
ehe_hrhs_wch_assessed_deliverable_percent



table(ehe$enc_location, ehe$HRHS)
ehe_hrhs_comm_assessed <- ehe[which(ehe$HRHS == 1 & ehe$offer_outcome_risks == 1 &
                                      (ehe$enc_location != 1 & ehe$enc_location != 5)), ]
ehe_hrhs_comm_assessed <- nrow(ehe_hrhs_comm_assessed)
ehe_hrhs_comm_assessed

ehe_hrhs_comm_assessed_deliverable <- 100
ehe_hrhs_comm_assessed_deliverable_percent <- percent(ehe_hrhs_comm_assessed/ehe_hrhs_comm_assessed_deliverable, accuracy = 0.1)
ehe_hrhs_comm_assessed_deliverable_percent



# Linkage to Care

table(ehe$plwha)
ehe_plwha <- ehe[which(ehe$plwha == 1), ]
dim(ehe_plwha)

ehe_plwha <- nrow(ehe_plwha)
ehe_plwha



table(ehe$ltc_services___1)
ehe$ehe_hiv_ltc[ehe$ltc_services___1 == 1] <- 1
table(ehe$ehe_hiv_ltc)

table(ehe$ehe_hiv_ltc)
ehe_hiv_ltc <- ehe[which(ehe$ehe_hiv_ltc == 1), ]
dim(ehe_hiv_ltc)
ehe_hiv_ltc <- nrow(ehe_hiv_ltc)
ehe_hiv_ltc

ehe_hiv_ltc_percent <- percent(ehe_hiv_ltc/ehe_plwha, accuracy = 0.1)
ehe_hiv_ltc_percent



# Ineligible HIV Linkage - Already Linked

table(ehe$ltc_hiv_declined_rsn___23)
table(ehe$ltc_hiv_prevented_rsn___16)
ehe$ehe_hiv_already_linked[ehe$ehe_hiv_ltc == 1 &
                             (ehe$ltc_hiv_declined_rsn___23 == 1 |
                                ehe$ltc_hiv_prevented_rsn___16 == 1)] <- 1
table(ehe$ehe_hiv_already_linked)

table(ehe$ehe_hiv_already_linked)
ehe_hiv_already_linked <- ehe[which(ehe$ehe_hiv_already_linked == 1), ]
dim(ehe_hiv_already_linked)
ehe_hiv_already_linked <- nrow(ehe_hiv_already_linked)
ehe_hiv_already_linked



# Ineligible HIV Linkage - Deceased

table(ehe$ltc_hiv_declined_rsn___35)
table(ehe$ltc_hiv_prevented_rsn___17)
ehe$ehe_hiv_deceased[ehe$ehe_hiv_ltc == 1 &
                       (ehe$ltc_hiv_declined_rsn___35 == 1 |
                          ehe$ltc_hiv_prevented_rsn___17 == 1)] <- 1
table(ehe$ehe_hiv_deceased)

table(ehe$ehe_hiv_deceased)
ehe_hiv_deceased <- ehe[which(ehe$ehe_hiv_deceased == 1), ]
dim(ehe_hiv_deceased)
ehe_hiv_deceased <- nrow(ehe_hiv_deceased)
ehe_hiv_deceased



# Ineligible HIV Linkage - Incarcerated

table(ehe$ltc_hiv_prevented_rsn___12)
ehe$ehe_hiv_incarcerated[ehe$ehe_hiv_ltc == 1 &
                           ehe$ltc_hiv_prevented_rsn___12 == 1] <- 1
table(ehe$ehe_hiv_incarcerated)

table(ehe$ehe_hiv_incarcerated)
ehe_hiv_incarcerated <- ehe[which(ehe$ehe_hiv_incarcerated == 1), ]
dim(ehe_hiv_incarcerated)
ehe_hiv_incarcerated <- nrow(ehe_hiv_incarcerated)
ehe_hiv_incarcerated



# Ineligible HIV Linkage - Inability to Contact

table(ehe$ltc_hiv_prevented_rsn___19)
ehe$ehe_hiv_inability_to_contact[ehe$ehe_hiv_ltc == 1 &
                                   ehe$ltc_hiv_prevented_rsn___19 == 1] <- 1
table(ehe$ehe_hiv_inability_to_contact)

table(ehe$ehe_hiv_inability_to_contact)
ehe_hiv_inability_to_contact <- ehe[which(ehe$ehe_hiv_inability_to_contact == 1), ]
dim(ehe_hiv_inability_to_contact)
ehe_hiv_inability_to_contact <- nrow(ehe_hiv_inability_to_contact)
ehe_hiv_inability_to_contact



# Ineligible HIV Linkage - Declined Linkage Service

table(ehe$ltc_hiv_final_ltc_status)
ehe$ehe_hiv_linkage_declined[(ehe$ehe_hiv_ltc == 1 &
                                ehe$ltc_hiv_final_ltc_status == 2) &
                               (is.na(ehe$ehe_hiv_already_linked) &
                                  is.na(ehe$ehe_hiv_deceased) &
                                  is.na(ehe$ehe_hiv_incarcerated) &
                                  is.na(ehe$ehe_hiv_inability_to_contact))] <- 1
table(ehe$ehe_hiv_linkage_declined)

table(ehe$ehe_hiv_linkage_declined)
ehe_hiv_linkage_declined <- ehe[which(ehe$ehe_hiv_linkage_declined == 1), ]
dim(ehe_hiv_linkage_declined)
ehe_hiv_linkage_declined <- nrow(ehe_hiv_linkage_declined)
ehe_hiv_linkage_declined




# Ineligible HIV Linkage - Linkage in Progress

table(ehe$ltc_hiv_prevented_rsn___18)
ehe$ehe_hiv_ongoing_linkage[ehe$ehe_hiv_ltc == 1 &
                              ehe$ltc_hiv_prevented_rsn___18 == 1] <- 1
table(ehe$ehe_hiv_ongoing_linkage)

table(ehe$ehe_hiv_ongoing_linkage)
ehe_hiv_ongoing_linkage <- ehe[which(ehe$ehe_hiv_ongoing_linkage == 1), ]
dim(ehe_hiv_ongoing_linkage)
ehe_hiv_ongoing_linkage <- nrow(ehe_hiv_ongoing_linkage)
ehe_hiv_ongoing_linkage



# HIV Ineligible Cases

ehe$ehe_hiv_ineligible_ltc[ehe$ehe_hiv_already_linked == 1 |
                             ehe$ehe_hiv_deceased == 1 |
                             ehe$ehe_hiv_incarcerated == 1 |
                             ehe$ehe_hiv_inability_to_contact == 1 |
                             ehe$ehe_hiv_linkage_declined == 1 |
                             ehe$ehe_hiv_ongoing_linkage == 1] <- 1
table(ehe$ehe_hiv_ineligible_ltc)

table(ehe$ehe_hiv_ineligible_ltc)
ehe_hiv_ineligible_ltc <- ehe[which(ehe$ehe_hiv_ineligible_ltc == 1), ]
dim(ehe_hiv_ineligible_ltc)
ehe_hiv_ineligible_ltc <- nrow(ehe_hiv_ineligible_ltc)
ehe_hiv_ineligible_ltc

ehe_hiv_ineligible_ltc_percent <- percent(ehe_hiv_ineligible_ltc/ehe_hiv_ltc, accuracy = 0.1)
ehe_hiv_ineligible_ltc_percent

ehe_hiv_already_linked_percent <- percent(ehe_hiv_already_linked/ehe_hiv_ineligible_ltc, accuracy = 0.1)
ehe_hiv_already_linked_percent

ehe_hiv_deceased_percent <- percent(ehe_hiv_deceased/ehe_hiv_ineligible_ltc, accuracy = 0.1)
ehe_hiv_deceased_percent

ehe_hiv_incarcerated_percent <- percent(ehe_hiv_incarcerated/ehe_hiv_ineligible_ltc, accuracy = 0.1)
ehe_hiv_incarcerated_percent

ehe_hiv_inability_to_contact_percent <- percent(ehe_hiv_inability_to_contact/ehe_hiv_ineligible_ltc, accuracy = 0.1)
ehe_hiv_inability_to_contact_percent

ehe_hiv_linkage_declined_percent <- percent(ehe_hiv_linkage_declined/ehe_hiv_ineligible_ltc, accuracy = 0.1)
ehe_hiv_linkage_declined_percent

ehe_hiv_ongoing_linkage_percent <- percent(ehe_hiv_ongoing_linkage/ehe_hiv_ineligible_ltc, accuracy = 0.1)
ehe_hiv_ongoing_linkage_percent



# HIV Eligibility to be Linked

ehe$ehe_hiv_eligible_ltc[ehe$ehe_hiv_ltc == 1 &
                           (is.na(ehe$ehe_hiv_already_linked) &
                              is.na(ehe$ehe_hiv_deceased) &
                              is.na(ehe$ehe_hiv_incarcerated) &
                              is.na(ehe$ehe_hiv_inability_to_contact) &
                              is.na(ehe$ehe_hiv_linkage_declined) &
                              is.na(ehe$ehe_hiv_ongoing_linkage))] <- 1
table(ehe$ehe_hiv_eligible_ltc)

table(ehe$ehe_hiv_eligible_ltc)
ehe_hiv_eligible_ltc <- ehe[which(ehe$ehe_hiv_eligible_ltc == 1), ]
dim(ehe_hiv_eligible_ltc)
ehe_hiv_eligible_ltc <- nrow(ehe_hiv_eligible_ltc)
ehe_hiv_eligible_ltc

ehe_hiv_eligible_ltc_percent <- percent(ehe_hiv_eligible_ltc/ehe_hiv_ltc, accuracy = 0.1)
ehe_hiv_eligible_ltc_percent


ehe_plwha_deliverable <- 60
ehe_plwha_deliverable_percent <- percent(ehe_hiv_eligible_ltc/ehe_plwha_deliverable, accuracy = 0.1)
ehe_plwha_deliverable_percent



table(ehe$ehe_hiv_eligible_ltc, ehe$diagnosis_hiv)
ehe$ehe_hiv_new_eligible_ltc[ehe$ehe_hiv_eligible_ltc == 1 &
                               ehe$diagnosis_hiv == 1] <- 1
table(ehe$ehe_hiv_new_eligible_ltc)

table(ehe$ehe_hiv_new_eligible_ltc)
ehe_hiv_new_eligible_ltc <- ehe[which(ehe$ehe_hiv_new_eligible_ltc == 1), ]
dim(ehe_hiv_new_eligible_ltc)
ehe_hiv_new_eligible_ltc <- nrow(ehe_hiv_new_eligible_ltc)
ehe_hiv_new_eligible_ltc

ehe_hiv_new_eligible_ltc_percent <- percent(ehe_hiv_new_eligible_ltc/ehe_hiv_eligible_ltc, accuracy = 0.1)
ehe_hiv_new_eligible_ltc_percent




table(ehe$ehe_hiv_eligible_ltc, ehe$diagnosis_hiv)
ehe$ehe_hiv_prev_eligible_ltc[ehe$ehe_hiv_eligible_ltc == 1 &
                                ehe$diagnosis_hiv == 2] <- 1
table(ehe$ehe_hiv_prev_eligible_ltc)

table(ehe$ehe_hiv_prev_eligible_ltc)
ehe_hiv_prev_eligible_ltc <- ehe[which(ehe$ehe_hiv_prev_eligible_ltc == 1), ]
dim(ehe_hiv_prev_eligible_ltc)
ehe_hiv_prev_eligible_ltc <- nrow(ehe_hiv_prev_eligible_ltc)
ehe_hiv_prev_eligible_ltc

ehe_hiv_prev_eligible_ltc_percent <- percent(ehe_hiv_prev_eligible_ltc/ehe_hiv_eligible_ltc, accuracy = 0.1)
ehe_hiv_prev_eligible_ltc_percent



table(ehe$ehe_hiv_eligible_ltc, ehe$diagnosis_hiv)
ehe$ehe_hiv_unk_eligible_ltc[(ehe$ehe_hiv_eligible_ltc == 1 &
                                (ehe$diagnosis_hiv == 3 |
                                   is.na(ehe$diagnosis_hiv)))] <- 1
table(ehe$ehe_hiv_unk_eligible_ltc)

table(ehe$ehe_hiv_unk_eligible_ltc)
ehe_hiv_unk_eligible_ltc <- ehe[which(ehe$ehe_hiv_unk_eligible_ltc == 1), ]
dim(ehe_hiv_unk_eligible_ltc)
ehe_hiv_unk_eligible_ltc <- nrow(ehe_hiv_unk_eligible_ltc)
ehe_hiv_unk_eligible_ltc

ehe_hiv_unk_eligible_ltc_percent <- percent(ehe_hiv_unk_eligible_ltc/ehe_hiv_eligible_ltc, accuracy = 0.1)
ehe_hiv_unk_eligible_ltc_percent



# HIV Open/Closed Cases

table(ehe$ltc_hiv_open_case_calc)
ehe$ehe_hiv_in_progress[ehe$ehe_hiv_eligible_ltc == 1 &
                          ehe$ltc_hiv_open_case_calc == 1] <- 1
table(ehe$ehe_hiv_in_progress)

table(ehe$ehe_hiv_in_progress)
ehe_hiv_in_progress <- ehe[which(ehe$ehe_hiv_in_progress == 1), ]
dim(ehe_hiv_in_progress)
ehe_hiv_in_progress <- nrow(ehe_hiv_in_progress)
ehe_hiv_in_progress

ehe_hiv_in_progress_percent <- percent(ehe_hiv_in_progress/ehe_hiv_eligible_ltc, accuracy = 0.1)
ehe_hiv_in_progress_percent



table(ehe$ehe_hiv_in_progress, ehe$diagnosis_hiv)
ehe$ehe_hiv_new_in_progress[ehe$ehe_hiv_in_progress == 1 &
                              ehe$diagnosis_hiv == 1] <- 1
table(ehe$ehe_hiv_new_in_progress)

table(ehe$ehe_hiv_new_in_progress)
ehe_hiv_new_in_progress <- ehe[which(ehe$ehe_hiv_new_in_progress == 1), ]
dim(ehe_hiv_new_in_progress)
ehe_hiv_new_in_progress <- nrow(ehe_hiv_new_in_progress)
ehe_hiv_new_in_progress

ehe_hiv_new_in_progress_percent <- percent(ehe_hiv_new_in_progress/ehe_hiv_new_eligible_ltc, accuracy = 0.1)
ehe_hiv_new_in_progress_percent



table(ehe$ehe_hiv_in_progress, ehe$diagnosis_hiv)
ehe$ehe_hiv_prev_in_progress[ehe$ehe_hiv_in_progress == 1 &
                               ehe$diagnosis_hiv == 2] <- 1
table(ehe$ehe_hiv_prev_in_progress)

table(ehe$ehe_hiv_prev_in_progress)
ehe_hiv_prev_in_progress <- ehe[which(ehe$ehe_hiv_prev_in_progress == 1), ]
dim(ehe_hiv_prev_in_progress)
ehe_hiv_prev_in_progress <- nrow(ehe_hiv_prev_in_progress)
ehe_hiv_prev_in_progress

ehe_hiv_prev_in_progress_percent <- percent(ehe_hiv_prev_in_progress/ehe_hiv_prev_eligible_ltc, accuracy = 0.1)
ehe_hiv_prev_in_progress_percent



table(ehe$ehe_hiv_in_progress, ehe$diagnosis_hiv)
ehe$ehe_hiv_unk_in_progress[ehe$ehe_hiv_in_progress == 1 &
                              (ehe$diagnosis_hiv == 3 |
                                 is.na(ehe$diagnosis_hiv))] <- 1
table(ehe$ehe_hiv_unk_in_progress)

table(ehe$ehe_hiv_unk_in_progress)
ehe_hiv_unk_in_progress <- ehe[which(ehe$ehe_hiv_unk_in_progress == 1), ]
dim(ehe_hiv_unk_in_progress)
ehe_hiv_unk_in_progress <- nrow(ehe_hiv_unk_in_progress)
ehe_hiv_unk_in_progress

ehe_hiv_unk_in_progress_percent <- percent(ehe_hiv_unk_in_progress/ehe_hiv_unk_eligible_ltc, accuracy = 0.1)
ehe_hiv_unk_in_progress_percent



table(ehe$ehe_hiv_eligible_ltc, ehe$ehe_hiv_in_progress)
ehe$ehe_hiv_closed_case[ehe$ehe_hiv_eligible_ltc == 1 &
                          is.na(ehe$ehe_hiv_in_progress)] <- 1
table(ehe$ehe_hiv_closed_case)

table(ehe$ehe_hiv_closed_case)
ehe_hiv_closed_case <- ehe[which(ehe$ehe_hiv_closed_case == 1), ]
dim(ehe_hiv_closed_case)
ehe_hiv_closed_case <- nrow(ehe_hiv_closed_case)
ehe_hiv_closed_case

ehe_hiv_closed_case_percent <- percent(ehe_hiv_closed_case/ehe_hiv_eligible_ltc, accuracy = 0.1)
ehe_hiv_closed_case_percent




table(ehe$ehe_hiv_in_progress)
ehe$ehe_hiv_ltc_days_open <- difftime(Sys.Date(), ehe$enc_date, units="days")
table(ehe$ehe_hiv_ltc_days_open)
ehe$ehe_hiv_in_progress_90days[ehe$ehe_hiv_in_progress == 1 &
                                 (ehe$ehe_hiv_ltc_days_open > 90)] <- 1
table(ehe$ehe_hiv_in_progress_90days)

table(ehe$ehe_hiv_in_progress_90days)
ehe_hiv_in_progress_90days <- ehe[which(ehe$ehe_hiv_in_progress_90days == 1), ]
dim(ehe_hiv_in_progress_90days)
ehe_hiv_in_progress_90days <- nrow(ehe_hiv_in_progress_90days)
ehe_hiv_in_progress_90days

ehe_hiv_in_progress_90days_percent <- percent(ehe_hiv_in_progress_90days/ehe_hiv_in_progress, accuracy = 0.1)
ehe_hiv_in_progress_90days_percent




# HIV Cases Linked to Care

table(ehe$ehe_hiv_closed_case, ehe$ltc_hiv_final_ltc_status)
ehe$ehe_hiv_linked[ehe$ehe_hiv_closed_case == 1 &
                     ehe$ltc_hiv_final_ltc_status == 1] <- 1
table(ehe$ehe_hiv_linked)

table(ehe$ehe_hiv_linked)
ehe_hiv_linked <- ehe[which(ehe$ehe_hiv_linked == 1), ]
dim(ehe_hiv_linked)
ehe_hiv_linked <- nrow(ehe_hiv_linked)
ehe_hiv_linked

ehe_hiv_linked_gauge <- (ehe_hiv_linked/ehe_hiv_eligible_ltc)*100
ehe_hiv_linked_gauge
ehe_hiv_linked_percent <- percent(ehe_hiv_linked/ehe_hiv_eligible_ltc, accuracy = 0.1)
ehe_hiv_linked_percent



table(ehe$diagnosis_hiv, ehe$ehe_hiv_eligible_ltc)
table(ehe$ehe_hiv_linked, ehe$diagnosis_hiv)
ehe$ehe_hiv_new_linked[ehe$ehe_hiv_linked == 1 &
                         ehe$diagnosis_hiv == 1] <- 1
table(ehe$ehe_hiv_new_linked)

table(ehe$ehe_hiv_new_linked)
ehe_hiv_new_linked <- ehe[which(ehe$ehe_hiv_new_linked == 1), ]
dim(ehe_hiv_new_linked)
ehe_hiv_new_linked <- nrow(ehe_hiv_new_linked)
ehe_hiv_new_linked

ehe_hiv_new_linked_percent <- percent(ehe_hiv_new_linked/ehe_hiv_new_eligible_ltc, accuracy = 0.1)
ehe_hiv_new_linked_percent



table(ehe$diagnosis_hiv, ehe$ehe_hiv_eligible_ltc)
table(ehe$ehe_hiv_linked, ehe$diagnosis_hiv)
ehe$ehe_hiv_prev_linked[ehe$ehe_hiv_linked == 1 &
                          ehe$diagnosis_hiv == 2] <- 1
table(ehe$ehe_hiv_prev_linked)

table(ehe$ehe_hiv_prev_linked)
ehe_hiv_prev_linked <- ehe[which(ehe$ehe_hiv_prev_linked == 1), ]
dim(ehe_hiv_prev_linked)
ehe_hiv_prev_linked <- nrow(ehe_hiv_prev_linked)
ehe_hiv_prev_linked

ehe_hiv_prev_linked_percent <- percent(ehe_hiv_prev_linked/ehe_hiv_prev_eligible_ltc, accuracy = 0.1)
ehe_hiv_prev_linked_percent




ehe$ehe_hiv_not_linked[ehe$ehe_hiv_eligible_ltc == 1 & is.na(ehe$ehe_hiv_in_progress) & is.na(ehe$ehe_hiv_linked)] <- 1
table(ehe$ehe_hiv_not_linked)

table(ehe$ehe_hiv_not_linked)
ehe_hiv_not_linked <- ehe[which(ehe$ehe_hiv_not_linked == 1), ]
dim(ehe_hiv_not_linked)
ehe_hiv_not_linked <- nrow(ehe_hiv_not_linked)
ehe_hiv_not_linked

ehe_hiv_not_linked_percent <- percent(ehe_hiv_not_linked/ehe_hiv_closed_case, accuracy = 0.1)
ehe_hiv_not_linked_percent



table(ehe$ehe_hiv_not_linked, ehe$diagnosis_hiv)
ehe$ehe_hiv_new_not_linked[ehe$ehe_hiv_not_linked == 1 &
                             ehe$diagnosis_hiv == 1] <- 1
table(ehe$ehe_hiv_new_not_linked)

table(ehe$ehe_hiv_new_not_linked)
ehe_hiv_new_not_linked <- ehe[which(ehe$ehe_hiv_new_not_linked == 1), ]
dim(ehe_hiv_new_not_linked)
ehe_hiv_new_not_linked <- nrow(ehe_hiv_new_not_linked)
ehe_hiv_new_not_linked

ehe_hiv_new_not_linked_percent <- percent(ehe_hiv_new_not_linked/ehe_hiv_new_eligible_ltc, accuracy = 0.1)
ehe_hiv_new_not_linked_percent



table(ehe$ehe_hiv_not_linked, ehe$diagnosis_hiv)
ehe$ehe_hiv_prev_not_linked[ehe$ehe_hiv_not_linked == 1 &
                              ehe$diagnosis_hiv == 2] <- 1
table(ehe$ehe_hiv_prev_not_linked)

table(ehe$ehe_hiv_prev_not_linked)
ehe_hiv_prev_not_linked <- ehe[which(ehe$ehe_hiv_prev_not_linked == 1), ]
dim(ehe_hiv_prev_not_linked)
ehe_hiv_prev_not_linked <- nrow(ehe_hiv_prev_not_linked)
ehe_hiv_prev_not_linked

ehe_hiv_prev_not_linked_percent <- percent(ehe_hiv_prev_not_linked/ehe_hiv_prev_eligible_ltc, accuracy = 0.1)
ehe_hiv_prev_not_linked_percent




# HIV Reasons Not Linked to Care

ehe$ehe_hiv_not_linked_med_staff[(ehe$ehe_hiv_closed_case == 1 & is.na(ehe$ehe_hiv_linked)) &
                                   (ehe$ltc_hiv_prevented_rsn___1 == 1 |
                                      ehe$ltc_hiv_prevented_rsn___2 == 1 |
                                      ehe$ltc_hiv_prevented_rsn___11 == 1)] <- 1
table(ehe$ehe_hiv_not_linked_med_staff)

table(ehe$ehe_hiv_not_linked_med_staff)
ehe_hiv_not_linked_med_staff <- ehe[which(ehe$ehe_hiv_not_linked_med_staff == 1), ]
dim(ehe_hiv_not_linked_med_staff)
ehe_hiv_not_linked_med_staff <- nrow(ehe_hiv_not_linked_med_staff)
ehe_hiv_not_linked_med_staff

ehe_hiv_not_linked_med_staff_percent <- percent(ehe_hiv_not_linked_med_staff/ehe_hiv_not_linked, accuracy = 0.1)
ehe_hiv_not_linked_med_staff_percent



ehe$ehe_hiv_not_linked_family[(ehe$ehe_hiv_closed_case == 1 & is.na(ehe$ehe_hiv_linked)) &
                                (ehe$ltc_hiv_prevented_rsn___3 == 1)] <- 1
table(ehe$ehe_hiv_not_linked_family)

table(ehe$ehe_hiv_not_linked_family)
ehe_hiv_not_linked_family <- ehe[which(ehe$ehe_hiv_not_linked_family == 1), ]
dim(ehe_hiv_not_linked_family)
ehe_hiv_not_linked_family <- nrow(ehe_hiv_not_linked_family)
ehe_hiv_not_linked_family

ehe_hiv_not_linked_family_percent <- percent(ehe_hiv_not_linked_family/ehe_hiv_not_linked, accuracy = 0.1)
ehe_hiv_not_linked_family_percent



ehe$ehe_hiv_not_linked_not_talking[(ehe$ehe_hiv_closed_case == 1 & is.na(ehe$ehe_hiv_linked)) &
                                     (ehe$ltc_hiv_prevented_rsn___4 == 1)] <- 1
table(ehe$ehe_hiv_not_linked_not_talking)

table(ehe$ehe_hiv_not_linked_not_talking)
ehe_hiv_not_linked_not_talking <- ehe[which(ehe$ehe_hiv_not_linked_not_talking == 1), ]
dim(ehe_hiv_not_linked_not_talking)
ehe_hiv_not_linked_not_talking <- nrow(ehe_hiv_not_linked_not_talking)
ehe_hiv_not_linked_not_talking

ehe_hiv_not_linked_not_talking_percent <- percent(ehe_hiv_not_linked_not_talking/ehe_hiv_not_linked, accuracy = 0.1)
ehe_hiv_not_linked_not_talking_percent



ehe$ehe_hiv_not_linked_safety[(ehe$ehe_hiv_closed_case == 1 & is.na(ehe$ehe_hiv_linked)) &
                                (ehe$ltc_hiv_prevented_rsn___5 == 1)] <- 1
table(ehe$ehe_hiv_not_linked_safety)

table(ehe$ehe_hiv_not_linked_safety)
ehe_hiv_not_linked_safety <- ehe[which(ehe$ehe_hiv_not_linked_safety == 1), ]
dim(ehe_hiv_not_linked_safety)
ehe_hiv_not_linked_safety <- nrow(ehe_hiv_not_linked_safety)
ehe_hiv_not_linked_safety

ehe_hiv_not_linked_safety_percent <- percent(ehe_hiv_not_linked_safety/ehe_hiv_not_linked, accuracy = 0.1)
ehe_hiv_not_linked_safety_percent



ehe$ehe_hiv_not_linked_medical[(ehe$ehe_hiv_closed_case == 1 & is.na(ehe$ehe_hiv_linked)) &
                                 (ehe$ltc_hiv_prevented_rsn___6 == 1 |
                                    ehe$ltc_hiv_prevented_rsn___8)] <- 1
table(ehe$ehe_hiv_not_linked_medical)

table(ehe$ehe_hiv_not_linked_medical)
ehe_hiv_not_linked_medical <- ehe[which(ehe$ehe_hiv_not_linked_medical == 1), ]
dim(ehe_hiv_not_linked_medical)
ehe_hiv_not_linked_medical <- nrow(ehe_hiv_not_linked_medical)
ehe_hiv_not_linked_medical

ehe_hiv_not_linked_medical_percent <- percent(ehe_hiv_not_linked_medical/ehe_hiv_not_linked, accuracy = 0.1)
ehe_hiv_not_linked_medical_percent



ehe$ehe_hiv_not_linked_contact[(ehe$ehe_hiv_closed_case == 1 & is.na(ehe$ehe_hiv_linked)) &
                                 (ehe$ltc_hiv_prevented_rsn___20 == 1)] <- 1
table(ehe$ehe_hiv_not_linked_contact)

table(ehe$ehe_hiv_not_linked_contact)
ehe_hiv_not_linked_contact <- ehe[which(ehe$ehe_hiv_not_linked_contact == 1), ]
dim(ehe_hiv_not_linked_contact)
ehe_hiv_not_linked_contact <- nrow(ehe_hiv_not_linked_contact)
ehe_hiv_not_linked_contact

ehe_hiv_not_linked_contact_percent <- percent(ehe_hiv_not_linked_contact/ehe_hiv_not_linked, accuracy = 0.1)
ehe_hiv_not_linked_contact_percent



ehe$ehe_hiv_not_linked_language[(ehe$ehe_hiv_closed_case == 1 & is.na(ehe$ehe_hiv_linked)) &
                                  (ehe$ltc_hiv_prevented_rsn___9 == 1)] <- 1
table(ehe$ehe_hiv_not_linked_language)

table(ehe$ehe_hiv_not_linked_language)
ehe_hiv_not_linked_language <- ehe[which(ehe$ehe_hiv_not_linked_language == 1), ]
dim(ehe_hiv_not_linked_language)
ehe_hiv_not_linked_language <- nrow(ehe_hiv_not_linked_language)
ehe_hiv_not_linked_language

ehe_hiv_not_linked_language_percent <- percent(ehe_hiv_not_linked_language/ehe_hiv_not_linked, accuracy = 0.1)
ehe_hiv_not_linked_language_percent



ehe$ehe_hiv_not_linked_other[(ehe$ehe_hiv_closed_case == 1 & is.na(ehe$ehe_hiv_linked)) &
                               (ehe$ltc_hiv_prevented_rsn___0 == 1)] <- 1
table(ehe$ehe_hiv_not_linked_other)

table(ehe$ehe_hiv_not_linked_other)
ehe_hiv_not_linked_other <- ehe[which(ehe$ehe_hiv_not_linked_other == 1), ]
dim(ehe_hiv_not_linked_other)
ehe_hiv_not_linked_other <- nrow(ehe_hiv_not_linked_other)
ehe_hiv_not_linked_other

ehe_hiv_not_linked_other_percent <- percent(ehe_hiv_not_linked_other/ehe_hiv_not_linked, accuracy = 0.1)
ehe_hiv_not_linked_other_percent

```


The Ending the HIV Epidemic (EHE) testing program...(plan to provide an overall description and background for EHE).


```{r, echo = FALSE}

ehe_testing_tbl <- data.frame(matrix(ncol = 2, nrow = 0))
colnames(ehe_testing_tbl) <- c('', 'EHE')
ehe_testing_tbl[nrow(ehe_testing_tbl) + 1,] <- list('Number of Tests', ehe_tests)
ehe_testing_tbl[nrow(ehe_testing_tbl) + 1,] <- list('Positives', ehe_positive)
ehe_testing_tbl[nrow(ehe_testing_tbl) + 1,] <- list('New Positives', ehe_new_positive)
ehe_testing_tbl[nrow(ehe_testing_tbl) + 1,] <- list('Positivity Rate', ehe_positivity_rate)
ehe_testing_tbl %>%
  kbl(table.attr = 'data-quarto-disable-processing="true"') %>%
  kable_paper(bootstrap_options = "striped", full_width = F) %>%
  kable_styling(full_width = F, font_size = 16)

```


EHE testing is reported on a monthly basis. The report sent to the Ohio Department of Health (ODH) each month consists of the total number of EHE-funded tests, and how many individuals were newly diagnosed with HIV from testing. The ODH report is divided into two different files, one comprising the aggregate data for testing by site, and the positivity data report by site. The aggregate data is further divided into several tabs, each depending on the site where the test occurred. The aggregate data report is essentially divided by the two ED testing sites (UCMC and WCH), the community sites (termed non-traditional testing venues), and the syringe exchange sites. It also consists of the demographic and population data for those tested at those sites. The positivity report identifies the total number of positive tests done at each site per month. The table to the right shows the total number of EHE tests and the overall positivity rate. The figure below shows the monthly EHE testing numbers.

[It is important to note that there may be a few duplicated tests due to the transition to the new year, and records being in both the 2023 and 2024 databases if an open linkage case from 2023 is actively being worked in the 2024 database. Continuous review and data cleaning occurs until all cases from the prior year are closed.]{style="color: green;"}



```{r, echo = FALSE, fig.align='center'}

# EHE Monthly Testing
monthly_ehe_tests <- monthly_ehe_tests[order(monthly_ehe_tests$Date), ]
monthly_ehe_tests_plot <- plot_ly(data = monthly_ehe_tests,
                                  x = ~Date,
                                  y = ~ehe_tests,
                                  type = 'bar',
                                  name = 'EHE Tests',
                                  text = ~ehe_tests,
                                  textposition = 'auto',
                                  marker = list(color = 'darkgreen')) %>%
  layout(yaxis = list(title = 'EHE Tests'), barmode = 'stack',
         xaxis = list(tickangle = 45))
monthly_ehe_tests_plot

```
<br>


## EHE Deliverables Summary

The deliverables highlighted below are the numbers that were noted on the 2024 EHE Workplan as what our program would accomplish within the year of funding awarded. The data shown below covers EHE program deliverables starting **August 1st, 2024 through May 31st, 2025**. A summary table of the EHE deliverables, the number of each deliverable achieved, and the percent of the deliverables met are shown below:


```{r, echo = FALSE, fig.align='center', fig.asp=0.50}

# EHE Deliverable Summary Table
ehe_deliverables_tbl <- data.frame(matrix(ncol = 4, nrow = 0))
colnames(ehe_deliverables_tbl) <- c('EHE Deliverable', 'Achieved', 'Goal', '%')
ehe_deliverables_tbl[nrow(ehe_deliverables_tbl) + 1,] <- list('PLWHA not in care', ehe_hiv_eligible_ltc, ehe_plwha_deliverable, ehe_plwha_deliverable_percent)
ehe_deliverables_tbl[nrow(ehe_deliverables_tbl) + 1,] <- list('% PLWHA linked', ehe_hiv_linked_percent, '80%', '')
ehe_deliverables_tbl[nrow(ehe_deliverables_tbl) + 1,] <- list('MSM assessed', ehe_msm_assessed, ehe_msm_assessed_deliverable, ehe_msm_assessed_deliverable_percent)
ehe_deliverables_tbl[nrow(ehe_deliverables_tbl) + 1,] <- list('MSM tested', ehe_msm_tested, ehe_msm_tested_deliverable, ehe_msm_tested_deliverable_percent)
ehe_deliverables_tbl[nrow(ehe_deliverables_tbl) + 1,] <- list('MSM tested at UCMC', ehe_msm_ucmc_test, ehe_msm_ucmc_test_deliverable, ehe_msm_ucmc_test_deliverable_percent)
ehe_deliverables_tbl[nrow(ehe_deliverables_tbl) + 1,] <- list('MSM tested at WCH', ehe_msm_wch_test, ehe_msm_wch_test_deliverable, ehe_msm_wch_test_deliverable_percent)
ehe_deliverables_tbl[nrow(ehe_deliverables_tbl) + 1,] <- list('MSM tested in Community', ehe_msm_comm_test, ehe_msm_comm_test_deliverable, ehe_msm_comm_test_deliverable_percent)
ehe_deliverables_tbl[nrow(ehe_deliverables_tbl) + 1,] <- list('MSM/Youth tested', ehe_msm_youth_tested, ehe_msm_youth_tested_deliverable, ehe_msm_youth_tested_deliverable_percent)
ehe_deliverables_tbl[nrow(ehe_deliverables_tbl) + 1,] <- list('MSM/IDU tested', ehe_msm_idu_tested, ehe_msm_idu_tested_deliverable, ehe_msm_idu_tested_deliverable_percent)
ehe_deliverables_tbl[nrow(ehe_deliverables_tbl) + 1,] <- list('MSM new positive', ehe_msm_new_positive, ehe_msm_new_positive_deliverable, ehe_msm_new_positive_deliverable_percent)
ehe_deliverables_tbl[nrow(ehe_deliverables_tbl) + 1,] <- list('HRHS assessed', ehe_hrhs_assessed, ehe_hrhs_assessed_deliverable, ehe_hrhs_assessed_deliverable_percent)
ehe_deliverables_tbl[nrow(ehe_deliverables_tbl) + 1,] <- list('HRHS assessed at UC', ehe_hrhs_ucmc_assessed, ehe_hrhs_ucmc_assessed_deliverable, ehe_hrhs_ucmc_assessed_deliverable_percent)
ehe_deliverables_tbl[nrow(ehe_deliverables_tbl) + 1,] <- list('HRHS assessed at WCH', ehe_hrhs_wch_assessed, ehe_hrhs_wch_assessed_deliverable, ehe_hrhs_wch_assessed_deliverable_percent)
ehe_deliverables_tbl[nrow(ehe_deliverables_tbl) + 1,] <- list('HRHS assessed in Community', ehe_hrhs_comm_assessed, ehe_hrhs_comm_assessed_deliverable, ehe_hrhs_comm_assessed_deliverable_percent)
ehe_deliverables_tbl %>%
  kbl(align = 'lccc', table.attr = 'data-quarto-disable-processing="true"') %>%
  kable_paper(bootstrap_options = "striped", full_width = F) %>%
  pack_rows("PLWHA", 1, 2, label_row_css = "background-color: #F0F0F0") %>%
  pack_rows("MSM", 3, 10, label_row_css = "background-color: #F0F0F0") %>%
  pack_rows("HRHS", 11, 14, label_row_css = "background-color: #F0F0F0") %>%
  add_indent(c(2,5,6,7,8,9,12,13,14)) %>%
  kable_styling(full_width = F, font_size = 12)

```

<br>

## PLWHA

The first impact objective encompasses population-based objectives centered around people living with HIV/AIDS (PLWHA) that are identified not in care. This objective has EIP staff identify those either newly diagnosed or previously diagnosed and determine whether they are out of care and require linkage to care services. This objective is inclusive of those who are women of color (WOC), youth (18-29 years old), and injection drug users (IDU). The statement for the actual deliverables promised for this objective is noted below:

- *By May 31, 2025, EIP will identify 60 PLWHA not in care (newly and previously diagnosed) and provide Prevention with Positives and Linkage to Care services such that 80% are engaged in HIV medical care as prioritized by RFP workplan table. Of note, this number PLWHA includes newly diagnosed positives found by ED staff testing that, while apart from the core CTR, would not be possible absent the existence of the CTR (as detailed in Program Narrative).*

From this statement, we specifically state deliverables for how many PLWHA who are out of care that will be identified by our program, and successfully link 80% of those individuals to care. Additional metrics were noted in this section, but no specific details on the numbers for those metrics were provided. Therefore, we stated we would monitor and report those as needed. These metrics are shown in the table under 'Additional Metrics'.

PLWHA are identified in several different ways within the program, including: **self-report of a positive test on assessment of prior HIV testing history, reason for offering an HIV test was due to a prior HIV positive result, declining an HIV test due to prior positive result, a final positive result through HIV testing, or having an HIV linkage case open with a new or previous HIV status**. EIP staff are meant to identify all PLWHA encountered through the program, and further follow-up and discussion are meant to determine who is currently out of care. The deliverable for all PLWHA identified out of care are those that are “eligible” to be linked to care. They are considered “ineligible” based on the following criteria: they are already linked to care, deceased, currently incarcerated, inaccurate contact information, or they declined EIP linkage services.

The total number of HIV linkage to care (LTC) cases initiated for PLWHA during this time period is **`r ehe_hiv_ltc`**, with the total number of "eligible" LTC cases for PLWHA being `r ehe_hiv_eligible_ltc` (*`r ehe_hiv_eligible_ltc_percent` of all HIV LTC cases initiated, `r ehe_hiv_eligible_ltc`/`r ehe_hiv_ltc`*). [**Therefore, EIP has identified `r ehe_hiv_eligible_ltc` PLWHA for the EHE deliverable, which is `r ehe_plwha_deliverable_percent` of the total promise of `r ehe_plwha_deliverable`**]{style="color: darkgreen;"}. The total number of these "eligible" HIV LTC cases that have been successfully linked to care is `r ehe_hiv_linked`, which is [**`r ehe_hiv_linked_percent`**]{style="color: darkgreen;"} of those "eligible" (*`r ehe_hiv_linked`/`r ehe_hiv_eligible_ltc`*).


```{r, echo=FALSE, fig.asp=0.50}

# EHE PLWHA Deliverable
ehe_plwha_gauge <- plot_ly(
  domain = list(x = c(0, 0.5), y = c(0, 1)),
  value = ehe_hiv_eligible_ltc,
  title = list(text = "PLWHA Identified Not in Care", font = list(size = 24)),
  type = "indicator",
  mode = "gauge+number",
  gauge = list(
    axis =list(range = list(0, 60)),
    bar = list(color = "darkgreen"),
    bgcolor = "white",
    borderwidth = 2,
    bordercolor = "gray")) 
ehe_plwha_gauge <- ehe_plwha_gauge %>%
  layout(margin = list(l=100,r=150))
config(ehe_plwha_gauge, displayModeBar = FALSE)

```

```{r, echo=FALSE, fig.asp=0.50}

# EHE Linkage Rate Deliverable
ehe_linkage_gauge <- plot_ly(
  domain = list(x = c(0, 0.5), y = c(0, 1)),
  value = ehe_hiv_linked_gauge,
  number = list(suffix = "%"),
  title = list(text = "% PLWHA Linked to Care", font = list(size = 24)),
  type = "indicator",
  mode = "gauge+number",
  gauge = list(
    axis =list(range = list(0, 100)),
    bar = list(color = "darkgreen"),
    bgcolor = "white",
    borderwidth = 2,
    bordercolor = "gray",
    threshold = list(
      line = list(color = "red", width = 4),
      thickness = 0.75,
      value = 80))) 
ehe_linkage_gauge <- ehe_linkage_gauge %>%
  layout(margin = list(l=100,r=150))
config(ehe_linkage_gauge, displayModeBar = FALSE)

```


We do not separate linkage numbers based on the HIV testing program (CTR/EHE), so these numbers are pulled the same as the numbers that are reported for the linkage deliverables shown for the CTR program. If there are differences in the documented numbers for linkage between these two testing programs, it is likely due to the timeframe used for each program deliverable. The HIV Linkage flow diagram for the EHE deliverable timeframe is shown below to provide an understanding of where the linkage numbers are coming from.


```{r, echo=FALSE, warning=FALSE}

grid_data <- tibble(x= 1:100, y= 1:100)

grid_data %>% 
  ggplot(aes(x, y)) +
  scale_x_continuous(minor_breaks = seq(10, 100, 10)) +
  scale_y_continuous(minor_breaks = seq(10, 100, 10)) +
  theme_linedraw() ->
  grid


grid +
  # HIV Linkage Cases
  geom_rect(xmin = 0, xmax = 22, ymin = 90, ymax = 100, color = 'black',
            fill = 'lightblue', size = 0.25, size = 0.25) +
  annotate('text', x = 10.5, y = 97, label = 'HIV Linkage Cases', size = 2) +
  geom_rect(xmin = 0, xmax = 22, ymin = 90, ymax = 100, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 10.5, y = 93, label = ehe_hiv_ltc, size = 2, color = 'blue') +
  
  # Ineligible for Linkage
  geom_rect(xmin = 41, xmax = 63, ymin = 75, ymax = 85, color = 'gray',
            fill = 'white', size = 0.25) +
  annotate('text', x = 52.5, y = 82, label = 'Ineligible for Linkage', size = 2) +
  geom_rect(xmin = 41, xmax = 63, ymin = 75, ymax = 85, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 51.5, y = 78, label = ehe_hiv_ineligible_ltc, size = 2, color = 'blue') +
  annotate('text', x = 60, y = 78, label = ehe_hiv_ineligible_ltc_percent, size = 2, color = 'steelblue') +
  
  
  # Reasons Ineligible for Linkage
  geom_rect(xmin = 83, xmax = 100, ymin = 75, ymax = 85, color = NA,
            fill = 'white', size = 0.25) +
  annotate('text', x = 87, y = 85, label = 'Already Linked', size = 2) +
  annotate('text', x = 87, y = 82, label = '        Deceased', size = 2) +
  annotate('text', x = 87, y = 79, label = '    Incarcerated', size = 2) +
  annotate('text', x = 87, y = 76, label = 'Inability to Contact', size = 2) +
  annotate('text', x = 87, y = 73, label = '          Declined', size = 2) +
  annotate('text', x = 87, y = 70, label = 'Ongoing linkage ', size = 2) +
  geom_rect(xmin = 41, xmax = 63, ymin = 75, ymax = 85, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 94, y = 85, label = ehe_hiv_already_linked, size = 2, color = 'blue') +
  annotate('text', x = 98, y = 85, label = ehe_hiv_already_linked_percent, size = 2, color = 'steelblue') +
  annotate('text', x = 94, y = 82, label = ehe_hiv_deceased, size = 2, color = 'blue') +
  annotate('text', x = 98, y = 82, label = ehe_hiv_deceased_percent, size = 2, color = 'steelblue') +
  annotate('text', x = 94, y = 79, label = ehe_hiv_incarcerated, size = 2, color = 'blue') +
  annotate('text', x = 98, y = 79, label = ehe_hiv_incarcerated_percent, size = 2, color = 'steelblue') +
  annotate('text', x = 94, y = 76, label = ehe_hiv_inability_to_contact, size = 2, color = 'blue') +
  annotate('text', x = 98, y = 76, label = ehe_hiv_inability_to_contact_percent, size = 2, color = 'steelblue') +
  annotate('text', x = 94, y = 73, label = ehe_hiv_linkage_declined, size = 2, color = 'blue') +
  annotate('text', x = 98, y = 73, label = ehe_hiv_linkage_declined_percent, size = 2, color = 'steelblue') +
  annotate('text', x = 94, y = 70, label = ehe_hiv_ongoing_linkage, size = 2, color = 'blue') +
  annotate('text', x = 98, y = 70, label = ehe_hiv_ongoing_linkage_percent, size = 2, color = 'steelblue') +
  
  
  # Eligible for Linkage
  geom_rect(xmin = 0, xmax = 22, ymin = 60, ymax = 70, color = 'black',
            fill = 'lightblue', size = 0.25, size = 0.25) +
  annotate('text', x = 10.5, y = 67, label = 'Eligible for Linkage', size = 2) +
  geom_rect(xmin = 0, xmax = 22, ymin = 60, ymax = 70, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 10.5, y = 63, label = ehe_hiv_eligible_ltc, size = 2, color = 'blue') +
  annotate('text', x = 19, y = 63, label = ehe_hiv_eligible_ltc_percent, size = 2, color = 'steelblue') +
  
  
  # New vs. Prev vs. Unk Eligibility
  geom_rect(xmin = 25, xmax = 35, ymin = 60, ymax = 70, color = NA,
            fill = 'white', size = 0.25, size = 0.25) +
  annotate('text', x = 26, y = 69, label = 'New Dx:', size = 2) +
  annotate('text', x = 26, y = 65, label = 'Prev Dx:', size = 2) +
  annotate('text', x = 26, y = 61, label = 'Unk Dx:', size = 2) +
  geom_rect(xmin = 0, xmax = 22, ymin = 60, ymax = 70, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 30, y = 69, label = ehe_hiv_new_eligible_ltc, size = 2, color = 'blue') +
  annotate('text', x = 34, y = 69, label = ehe_hiv_new_eligible_ltc_percent, size = 2, color = 'steelblue') +
  annotate('text', x = 30, y = 65, label = ehe_hiv_prev_eligible_ltc, size = 2, color = 'blue') +
  annotate('text', x = 34, y = 65, label = ehe_hiv_prev_eligible_ltc_percent, size = 2, color = 'steelblue') +
  annotate('text', x = 30, y = 61, label = ehe_hiv_unk_eligible_ltc, size = 2, color = 'blue') +
  annotate('text', x = 34, y = 61, label = ehe_hiv_unk_eligible_ltc_percent, size = 2, color = 'steelblue') +
  
  
  # In Progress
  geom_rect(xmin = 41, xmax = 63, ymin = 45, ymax = 55, color = 'gray',
            fill = 'white', size = 0.25) +
  annotate('text', x = 50.5, y = 52, label = 'In Progress', size = 2) +
  geom_rect(xmin = 41, xmax = 63, ymin = 45, ymax = 55, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 51.5, y = 48, label = ehe_hiv_in_progress, size = 2, color = 'blue') +
  annotate('text', x = 60, y = 48, label = ehe_hiv_in_progress_percent, size = 2, color = 'steelblue') +
  
  
  # In Progress over 90 days
  geom_rect(xmin = 41, xmax = 63, ymin = 37, ymax = 44, color = NA,
            fill = 'white', size = 0.25, size = 0.25) +
  annotate('text', x = 52, y = 42, label = '>90 days:', size = 2) +
  geom_rect(xmin = 41, xmax = 63, ymin = 37, ymax = 44, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 56, y = 42, label = ehe_hiv_in_progress_90days, size = 2, color = 'blue') +
  annotate('text', x = 60, y = 42, label = ehe_hiv_in_progress_90days_percent, size = 2, color = 'steelblue') +
  
  
  # New vs. Prev vs. Unk In Progress
  geom_rect(xmin = 66, xmax = 88, ymin = 45, ymax = 55, color = NA,
            fill = 'white', size = 0.25, size = 0.25) +
  annotate('text', x = 67, y = 54, label = 'New Dx:', size = 2) +
  annotate('text', x = 67, y = 50, label = 'Prev Dx:', size = 2) +
  annotate('text', x = 67, y = 46, label = 'Unk Dx:', size = 2) +
  geom_rect(xmin = 66, xmax = 88, ymin = 45, ymax = 55, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 71, y = 54, label = ehe_hiv_new_in_progress, size = 2, color = 'blue') +
  annotate('text', x = 75, y = 54, label = ehe_hiv_new_in_progress_percent, size = 2, color = 'steelblue') +
  annotate('text', x = 71, y = 50, label = ehe_hiv_prev_in_progress, size = 2, color = 'blue') +
  annotate('text', x = 75, y = 50, label = ehe_hiv_prev_in_progress_percent, size = 2, color = 'steelblue') +
  annotate('text', x = 71, y = 46, label = ehe_hiv_unk_in_progress, size = 2, color = 'blue') +
  annotate('text', x = 75, y = 46, label = ehe_hiv_unk_in_progress_percent, size = 2, color = 'steelblue') +
  
  
  # Closed Cases
  geom_rect(xmin = 0, xmax = 22, ymin = 30, ymax = 40, color = 'black',
            fill = 'lightblue', size = 0.25, size = 0.25) +
  annotate('text', x = 10.5, y = 37, label = 'Closed Cases', size = 2) +
  geom_rect(xmin = 0, xmax = 22, ymin = 30, ymax = 40, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 10.5, y = 33, label = ehe_hiv_closed_case, size = 2, color = 'blue') +
  annotate('text', x = 19, y = 33, label = ehe_hiv_closed_case_percent, size = 2, color = 'steelblue') +
  
  
  # Not Linked
  geom_rect(xmin = 41, xmax = 63, ymin = 15, ymax = 25, color = 'gray',
            fill = 'white', size = 0.25) +
  annotate('text', x = 50.5, y = 22, label = 'Not Linked', size = 2) +
  geom_rect(xmin = 41, xmax = 63, ymin = 15, ymax = 25, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 51.5, y = 18, label = ehe_hiv_not_linked, size = 2, color = 'blue') +
  annotate('text', x = 60, y = 18, label = ehe_hiv_not_linked_percent, size = 2, color = 'steelblue') +
  
  
  # New vs. Prev Not Linked
  geom_rect(xmin = 41, xmax = 63, ymin = 7, ymax = 14, color = NA,
            fill = 'white', size = 0.25, size = 0.25) +
  annotate('text', x = 52, y = 12, label = 'New Dx:', size = 2) +
  annotate('text', x = 52, y = 8, label = 'Prev Dx:', size = 2) +
  geom_rect(xmin = 41, xmax = 63, ymin = 7, ymax = 14, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 56, y = 12, label = ehe_hiv_new_not_linked, size = 2, color = 'blue') +
  annotate('text', x = 60, y = 12, label = ehe_hiv_new_not_linked_percent, size = 2, color = 'steelblue') +
  annotate('text', x = 56, y = 8, label = ehe_hiv_prev_not_linked, size = 2, color = 'blue') +
  annotate('text', x = 60, y = 8, label = ehe_hiv_prev_not_linked_percent, size = 2, color = 'steelblue') +
  
  
  # Reasons Not Linked
  geom_rect(xmin = 83, xmax = 100, ymin = 0, ymax = 30, color = NA,
            fill = 'white', size = 0.25) +
  annotate('text', x = 87, y = 26, label = 'Med Staff interferes    ', size = 2) +
  annotate('text', x = 87, y = 23, label = '  Family interferes', size = 2) +
  annotate('text', x = 87, y = 20, label = '    Refuses to talk', size = 2) +
  annotate('text', x = 87, y = 17, label = '    Personal safety', size = 2) +
  annotate('text', x = 87, y = 14, label = '    Medical course', size = 2) +
  annotate('text', x = 87, y = 11, label = 'Unable to contact', size = 2) +
  annotate('text', x = 87, y = 8, label = ' Language barrier', size = 2) +
  annotate('text', x = 87, y = 5, label = '                   Other', size = 2) +
  geom_rect(xmin = 41, xmax = 63, ymin = 0, ymax = 30, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 94, y = 26, label = ehe_hiv_not_linked_med_staff, size = 2, color = 'blue') +
  annotate('text', x = 98, y = 26, label = ehe_hiv_not_linked_med_staff_percent, size = 2, color = 'steelblue') +
  annotate('text', x = 94, y = 23, label = ehe_hiv_not_linked_family, size = 2, color = 'blue') +
  annotate('text', x = 98, y = 23, label = ehe_hiv_not_linked_family_percent, size = 2, color = 'steelblue') +
  annotate('text', x = 94, y = 20, label = ehe_hiv_not_linked_not_talking, size = 2, color = 'blue') +
  annotate('text', x = 98, y = 20, label = ehe_hiv_not_linked_not_talking_percent, size = 2, color = 'steelblue') +
  annotate('text', x = 94, y = 17, label = ehe_hiv_not_linked_safety, size = 2, color = 'blue') +
  annotate('text', x = 98, y = 17, label = ehe_hiv_not_linked_safety_percent, size = 2, color = 'steelblue') +
  annotate('text', x = 94, y = 14, label = ehe_hiv_not_linked_medical, size = 2, color = 'blue') +
  annotate('text', x = 98, y = 14, label = ehe_hiv_not_linked_medical_percent, size = 2, color = 'steelblue') +
  annotate('text', x = 94, y = 11, label = ehe_hiv_not_linked_contact, size = 2, color = 'blue') +
  annotate('text', x = 98, y = 11, label = ehe_hiv_not_linked_contact_percent, size = 2, color = 'steelblue') +
  annotate('text', x = 94, y = 8, label = ehe_hiv_not_linked_language, size = 2, color = 'blue') +
  annotate('text', x = 98, y = 8, label = ehe_hiv_not_linked_language_percent, size = 2, color = 'steelblue') +
  annotate('text', x = 94, y = 5, label = ehe_hiv_not_linked_other, size = 2, color = 'blue') +
  annotate('text', x = 98, y = 5, label = ehe_hiv_not_linked_other_percent, size = 2, color = 'steelblue') +
  
  
  # Linked to Care
  geom_rect(xmin = 0, xmax = 22, ymin = 0, ymax = 10, color = 'black',
            fill = 'lightblue', size = 0.25, size = 0.25) +
  annotate('text', x = 10.5, y = 7, label = 'Linked to Care', size = 2) +
  geom_rect(xmin = 0, xmax = 22, ymin = 0, ymax = 10, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 10.5, y = 3, label = ehe_hiv_linked, size = 2, color = 'blue') +
  annotate('text', x = 19, y = 3, label = ehe_hiv_linked_percent, size = 2, color = 'steelblue') +
  
  
  # New vs. Prev Linked to Care
  geom_rect(xmin = 25, xmax = 35, ymin = 0, ymax = 10, color = NA,
            fill = 'white', size = 0.25, size = 0.25) +
  annotate('text', x = 26, y = 7, label = 'New Dx:', size = 2) +
  annotate('text', x = 26, y = 3, label = 'Prev Dx:', size = 2) +
  geom_rect(xmin = 0, xmax = 22, ymin = 0, ymax = 10, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 30, y = 7, label = ehe_hiv_new_linked, size = 2, color = 'blue') +
  annotate('text', x = 34, y = 7, label = ehe_hiv_new_linked_percent, size = 2, color = 'steelblue') +
  annotate('text', x = 30, y = 3, label = ehe_hiv_prev_linked, size = 2, color = 'blue') +
  annotate('text', x = 34, y = 3, label = ehe_hiv_prev_linked_percent, size = 2, color = 'steelblue') +
  
  
  # Down Arrow 1
  geom_segment(
    x = 10.5, xend = 10.5, y = 90, yend = 70, 
    size = 0.15, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(2,"mm"), type = "closed")) +
  
  # Down Arrow 2
  geom_segment(
    x = 10.5, xend = 10.5, y = 60, yend = 40, 
    size = 0.15, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(2,"mm"), type = "closed")) +
  
  # Down Arrow 3
  geom_segment(
    x = 10.5, xend = 10.5, y = 30, yend = 10, 
    size = 0.15, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(2,"mm"), type = "closed")) +
  
  # Right Arrow 1
  geom_segment(
    x = 10.5, xend = 41, y = 80, yend = 80, 
    size = 0.05, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(1,"mm"), type = "closed"), color = 'darkgray') +
  
  # Right Arrow 2
  geom_segment(
    x = 10.5, xend = 41, y = 50, yend = 50, 
    size = 0.05, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(1,"mm"), type = "closed"), color = 'darkgray') +
  
  # Right Arrow 3
  geom_segment(
    x = 10.5, xend = 41, y = 20, yend = 20, 
    size = 0.05, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(1,"mm"), type = "closed"), color = 'darkgray') +
  
  # Right Line 1
  geom_segment(
    x = 63, xend = 81, y = 80, yend = 80, 
    size = 0.15, linejoin = "mitre", lineend = "butt", linetype = "dotted") +
  
  # Right Line 2
  geom_segment(
    x = 63, xend = 80, y = 20, yend = 20, 
    size = 0.15, linejoin = "mitre", lineend = "butt", linetype = "dotted")->
  grid

grid + theme_void()

```
<br>


## MSM

There were additional deliverables made for population-based objectives, and the first focuses on those who identify as men who have sex with men (MSM). Individuals are only identified as a part of this population group if they complete the necessary portions on the EIP assessment. The statement for the actual deliverables promised for this objective is noted below:

- *By May 31, 2025, EIP will identify 80 MSM for risk-assessment and prevention intervention including client-centered risk reduction counseling and PrEP education/referral. EIP will provide HIV testing to 30 MSM, inclusive of the following (5 UCMC site, 5 WCH site, 20 community/outpatient sites; 10 Youth (18-29), and 10 IDU). EIP will identify 3 HIV(+) MSM for the PLWHA program (Workplan Form 4, Part 1). Of note, this does not include MSM PLWHA who are either previously diagnosed or those newly diagnosed by usual ED staff apart from CTR.*

From this statement, we specifically state deliverables for how many MSM will be assessed for risk and/or need, and how many MSM will be tested using EHE-funded tests. Additionally, EIP states a specific number of tests at each site (UCMC, WCH, community sites). Additional metrics were noted in this section, but no specific details on the numbers for those metrics were provided. Therefore, we stated we would monitor and report those as needed. These metrics are shown in the table in the next section.

For those individuals who identify as a male, they are determined to be a MSM if they meet at least one of the following criteria: *their sexual orientation is homosexual or bisexual, they report sex with a male or a transgender male within the past year, or they are a PLWHA and their reported risk was MSM*. [**The total number of individuals who are MSM that have been assessed during this time period is `r ehe_msm_assessed`, which is `r ehe_msm_assessed_deliverable_percent` of the total promise of `r ehe_msm_assessed_deliverable`**]{style="color: darkgreen;"}.


```{r, echo = FALSE, fig.asp=0.50}

# EHE MSM Assessed Deliverable
ehe_msm_assessed_gauge <- plot_ly(
  domain = list(x = c(0, 0.5), y = c(0, 1)),
  value = ehe_msm_assessed,
  title = list(text = "MSM EHE Assessed", font = list(size = 24)),
  type = "indicator",
  mode = "gauge+number",
  gauge = list(
    axis =list(range = list(0, 80)),
    bar = list(color = "darkgreen"),
    bgcolor = "white",
    borderwidth = 2,
    bordercolor = "gray")) 
ehe_msm_assessed_gauge <- ehe_msm_assessed_gauge %>%
  layout(margin = list(l=100,r=150))
config(ehe_msm_assessed_gauge, displayModeBar = FALSE)

```


[**The total number of individuals who are MSM that have been tested through the EHE program is `r ehe_msm_tested`, which is `r ehe_msm_tested_deliverable_percent` of the total promise of `r ehe_msm_tested_deliverable`**]{style="color: darkgreen;"}. In addition to the total number of tests, there were deliverables for the location where those tests were conducted. For the University of Cincinnati Medical Center (UCMC), this includes only those EHE tests that were conducted within the emergency department (UCMC ED). [**There were a total number of `r ehe_msm_ucmc_test` EHE tests that were conducted at UCMC, which is `r ehe_msm_ucmc_test_deliverable_percent` of the total promise of `r ehe_msm_ucmc_test_deliverable`**]{style="color: darkgreen;"}. For West Chester Hospital (WCH), this includes only those EHE tests that were conducted within the emergency department (WCH ED). [**There were a total number of `r ehe_msm_wch_test` EHE tests that were conducted at WCH, which is `r ehe_msm_wch_test_deliverable_percent` of the total promise of `r ehe_msm_wch_test_deliverable`**]{style="color: darkgreen;"}. For the community-based tests, this includes all tests that were conducted anywhere EIP operates that does not include one of the EDs (UCMC or WCH). [**There were a total number of `r ehe_msm_comm_test` EHE tests that were conducted in the community, which is `r ehe_msm_comm_test_deliverable_percent` of the total promise of `r ehe_msm_comm_test_deliverable`**]{style="color: darkgreen;"}.


```{r echo=FALSE, fig.asp=0.50}

# EHE MSM Tested Deliverable
ehe_msm_tested_gauge <- plot_ly(
  domain = list(x = c(0, 0.5), y = c(0, 1)),
  value = ehe_msm_tested,
  title = list(text = "MSM EHE Tested", font = list(size = 24)),
  type = "indicator",
  mode = "gauge+number",
  gauge = list(
    axis =list(range = list(0, 30)),
    bar = list(color = "darkgreen"),
    bgcolor = "white",
    borderwidth = 2,
    bordercolor = "gray")) 
ehe_msm_tested_gauge <- ehe_msm_tested_gauge %>%
  layout(margin = list(l=100,r=150))
config(ehe_msm_tested_gauge, displayModeBar = FALSE)

```


```{r echo=FALSE, fig.asp=0.45}

# EHE MSM Tested by Site Deliverables
ehe_msm_tested_site_bullet <- plot_ly() %>%
  add_trace(type = "indicator",
            mode = "number+gauge",
            value = ehe_msm_ucmc_test,
            domain = list(x = c(0.20, 0.65), y = c(0.08, 0.3)),
            title =list(text = "<b>UCMC</b><br><span style='color: gray; font-size:0.6em'>MSM Tested Deliverable: 5</span>"),
            gauge = list(shape = "bullet",
                         axis = list(range = c(0, 20)),
                         threshold = list(line = list(color = "red", width = 2),
                                          thickness = 0.75,
                                          value = 5),
                         bar = list(color = "darkgreen"))) %>%
  add_trace(type = "indicator",
            mode = "number+gauge",
            value = ehe_msm_wch_test,
            domain = list(x = c(0.20, 0.65), y = c(0.4, 0.6)),
            title = list(text = "<b>WCH</b><br><span style='color: gray; font-size:0.6em'>MSM Tested Deliverable: 5</span>"),
            gauge = list(shape = "bullet",
                         axis = list(range = list(0, 20)),
                         threshold = list(line = list(color = "red", width = 2),
                                          thickness = 0.75,
                                          value = 5),
                         bar = list(color = "darkgreen"))) %>%
  add_trace(type =  "indicator",
            mode = "number+gauge",
            value = ehe_msm_comm_test,
            domain = list(x = c(0.20, 0.65), y = c(0.7, 0.9)),
            title = list(text = "<b>Community</b><br><span style='color: gray; font-size:0.6em'>MSM Tested Deliverable: 20</span>"),
            gauge = list(shape = "bullet",
                         axis = list(range = list(0, 20)),
                         threshold = list(line = list(color = "red", width = 2),
                                          thickness = 0.75,
                                          value = 20),
                         bar = list(color = "darkgreen")))
config(ehe_msm_tested_site_bullet, displayModeBar = FALSE)

```


While we do not separate the linkage data between the various testing programs, we can identify which testing programs identify new positive HIV diagnoses. According to the EHE workplan, EIP has promised to identify a certain number of individuals who are newly diagnosed for HIV. [**There were a total number of `r ehe_msm_new_positive` EHE tests that resulted in a new positive diagnosis for the individual tested, which is `r ehe_msm_new_positive_deliverable_percent` of the total promise of `r ehe_msm_new_positive_deliverable`**]{style="color: darkgreen;"}. This number of new positive diagnoses are only those that were tested through the EHE program, and this only considers *new* positive diagnoses, not those that were tested and later determined to be an individual known to be positive.


```{r, echo = FALSE, fig.asp=0.50}

# EHE MSM New Positive Deliverable
ehe_msm_positive_gauge <- plot_ly(
  domain = list(x = c(0, 0.5), y = c(0, 1)),
  value = ehe_msm_new_positive,
  title = list(text = "MSM EHE New Positive", font = list(size = 24)),
  type = "indicator",
  mode = "gauge+number",
  gauge = list(
    axis =list(range = list(0, 3)),
    bar = list(color = "darkgreen"),
    bgcolor = "white",
    borderwidth = 2,
    bordercolor = "gray")) 
ehe_msm_positive_gauge <- ehe_msm_positive_gauge %>%
  layout(margin = list(l=100,r=150))
config(ehe_msm_positive_gauge, displayModeBar = FALSE)

```


Finally, the EHE program addresses particular population groups for testing. Within the population of MSM, we additionally have deliverables for youth and IDU. For those that are considered in the youth population, EHE defines those between the age of 18-19 years old. However, EIP often encounters individuals younger than the age of 18, so the definition used here are those below the age of 29. [**There were a total number of `r ehe_msm_youth_tested` EHE tests where the individual was both MSM/Youth, which is `r ehe_msm_youth_tested_deliverable_percent` of the total promise of `r ehe_msm_youth_tested_deliverable`**]{style="color: darkgreen;"}. For those that are considered in the IDU population, the individual needs to complete the necessary section within the EIP assessment. We define those who endorse injection drug use behavior ever in their lifetime on the NIDA-Modified ASSIST, or those who are HIV positive and their risk was injection drug use as a part of the IDU population. [**There were a total number of `r ehe_msm_idu_tested` EHE tests where the individual was both MSM/IDU, which is `r ehe_msm_idu_tested_deliverable_percent` of the total promise of `r ehe_msm_idu_tested_deliverable`**]{style="color: darkgreen;"}.


```{r echo=FALSE, fig.asp=0.50}

# MSM Youth Tested Deliverable
ehe_msm_youth_tested_gauge <- plot_ly(
  domain = list(x = c(0, 0.5), y = c(0, 1)),
  value = ehe_msm_youth_tested,
  title = list(text = "MSM/Youth EHE Tested", font = list(size = 24)),
  type = "indicator",
  mode = "gauge+number",
  gauge = list(
    axis =list(range = list(0, 10)),
    bar = list(color = "darkgreen"),
    bgcolor = "white",
    borderwidth = 2,
    bordercolor = "gray")) 
ehe_msm_youth_tested_gauge <- ehe_msm_youth_tested_gauge %>%
  layout(margin = list(l=100,r=150))
config(ehe_msm_youth_tested_gauge, displayModeBar = FALSE)

```


```{r echo=FALSE, fig.asp=0.50}

# MSM IDU Tested Deliverable
ehe_msm_idu_tested_gauge <- plot_ly(
  domain = list(x = c(0, 0.5), y = c(0, 1)),
  value = ehe_msm_idu_tested,
  title = list(text = "MSM/IDU EHE Tested", font = list(size = 24)),
  type = "indicator",
  mode = "gauge+number",
  gauge = list(
    axis =list(range = list(0, 10)),
    bar = list(color = "darkgreen"),
    bgcolor = "white",
    borderwidth = 2,
    bordercolor = "gray")) 
ehe_msm_idu_tested_gauge <- ehe_msm_idu_tested_gauge %>%
  layout(margin = list(l=100,r=150))
config(ehe_msm_idu_tested_gauge, displayModeBar = FALSE)

```


## HRHS

There were additional deliverables made for population-based objectives, and the second focuses on those who identify as heterosexual that are at high risk for contracting HIV by endorsing high-risk heterosexual sex (HRHS) behaviors. Individuals are only identified as a part of this population group if they complete the necessary portions on the EIP assessment. The statement for the actual deliverables promised for this objective is noted below:

- *By May 31, 2025, UC EIP will identify 550 HRHS for risk-assessment and prevention intervention including 400 UCMC site, 50 WCH site, and 100 community/outpatient sites).*

From this statement, we specifically state deliverables for how many HRHS will be assessed for risk and/or need, and state a specific number of assessments at each site (UCMC, WCH, community sites). Additional metrics were noted in this section, but no specific details on the numbers for those metrics were provided. Therefore, we stated we would monitor and report those as needed. These metrics are shown in the table in the next section.

For those individuals who identify as a heterosexual (men who have sex with women, or women who have sex with men), they are determined to be HRHS if they meet at least one of the following criteria: *heterosexual women that have unprotected sex with men or MSM, heterosexual men/women that have sex with an IDU, an HIV positive partner, a STD positive partner, more than three partners, or heterosexual men/women that exchange money/drugs for sex*.

[**The total number of individuals who are HRHS that have been assessed during this time period is `r ehe_hrhs_assessed`, which is `r ehe_hrhs_assessed_deliverable_percent` of the total promise of `r ehe_hrhs_assessed_deliverable`**]{style="color: darkgreen;"}. In addition to the total number of assessments, there were deliverables for the location where those assessments were conducted. For UCMC, this includes only those assessments that were accompanied by an EHE test that were conducted within the emergency department (UCMC ED). [**There were a total number of `r ehe_hrhs_ucmc_assessed` EHE HRHS assessments that were conducted at UCMC, which is `r ehe_hrhs_ucmc_assessed_deliverable_percent` of the total promise of `r ehe_hrhs_ucmc_assessed_deliverable`**]{style="color: darkgreen;"}. For WCH, this includes only those assessments that were accompanied by an EHE test that were conducted within the emergency department (WCH ED). [**There were a total number of `r ehe_hrhs_wch_assessed` EHE HRHS assessments that were conducted at WCH, which is `r ehe_hrhs_wch_assessed_deliverable_percent` of the total promise of `r ehe_hrhs_wch_assessed_deliverable`**]{style="color: darkgreen;"}. For the community-based assessments, this includes only those assessments that were accompanied by an EHE test that were conducted anywhere EIP operates that does not include one of the EDs (UCMC or WCH). [**There were a total number of `r ehe_hrhs_comm_assessed` EHE HRHS assessments that were conducted in the community, which is `r ehe_hrhs_comm_assessed_deliverable_percent` of the total promise of `r ehe_hrhs_comm_assessed_deliverable`**]{style="color: darkgreen;"}.


```{r echo=FALSE, fig.asp=0.50}

# EHE HRHS Assessed Deliverable
ehe_hrhs_assessed_gauge <- plot_ly(
  domain = list(x = c(0, 0.5), y = c(0, 1)),
  value = ehe_hrhs_assessed,
  title = list(text = "HRHS EHE Assessed", font = list(size = 24)),
  type = "indicator",
  mode = "gauge+number",
  gauge = list(
    axis =list(range = list(0, 550)),
    bar = list(color = "darkgreen"),
    bgcolor = "white",
    borderwidth = 2,
    bordercolor = "gray")) 
ehe_hrhs_assessed_gauge <- ehe_hrhs_assessed_gauge %>%
  layout(margin = list(l=100,r=150))
config(ehe_hrhs_assessed_gauge, displayModeBar = FALSE)

```


```{r echo=FALSE, fig.asp=0.45}

# EHE HRHS Assessed by Site Deliverables
ehe_hrhs_site_bullet <- plot_ly() %>%
  add_trace(type = "indicator",
            mode = "number+gauge",
            value = ehe_hrhs_ucmc_assessed,
            domain = list(x = c(0.22, 0.65), y = c(0.08, 0.3)),
            title =list(text = "<b>UCMC</b><br><span style='color: gray; font-size:0.5em'>HRHS Assessed Deliverable: 400</span>"),
            gauge = list(shape = "bullet",
                         axis = list(range = c(0, 350)),
                         threshold = list(line = list(color = "red", width = 2),
                                          thickness = 0.75,
                                          value = 350),
                         bar = list(color = "darkgreen"))) %>%
  add_trace(type = "indicator",
            mode = "number+gauge",
            value = ehe_hrhs_wch_assessed,
            domain = list(x = c(0.22, 0.65), y = c(0.4, 0.6)),
            title = list(text = "<b>WCH</b><br><span style='color: gray; font-size:0.5em'>HRHS Assessed Deliverable: 50</span>"),
            gauge = list(shape = "bullet",
                         axis = list(range = list(0, 350)),
                         threshold = list(line = list(color = "red", width = 2),
                                          thickness = 0.75,
                                          value = 50),
                         bar = list(color = "darkgreen"))) %>%
  add_trace(type =  "indicator",
            mode = "number+gauge",
            value = ehe_hrhs_comm_assessed,
            domain = list(x = c(0.22, 0.65), y = c(0.7, 0.9)),
            title = list(text = "<b>Community</b><br><span style='color: gray; font-size:0.5em'>HRHS Assessed Deliverable: 100</span>"),
            gauge = list(shape = "bullet",
                         axis = list(range = list(0, 350)),
                         threshold = list(line = list(color = "red", width = 2),
                                          thickness = 0.75,
                                          value = 50),
                         bar = list(color = "darkgreen")))
config(ehe_hrhs_site_bullet, displayModeBar = FALSE)

```


## Additional EHE Metrics

Additional metrics still to code for:

- #/% of PLWHA assessed
- #/% of PLWHA tested for HCV
- Number of MSM approached
- #/% MSM tested for HCV
- #/% MSM linked for HCV
- #/% HRHS approached
- #/% HRHS HIV+



