---
title: "EIP Population"
description: |
  The purpose of this page is to show the demographic population data for those individuals that EIP has worked with for various clinical purposes. This page shows the entire EIP popluation data, and the population data for individuals seen at specific sites is shown on those pages listed under the Sites tab.
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=F}
rm(list=ls(all=T))

library(dplyr)
library(tidyverse)
library(lubridate)
library(plotly)
library(ggplot2)
library(reactable)
library(htmltools)
library(lubridate)
library(hrbrthemes)
library(gt)
library(janitor)
library(scales)
library(apyramid)


#######################################################################################################
#########################################  EIP Database Data  #########################################
#######################################################################################################

eip <- read.csv('M:/EIP Data/EIP Database/REDCap Ver 5.0/EIP Database Data 20230620_1336.csv')
dim(eip)

# Person-level data is only visit_001_arm_1, use to match to encounters

table(eip$redcap_event_name)
person <- eip[which(eip$redcap_event_name == 'visit_001_arm_1'), ]
dim(person)

person <- select(person, record_id, mrn, dob, 
                 race___1, race___2, race___3, race___4, race___5, race___6, ethnicity,
                 sex_raised, sex_selfdefined, insurance, address_county,
                 address_zip_code)
dim(person)

eip <- select(eip, -mrn, -dob, 
              -race___1, -race___2, -race___3, -race___4, -race___5, 
              -race___6, -ethnicity,
              -sex_raised, -sex_selfdefined, -insurance, -address_county,
              -address_zip_code)

# Merge person dataset with full eip dataset

dim(eip)
dim(person)
eip <- merge(eip, person, by='record_id', all.x=T)
dim(eip)
eip <- distinct(eip)
dim(eip)


# Formatting variables

summary(eip$enc_date)
eip$enc_date <- as.Date(eip$enc_date, format='%m/%d/%Y')
summary(eip$enc_date)

summary(eip$dob)
eip$dob <- as.Date(eip$dob, format='%m/%d/%Y')
summary(eip$dob)


table(eip$race___1)
White <- eip[which(eip$race___1 == '1'), ]
dim(White)
White <- select(White, record_id)
White$White <- 1
table(White$White)
White <- distinct(White)
dim(White)
head(White)

table(eip$race___2)
Black <- eip[which(eip$race___2 == '1'), ]
dim(Black)
Black <- select(Black, record_id)
Black$Black <- 1
table(Black$Black)
Black <- distinct(Black)
dim(Black)
head(Black)

table(eip$race___3)
Asian <- eip[which(eip$race___3 == '1'), ]
dim(Asian)
Asian <- select(Asian, record_id)
Asian$Asian <- 1
table(Asian$Asian)
Asian <- distinct(Asian)
dim(Asian)
head(Asian)

table(eip$race___4)
AmIn <- eip[which(eip$race___4 == '1'), ]
dim(AmIn)
AmIn <- select(AmIn, record_id)
AmIn$AmIn <- 1
table(AmIn$AmIn)
AmIn <- distinct(AmIn)
dim(AmIn)
head(AmIn)

table(eip$race___5)
RaceOther <- eip[which(eip$race___5 == '1'), ]
dim(RaceOther)
RaceOther <- select(RaceOther, record_id)
RaceOther$RaceOther <- 1
table(RaceOther$RaceOther)
RaceOther <- distinct(RaceOther)
dim(RaceOther)
head(RaceOther)

table(eip$race___6)
RaceUnk <- eip[which(eip$race___6 == '1'), ]
dim(RaceUnk)
RaceUnk <- select(RaceUnk, record_id)
RaceUnk$RaceUnk <- 1
table(RaceUnk$RaceUnk)
RaceUnk <- distinct(RaceUnk)
dim(RaceUnk)
head(RaceUnk)

table(eip$ethnicity)
RaceHisp <- eip[which(eip$ethnicity == 1), ]
dim(RaceHisp)
RaceHisp <- select(RaceHisp, record_id)
RaceHisp$RaceHisp <- 1
table(RaceHisp$RaceHisp)
RaceHisp <- distinct(RaceHisp)
dim(RaceHisp)
head(RaceHisp)


race <- select(eip, record_id)
race <- distinct(race)
dim(race)


dim(race)
race <- merge(race, White, by = 'record_id', all.x = T)
race <- merge(race, Black, by = 'record_id', all.x = T)
race <- merge(race, Asian, by = 'record_id', all.x = T)
race <- merge(race, AmIn, by = 'record_id', all.x = T)
race <- merge(race, RaceOther, by = 'record_id', all.x = T)
race <- merge(race, RaceUnk, by = 'record_id', all.x = T)
race <- merge(race, RaceHisp, by = 'record_id', all.x = T)
dim(race)
head(race)

race$White[is.na(race$White)] <- 0
race$Black[is.na(race$Black)] <- 0
race$Asian[is.na(race$Asian)] <- 0
race$AmIn[is.na(race$AmIn)] <- 0
race$RaceOther[is.na(race$RaceOther)] <- 0
race$RaceUnk[is.na(race$RaceUnk)] <- 0
race$RaceHisp[is.na(race$RaceHisp)] <- 0

race$RaceNumber <- race$White + race$Black + race$Asian + race$AmIn + race$RaceOther + race$RaceUnk + race$RaceHisp
table(race$RaceNumber)
head(race)

race$race[race$RaceNumber == 1 & race$Black == 1] <- 'Black/African American'
race$race[race$RaceNumber == 1 & race$White == 1] <- 'White'
race$race[race$RaceNumber == 1 & race$Asian == 1] <- 'Asian/Pacific Islander'
race$race[race$RaceNumber == 1 & race$AmIn == 1] <- 'American Indian/Alaska native'
race$race[race$RaceNumber == 1 & race$RaceOther == 1] <- 'Other'
race$race[(race$RaceNumber == 1 & race$RaceHisp == 1) |
            (race$RaceNumber > 1 & race$RaceHisp == 1)] <- 'Hispanic/Latinx'
race$race[race$RaceNumber > 1 & race$RaceHisp != 1] <- 'Biracial/Multiracial'
race$race[race$RaceNumber == 0 | is.na(race$RaceNumber) | race$RaceUnk == 1] <- 'Unknown'
table(race$race)

dim(eip)
dim(race)
eip <- merge(eip, race, by = 'record_id', all.x = T)
dim(eip)
table(eip$race)




table(eip$sex_raised)
eip$sex[eip$sex_raised == 1] <- 'Male'
eip$sex[eip$sex_raised == 2] <- 'Female'
eip$sex[eip$sex_raised == 3 | is.na(eip$sex_raised) | eip$sex_raised == ''] <- 'Unknown/Unassigned'
table(eip$sex)



table(eip$sex_raised, eip$sex_selfdefined)
eip$gender[eip$sex_raised == 1 & eip$sex_selfdefined == 1] <- 'Male'
eip$gender[eip$sex_raised == 2 & eip$sex_selfdefined == 2] <- 'Female'
eip$gender[(eip$sex_raised == 1 & eip$sex_selfdefined == 2) |
             (eip$sex_raised == 2 & eip$sex_selfdefined == 1) |
             (eip$sex_raised == 1 & eip$sex_selfdefined == 3) |
             (eip$sex_raised == 2 & eip$sex_selfdefined == 3)] <- 'Transgender/Nonbinary'
eip$gender[(eip$sex_raised == 3 & eip$sex_selfdefined == 3) |
             is.na(eip$sex_raised) | is.na(eip$sex_selfdefined)] <- 'Unknown'
table(eip$gender)


table(eip$insurance)
eip$insurance[eip$insurance == 1] <- 'None'
eip$insurance[eip$insurance == 2] <- 'UC Health (Levy)'
eip$insurance[eip$insurance == 3] <- 'Medicaid'
eip$insurance[eip$insurance == 4] <- 'Medicare'
eip$insurance[eip$insurance == 5] <- 'Military/VA'
eip$insurance[eip$insurance == 6] <- 'Private'
eip$insurance[eip$insurance == 7] <- 'Dual Medicaid/Medicare'
eip$insurance[is.na(eip$insurance)] <- 'Unknown'
table(eip$insurance)



# Populations of Interest
### WOC, Youth (18-24), MSM, IDU, HRHS, PLWHA

table(eip$race, eip$gender)
eip$WOC[(eip$race != 'White' & eip$race != 'Unknown') & eip$gender == 'Female'] <- 1
table(eip$WOC)


table(eip$age)
eip$Youth[eip$age >= 13 & eip$age <= 29] <- 1
table(eip$Youth)


eip$MSM[eip$gender == 'Male' & ((eip$sex_orientation == '2' | eip$sex_orientation == '4') |
                                  (eip$sex_w_man___1 == '1' | eip$sex_w_man___2 == '1' |
                                     eip$sex_w_man___3 == '1') |
                                  (eip$sex_w_ftm___1 == '1' | eip$sex_w_ftm___2 == '1' |
                                     eip$sex_w_ftm___3 == '1') |
                                  (eip$sex_msm___1 == '1' | eip$sex_msm___2 == '1' |
                                     eip$sex_msm___3 == '1') |
                                  (eip$hiv_dx_risks___2 == '1'))] <- 1
table(eip$MSM)


eip$IDU[eip$idu_calc == 1 | eip$hiv_dx_risks___3 == '1'] <- 1
table(eip$IDU)


# For HRHS, all sexual behavior is within the previous 12 months
### Heterosexual males that have unprotected sex with women
### Heterosexual women that have unprotected sex with men
### Heterosexual women that have sex with MSM
### Heterosexual men/women that have sex with IDU
### Heterosexual men/women that have sex with HIV+ partner
### Heterosexual men/women that exchange money/drugs for sex
### Heterosexual men/women that have sex with STD+ partner
### Heterosexual men/women that have more than 3 partners

eip$Hetero[(eip$gender == 'Male' & (eip$sex_w_woman___1 == '1' |
                                      eip$sex_w_woman___2 == '1' | eip$sex_w_woman___3 == '1')) |
             (eip$gender == 'Female' & (eip$sex_w_man___1 == '1' | eip$sex_w_man___2 == '1' |
                                          eip$sex_w_man___3 == '1'))] <- 1
table(eip$Hetero)


eip$HRHS[(eip$Hetero == 1) & ((((eip$sex_w_woman___6 == '1' | eip$sex_w_woman___7 == '1') |
                                  (is.na(eip$sex_w_woman___6) & is.na(eip$sex_w_woman___7) &
                                     is.na(eip$sex_w_woman___8)))) | (((eip$sex_w_man___6 == '1' |
                                                                          eip$sex_w_man___7 == '1') |
                                                                         (is.na(eip$sex_w_man___6) &
                                                                            is.na(eip$sex_w_man___7) &
                                                                            is.na(eip$sex_w_man___8)))) |
                                (eip$sex_msm___1 == '1' | eip$sex_msm___2 == '1' | eip$sex_msm___3 == '1') |
                                (eip$sex_idu___1 == '1' | eip$sex_idu___2 == '1' | eip$sex_idu___3 == '1') |
                                (eip$sex_hiv_pos___1 == '1' | eip$sex_hiv_pos___2 == '1' |
                                   eip$sex_hiv_pos___3 == '1') | (eip$sex_receivemoney___1 == '1' |
                                                                    eip$sex_receivemoney___2 == '1' |
                                                                    eip$sex_receivemoney___3 == '1' |
                                                                    eip$sex_receivedrugs___1 == '1' |
                                                                    eip$sex_receivedrugs___2 == '1' |
                                                                    eip$sex_receivedrugs___3 == '1' |
                                                                    eip$sex_paymoney___1 == '1' |
                                                                    eip$sex_paymoney___2 == '1' |
                                                                    eip$sex_paymoney___3 == '1' |
                                                                    eip$sex_paydrugs___1 == '1' |
                                                                    eip$sex_paydrugs___2 == '1' |
                                                                    eip$sex_paydrugs___3 == '1')  |
                                (eip$sex_sti_pos___1 == '1' | eip$sex_sti_pos___2 == '1' |
                                   eip$sex_sti_pos___3 == '1') | (eip$sex_partners_past_year >= 3))] <- 1
table(eip$HRHS)




# Appalachian

eip$appalachian_pt[eip$address_zip_code == 43006 | eip$address_zip_code == 43056 |
                     eip$address_zip_code == 43076 | eip$address_zip_code == 43101 |
                     eip$address_zip_code == 43102 | eip$address_zip_code == 43107 |
                     eip$address_zip_code == 43111 | eip$address_zip_code == 43115 |
                     eip$address_zip_code == 43127 | eip$address_zip_code == 43135 |
                     eip$address_zip_code == 43138 | eip$address_zip_code == 43144 |
                     eip$address_zip_code == 43148 | eip$address_zip_code == 43149 |
                     eip$address_zip_code == 43150 | eip$address_zip_code == 43152 |
                     eip$address_zip_code == 43155 | eip$address_zip_code == 43158 |
                     eip$address_zip_code == 43160 | eip$address_zip_code == 43164 |
                     eip$address_zip_code == 43701 | eip$address_zip_code == 43702 |
                     eip$address_zip_code == 43711 | eip$address_zip_code == 43713 |
                     eip$address_zip_code == 43716 | eip$address_zip_code == 43717 |
                     eip$address_zip_code == 43718 | eip$address_zip_code == 43719 |
                     eip$address_zip_code == 43720 | eip$address_zip_code == 43722 |
                     eip$address_zip_code == 43723 | eip$address_zip_code == 43724 |
                     eip$address_zip_code == 43725 | eip$address_zip_code == 43727 |
                     eip$address_zip_code == 43728 | eip$address_zip_code == 43730 |
                     eip$address_zip_code == 43731 | eip$address_zip_code == 43732 |
                     eip$address_zip_code == 43733 | eip$address_zip_code == 43734 |
                     eip$address_zip_code == 43735 | eip$address_zip_code == 43736 |
                     eip$address_zip_code == 43738 | eip$address_zip_code == 43739 |
                     eip$address_zip_code == 43746 | eip$address_zip_code == 43747 |
                     eip$address_zip_code == 43748 | eip$address_zip_code == 43749 |
                     eip$address_zip_code == 43750 | eip$address_zip_code == 43752 |
                     eip$address_zip_code == 43754 | eip$address_zip_code == 43755 |
                     eip$address_zip_code == 43756 | eip$address_zip_code == 43757 |
                     eip$address_zip_code == 43758 | eip$address_zip_code == 43759 |
                     eip$address_zip_code == 43760 | eip$address_zip_code == 43761 |
                     eip$address_zip_code == 43762 | eip$address_zip_code == 43764 |
                     eip$address_zip_code == 43766 | eip$address_zip_code == 43767 |
                     eip$address_zip_code == 43768 | eip$address_zip_code == 43771 |
                     eip$address_zip_code == 43772 | eip$address_zip_code == 43773 |
                     eip$address_zip_code == 43777 | eip$address_zip_code == 43778 |
                     eip$address_zip_code == 43779 | eip$address_zip_code == 43780 |
                     eip$address_zip_code == 43782 | eip$address_zip_code == 43783 |
                     eip$address_zip_code == 43786 | eip$address_zip_code == 43787 |
                     eip$address_zip_code == 43788 | eip$address_zip_code == 43791 |
                     eip$address_zip_code == 43793 | eip$address_zip_code == 43802 |
                     eip$address_zip_code == 43803 | eip$address_zip_code == 43804 |
                     eip$address_zip_code == 43805 | eip$address_zip_code == 43811 |
                     eip$address_zip_code == 43812 | eip$address_zip_code == 43821 |
                     eip$address_zip_code == 43822 | eip$address_zip_code == 43824 |
                     eip$address_zip_code == 43828 | eip$address_zip_code == 43830 |
                     eip$address_zip_code == 43832 | eip$address_zip_code == 43836 |
                     eip$address_zip_code == 43837 | eip$address_zip_code == 43840 |
                     eip$address_zip_code == 43842 | eip$address_zip_code == 43843 |
                     eip$address_zip_code == 43844 | eip$address_zip_code == 43845 |
                     eip$address_zip_code == 43901 | eip$address_zip_code == 43902 |
                     eip$address_zip_code == 43903 | eip$address_zip_code == 43905 |
                     eip$address_zip_code == 43906 | eip$address_zip_code == 43907 |
                     eip$address_zip_code == 43908 | eip$address_zip_code == 43909 |
                     eip$address_zip_code == 43910 | eip$address_zip_code == 43912 |
                     eip$address_zip_code == 43913 | eip$address_zip_code == 43914 |
                     eip$address_zip_code == 43915 | eip$address_zip_code == 43916 |
                     eip$address_zip_code == 43917 | eip$address_zip_code == 43920 |
                     eip$address_zip_code == 43925 | eip$address_zip_code == 43926 |
                     eip$address_zip_code == 43927 | eip$address_zip_code == 43928 |
                     eip$address_zip_code == 43930 | eip$address_zip_code == 43931 |
                     eip$address_zip_code == 43932 | eip$address_zip_code == 43933 |
                     eip$address_zip_code == 43934 | eip$address_zip_code == 43935 |
                     eip$address_zip_code == 43937 | eip$address_zip_code == 43938 |
                     eip$address_zip_code == 43939 | eip$address_zip_code == 43940 |
                     eip$address_zip_code == 43941 | eip$address_zip_code == 43942 |
                     eip$address_zip_code == 43943 | eip$address_zip_code == 43944 |
                     eip$address_zip_code == 43945 | eip$address_zip_code == 43946 |
                     eip$address_zip_code == 43947 | eip$address_zip_code == 43948 |
                     eip$address_zip_code == 43950 | eip$address_zip_code == 43951 |
                     eip$address_zip_code == 43952 | eip$address_zip_code == 43953 |
                     eip$address_zip_code == 43961 | eip$address_zip_code == 43962 |
                     eip$address_zip_code == 43963 | eip$address_zip_code == 43964 |
                     eip$address_zip_code == 43967 | eip$address_zip_code == 43968 |
                     eip$address_zip_code == 43970 | eip$address_zip_code == 43971 |
                     eip$address_zip_code == 43972 | eip$address_zip_code == 43973 |
                     eip$address_zip_code == 43974 | eip$address_zip_code == 43976 |
                     eip$address_zip_code == 43977 | eip$address_zip_code == 43981 |
                     eip$address_zip_code == 43983 | eip$address_zip_code == 43984 |
                     eip$address_zip_code == 43985 | eip$address_zip_code == 43986 |
                     eip$address_zip_code == 43988 | eip$address_zip_code == 44003 |
                     eip$address_zip_code == 44004 | eip$address_zip_code == 44005 |
                     eip$address_zip_code == 44010 | eip$address_zip_code == 44030 |
                     eip$address_zip_code == 44032 | eip$address_zip_code == 44041 |
                     eip$address_zip_code == 44046 | eip$address_zip_code == 44047 |
                     eip$address_zip_code == 44048 | eip$address_zip_code == 44057 |
                     eip$address_zip_code == 44062 | eip$address_zip_code == 44064 |
                     eip$address_zip_code == 44068 | eip$address_zip_code == 44076 |
                     eip$address_zip_code == 44082 | eip$address_zip_code == 44084 |
                     eip$address_zip_code == 44085 | eip$address_zip_code == 44086 |
                     eip$address_zip_code == 44088 | eip$address_zip_code == 44093 |
                     eip$address_zip_code == 44099 | eip$address_zip_code == 44231 |
                     eip$address_zip_code == 44288 | eip$address_zip_code == 44401 |
                     eip$address_zip_code == 44402 | eip$address_zip_code == 44403 |
                     eip$address_zip_code == 44404 | eip$address_zip_code == 44405 |
                     eip$address_zip_code == 44406 | eip$address_zip_code == 44408 |
                     eip$address_zip_code == 44410 | eip$address_zip_code == 44411 |
                     eip$address_zip_code == 44412 | eip$address_zip_code == 44413 |
                     eip$address_zip_code == 44415 | eip$address_zip_code == 44416 |
                     eip$address_zip_code == 44417 | eip$address_zip_code == 44418 |
                     eip$address_zip_code == 44420 | eip$address_zip_code == 44422 |
                     eip$address_zip_code == 44423 | eip$address_zip_code == 44424 |
                     eip$address_zip_code == 44425 | eip$address_zip_code == 44427 |
                     eip$address_zip_code == 44428 | eip$address_zip_code == 44429 |
                     eip$address_zip_code == 44430 | eip$address_zip_code == 44431 |
                     eip$address_zip_code == 44432 | eip$address_zip_code == 44436 |
                     eip$address_zip_code == 44437 | eip$address_zip_code == 44438 |
                     eip$address_zip_code == 44439 | eip$address_zip_code == 44440 |
                     eip$address_zip_code == 44441 | eip$address_zip_code == 44442 |
                     eip$address_zip_code == 44443 | eip$address_zip_code == 44444 |
                     eip$address_zip_code == 44445 | eip$address_zip_code == 44446 |
                     eip$address_zip_code == 44449 | eip$address_zip_code == 44450 |
                     eip$address_zip_code == 44451 | eip$address_zip_code == 44452 |
                     eip$address_zip_code == 44453 | eip$address_zip_code == 44454 |
                     eip$address_zip_code == 44455 | eip$address_zip_code == 44460 |
                     eip$address_zip_code == 44470 | eip$address_zip_code == 44471 |
                     eip$address_zip_code == 44473 | eip$address_zip_code == 44481 |
                     eip$address_zip_code == 44482 | eip$address_zip_code == 44483 |
                     eip$address_zip_code == 44484 | eip$address_zip_code == 44485 |
                     eip$address_zip_code == 44486 | eip$address_zip_code == 44490 |
                     eip$address_zip_code == 44491 | eip$address_zip_code == 44492 |
                     eip$address_zip_code == 44493 | eip$address_zip_code == 44501 |
                     eip$address_zip_code == 44502 | eip$address_zip_code == 44503 |
                     eip$address_zip_code == 44504 | eip$address_zip_code == 44505 |
                     eip$address_zip_code == 44506 | eip$address_zip_code == 44507 |
                     eip$address_zip_code == 44509 | eip$address_zip_code == 44510 |
                     eip$address_zip_code == 44511 | eip$address_zip_code == 44512 |
                     eip$address_zip_code == 44513 | eip$address_zip_code == 44514 |
                     eip$address_zip_code == 44515 | eip$address_zip_code == 44555 |
                     eip$address_zip_code == 44601 | eip$address_zip_code == 44607 |
                     eip$address_zip_code == 44608 | eip$address_zip_code == 44609 |
                     eip$address_zip_code == 44610 | eip$address_zip_code == 44611 |
                     eip$address_zip_code == 44612 | eip$address_zip_code == 44615 |
                     eip$address_zip_code == 44617 | eip$address_zip_code == 44619 |
                     eip$address_zip_code == 44620 | eip$address_zip_code == 44621 |
                     eip$address_zip_code == 44622 | eip$address_zip_code == 44624 |
                     eip$address_zip_code == 44625 | eip$address_zip_code == 44626 |
                     eip$address_zip_code == 44627 | eip$address_zip_code == 44628 |
                     eip$address_zip_code == 44629 | eip$address_zip_code == 44633 |
                     eip$address_zip_code == 44634 | eip$address_zip_code == 44637 |
                     eip$address_zip_code == 44638 | eip$address_zip_code == 44639 |
                     eip$address_zip_code == 44643 | eip$address_zip_code == 44644 |
                     eip$address_zip_code == 44651 | eip$address_zip_code == 44653 |
                     eip$address_zip_code == 44654 | eip$address_zip_code == 44656 |
                     eip$address_zip_code == 44657 | eip$address_zip_code == 44660 |
                     eip$address_zip_code == 44661 | eip$address_zip_code == 44663 |
                     eip$address_zip_code == 44665 | eip$address_zip_code == 44671 |
                     eip$address_zip_code == 44672 | eip$address_zip_code == 44675 |
                     eip$address_zip_code == 44676 | eip$address_zip_code == 44678 |
                     eip$address_zip_code == 44679 | eip$address_zip_code == 44680 |
                     eip$address_zip_code == 44681 | eip$address_zip_code == 44682 |
                     eip$address_zip_code == 44683 | eip$address_zip_code == 44687 |
                     eip$address_zip_code == 44688 | eip$address_zip_code == 44689 |
                     eip$address_zip_code == 44690 | eip$address_zip_code == 44693 |
                     eip$address_zip_code == 44695 | eip$address_zip_code == 44697 |
                     eip$address_zip_code == 44699 | eip$address_zip_code == 44730 |
                     eip$address_zip_code == 44842 | eip$address_zip_code == 45101 |
                     eip$address_zip_code == 45102 | eip$address_zip_code == 45103 |
                     eip$address_zip_code == 45105 | eip$address_zip_code == 45106 |
                     eip$address_zip_code == 45107 | eip$address_zip_code == 45112 |
                     eip$address_zip_code == 45115 | eip$address_zip_code == 45118 |
                     eip$address_zip_code == 45119 | eip$address_zip_code == 45120 |
                     eip$address_zip_code == 45121 | eip$address_zip_code == 45122 |
                     eip$address_zip_code == 45123 | eip$address_zip_code == 45130 |
                     eip$address_zip_code == 45131 | eip$address_zip_code == 45132 |
                     eip$address_zip_code == 45133 | eip$address_zip_code == 45135 |
                     eip$address_zip_code == 45140 | eip$address_zip_code == 45142 |
                     eip$address_zip_code == 45144 | eip$address_zip_code == 45147 |
                     eip$address_zip_code == 45148 | eip$address_zip_code == 45150 |
                     eip$address_zip_code == 45153 | eip$address_zip_code == 45154 |
                     eip$address_zip_code == 45155 | eip$address_zip_code == 45156 |
                     eip$address_zip_code == 45157 | eip$address_zip_code == 45158 |
                     eip$address_zip_code == 45159 | eip$address_zip_code == 45160 |
                     eip$address_zip_code == 45162 | eip$address_zip_code == 45167 |
                     eip$address_zip_code == 45168 | eip$address_zip_code == 45171 |
                     eip$address_zip_code == 45172 | eip$address_zip_code == 45176 |
                     eip$address_zip_code == 45244 | eip$address_zip_code == 45245 |
                     eip$address_zip_code == 45255 | eip$address_zip_code == 45601 |
                     eip$address_zip_code == 45612 | eip$address_zip_code == 45613 |
                     eip$address_zip_code == 45614 | eip$address_zip_code == 45616 |
                     eip$address_zip_code == 45617 | eip$address_zip_code == 45618 |
                     eip$address_zip_code == 45619 | eip$address_zip_code == 45620 |
                     eip$address_zip_code == 45621 | eip$address_zip_code == 45622 |
                     eip$address_zip_code == 45623 | eip$address_zip_code == 45624 |
                     eip$address_zip_code == 45628 | eip$address_zip_code == 45629 |
                     eip$address_zip_code == 45630 | eip$address_zip_code == 45631 |
                     eip$address_zip_code == 45633 | eip$address_zip_code == 45634 |
                     eip$address_zip_code == 45636 | eip$address_zip_code == 45638 |
                     eip$address_zip_code == 45640 | eip$address_zip_code == 45642 |
                     eip$address_zip_code == 45643 | eip$address_zip_code == 45644 |
                     eip$address_zip_code == 45645 | eip$address_zip_code == 45646 |
                     eip$address_zip_code == 45647 | eip$address_zip_code == 45648 |
                     eip$address_zip_code == 45650 | eip$address_zip_code == 45651 |
                     eip$address_zip_code == 45652 | eip$address_zip_code == 45653 |
                     eip$address_zip_code == 45654 | eip$address_zip_code == 45656 |
                     eip$address_zip_code == 45657 | eip$address_zip_code == 45658 |
                     eip$address_zip_code == 45659 | eip$address_zip_code == 45660 |
                     eip$address_zip_code == 45661 | eip$address_zip_code == 45662 |
                     eip$address_zip_code == 45663 | eip$address_zip_code == 45669 |
                     eip$address_zip_code == 45671 | eip$address_zip_code == 45672 |
                     eip$address_zip_code == 45673 | eip$address_zip_code == 45674 |
                     eip$address_zip_code == 45675 | eip$address_zip_code == 45677 |
                     eip$address_zip_code == 45678 | eip$address_zip_code == 45679 |
                     eip$address_zip_code == 45680 | eip$address_zip_code == 45681 |
                     eip$address_zip_code == 45682 | eip$address_zip_code == 45683 |
                     eip$address_zip_code == 45684 | eip$address_zip_code == 45685 |
                     eip$address_zip_code == 45686 | eip$address_zip_code == 45687 |
                     eip$address_zip_code == 45688 | eip$address_zip_code == 45690 |
                     eip$address_zip_code == 45692 | eip$address_zip_code == 45693 |
                     eip$address_zip_code == 45694 | eip$address_zip_code == 45695 |
                     eip$address_zip_code == 45696 | eip$address_zip_code == 45697 |
                     eip$address_zip_code == 45698 | eip$address_zip_code == 45699 |
                     eip$address_zip_code == 45701 | eip$address_zip_code == 45710 |
                     eip$address_zip_code == 45711 | eip$address_zip_code == 45712 |
                     eip$address_zip_code == 45713 | eip$address_zip_code == 45714 |
                     eip$address_zip_code == 45715 | eip$address_zip_code == 45716 |
                     eip$address_zip_code == 45717 | eip$address_zip_code == 45719 |
                     eip$address_zip_code == 45720 | eip$address_zip_code == 45721 |
                     eip$address_zip_code == 45723 | eip$address_zip_code == 45724 |
                     eip$address_zip_code == 45727 | eip$address_zip_code == 45729 |
                     eip$address_zip_code == 45732 | eip$address_zip_code == 45734 |
                     eip$address_zip_code == 45735 | eip$address_zip_code == 45739 |
                     eip$address_zip_code == 45740 | eip$address_zip_code == 45741 |
                     eip$address_zip_code == 45742 | eip$address_zip_code == 45743 |
                     eip$address_zip_code == 45744 | eip$address_zip_code == 45745 |
                     eip$address_zip_code == 45746 | eip$address_zip_code == 45750 |
                     eip$address_zip_code == 45760 | eip$address_zip_code == 45761 |
                     eip$address_zip_code == 45764 | eip$address_zip_code == 45766 |
                     eip$address_zip_code == 45767 | eip$address_zip_code == 45768 |
                     eip$address_zip_code == 45769 | eip$address_zip_code == 45770 |
                     eip$address_zip_code == 45771 | eip$address_zip_code == 45772 |
                     eip$address_zip_code == 45773 | eip$address_zip_code == 45775 |
                     eip$address_zip_code == 45776 | eip$address_zip_code == 45777 |
                     eip$address_zip_code == 45778 | eip$address_zip_code == 45779 |
                     eip$address_zip_code == 45780 | eip$address_zip_code == 45782 |
                     eip$address_zip_code == 45783 | eip$address_zip_code == 45784 |
                     eip$address_zip_code == 45786 | eip$address_zip_code == 45787 |
                     eip$address_zip_code == 45788 | eip$address_zip_code == 45789 |
                     (eip$appalachian == 1 | eip$appalachian_family == 1)] <- 1
table(eip$appalachian_pt)




############################################################################################
################################  Creating Patient Dataset  ################################
############################################################################################

dim(eip)
eip_pt <- select(eip, record_id, enc_date)
dim(eip_pt)
head(eip_pt)
eip_pt <- eip_pt[which(eip_pt$enc_date >= '2023-01-01' & eip_pt$enc_date <= '2023-12-31'), ]
dim(eip_pt)
eip_pt <- select(eip_pt, record_id)
head(eip_pt)
eip_pt <- distinct(eip_pt)
dim(eip_pt)
head(eip_pt)
eip_pt$unique_pt <- 1
head(eip_pt)
eip_pt <- distinct(eip_pt)


pt_age <- select(eip, record_id, dob)
dim(pt_age)
head(pt_age)
pt_age <- distinct(pt_age)
dim(pt_age)
pt_age$age <- trunc((pt_age$dob %--% '2022-01-01')/years(1))
summary(pt_age$age)
table(pt_age$age) # set 65+ to maximum age range
pt_age$age_category[pt_age$age >= 0 & pt_age$age <= 12] <- 'Under 13'
pt_age$age_category[pt_age$age >= 13 & pt_age$age <= 17] <- '13-17'
pt_age$age_category[pt_age$age >= 18 & pt_age$age <= 24] <- '18-24'
pt_age$age_category[pt_age$age >= 25 & pt_age$age <= 34] <- '25-34'
pt_age$age_category[pt_age$age >= 35 & pt_age$age <= 44] <- '35-44'
pt_age$age_category[pt_age$age >= 45 & pt_age$age <= 54] <- '45-54'
pt_age$age_category[pt_age$age >= 55 & pt_age$age <= 64] <- '55-64'
pt_age$age_category[pt_age$age >= 65 & pt_age$age <= 110] <- '65+'
pt_age$age_category[is.na(pt_age$age) | pt_age$age > 110] <- 'Unknown'
table(pt_age$age_category)
pt_age <- select(pt_age, record_id, age, age_category)
dim(pt_age)
dim(eip_pt)
eip_pt <- merge(eip_pt, pt_age, by = 'record_id', all.x = T)
dim(eip_pt)
eip_pt$age[(is.na(eip_pt$age))] <- ''
head(eip_pt)
eip_pt <- distinct(eip_pt)

pt_race <- select(eip, record_id, race)
dim(pt_race)
head(pt_race)
pt_race <- distinct(pt_race)
dim(pt_race)
dim(eip_pt)
eip_pt <- merge(eip_pt, pt_race, by = 'record_id', all.x = T)
dim(eip_pt)
head(eip_pt)
eip_pt$race[(is.na(eip_pt$race))] <- ''
rm(pt_race)
eip_pt <- distinct(eip_pt)

pt_sex <- select(eip, record_id, sex)
dim(pt_sex)
head(pt_sex)
pt_sex <- distinct(pt_sex)
dim(pt_sex)
dim(eip_pt)
eip_pt <- merge(eip_pt, pt_sex, by = 'record_id', all.x = T)
dim(eip_pt)
head(eip_pt)
eip_pt$sex[(is.na(eip_pt$sex_at_birth))] <- ''
rm(pt_sex)
eip_pt <- distinct(eip_pt)

pt_gender <- select(eip, record_id, gender)
dim(pt_gender)
head(pt_gender)
pt_gender <- distinct(pt_gender)
dim(pt_gender)
dim(eip_pt)
eip_pt <- merge(eip_pt, pt_gender, by = 'record_id', all.x = T)
dim(eip_pt)
head(eip_pt)
eip_pt$gender[(is.na(eip_pt$gender))] <- ''
rm(pt_gender)
eip_pt <- distinct(eip_pt)

pt_insurance <- select(eip, record_id, insurance)
dim(pt_insurance)
head(pt_insurance)
pt_insurance <- distinct(pt_insurance)
dim(pt_insurance)
dim(eip_pt)
eip_pt <- merge(eip_pt, pt_insurance, by = 'record_id', all.x = T)
dim(eip_pt)
head(eip_pt)
eip_pt$insurance[(is.na(eip_pt$insurance))] <- ''
rm(pt_insurance)
eip_pt <- distinct(eip_pt)

pt_appalachian <- select(eip, record_id, appalachian_pt)
dim(pt_appalachian)
head(pt_appalachian)
pt_appalachian <- distinct(pt_appalachian)
dim(pt_appalachian)
dim(eip_pt)
eip_pt <- merge(eip_pt, pt_appalachian, by = 'record_id', all.x = T)
dim(eip_pt)
head(eip_pt)
eip_pt$appalachian_pt[(is.na(eip_pt$appalachian_pt))] <- ''
rm(pt_appalachian)
eip_pt <- distinct(eip_pt)

pt_msm <- select(eip, record_id, MSM)
dim(pt_msm)
head(pt_msm)
table(pt_msm$MSM)
pt_msm <- pt_msm[which(pt_msm$MSM == 1), ]
dim(pt_msm)
pt_msm <- distinct(pt_msm)
dim(pt_msm)
head(pt_msm)
dim(eip_pt)
eip_pt <- merge(eip_pt, pt_msm, by = 'record_id', all.x = T)
dim(eip_pt)
head(eip_pt)
eip_pt$MSM[is.na(eip_pt$MSM)] <- ''
head(eip_pt)
table(eip_pt$MSM)
rm(pt_msm)
eip_pt <- distinct(eip_pt)

pt_idu <- select(eip, record_id, IDU)
dim(pt_idu)
head(pt_idu)
table(pt_idu$IDU)
pt_idu <- pt_idu[which(pt_idu$IDU == 1), ]
dim(pt_idu)
pt_idu <- distinct(pt_idu)
dim(pt_idu)
head(pt_idu)
dim(eip_pt)
eip_pt <- merge(eip_pt, pt_idu, by = 'record_id', all.x = T)
dim(eip_pt)
head(eip_pt)
eip_pt$IDU[is.na(eip_pt$IDU)] <- ''
head(eip_pt)
table(eip_pt$IDU)
rm(pt_idu)
eip_pt <- distinct(eip_pt)

pt_woc <- select(eip, record_id, WOC)
dim(pt_woc)
head(pt_woc)
table(pt_woc$WOC)
pt_woc <- pt_woc[which(pt_woc$WOC == 1), ]
dim(pt_woc)
pt_woc <- distinct(pt_woc)
dim(pt_woc)
head(pt_woc)
dim(eip_pt)
eip_pt <- merge(eip_pt, pt_woc, by = 'record_id', all.x = T)
dim(eip_pt)
head(eip_pt)
eip_pt$WOC[is.na(eip_pt$WOC)] <- ''
head(eip_pt)
table(eip_pt$WOC)
rm(pt_woc)
eip_pt <- distinct(eip_pt)

pt_youth <- select(eip, record_id, Youth)
dim(pt_youth)
head(pt_youth)
table(pt_youth$Youth)
pt_youth <- pt_youth[which(pt_youth$Youth == 1), ]
dim(pt_youth)
pt_youth <- distinct(pt_youth)
dim(pt_youth)
head(pt_youth)
dim(eip_pt)
eip_pt <- merge(eip_pt, pt_youth, by = 'record_id', all.x = T)
dim(eip_pt)
head(eip_pt)
eip_pt$Youth[is.na(eip_pt$Youth)] <- ''
head(eip_pt)
table(eip_pt$Youth)
rm(pt_youth)
eip_pt <- distinct(eip_pt)

pt_hrhs <- select(eip, record_id, HRHS)
dim(pt_hrhs)
head(pt_hrhs)
table(pt_hrhs$HRHS)
pt_hrhs <- pt_hrhs[which(pt_hrhs$HRHS == 1), ]
dim(pt_hrhs)
pt_hrhs <- distinct(pt_hrhs)
dim(pt_hrhs)
head(pt_hrhs)
dim(eip_pt)
eip_pt <- merge(eip_pt, pt_hrhs, by = 'record_id', all.x = T)
dim(eip_pt)
head(eip_pt)
eip_pt$HRHS[is.na(eip_pt$HRHS)] <- ''
head(eip_pt)
table(eip_pt$HRHS)
rm(pt_hrhs)
eip_pt <- distinct(eip_pt)


summary(eip_pt$age)
class(eip_pt$age)
eip_pt$age <- as.numeric(eip_pt$age)
summary(eip_pt$age)


table(eip_pt$unique_pt)
unique_patients <- sum(eip_pt$unique_pt)
unique_patients

```

The information on this page only includes data since the start of 2023. EIP has encountered a total of [ **`r unique_patients`**]{style="color: red;"} unique individuals at all sites.

The demographic information for this EIP population is shown on this page. For further information regarding the population demographics of individuals at particular sites, please refer to those pages listed under the **Site** tab in the navigation bar.

## Age Distribution

> Since age is based on the individual's date of birth (DOB) and the date of their encounter, this can change the individual's age over time with various EIP encounters. The data here is shown only for 2023, so age distribution can be presented. When this information is combined with historical EIP data, age distribution will be based on encounter-level data, rather than patient-level data.


This shows the EIP patient population's age distribution by sex, exluding those with an unknown or unassigned sex at birth.

```{r}
age_dist <- select(eip_pt, age, sex)
age_dist <- age_dist[which(age_dist$sex != 'Unknown/Unassigned'), ]
age_dist$age <- as.factor(age_dist$age)

age_dist <- age_pyramid(
  age_dist,
  age_group = "age",
  split_by = "sex",
  stack_by = NULL,
  count = NULL,
  proportional = FALSE,
  na.rm = TRUE,
  show_midpoint = TRUE,
  vertical_lines = FALSE,
  horizontal_lines = TRUE,
  pyramid = TRUE,
  pal = NULL
)

age_dist + labs(title = "EIP Patient Age Distribution by Sex", x = "Age", y = "Counts") + theme_bw()


```


This shows the EIP patient population's age category stratified by sex, excluding those with an unknown or undetermined sex at birth.

```{r}
age_cat_dist <- select(eip_pt, age_category, sex)
age_cat_dist <- age_cat_dist[which(age_cat_dist$sex != 'Unknown/Unassigned'), ]
age_cat_dist$age_category <- as.factor(age_cat_dist$age_category)

age_cat_dist <- age_pyramid(
  age_cat_dist,
  age_group = "age_category",
  split_by = "sex",
  stack_by = NULL,
  count = NULL,
  proportional = FALSE,
  na.rm = TRUE,
  show_midpoint = TRUE,
  vertical_lines = FALSE,
  horizontal_lines = TRUE,
  pyramid = TRUE,
  pal = NULL
)

age_cat_dist + labs(title = "EIP Patient Age Category by Sex", x = "Age Category", y = "Counts") + theme_bw()


```


This histogram shows the ages of individuals seen by EIP grouped by age categories. The age categories in this histogram were chosen because they are the categories used in both the CTR and EHE reports to ODH. The total numbers of individuals within each category as well as the percent of the total individuals encountered by EIP are shown in the table.

```{r}
pt_age_cat <- ggplot(eip_pt, aes(x = age_category))  
pt_age_cat <-  pt_age_cat + geom_bar(fill = "lightblue") + theme_classic() +
  xlab("Age Category") + ylab("Count")

ggplotly(pt_age_cat)

```

```{r, layout="l-body-outset"}
pt_age_cat_tbl <- table(eip_pt$age_category)

pt_age_cat_tbl_perc <- eip_pt %>%
  group_by(age_category) %>%
  summarise(Percent = n()/nrow(.)*100)
pt_age_cat_tbl_perc <- as.data.frame(pt_age_cat_tbl_perc)
pt_age_cat_tbl_perc <- na.omit(pt_age_cat_tbl_perc)
pt_age_cat_tbl_perc$Percent <- round(pt_age_cat_tbl_perc$Percent, digits = 0)
pt_age_cat_tbl_perc <- spread(pt_age_cat_tbl_perc, age_category, Percent)
pt_age_cat_tbl <- rbind(pt_age_cat_tbl, pt_age_cat_tbl_perc)
pt_age_cat_tbl$Data <- c("Total", "Percent (%)")
pt_age_cat_tbl <- pt_age_cat_tbl[, c(9, 1, 2, 3, 4, 5, 6, 7, 8)]

pt_age_cat_tbl %>%
  reactable()

```

The following histogram shows the complete age distribution of all individuals that EIP has encountered, with the density curve overlying the histogram.

```{r}

pt_age_dens <- density(eip_pt$age, na.rm = TRUE)

pt_age <- plot_ly(x = ~eip_pt$age,
              type = "histogram",
              name = "Histogram",
              xbins = list(size = 1)) %>% 
  layout(title = "Histogram of EIP Patient Age",
         xaxis = list(title = "Age",
                      zeroline = FALSE),
         yaxis = list(title = "Count",
                      zeroline = FALSE)) %>% 
  add_lines(x = pt_age_dens$x, y = pt_age_dens$y, yaxis = "y2", name = "Density") %>% 
  layout(yaxis2 = list(overlaying = "y",
                       side = "right",
                       rangemode = "tozero"))
pt_age

```

The following two histograms also show the overall age distribution of the EIP population. They also allow the ability to filter and select based on self-reported gender (first histogram) and the self-reported race (second histogram). You can filter the information by selecting/deselecting the gender/race from the legend on the right side of the graph. If multiple categories are selected, the histogram shows the cumulative total for each age among the categories selected. If you just want to see the particular age distribution for a single gender/race, you can deselect all other options.

```{r}
eip_pt_male <- eip_pt %>% filter(gender == "Male", na.rm = TRUE)
eip_pt_male <- select(eip_pt_male, age, gender)
eip_pt_female <- eip_pt %>% filter(gender == "Female", na.rm = TRUE)
eip_pt_female <- select(eip_pt_female, age, gender)
eip_pt_trans <- eip_pt %>% filter(gender == "Transgender/Nonbinary", na.rm = TRUE)
eip_pt_trans <- select(eip_pt_trans, age, gender)
eip_pt_unk <- eip_pt %>% filter(gender == "Unknown", na.rm = TRUE)
eip_pt_unk <- select(eip_pt_unk, age, gender)



pt_age_gender <- plot_ly(alpha = 0.5) %>%
  add_histogram(x = ~eip_pt_male$age,
                name = "Male",
                xbins = list(size = 1)) %>% 
  add_histogram(x = ~eip_pt_female$age,
                name = "Female",
                xbins = list(size = 1)) %>% 
  add_histogram(x = ~eip_pt_trans$age,
                name = "Transgender/Nonbinary",
                xbins = list(size = 1)) %>% 
  add_histogram(x = ~eip_pt_unk$age,
                name = "Unknown",
                xbins = list(size = 1)) %>% 
  layout(barmode = "stack",
         title = "Age distribution based on Gender",
         xaxis = list(title = "Age",
                      zeroline = FALSE),
         yaxis = list(title = "Count",
                      zeroline = FALSE))
pt_age_gender

```

```{r}
eip_pt_amin <- eip_pt %>% filter(race == "American Indian/Alaska native", na.rm = TRUE)
eip_pt_amin <- select(eip_pt_amin, age, race)
eip_pt_asian <- eip_pt %>% filter(race == "Asian/Pacific Islander", na.rm = TRUE)
eip_pt_asian <- select(eip_pt_asian, age, race)
eip_pt_biracial <- eip_pt %>% filter(race == "Biracial/Multiracial", na.rm = TRUE)
eip_pt_biracial <- select(eip_pt_biracial, age, race)
eip_pt_black <- eip_pt %>% filter(race == "Black/African American", na.rm = TRUE)
eip_pt_black <- select(eip_pt_black, age, race)
eip_pt_hisp <- eip_pt %>% filter(race == "Hispanic/Latinx", na.rm = TRUE)
eip_pt_hisp <- select(eip_pt_hisp, age, race)
eip_pt_otherrace <- eip_pt %>% filter(race == "Other", na.rm = TRUE)
eip_pt_otherrace <- select(eip_pt_otherrace, age, race)
eip_pt_unkrace <- eip_pt %>% filter(race == "Unknown", na.rm = TRUE)
eip_pt_unkrace <- select(eip_pt_unkrace, age, race)
eip_pt_white <- eip_pt %>% filter(race == "White", na.rm = TRUE)
eip_pt_white <- select(eip_pt_white, age, race)


pt_age_race <- plot_ly(alpha = 0.5) %>%
  add_histogram(x = ~eip_pt_amin$age,
                name = "American Indian/Alaska native",
                xbins = list(size = 1)) %>% 
  add_histogram(x = ~eip_pt_asian$age,
                name = "Asian/Pacific Islander",
                xbins = list(size = 1)) %>% 
  add_histogram(x = ~eip_pt_biracial$age,
                name = "Biracial/Multiracial",
                xbins = list(size = 1)) %>% 
  add_histogram(x = ~eip_pt_black$age,
                name = "Black/African American",
                xbins = list(size = 1)) %>%  
  add_histogram(x = ~eip_pt_hisp$age,
                name = "Hispanic/Latinx",
                xbins = list(size = 1)) %>% 
  add_histogram(x = ~eip_pt_white$age,
                name = "White",
                xbins = list(size = 1)) %>%
  layout(barmode = "stack",
         title = "Age distribution based on Race",
         xaxis = list(title = "Age",
                      zeroline = FALSE),
         yaxis = list(title = "Count",
                      zeroline = FALSE))
pt_age_race

```

## Sex and Gender Identity

EIP collects an individual's sex assigned at birth as well as their self-defined gender identity. The chart below shows the data regarding the individual's sex assigned at birth, with the table and percentages also provided below the chart.

```{r, layout="l-body-outset"}
pt_sex <- ggplot(eip_pt, aes(x = sex))  
pt_sex <-  pt_sex + geom_bar(fill = "lightblue") + theme_classic()

ggplotly(pt_sex)


pt_sex_tbl <- table(eip_pt$sex)
pt_sex_tbl_perc <- eip_pt %>%
  group_by(sex) %>%
  summarise(Percent = n()/nrow(.)*100)
pt_sex_tbl_perc <- as.data.frame(pt_sex_tbl_perc)
pt_sex_tbl_perc <- na.omit(pt_sex_tbl_perc)
pt_sex_tbl_perc$Percent <- round(pt_sex_tbl_perc$Percent, digits = 0)
pt_sex_tbl_perc <- spread(pt_sex_tbl_perc, sex, Percent)
pt_sex_tbl <- rbind(pt_sex_tbl, pt_sex_tbl_perc)
pt_sex_tbl$Data <- c("Total", "Percent (%)")
pt_sex_tbl <- pt_sex_tbl[, c(4, 1, 2, 3)]

pt_sex_tbl %>%
  reactable()

```

The following interactive graph allows for the ability to filter the age category of EIP individuals based on their sex assigned at birth.

```{r}
eip_pt_male_sex <- eip_pt %>% filter(sex == "Male", na.rm = TRUE)
eip_pt_male_sex <- select(eip_pt_male_sex, age_category, sex)
eip_pt_female_sex <- eip_pt %>% filter(sex == "Female", na.rm = TRUE)
eip_pt_female_sex <- select(eip_pt_female_sex, age_category, sex)
eip_pt_unk_sex <- eip_pt %>% filter(sex == "Unknown", na.rm = TRUE)
eip_pt_unk_sex <- select(eip_pt_unk_sex, age_category, sex)

pt_age_cat_sex <- plot_ly(alpha = 0.5) %>%
  add_histogram(x = ~eip_pt_male_sex$age_category,
                name = "Male",
                xbins = list(size = 1)) %>% 
  add_histogram(x = ~eip_pt_female_sex$age_category,
                name = "Female",
                xbins = list(size = 1)) %>%
  add_histogram(x = ~eip_pt_unk_sex$age_category,
                name = "Unknown",
                xbins = list(size = 1)) %>% 
  layout(title = "Age Category based on Sex",
         xaxis = list(title = "Age Category",
                      zeroline = FALSE,
                      categoryorder = "array",
                      categoryarray = c("13-17", "18-24", "25-34", "35-44", "45-54", "55-64", "65+", "Unknown")),
         yaxis = list(title = "Count",
                      zeroline = FALSE))
pt_age_cat_sex

```

For an individual's gender identity, EIP staff allow the individual to self-report their current gender. This information is shown below in the chart and the subsequent table expressing the percentage of all EIP patients/clients.

```{r, layout="l-body-outset"}
pt_gender <- ggplot(eip_pt, aes(x = gender))  
pt_gender <-  pt_gender + geom_bar(fill = "lightblue") + theme_classic()

ggplotly(pt_gender)


pt_gender_tbl <- table(eip_pt$gender)
pt_sex_tbl_perc <- eip_pt %>%
  group_by(gender) %>%
  summarise(Percent = n()/nrow(.)*100)
pt_sex_tbl_perc <- as.data.frame(pt_sex_tbl_perc)
pt_sex_tbl_perc <- na.omit(pt_sex_tbl_perc)
pt_sex_tbl_perc$Percent <- round(pt_sex_tbl_perc$Percent, digits = 0)
pt_sex_tbl_perc <- spread(pt_sex_tbl_perc, gender, Percent)
pt_gender_tbl <- rbind(pt_gender_tbl, pt_sex_tbl_perc)
pt_gender_tbl$Data <- c("Total", "Percent (%)")
pt_gender_tbl <- pt_gender_tbl[, c(5, 1, 2, 3, 4)]

pt_gender_tbl %>%
  reactable()

```

The following chart allows for the ability to filter the individual's age category based on their self-reported gender identity.

```{r}
eip_pt_male_gender <- eip_pt %>% filter(gender == "Male", na.rm = TRUE)
eip_pt_male_gender <- select(eip_pt_male_gender, age_category, gender)
eip_pt_female_gender <- eip_pt %>% filter(gender == "Female", na.rm = TRUE)
eip_pt_female_gender <- select(eip_pt_female_gender, age_category, gender)
eip_pt_trans_gender <- eip_pt %>% filter(gender == "Unknown", na.rm = TRUE)
eip_pt_trans_gender <- select(eip_pt_trans_gender, age_category, gender)
eip_pt_unk_gender <- eip_pt %>% filter(gender == "Unknown", na.rm = TRUE)
eip_pt_unk_gender <- select(eip_pt_unk_gender, age_category, gender)

pt_age_cat_gender <- plot_ly(alpha = 0.5) %>%
  add_histogram(x = ~eip_pt_male_gender$age_category,
                name = "Male",
                xbins = list(size = 1)) %>% 
  add_histogram(x = ~eip_pt_female_gender$age_category,
                name = "Female",
                xbins = list(size = 1)) %>%
  add_histogram(x = ~eip_pt_trans_gender$age_category,
                name = "Transgender/Nonbinary",
                xbins = list(size = 1)) %>%
  add_histogram(x = ~eip_pt_unk_gender$age_category,
                name = "Unknown",
                xbins = list(size = 1)) %>% 
  layout(title = "Age Category based on Gender",
         xaxis = list(title = "Age Category",
                      zeroline = FALSE,
                      categoryorder = "array",
                      categoryarray = c("13-17", "18-24", "25-34", "35-44", "45-54", "55-64", "65+", "Unknown")),
         yaxis = list(title = "Count",
                      zeroline = FALSE))
pt_age_cat_gender

```



## Race and Ethnicity

Placeholder for data on race and ethnicity data

## Insurance Coverage

Placeholder for data on insurance coverage.

## Populations of Interest

Placeholder for data on populations of interest.
