---
title: "Hepatitis C Virus (HCV)"
lightbox:
  match: auto
format:
  html: 
    grid:
      sidebar-width: 200px
      body-width: 1050px
      margin-width: 250px
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r Data, include=FALSE}

rm(list=ls(all=T))

library(dplyr)
library(tidyverse)
library(stringr)
library(plotly)
library(kableExtra)
library(reactable)
library(scales)
library(shinydashboard)
library(ggplot2)
library(lubridate)
library(forcats)
library(htmltools)
library(hrbrthemes)
library(janitor)
library(apyramid)


# EIP Database Data
eip <- read.csv('M:/EIP Data/EIP Database/REDCap 2024/EIP Database Data 20241104_0955.csv')
dim(eip)

# HCV Epic Dashboard Data
hcv_jan24 <- read.csv('M:/EIP Data/External Data Sources/Epic Data/HCV Dashboard/Monthly Data/HCV Dashboard Data 01_2024.csv')
dim(hcv_jan24)
hcv_feb24 <- read.csv('M:/EIP Data/External Data Sources/Epic Data/HCV Dashboard/Monthly Data/HCV Dashboard Data 02_2024.csv')
dim(hcv_feb24)
hcv_mar24 <- read.csv('M:/EIP Data/External Data Sources/Epic Data/HCV Dashboard/Monthly Data/HCV Dashboard Data 03_2024.csv')
dim(hcv_mar24)
hcv_apr24 <- read.csv('M:/EIP Data/External Data Sources/Epic Data/HCV Dashboard/Monthly Data/HCV Dashboard Data 04_2024.csv')
dim(hcv_apr24)
hcv_may24 <- read.csv('M:/EIP Data/External Data Sources/Epic Data/HCV Dashboard/Monthly Data/HCV Dashboard Data 05_2024.csv')
dim(hcv_may24)
hcv_jun24 <- read.csv('M:/EIP Data/External Data Sources/Epic Data/HCV Dashboard/Monthly Data/HCV Dashboard Data 06_2024.csv')
dim(hcv_jun24)
hcv_jul24 <- read.csv('M:/EIP Data/External Data Sources/Epic Data/HCV Dashboard/Monthly Data/HCV Dashboard Data 07_2024.csv')
dim(hcv_jul24)
hcv_aug24 <- read.csv('M:/EIP Data/External Data Sources/Epic Data/HCV Dashboard/Monthly Data/HCV Dashboard Data 08_2024.csv')
dim(hcv_aug24)
hcv_sep24 <- read.csv('M:/EIP Data/External Data Sources/Epic Data/HCV Dashboard/Monthly Data/HCV Dashboard Data 09_2024.csv')
dim(hcv_sep24)
hcv_oct24 <- read.csv('M:/EIP Data/External Data Sources/Epic Data/HCV Dashboard/Monthly Data/HCV Dashboard Data 10_2024.csv')
dim(hcv_oct24)
hcv_nov24 <- read.csv('M:/EIP Data/External Data Sources/Epic Data/HCV Dashboard/Monthly Data/HCV Dashboard Data 11_2024.csv')
dim(hcv_nov24)

hcv <- rbind(hcv_jan24, hcv_feb24, hcv_mar24, hcv_apr24, hcv_may24, hcv_jun24,
             hcv_jul24, hcv_aug24, hcv_sep24, hcv_oct24, hcv_nov24)
dim(hcv)
hcv <- distinct(hcv)
dim(hcv)
head(hcv)

```

```{r HCV Dashboard, include=FALSE}

# Separating the MRN into a separate column

hcv$Patient.Name..MRN. <- iconv(hcv$Patient.Name..MRN., to = "UTF-8", sub = "byte")
hcv$Patient.Name..MRN. <- enc2utf8(hcv$Patient.Name..MRN.)
mrn_loc <- nchar(hcv$Patient.Name..MRN., type = "bytes") - 7
hcv$mrn <- substr(hcv$Patient.Name..MRN., mrn_loc, mrn_loc + 6)
head(hcv)


# Removing variables that are not needed
hcv <- select(hcv, mrn, Order.ID, Order.Date, Order.Time, Order.Status, Lab.Status, Last.Lab.Results)
head(hcv)


# Filtering to only include Completed tests and those from UCMC ED
table(hcv$Order.Status)
hcv <- hcv[which(hcv$Order.Status == 'Completed'), ]
dim(hcv)
table(hcv$Lab.Status)
hcv <- hcv[which(hcv$Lab.Status == 'Final result' |
                   hcv$Lab.Status == 'Edited Result - FINAL'), ]
dim(hcv)
head(hcv)
hcv <- select(hcv, -Order.Status, -Lab.Status)
head(hcv)


# Renaming variables
colnames(hcv)[2] <- 'order_id'
colnames(hcv)[3] <- 'order_date'
colnames(hcv)[4] <- 'order_time'
colnames(hcv)[5] <- 'lab_result'
head(hcv)


# Creating Ab and RNA variables
table(hcv$lab_result)

hcv$hcv_ab_result[str_detect(hcv$lab_result, "HCV Ab: Nonreactive")] <- 0
hcv$hcv_ab_result[str_detect(hcv$lab_result, "HCV Ab: NONREACTIVE")] <- 0
hcv$hcv_ab_result[str_detect(hcv$lab_result, "HCV Ab: Reactive")] <- 1
hcv$hcv_ab_result[str_detect(hcv$lab_result, "HCV Ab: REACTIVE")] <- 1
hcv$hcv_ab_result[is.na(hcv$hcv_ab_result) |
                    str_detect(hcv$lab_result, "HCV Ab: CANCELED")] <- ''
table(hcv$hcv_ab_result)
head(hcv)


hcv$hcv_rna_result[str_detect(hcv$lab_result, "International Units: Not Detected")] <- 0
hcv$hcv_rna_result[str_detect(hcv$lab_result, "International Units: <15")] <- 0
hcv$hcv_rna_result[str_detect(hcv$lab_result, "International Units:") &
                     is.na(hcv$hcv_rna_result)] <- 1
hcv$hcv_rna_result[is.na(hcv$hcv_rna_result)] <- ''
table(hcv$hcv_rna_result)
head(hcv)


hcv <- select(hcv, -lab_result)
head(hcv)
dim(hcv)
hcv <- distinct(hcv)
dim(hcv)


# Creating variables for total number of daily tests

hcv$hcv_ab_tested[hcv$hcv_ab_result == 0 | hcv$hcv_ab_result == 1] <- 1
hcv$hcv_ab_tested[is.na(hcv$hcv_ab_tested)] <- 0
table(hcv$hcv_ab_tested)
hcv_ab_tested <- hcv[which(hcv$hcv_ab_tested == 1), ]
hcv_ab_tested <- nrow(hcv_ab_tested)
hcv_ab_tested

hcv$hcv_rna_tested[hcv$hcv_rna_result == 0 | hcv$hcv_rna_result == 1] <- 1
hcv$hcv_rna_tested[is.na(hcv$hcv_rna_tested)] <- 0
table(hcv$hcv_rna_tested)
hcv_rna_tested <- hcv[which(hcv$hcv_rna_tested == 1), ]
hcv_rna_tested <- nrow(hcv_rna_tested)
hcv_rna_tested

hcv$hcv_ab_positive[hcv$hcv_ab_result == 1] <- 1
hcv$hcv_ab_positive[is.na(hcv$hcv_ab_positive)] <- 0
table(hcv$hcv_ab_positive)
hcv_ab_positive <- hcv[which(hcv$hcv_ab_positive == 1), ]
hcv_ab_positive <- nrow(hcv_ab_positive)
hcv_ab_positive

hcv_ab_positivity_rate <- percent(hcv_ab_positive/hcv_ab_tested, accuracy = 0.01)
hcv_ab_positivity_rate

hcv$hcv_rna_positive[hcv$hcv_rna_result == 1] <- 1
hcv$hcv_rna_positive[is.na(hcv$hcv_rna_positive)] <- 0
table(hcv$hcv_rna_positive)
hcv_rna_positive <- hcv[which(hcv$hcv_rna_positive == 1), ]
hcv_rna_positive <- nrow(hcv_rna_positive)
hcv_rna_positive

head(hcv)


# Sorting HCV dataset

hcv$order_date <- as.Date(hcv$order_date, format = '%m/%d/%Y')
head(hcv)

# Calculate number of negative tests
hcv <- mutate(hcv, hcv_ab_negative = hcv_ab_tested - hcv_ab_positive)
hcv <- hcv[order(hcv$order_date), ]
head(hcv)

# Aggregate data by order_date
daily_hcv_tests <- hcv %>%
  group_by(order_date) %>%
  summarise(total_tests = sum(hcv_ab_tested),
            total_positive = sum(hcv_ab_positive),
            total_negative = sum(hcv_ab_negative))

hcv <- hcv %>%
  mutate(monthly_date = floor_date(order_date, "month"))
monthly_hcv_tests <- hcv %>%
  group_by(monthly_date) %>%
  summarise(total_tests = sum(hcv_ab_tested),
            total_positive = sum(hcv_ab_positive),
            total_negative = sum(hcv_ab_negative))



# Unique patients

hcv_pts <- select(hcv, mrn)
dim(hcv_pts)
hcv_pts <- distinct(hcv_pts)
dim(hcv_pts)



table(hcv$hcv_ab_tested)
hcv_pts_ab_tested <- hcv[which(hcv$hcv_ab_tested == 1), ]
dim(hcv_pts_ab_tested)
head(hcv_pts_ab_tested)
hcv_pts_ab_tested <- select(hcv_pts_ab_tested, mrn, hcv_ab_tested)
head(hcv_pts_ab_tested)
dim(hcv_pts_ab_tested)
hcv_pts_ab_tested <- distinct(hcv_pts_ab_tested)
dim(hcv_pts_ab_tested)

dim(hcv_pts)
dim(hcv_pts_ab_tested)
hcv_pts <- merge(hcv_pts, hcv_pts_ab_tested, by = 'mrn', all.x = T)
dim(hcv_pts)
head(hcv_pts)



table(hcv$hcv_ab_positive)
hcv_pts_ab_positive <- hcv[which(hcv$hcv_ab_positive == 1), ]
dim(hcv_pts_ab_positive)
head(hcv_pts_ab_positive)
hcv_pts_ab_positive <- select(hcv_pts_ab_positive, mrn, hcv_ab_positive)
head(hcv_pts_ab_positive)
dim(hcv_pts_ab_positive)
hcv_pts_ab_positive <- distinct(hcv_pts_ab_positive)
dim(hcv_pts_ab_positive)

dim(hcv_pts)
dim(hcv_pts_ab_positive)
hcv_pts <- merge(hcv_pts, hcv_pts_ab_positive, by = 'mrn', all.x = T)
dim(hcv_pts)
head(hcv_pts)



#####################################################################################################
############################################  EIP Data  #############################################
#####################################################################################################


### Person-level data is only visit_001_arm_1, use to match to encounters

table(eip$redcap_event_name)
person <- eip[which(eip$redcap_event_name == 'visit_001_arm_1'), ]
dim(person)

person <- select(person, record_id, mrn, dob, 
                 race___1, race___2, race___3, race___4, race___5, race___6, ethnicity,
                 sex_raised, sex_selfdefined)
dim(person)

eip <- select(eip, -mrn, -dob, 
              -race___1, -race___2, -race___3, -race___4, -race___5, 
              -race___6, -ethnicity,
              -sex_raised, -sex_selfdefined)

# Merge person dataset with full eip dataset

dim(eip)
dim(person)
eip <- merge(eip, person, by = 'record_id', all.x=T)
dim(eip)
eip <- distinct(eip)
dim(eip)




# EIP HCV Dashboard Follow-up

eip_hcv <- select(eip, mrn, ltc_hcv_dashboard, ltc_hcv_initial_contact, hcv_rna_result,
                  ltc_hcv_referral_uc_pharmacy___2, ltc_hcv_referral_uc_pharmacy___3,
                  ltc_hcv_referral_uc_pharmacy_telehealth, ltc_hcv_final_ltc_status,
                  ltc_hcv_declined_rsn___23, ltc_hcv_declined_rsn___27, ltc_hcv_declined_rsn___3,
                  ltc_hcv_declined_rsn___5, ltc_hcv_declined_rsn___6, ltc_hcv_declined_rsn___7,
                  ltc_hcv_declined_rsn___8, ltc_hcv_declined_rsn___9, ltc_hcv_declined_rsn___10,
                  ltc_hcv_declined_rsn___28, ltc_hcv_declined_rsn___29, ltc_hcv_declined_rsn___30,
                  ltc_hcv_declined_rsn___33, ltc_hcv_declined_rsn___25, ltc_hcv_declined_rsn___34,
                  ltc_hcv_declined_rsn___35, ltc_hcv_declined_rsn___0, ltc_hcv_prevented_rsn___1,
                  ltc_hcv_prevented_rsn___2, ltc_hcv_prevented_rsn___11, ltc_hcv_prevented_rsn___3,
                  ltc_hcv_prevented_rsn___4, ltc_hcv_prevented_rsn___5, ltc_hcv_prevented_rsn___6,
                  ltc_hcv_prevented_rsn___8, ltc_hcv_prevented_rsn___9, ltc_hcv_prevented_rsn___12,
                  ltc_hcv_prevented_rsn___19, ltc_hcv_prevented_rsn___20, ltc_hcv_prevented_rsn___15,
                  ltc_hcv_prevented_rsn___16, ltc_hcv_prevented_rsn___17, ltc_hcv_prevented_rsn___18,
                  ltc_hcv_prevented_rsn___0, ltc_hcv_open_case_calc, ltc_services___2)
dim(eip_hcv)
head(eip_hcv)


# Creating main dataset to match everything back to

eip_hcv_main <- select(eip_hcv, mrn)
dim(eip_hcv_main)
eip_hcv_main$exclude[is.na(eip_hcv_main$mrn)] <- 1
table(eip_hcv_main$exclude)
eip_hcv_main <- eip_hcv_main[which(is.na(eip_hcv_main$exclude)), ]
dim(eip_hcv_main)
eip_hcv_main <- select(eip_hcv_main, mrn)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)

# Creating EIP variable to know if there are EIP records for each dashboard patient
eip_hcv_main$eip_record <- 1
head(eip_hcv_main)




# HCV RNA Results

table(eip_hcv$hcv_rna_result)
hcv_rna_known <- eip_hcv[which(eip_hcv$hcv_rna_result == 1 |
                                 eip_hcv$hcv_rna_result == 2), ]
hcv_rna_known <- select(hcv_rna_known, mrn)
head(hcv_rna_known)
dim(hcv_rna_known)
hcv_rna_known <- distinct(hcv_rna_known)
dim(hcv_rna_known)
hcv_rna_known$hcv_rna_known <- 1

dim(hcv_rna_known)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_rna_known, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_rna_known)



table(eip_hcv$hcv_rna_result)
hcv_rna_pos <- eip_hcv[which(eip_hcv$hcv_rna_result == 1), ]
hcv_rna_pos <- select(hcv_rna_pos, mrn)
head(hcv_rna_pos)
dim(hcv_rna_pos)
hcv_rna_pos <- distinct(hcv_rna_pos)
dim(hcv_rna_pos)
hcv_rna_pos$hcv_rna_pos <- 1

dim(hcv_rna_pos)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_rna_pos, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_rna_pos)



table(eip_hcv$hcv_rna_result)
hcv_rna_neg <- eip_hcv[which(eip_hcv$hcv_rna_result == 2), ]
hcv_rna_neg <- select(hcv_rna_neg, mrn)
head(hcv_rna_neg)
dim(hcv_rna_neg)
hcv_rna_neg <- distinct(hcv_rna_neg)
dim(hcv_rna_neg)
hcv_rna_neg$hcv_rna_neg <- 1

dim(hcv_rna_neg)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_rna_neg, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_rna_neg)




# Followed-up (ED or In Hospital)
## For those HCV RNA Negative - only follow-up in ED
## For all other HCV Ab+ - follow-up in ED or Phone


# HCV RNA Negative Follow-up

table(eip_hcv$hcv_rna_result, eip_hcv$ltc_hcv_dashboard)
hcv_rna_neg_fu <- eip_hcv[which(eip_hcv$hcv_rna_result == 2 & eip_hcv$ltc_hcv_dashboard == 1), ]
hcv_rna_neg_fu <- select(hcv_rna_neg_fu, mrn)
head(hcv_rna_neg_fu)
dim(hcv_rna_neg_fu)
hcv_rna_neg_fu <- distinct(hcv_rna_neg_fu)
dim(hcv_rna_neg_fu)
hcv_rna_neg_fu$hcv_rna_neg_fu <- 1

dim(hcv_rna_neg_fu)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_rna_neg_fu, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_rna_neg_fu)


table(eip_hcv$hcv_rna_result, eip_hcv$ltc_hcv_initial_contact)
hcv_rna_neg_fu_ed <- eip_hcv[which(eip_hcv$hcv_rna_result == 2 &
                                     eip_hcv$ltc_hcv_dashboard == 1 &
                                     eip_hcv$ltc_hcv_initial_contact == 1), ]
hcv_rna_neg_fu_ed <- select(hcv_rna_neg_fu_ed, mrn)
head(hcv_rna_neg_fu_ed)
dim(hcv_rna_neg_fu_ed)
hcv_rna_neg_fu_ed <- distinct(hcv_rna_neg_fu_ed)
dim(hcv_rna_neg_fu_ed)
hcv_rna_neg_fu_ed$hcv_rna_neg_fu_ed <- 1

dim(hcv_rna_neg_fu_ed)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_rna_neg_fu_ed, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_rna_neg_fu_ed)



# HCV Ab+ but not RNA Negative needing Follow-up

table(eip_hcv$hcv_rna_result, eip_hcv$ltc_hcv_dashboard)
eip_hcv$hcv_fu_needed[eip_hcv$hcv_rna_result != 2] <- 1
table(eip_hcv$hcv_fu_needed)
hcv_fu_needed <- eip_hcv[which(eip_hcv$hcv_fu_needed == 1), ]
hcv_fu_needed <- select(hcv_fu_needed, mrn)
head(hcv_fu_needed)
dim(hcv_fu_needed)
hcv_fu_needed <- distinct(hcv_fu_needed)
dim(hcv_fu_needed)
hcv_fu_needed$hcv_fu_needed <- 1

dim(hcv_fu_needed)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_fu_needed, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_fu_needed)



table(eip_hcv$hcv_fu_needed, eip_hcv$ltc_hcv_dashboard)
hcv_no_edu <- eip_hcv[which(eip_hcv$hcv_fu_needed == 1 & eip_hcv$ltc_hcv_dashboard == 0), ]
hcv_no_edu <- select(hcv_no_edu, mrn)
head(hcv_no_edu)
dim(hcv_no_edu)
hcv_no_edu <- distinct(hcv_no_edu)
dim(hcv_no_edu)
hcv_no_edu$hcv_no_education <- 1

dim(hcv_no_edu)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_no_edu, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_no_education)



table(eip_hcv$hcv_fu_needed, eip_hcv$ltc_hcv_dashboard)
hcv_edu <- eip_hcv[which(eip_hcv$hcv_fu_needed == 1 & eip_hcv$ltc_hcv_dashboard == 1), ]
hcv_edu <- select(hcv_edu, mrn)
head(hcv_edu)
dim(hcv_edu)
hcv_edu <- distinct(hcv_edu)
dim(hcv_edu)
hcv_edu$hcv_education <- 1

dim(hcv_edu)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_edu, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_education)



table(eip_hcv$hcv_fu_needed, eip_hcv$ltc_hcv_initial_contact)
hcv_edu_ed <- eip_hcv[which(eip_hcv$hcv_fu_needed == 1 &
                              eip_hcv$ltc_hcv_dashboard == 1 &
                              eip_hcv$ltc_hcv_initial_contact == 1), ]
hcv_edu_ed <- select(hcv_edu_ed, mrn)
head(hcv_edu_ed)
dim(hcv_edu_ed)
hcv_edu_ed <- distinct(hcv_edu_ed)
dim(hcv_edu_ed)
hcv_edu_ed$hcv_education_ed <- 1

dim(hcv_edu_ed)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_edu_ed, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_education_ed)



table(eip_hcv$hcv_fu_needed, eip_hcv$ltc_hcv_initial_contact)
hcv_edu_phone <- eip_hcv[which(eip_hcv$hcv_fu_needed == 1 &
                                 eip_hcv$ltc_hcv_dashboard == 1 &
                                 eip_hcv$ltc_hcv_initial_contact == 2), ]
hcv_edu_phone <- select(hcv_edu_phone, mrn)
head(hcv_edu_phone)
dim(hcv_edu_phone)
hcv_edu_phone <- distinct(hcv_edu_phone)
dim(hcv_edu_phone)
hcv_edu_phone$hcv_education_phone <- 1

dim(hcv_edu_phone)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_edu_phone, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_education_phone)



table(eip_hcv$hcv_fu_needed, eip_hcv$ltc_hcv_initial_contact)
hcv_edu_other <- eip_hcv[which(eip_hcv$hcv_fu_needed == 1 &
                                 eip_hcv$ltc_hcv_dashboard == 1 &
                                 eip_hcv$ltc_hcv_initial_contact == 3), ]
hcv_edu_other <- select(hcv_edu_other, mrn)
head(hcv_edu_other)
dim(hcv_edu_other)
hcv_edu_other <- distinct(hcv_edu_other)
dim(hcv_edu_other)
hcv_edu_other$hcv_education_other <- 1

dim(hcv_edu_other)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_edu_other, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_education_other)



# HCV Linkage

eip_hcv$hcv_linked[eip_hcv$ltc_hcv_referral_uc_pharmacy___2 == 1 | eip_hcv$ltc_hcv_referral_uc_pharmacy___3 == 1] <- 1
hcv_linked <- eip_hcv[which(eip_hcv$hcv_linked == 1), ]
hcv_linked <- select(hcv_linked, mrn)
head(hcv_linked)
dim(hcv_linked)

if (nrow(hcv_linked) > 0) {
  hcv_linked <- select(hcv_linked, mrn)
  hcv_linked <- distinct(hcv_linked)
  hcv_linked$hcv_linked <- 1
} else {
  hcv_linked <- data.frame()
  empty_row <- data.frame(mrn = NA, hcv_linked = NA)
  hcv_linked <- rbind(hcv_linked, empty_row)
}
dim(hcv_linked)
head(hcv_linked)

dim(hcv_linked)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_linked, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_linked)



hcv_linked_other <- eip_hcv[which(eip_hcv$ltc_hcv_final_ltc_status == 1 & is.na(eip_hcv$hcv_linked)), ]
hcv_linked_other <- select(hcv_linked_other, mrn)
head(hcv_linked_other)
dim(hcv_linked_other)

if (nrow(hcv_linked_other) > 0) {
  hcv_linked_other <- select(hcv_linked_other, mrn)
  hcv_linked_other <- distinct(hcv_linked_other)
  hcv_linked_other$hcv_linked_other <- 1
} else {
  hcv_linked_other <- data.frame()
  empty_row <- data.frame(mrn = NA, hcv_linked_other = NA)
  hcv_linked_other <- rbind(hcv_linked_other, empty_row)
}
dim(hcv_linked_other)
head(hcv_linked_other)

dim(hcv_linked_other)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_linked_other, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_linked_other)


###  Reasons unable to follow-up

# Ineligible HCV Linkage - Already Linked

table(eip_hcv$ltc_hcv_declined_rsn___23)
table(eip_hcv$ltc_hcv_prevented_rsn___16)
eip_hcv$hcv_dash_already_linked[eip_hcv$ltc_hcv_declined_rsn___23 == 1 |
                                  eip_hcv$ltc_hcv_prevented_rsn___16 == 1] <- 1
table(eip_hcv$hcv_dash_already_linked)
hcv_dash_already_linked <- eip_hcv[which(eip_hcv$hcv_dash_already_linked == 1), ]
hcv_dash_already_linked <- select(hcv_dash_already_linked, mrn)
head(hcv_dash_already_linked)
dim(hcv_dash_already_linked)
hcv_dash_already_linked <- distinct(hcv_dash_already_linked)
dim(hcv_dash_already_linked)
hcv_dash_already_linked$hcv_dash_already_linked <- 1

dim(hcv_dash_already_linked)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_dash_already_linked, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_dash_already_linked)
table(eip_hcv_main$hcv_no_education, eip_hcv_main$hcv_dash_already_linked)
hcv_dash_already_linked <- eip_hcv_main[which(eip_hcv_main$hcv_no_education == 1 &
                                                eip_hcv_main$hcv_dash_already_linked == 1), ]
dim(hcv_dash_already_linked)
hcv_dash_already_linked <- nrow(hcv_dash_already_linked)
hcv_dash_already_linked


# Ineligible HCV Linkage - Deceased

table(eip_hcv$ltc_hcv_declined_rsn___35)
table(eip_hcv$ltc_hcv_prevented_rsn___17)
eip_hcv$hcv_dash_deceased[eip_hcv$ltc_hcv_declined_rsn___35 == 1 |
                            eip_hcv$ltc_hcv_prevented_rsn___17 == 1] <- 1
table(eip_hcv$hcv_dash_deceased)
hcv_dash_deceased <- eip_hcv[which(eip_hcv$hcv_dash_deceased == 1), ]
hcv_dash_deceased <- select(hcv_dash_deceased, mrn)
head(hcv_dash_deceased)
dim(hcv_dash_deceased)
hcv_dash_deceased <- distinct(hcv_dash_deceased)
dim(hcv_dash_deceased)
hcv_dash_deceased$hcv_dash_deceased <- 1

dim(hcv_dash_deceased)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_dash_deceased, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_dash_deceased)
table(eip_hcv_main$hcv_no_education, eip_hcv_main$hcv_dash_deceased)
hcv_dash_deceased <- eip_hcv_main[which(eip_hcv_main$hcv_no_education == 1 &
                                                eip_hcv_main$hcv_dash_deceased == 1), ]
dim(hcv_dash_deceased)
hcv_dash_deceased <- nrow(hcv_dash_deceased)
hcv_dash_deceased


# Ineligible HCV Linkage - Incarcerated

table(eip_hcv$ltc_hcv_prevented_rsn___12)
eip_hcv$hcv_dash_incarcerated[eip_hcv$ltc_hcv_prevented_rsn___12 == 1] <- 1
table(eip_hcv$hcv_dash_incarcerated)
hcv_dash_incarcerated <- eip_hcv[which(eip_hcv$hcv_dash_incarcerated == 1), ]
hcv_dash_incarcerated <- select(hcv_dash_incarcerated, mrn)
head(hcv_dash_incarcerated)
dim(hcv_dash_incarcerated)
hcv_dash_incarcerated <- distinct(hcv_dash_incarcerated)
dim(hcv_dash_incarcerated)
hcv_dash_incarcerated$hcv_dash_incarcerated <- 1

dim(hcv_dash_incarcerated)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_dash_incarcerated, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_dash_incarcerated)
table(eip_hcv_main$hcv_no_education, eip_hcv_main$hcv_dash_incarcerated)
hcv_dash_incarcerated <- eip_hcv_main[which(eip_hcv_main$hcv_no_education == 1 &
                                          eip_hcv_main$hcv_dash_incarcerated == 1), ]
dim(hcv_dash_incarcerated)
hcv_dash_incarcerated <- nrow(hcv_dash_incarcerated)
hcv_dash_incarcerated


# Ineligible HCV Linkage - Inability to Contact

table(eip_hcv$ltc_hcv_prevented_rsn___19)
eip_hcv$hcv_dash_inability_to_contact[eip_hcv$ltc_hcv_prevented_rsn___19 == 1] <- 1
table(eip_hcv$hcv_dash_inability_to_contact)
hcv_dash_inability_to_contact <- eip_hcv[which(eip_hcv$hcv_dash_inability_to_contact == 1), ]
hcv_dash_inability_to_contact <- select(hcv_dash_inability_to_contact, mrn)
head(hcv_dash_inability_to_contact)
dim(hcv_dash_inability_to_contact)
hcv_dash_inability_to_contact <- distinct(hcv_dash_inability_to_contact)
dim(hcv_dash_inability_to_contact)
hcv_dash_inability_to_contact$hcv_dash_inability_to_contact <- 1

dim(hcv_dash_inability_to_contact)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_dash_inability_to_contact, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_dash_inability_to_contact)
table(eip_hcv_main$hcv_no_education, eip_hcv_main$hcv_dash_inability_to_contact)
hcv_dash_inability_to_contact <- eip_hcv_main[which(eip_hcv_main$hcv_no_education == 1 &
                                          eip_hcv_main$hcv_dash_inability_to_contact == 1), ]
dim(hcv_dash_inability_to_contact)
hcv_dash_inability_to_contact <- nrow(hcv_dash_inability_to_contact)
hcv_dash_inability_to_contact


# Ineligible HCV Linkage - Declined Linkage Service

eip_hcv$hcv_dash_linkage_declined[eip_hcv$ltc_hcv_final_ltc_status == 2 &
                                    (is.na(eip_hcv$hcv_dash_already_linked) &
                                       is.na(eip_hcv$hcv_dash_deceased) &
                                       is.na(eip_hcv$hcv_dash_incarcerated) &
                                       is.na(eip_hcv$hcv_dash_inability_to_contact))] <- 1
table(eip_hcv$hcv_dash_linkage_declined)
hcv_dash_linkage_declined <- eip_hcv[which(eip_hcv$hcv_dash_linkage_declined == 1), ]
hcv_dash_linkage_declined <- select(hcv_dash_linkage_declined, mrn)
head(hcv_dash_linkage_declined)
dim(hcv_dash_linkage_declined)
hcv_dash_linkage_declined <- distinct(hcv_dash_linkage_declined)
dim(hcv_dash_linkage_declined)
hcv_dash_linkage_declined$hcv_dash_linkage_declined <- 1

dim(hcv_dash_linkage_declined)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_dash_linkage_declined, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_dash_linkage_declined)
table(eip_hcv_main$hcv_no_education, eip_hcv_main$hcv_dash_linkage_declined)
hcv_dash_linkage_declined <- eip_hcv_main[which(eip_hcv_main$hcv_no_education == 1 &
                                          eip_hcv_main$hcv_dash_linkage_declined == 1), ]
dim(hcv_dash_linkage_declined)
hcv_dash_linkage_declined <- nrow(hcv_dash_linkage_declined)
hcv_dash_linkage_declined


# Ineligible HCV Linkage - Linkage in Progress

table(eip_hcv$ltc_hcv_prevented_rsn___18)
eip_hcv$hcv_dash_ongoing_linkage[eip_hcv$ltc_hcv_prevented_rsn___18 == 1] <- 1
table(eip_hcv$hcv_dash_ongoing_linkage)
hcv_dash_ongoing_linkage <- eip_hcv[which(eip_hcv$hcv_dash_ongoing_linkage == 1), ]
hcv_dash_ongoing_linkage <- select(hcv_dash_ongoing_linkage, mrn)
head(hcv_dash_ongoing_linkage)
dim(hcv_dash_ongoing_linkage)
hcv_dash_ongoing_linkage <- distinct(hcv_dash_ongoing_linkage)
dim(hcv_dash_ongoing_linkage)
hcv_dash_ongoing_linkage$hcv_dash_ongoing_linkage <- 1

dim(hcv_dash_ongoing_linkage)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_dash_ongoing_linkage, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_dash_ongoing_linkage)
table(eip_hcv_main$hcv_no_education, eip_hcv_main$hcv_dash_ongoing_linkage)
hcv_dash_ongoing_linkage <- eip_hcv_main[which(eip_hcv_main$hcv_no_education == 1 &
                                          eip_hcv_main$hcv_dash_ongoing_linkage == 1), ]
dim(hcv_dash_ongoing_linkage)
hcv_dash_ongoing_linkage <- nrow(hcv_dash_ongoing_linkage)
hcv_dash_ongoing_linkage


# HCV Open/Closed Cases

table(eip_hcv$ltc_hcv_open_case_calc)
eip_hcv$hcv_dash_in_progress[eip_hcv$ltc_hcv_open_case_calc == 1] <- 1
table(eip_hcv$hcv_dash_in_progress)
hcv_dash_in_progress <- eip_hcv[which(eip_hcv$hcv_dash_in_progress == 1), ]
hcv_dash_in_progress <- select(hcv_dash_in_progress, mrn)
head(hcv_dash_in_progress)
dim(hcv_dash_in_progress)
hcv_dash_in_progress <- distinct(hcv_dash_in_progress)
dim(hcv_dash_in_progress)
hcv_dash_in_progress$hcv_dash_in_progress <- 1

dim(hcv_dash_in_progress)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_dash_in_progress, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_dash_in_progress)
table(eip_hcv_main$hcv_no_education, eip_hcv_main$hcv_dash_in_progress)
hcv_dash_in_progress <- eip_hcv_main[which(eip_hcv_main$hcv_no_education == 1 &
                                          eip_hcv_main$hcv_dash_in_progress == 1), ]
dim(hcv_dash_in_progress)
hcv_dash_in_progress <- nrow(hcv_dash_in_progress)
hcv_dash_in_progress


# HCV Reasons Not Linked to Care

eip_hcv$hcv_dash_not_linked_med_staff[eip_hcv$ltc_hcv_prevented_rsn___1 == 1 |
                                        eip_hcv$ltc_hcv_prevented_rsn___2 == 1 |
                                        eip_hcv$ltc_hcv_prevented_rsn___11 == 1] <- 1
table(eip_hcv$hcv_dash_not_linked_med_staff)
hcv_dash_not_linked_med_staff <- eip_hcv[which(eip_hcv$hcv_dash_not_linked_med_staff == 1), ]
hcv_dash_not_linked_med_staff <- select(hcv_dash_not_linked_med_staff, mrn)
head(hcv_dash_not_linked_med_staff)
dim(hcv_dash_not_linked_med_staff)
hcv_dash_not_linked_med_staff <- distinct(hcv_dash_not_linked_med_staff)
dim(hcv_dash_not_linked_med_staff)
hcv_dash_not_linked_med_staff$hcv_dash_not_linked_med_staff <- 1

dim(hcv_dash_not_linked_med_staff)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_dash_not_linked_med_staff, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_dash_not_linked_med_staff)
table(eip_hcv_main$hcv_no_education, eip_hcv_main$hcv_dash_not_linked_med_staff)
hcv_dash_not_linked_med_staff <- eip_hcv_main[which(eip_hcv_main$hcv_no_education == 1 &
                                          eip_hcv_main$hcv_dash_not_linked_med_staff == 1), ]
dim(hcv_dash_not_linked_med_staff)
hcv_dash_not_linked_med_staff <- nrow(hcv_dash_not_linked_med_staff)
hcv_dash_not_linked_med_staff



eip_hcv$hcv_dash_not_linked_family[eip_hcv$ltc_hcv_prevented_rsn___3 == 1] <- 1
table(eip_hcv$hcv_dash_not_linked_family)
hcv_dash_not_linked_family <- eip_hcv[which(eip_hcv$hcv_dash_not_linked_family == 1), ]
hcv_dash_not_linked_family <- select(hcv_dash_not_linked_family, mrn)
head(hcv_dash_not_linked_family)
dim(hcv_dash_not_linked_family)
hcv_dash_not_linked_family <- distinct(hcv_dash_not_linked_family)
dim(hcv_dash_not_linked_family)
hcv_dash_not_linked_family$hcv_dash_not_linked_family <- 1

dim(hcv_dash_not_linked_family)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_dash_not_linked_family, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_dash_not_linked_family)
table(eip_hcv_main$hcv_no_education, eip_hcv_main$hcv_dash_not_linked_family)
hcv_dash_not_linked_family <- eip_hcv_main[which(eip_hcv_main$hcv_no_education == 1 &
                                          eip_hcv_main$hcv_dash_not_linked_family == 1), ]
dim(hcv_dash_not_linked_family)
hcv_dash_not_linked_family <- nrow(hcv_dash_not_linked_family)
hcv_dash_not_linked_family



eip_hcv$hcv_dash_not_linked_not_talking[eip_hcv$ltc_hcv_prevented_rsn___4 == 1] <- 1
table(eip_hcv$hcv_dash_not_linked_not_talking)
hcv_dash_not_linked_not_talking <- eip_hcv[which(eip_hcv$hcv_dash_not_linked_not_talking == 1), ]
hcv_dash_not_linked_not_talking <- select(hcv_dash_not_linked_not_talking, mrn)
head(hcv_dash_not_linked_not_talking)
dim(hcv_dash_not_linked_not_talking)
hcv_dash_not_linked_not_talking <- distinct(hcv_dash_not_linked_not_talking)
dim(hcv_dash_not_linked_not_talking)
hcv_dash_not_linked_not_talking$hcv_dash_not_linked_not_talking <- 1

dim(hcv_dash_not_linked_not_talking)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_dash_not_linked_not_talking, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_dash_not_linked_not_talking)
table(eip_hcv_main$hcv_no_education, eip_hcv_main$hcv_dash_not_linked_not_talking)
hcv_dash_not_linked_not_talking <- eip_hcv_main[which(eip_hcv_main$hcv_no_education == 1 &
                                          eip_hcv_main$hcv_dash_not_linked_not_talking == 1), ]
dim(hcv_dash_not_linked_not_talking)
hcv_dash_not_linked_not_talking <- nrow(hcv_dash_not_linked_not_talking)
hcv_dash_not_linked_not_talking



#eip_hcv$hcv_dash_not_linked_safety[eip_hcv$ltc_hcv_prevented_rsn___5 == 1] <- 1
#table(eip_hcv$hcv_dash_not_linked_safety)
#hcv_dash_not_linked_safety <- eip_hcv[which(eip_hcv$hcv_dash_not_linked_safety == 1), ]
#hcv_dash_not_linked_safety <- select(hcv_dash_not_linked_safety, mrn)
#head(hcv_dash_not_linked_safety)
#dim(hcv_dash_not_linked_safety)
#hcv_dash_not_linked_safety <- distinct(hcv_dash_not_linked_safety)
#dim(hcv_dash_not_linked_safety)
#hcv_dash_not_linked_safety$hcv_dash_not_linked_safety <- 1

#dim(hcv_dash_not_linked_safety)
#dim(eip_hcv_main)
#eip_hcv_main <- merge(eip_hcv_main, hcv_dash_not_linked_safety, by = 'mrn', all.x=T)
#dim(eip_hcv_main)
#eip_hcv_main <- distinct(eip_hcv_main)
#dim(eip_hcv_main)
#table(eip_hcv_main$hcv_dash_not_linked_safety)
#table(eip_hcv_main$hcv_no_education, eip_hcv_main$hcv_dash_not_linked_safety)
#hcv_dash_not_linked_safety <- eip_hcv_main[which(eip_hcv_main$hcv_no_education == 1 &
#                                          eip_hcv_main$hcv_dash_not_linked_safety == 1), ]
#dim(hcv_dash_not_linked_safety)
#hcv_dash_not_linked_safety <- nrow(hcv_dash_not_linked_safety)
#hcv_dash_not_linked_safety
hcv_dash_not_linked_safety <- 0



eip_hcv$hcv_dash_not_linked_medical[eip_hcv$ltc_hcv_prevented_rsn___6 == 1 |
                                      eip_hcv$ltc_hcv_prevented_rsn___8 == 1] <- 1
table(eip_hcv$hcv_dash_not_linked_medical)
hcv_dash_not_linked_medical <- eip_hcv[which(eip_hcv$hcv_dash_not_linked_medical == 1), ]
hcv_dash_not_linked_medical <- select(hcv_dash_not_linked_medical, mrn)
head(hcv_dash_not_linked_medical)
dim(hcv_dash_not_linked_medical)
hcv_dash_not_linked_medical <- distinct(hcv_dash_not_linked_medical)
dim(hcv_dash_not_linked_medical)
hcv_dash_not_linked_medical$hcv_dash_not_linked_medical <- 1

dim(hcv_dash_not_linked_medical)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_dash_not_linked_medical, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_dash_not_linked_medical)
table(eip_hcv_main$hcv_no_education, eip_hcv_main$hcv_dash_not_linked_medical)
hcv_dash_not_linked_medical <- eip_hcv_main[which(eip_hcv_main$hcv_no_education == 1 &
                                          eip_hcv_main$hcv_dash_not_linked_medical == 1), ]
dim(hcv_dash_not_linked_medical)
hcv_dash_not_linked_medical <- nrow(hcv_dash_not_linked_medical)
hcv_dash_not_linked_medical



eip_hcv$hcv_dash_not_linked_contact[eip_hcv$ltc_hcv_prevented_rsn___20 == 1] <- 1
table(eip_hcv$hcv_dash_not_linked_contact)
hcv_dash_not_linked_contact <- eip_hcv[which(eip_hcv$hcv_dash_not_linked_contact == 1), ]
hcv_dash_not_linked_contact <- select(hcv_dash_not_linked_contact, mrn)
head(hcv_dash_not_linked_contact)
dim(hcv_dash_not_linked_contact)
hcv_dash_not_linked_contact <- distinct(hcv_dash_not_linked_contact)
dim(hcv_dash_not_linked_contact)
hcv_dash_not_linked_contact$hcv_dash_not_linked_contact <- 1

dim(hcv_dash_not_linked_contact)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_dash_not_linked_contact, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_dash_not_linked_contact)
table(eip_hcv_main$hcv_no_education, eip_hcv_main$hcv_dash_not_linked_contact)
hcv_dash_not_linked_contact <- eip_hcv_main[which(eip_hcv_main$hcv_no_education == 1 &
                                          eip_hcv_main$hcv_dash_not_linked_contact == 1), ]
dim(hcv_dash_not_linked_contact)
hcv_dash_not_linked_contact <- nrow(hcv_dash_not_linked_contact)
hcv_dash_not_linked_contact



#eip_hcv$hcv_dash_not_linked_language[eip_hcv$ltc_hcv_prevented_rsn___9 == 1] <- 1
#table(eip_hcv$hcv_dash_not_linked_language)
#hcv_dash_not_linked_language <- eip_hcv[which(eip_hcv$hcv_dash_not_linked_language == 1), ]
#hcv_dash_not_linked_language <- select(hcv_dash_not_linked_language, mrn)
#head(hcv_dash_not_linked_language)
#dim(hcv_dash_not_linked_language)
#hcv_dash_not_linked_language <- distinct(hcv_dash_not_linked_language)
#dim(hcv_dash_not_linked_language)
#hcv_dash_not_linked_language$hcv_dash_not_linked_language <- 1

#dim(hcv_dash_not_linked_language)
#dim(eip_hcv_main)
#eip_hcv_main <- merge(eip_hcv_main, hcv_dash_not_linked_language, by = 'mrn', all.x=T)
#dim(eip_hcv_main)
#eip_hcv_main <- distinct(eip_hcv_main)
#dim(eip_hcv_main)
#table(eip_hcv_main$hcv_dash_not_linked_language)
#table(eip_hcv_main$hcv_no_education, eip_hcv_main$hcv_dash_not_linked_language)
#hcv_dash_not_linked_language <- eip_hcv_main[which(eip_hcv_main$hcv_no_education == 1 &
#                                          eip_hcv_main$hcv_dash_not_linked_language == 1), ]
#dim(hcv_dash_not_linked_language)
#hcv_dash_not_linked_language <- nrow(hcv_dash_not_linked_language)
#hcv_dash_not_linked_language
hcv_dash_not_linked_language <- 0



eip_hcv$hcv_dash_not_linked_other[eip_hcv$ltc_hcv_prevented_rsn___0 == 1] <- 1
table(eip_hcv$hcv_dash_not_linked_other)
hcv_dash_not_linked_other <- eip_hcv[which(eip_hcv$hcv_dash_not_linked_other == 1), ]
hcv_dash_not_linked_other <- select(hcv_dash_not_linked_other, mrn)
head(hcv_dash_not_linked_other)
dim(hcv_dash_not_linked_other)
hcv_dash_not_linked_other <- distinct(hcv_dash_not_linked_other)
dim(hcv_dash_not_linked_other)
hcv_dash_not_linked_other$hcv_dash_not_linked_other <- 1

dim(hcv_dash_not_linked_other)
dim(eip_hcv_main)
eip_hcv_main <- merge(eip_hcv_main, hcv_dash_not_linked_other, by = 'mrn', all.x=T)
dim(eip_hcv_main)
eip_hcv_main <- distinct(eip_hcv_main)
dim(eip_hcv_main)
table(eip_hcv_main$hcv_dash_not_linked_other)
table(eip_hcv_main$hcv_no_education, eip_hcv_main$hcv_dash_not_linked_other)
hcv_dash_not_linked_other <- eip_hcv_main[which(eip_hcv_main$hcv_no_education == 1 &
                                          eip_hcv_main$hcv_dash_not_linked_other == 1), ]
dim(hcv_dash_not_linked_other)
hcv_dash_not_linked_other <- nrow(hcv_dash_not_linked_other)
hcv_dash_not_linked_other




######################################################################################################
######################################################################################################
# Merging EIP REDCap Data with HCV Dashboard Data

head(hcv_pts)
head(eip_hcv_main)

dim(hcv_pts)
dim(eip_hcv_main)
hcv_pts <- merge(hcv_pts, eip_hcv_main, by = 'mrn', all.x = T)
dim(hcv_pts)
head(hcv_pts)



table(hcv_pts$hcv_ab_tested)
hcv_pts_ab_tested <- hcv_pts[which(hcv_pts$hcv_ab_tested == 1), ]
dim(hcv_pts_ab_tested)
head(hcv_pts_ab_tested)
hcv_pts_ab_tested <- select(hcv_pts_ab_tested, mrn)
head(hcv_pts_ab_tested)
dim(hcv_pts_ab_tested)
hcv_pts_ab_tested <- distinct(hcv_pts_ab_tested)
dim(hcv_pts_ab_tested)

hcv_pts_ab_tested <- nrow(hcv_pts_ab_tested)
hcv_pts_ab_tested



table(hcv_pts$hcv_ab_positive)
hcv_pts_ab_positive <- hcv_pts[which(hcv_pts$hcv_ab_positive == 1), ]
dim(hcv_pts_ab_positive)
head(hcv_pts_ab_positive)
hcv_pts_ab_positive <- select(hcv_pts_ab_positive, mrn)
head(hcv_pts_ab_positive)
dim(hcv_pts_ab_positive)
hcv_pts_ab_positive <- distinct(hcv_pts_ab_positive)
dim(hcv_pts_ab_positive)

hcv_pts_ab_positive <- nrow(hcv_pts_ab_positive)
hcv_pts_ab_positive
hcv_pts_ab_positive_percent <- percent(hcv_pts_ab_positive/hcv_pts_ab_tested, accuracy = 0.01)
hcv_pts_ab_positive_percent



table(hcv_pts$eip_record, hcv_pts$hcv_ab_positive)
no_eip_record_hcv_ab_pos <- hcv_pts[which(is.na(hcv_pts$eip_record) & hcv_pts$hcv_ab_positive == 1), ]
dim(no_eip_record_hcv_ab_pos)
head(no_eip_record_hcv_ab_pos)
no_eip_record_hcv_ab_pos <- select(no_eip_record_hcv_ab_pos, mrn)
head(no_eip_record_hcv_ab_pos)
dim(no_eip_record_hcv_ab_pos)
no_eip_record_hcv_ab_pos <- distinct(no_eip_record_hcv_ab_pos)
dim(no_eip_record_hcv_ab_pos)

no_eip_record_hcv_ab_pos <- nrow(no_eip_record_hcv_ab_pos)
no_eip_record_hcv_ab_pos
no_eip_record_hcv_ab_pos_percent <- percent(no_eip_record_hcv_ab_pos/hcv_pts_ab_positive, accuracy = 0.1)
no_eip_record_hcv_ab_pos_percent
#check <- hcv_pts[which(is.na(hcv_pts$eip_record) & hcv_pts$hcv_ab_positive == 1), ]
#check <- select(check, mrn)
#check



table(hcv_pts$hcv_ab_positive, hcv_pts$hcv_rna_neg)
hcv_pts$hcv_pts_rna_neg[hcv_pts$hcv_ab_positive == 1 & hcv_pts$hcv_rna_neg == 1] <- 1
hcv_pts_rna_neg <- hcv_pts[which(hcv_pts$hcv_ab_positive == 1 & hcv_pts$hcv_rna_neg == 1), ]
dim(hcv_pts_rna_neg)
head(hcv_pts_rna_neg)
hcv_pts_rna_neg <- select(hcv_pts_rna_neg, mrn)
head(hcv_pts_rna_neg)
dim(hcv_pts_rna_neg)
hcv_pts_rna_neg <- distinct(hcv_pts_rna_neg)
dim(hcv_pts_rna_neg)

hcv_pts_rna_neg <- nrow(hcv_pts_rna_neg)
hcv_pts_rna_neg
hcv_pts_rna_neg_percent <- percent(hcv_pts_rna_neg/hcv_pts_ab_positive, accuracy = 0.1)
hcv_pts_rna_neg_percent



table(hcv_pts$hcv_pts_rna_neg, hcv_pts$hcv_rna_neg_fu)
hcv_pts_rna_neg_fu <- hcv_pts[which(hcv_pts$hcv_pts_rna_neg == 1 & hcv_pts$hcv_rna_neg_fu == 1), ]
dim(hcv_pts_rna_neg_fu)
head(hcv_pts_rna_neg_fu)
hcv_pts_rna_neg_fu <- select(hcv_pts_rna_neg_fu, mrn)
head(hcv_pts_rna_neg_fu)
dim(hcv_pts_rna_neg_fu)
hcv_pts_rna_neg_fu <- distinct(hcv_pts_rna_neg_fu)
dim(hcv_pts_rna_neg_fu)

hcv_pts_rna_neg_fu <- nrow(hcv_pts_rna_neg_fu)
hcv_pts_rna_neg_fu
hcv_pts_rna_neg_fu_percent <- percent(hcv_pts_rna_neg_fu/hcv_pts_rna_neg, accuracy = 0.1)
hcv_pts_rna_neg_fu_percent



table(hcv_pts$hcv_rna_known)
hcv_pts_rna_known <- hcv_pts[which(hcv_pts$hcv_rna_known == 1), ]
dim(hcv_pts_rna_known)
head(hcv_pts_rna_known)
hcv_pts_rna_known <- select(hcv_pts_rna_known, mrn)
head(hcv_pts_rna_known)
dim(hcv_pts_rna_known)
hcv_pts_rna_known <- distinct(hcv_pts_rna_known)
dim(hcv_pts_rna_known)

hcv_pts_rna_known <- nrow(hcv_pts_rna_known)
hcv_pts_rna_known
hcv_pts_rna_known_percent <- percent(hcv_pts_rna_known/hcv_ab_positive, accuracy = 0.1)
hcv_pts_rna_known_percent



table(hcv_pts$hcv_rna_pos)
hcv_pts_rna_pos <- hcv_pts[which(hcv_pts$hcv_rna_pos == 1), ]
dim(hcv_pts_rna_pos)
head(hcv_pts_rna_pos)
hcv_pts_rna_pos <- select(hcv_pts_rna_pos, mrn)
head(hcv_pts_rna_pos)
dim(hcv_pts_rna_pos)
hcv_pts_rna_pos <- distinct(hcv_pts_rna_pos)
dim(hcv_pts_rna_pos)

hcv_pts_rna_pos <- nrow(hcv_pts_rna_pos)
hcv_pts_rna_pos
hcv_pts_rna_pos_percent <- percent(hcv_pts_rna_pos/hcv_pts_rna_known, accuracy = 0.1)
hcv_pts_rna_pos_percent



hcv_pts$hcv_pts_fu_needed[(hcv_pts$hcv_ab_positive == 1 & hcv_pts$eip_record == 1 &
                             (hcv_pts$hcv_fu_needed == 1 | is.na(hcv_pts$hcv_rna_neg)))] <- 1
hcv_pts_fu_needed <- hcv_pts[which(hcv_pts$hcv_pts_fu_needed == 1), ]
dim(hcv_pts_fu_needed)
head(hcv_pts_fu_needed)
hcv_pts_fu_needed <- select(hcv_pts_fu_needed, mrn)
head(hcv_pts_fu_needed)
dim(hcv_pts_fu_needed)
hcv_pts_fu_needed <- distinct(hcv_pts_fu_needed)
dim(hcv_pts_fu_needed)

hcv_pts_fu_needed <- nrow(hcv_pts_fu_needed)
hcv_pts_fu_needed
hcv_pts_fu_needed_percent <- percent(hcv_pts_fu_needed/hcv_pts_ab_positive, accuracy = 0.1)
hcv_pts_fu_needed_percent



table(hcv_pts$hcv_pts_fu_needed, hcv_pts$hcv_education)
hcv_pts$hcv_pts_educated[hcv_pts$hcv_pts_fu_needed == 1 & hcv_pts$hcv_education == 1] <- 1
hcv_pts_educated <- hcv_pts[which(hcv_pts$hcv_pts_educated == 1), ]
dim(hcv_pts_educated)
head(hcv_pts_educated)
hcv_pts_educated <- select(hcv_pts_educated, mrn)
head(hcv_pts_educated)
dim(hcv_pts_educated)
hcv_pts_educated <- distinct(hcv_pts_educated)
dim(hcv_pts_educated)

hcv_pts_educated <- nrow(hcv_pts_educated)
hcv_pts_educated
hcv_pts_educated_percent <- percent(hcv_pts_educated/hcv_pts_fu_needed, accuracy = 0.1)
hcv_pts_educated_percent



hcv_pts$hcv_pts_no_education[hcv_pts$hcv_pts_fu_needed & is.na(hcv_pts$hcv_pts_educated)] <- 1
table(hcv_pts$hcv_pts_no_education)
hcv_pts_no_education <- hcv_pts[which(hcv_pts$hcv_pts_no_education == 1), ]
dim(hcv_pts_no_education)
head(hcv_pts_no_education)
hcv_pts_no_education <- select(hcv_pts_no_education, mrn)
head(hcv_pts_no_education)
dim(hcv_pts_no_education)
hcv_pts_no_education <- distinct(hcv_pts_no_education)
dim(hcv_pts_no_education)

hcv_pts_no_education <- nrow(hcv_pts_no_education)
hcv_pts_no_education
hcv_pts_no_education_percent <- percent(hcv_pts_no_education/hcv_pts_fu_needed, accuracy = 0.1)
hcv_pts_no_education_percent




hcv_dash_already_linked_percent <- percent(hcv_dash_already_linked/hcv_pts_no_education, accuracy = 0.1)
hcv_dash_already_linked_percent

hcv_dash_deceased_percent <- percent(hcv_dash_deceased/hcv_pts_no_education, accuracy = 0.1)
hcv_dash_deceased_percent

hcv_dash_incarcerated_percent <- percent(hcv_dash_incarcerated/hcv_pts_no_education, accuracy = 0.1)
hcv_dash_incarcerated_percent

hcv_dash_inability_to_contact_percent <- percent(hcv_dash_inability_to_contact/hcv_pts_no_education, accuracy = 0.1)
hcv_dash_inability_to_contact_percent

hcv_dash_linkage_declined_percent <- percent(hcv_dash_linkage_declined/hcv_pts_no_education, accuracy = 0.1)
hcv_dash_linkage_declined_percent

hcv_dash_ongoing_linkage_percent <- percent(hcv_dash_ongoing_linkage/hcv_pts_no_education, accuracy = 0.1)
hcv_dash_ongoing_linkage_percent

hcv_dash_in_progress_percent <- percent(hcv_dash_in_progress/hcv_pts_no_education, accuracy = 0.1)
hcv_dash_in_progress_percent

hcv_dash_not_linked_med_staff_percent <- percent(hcv_dash_not_linked_med_staff/hcv_pts_no_education, accuracy = 0.1)
hcv_dash_not_linked_med_staff_percent

hcv_dash_not_linked_family_percent <- percent(hcv_dash_not_linked_family/hcv_pts_no_education, accuracy = 0.1)
hcv_dash_not_linked_family_percent

hcv_dash_not_linked_not_talking_percent <- percent(hcv_dash_not_linked_not_talking/hcv_pts_no_education, accuracy = 0.1)
hcv_dash_not_linked_not_talking_percent

hcv_dash_not_linked_safety_percent <- percent(hcv_dash_not_linked_safety/hcv_pts_no_education, accuracy = 0.1)
hcv_dash_not_linked_safety_percent

hcv_dash_not_linked_medical_percent <- percent(hcv_dash_not_linked_medical/hcv_pts_no_education, accuracy = 0.1)
hcv_dash_not_linked_medical_percent

hcv_dash_not_linked_contact_percent <- percent(hcv_dash_not_linked_contact/hcv_pts_no_education, accuracy = 0.1)
hcv_dash_not_linked_contact_percent

hcv_dash_not_linked_language_percent <- percent(hcv_dash_not_linked_language/hcv_pts_no_education, accuracy = 0.1)
hcv_dash_not_linked_language_percent

hcv_dash_not_linked_other_percent <- percent(hcv_dash_not_linked_other/hcv_pts_no_education, accuracy = 0.1)
hcv_dash_not_linked_other_percent




hcv_pts$hcv_pts_educated_ed[hcv_pts$hcv_pts_educated == 1 & hcv_pts$hcv_education_ed == 1] <- 1
hcv_pts_educated_ed <- hcv_pts[which(hcv_pts$hcv_pts_educated_ed == 1), ]
dim(hcv_pts_educated_ed)
head(hcv_pts_educated_ed)
hcv_pts_educated_ed <- select(hcv_pts_educated_ed, mrn)
head(hcv_pts_educated_ed)
dim(hcv_pts_educated_ed)
hcv_pts_educated_ed <- distinct(hcv_pts_educated_ed)
dim(hcv_pts_educated_ed)

hcv_pts_educated_ed <- nrow(hcv_pts_educated_ed)
hcv_pts_educated_ed
hcv_pts_educated_ed_percent <- percent(hcv_pts_educated_ed/hcv_pts_educated, accuracy = 0.1)
hcv_pts_educated_ed_percent



hcv_pts$hcv_pts_educated_phone[hcv_pts$hcv_pts_educated == 1 & hcv_pts$hcv_education_phone == 1] <- 1
hcv_pts_educated_phone <- hcv_pts[which(hcv_pts$hcv_pts_educated_phone == 1), ]
dim(hcv_pts_educated_phone)
head(hcv_pts_educated_phone)
hcv_pts_educated_phone <- select(hcv_pts_educated_phone, mrn)
head(hcv_pts_educated_phone)
dim(hcv_pts_educated_phone)
hcv_pts_educated_phone <- distinct(hcv_pts_educated_phone)
dim(hcv_pts_educated_phone)

hcv_pts_educated_phone <- nrow(hcv_pts_educated_phone)
hcv_pts_educated_phone
hcv_pts_educated_phone_percent <- percent(hcv_pts_educated_phone/hcv_pts_educated, accuracy = 0.1)
hcv_pts_educated_phone_percent



hcv_pts$hcv_pts_educated_other[hcv_pts$hcv_pts_educated == 1 & hcv_pts$hcv_education_other == 1] <- 1
hcv_pts_educated_other <- hcv_pts[which(hcv_pts$hcv_pts_educated_other == 1), ]
dim(hcv_pts_educated_other)
head(hcv_pts_educated_other)
hcv_pts_educated_other <- select(hcv_pts_educated_other, mrn)
head(hcv_pts_educated_other)
dim(hcv_pts_educated_other)
hcv_pts_educated_other <- distinct(hcv_pts_educated_other)
dim(hcv_pts_educated_other)

hcv_pts_educated_other <- nrow(hcv_pts_educated_other)
hcv_pts_educated_other
hcv_pts_educated_other_percent <- percent(hcv_pts_educated_other/hcv_pts_educated, accuracy = 0.1)
hcv_pts_educated_other_percent



hcv_pts$hcv_pts_linkage_total[hcv_pts$hcv_pts_educated == 1 &
                                (hcv_pts$hcv_linked == 1 | hcv_pts$hcv_linked_other == 1)] <- 1
hcv_pts_linkage_total <- hcv_pts[which(hcv_pts$hcv_pts_linkage_total == 1), ]
dim(hcv_pts_linkage_total)
head(hcv_pts_linkage_total)
hcv_pts_linkage_total <- select(hcv_pts_linkage_total, mrn)
head(hcv_pts_linkage_total)
dim(hcv_pts_linkage_total)
hcv_pts_linkage_total <- distinct(hcv_pts_linkage_total)
dim(hcv_pts_linkage_total)

hcv_pts_linkage_total <- nrow(hcv_pts_linkage_total)
hcv_pts_linkage_total
hcv_pts_linkage_total_percent <- percent(hcv_pts_linkage_total/hcv_pts_educated, accuracy = 0.1)
hcv_pts_linkage_total_percent



table(hcv_pts$hcv_pts_educated, hcv_pts$hcv_linked)
hcv_pts$hcv_pts_linked[hcv_pts$hcv_pts_educated == 1 & hcv_pts$hcv_linked == 1] <- 1
hcv_pts_linked <- hcv_pts[which(hcv_pts$hcv_pts_linked == 1), ]
dim(hcv_pts_linked)
head(hcv_pts_linked)
hcv_pts_linked <- select(hcv_pts_linked, mrn)
head(hcv_pts_linked)
dim(hcv_pts_linked)
hcv_pts_linked <- distinct(hcv_pts_linked)
dim(hcv_pts_linked)

hcv_pts_linked <- nrow(hcv_pts_linked)
hcv_pts_linked
hcv_pts_linked_percent <- percent(hcv_pts_linked/hcv_pts_linkage_total, accuracy = 0.1)
hcv_pts_linked_percent



hcv_pts$hcv_pts_linked_other[hcv_pts$hcv_pts_educated == 1 & hcv_pts$hcv_linked_other == 1] <- 1
hcv_pts_linked_other <- hcv_pts[which(hcv_pts$hcv_pts_linked_other == 1), ]
dim(hcv_pts_linked_other)
head(hcv_pts_linked_other)
hcv_pts_linked_other <- select(hcv_pts_linked_other, mrn)
head(hcv_pts_linked_other)
dim(hcv_pts_linked_other)
hcv_pts_linked_other <- distinct(hcv_pts_linked_other)
dim(hcv_pts_linked_other)

hcv_pts_linked_other <- nrow(hcv_pts_linked_other)
hcv_pts_linked_other
hcv_pts_linked_other_percent <- percent(hcv_pts_linked_other/hcv_pts_linkage_total, accuracy = 0.1)
hcv_pts_linked_other_percent




# Figuring out time of day the labs were ordered for HCV Ab Positives

dim(hcv)
head(hcv)
table(hcv$hcv_ab_positive)
hcv_ab_pos <- hcv[which(hcv$hcv_ab_positive == 1), ]
dim(hcv_ab_pos)


hcv_ab_pos$order_datetime <- as.POSIXct(paste(hcv_ab_pos$order_date, hcv_ab_pos$order_time), format = "%Y-%m-%d %I:%M:%S %p")
head(hcv_ab_pos)
hcv_ab_pos$order_datetime <- as.POSIXct(hcv_ab_pos$order_datetime)
hcv_ab_pos <- hcv_ab_pos %>%
  mutate(estimated_result_time = order_datetime + lubridate::minutes(233))
hcv_ab_pos$result_day <- weekdays(hcv_ab_pos$estimated_result_time)
hcv_ab_pos$result_hour <- as.numeric(format(hcv_ab_pos$estimated_result_time, "%H"))

time_category <- function(hour) {
  ifelse(hour >= 6 & hour < 12, "morning",
         ifelse(hour >= 12 & hour < 18, "afternoon",
                ifelse(hour >= 18 & hour < 24, "evening", "overnight")))
}

hcv_ab_pos$result_time_category <- sapply(hcv_ab_pos$result_hour, time_category)
hcv_ab_pos$result_day_time <- paste(hcv_ab_pos$result_day, hcv_ab_pos$result_time_category)
hcv_ab_pos$result_day <- factor(hcv_ab_pos$result_day, levels = c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"))


result_time_order <- c(
  "Sunday overnight", "Sunday morning", "Sunday afternoon", "Sunday evening",
  "Monday overnight", "Monday morning", "Monday afternoon", "Monday evening",
  "Tuesday overnight", "Tuesday morning", "Tuesday afternoon", "Tuesday evening",
  "Wednesday overnight", "Wednesday morning", "Wednesday afternoon", "Wednesday evening",
  "Thursday overnight", "Thursday morning", "Thursday afternoon", "Thursday evening",
  "Friday overnight", "Friday morning", "Friday afternoon", "Friday evening",
  "Saturday overnight", "Saturday morning", "Saturday afternoon", "Saturday evening"
)
hcv_ab_pos$result_day_time <- factor(hcv_ab_pos$result_day_time, levels = result_time_order)
hcv_ab_pos_summary <- hcv_ab_pos %>%
  group_by(result_day_time) %>%
  mutate(result_time_category = time_category(result_hour)) %>%
  group_by(result_day_time, result_time_category) %>%
  summarise(frequency = n())


# Adding in staff times
## JF: M/F 10a-10p and T 9a-9p
## RK: M-Th 7a-5p or T-F 7a-7p (alternating weeks)
## KA: W-Sun 3p-11p
# Estimating 7a-11p coverage M-Sun, which is M morning through Sun evening, except overnights
has_staff_coverage <- function(time_period) {
  staff_coverage_periods <- c("Monday morning", "Monday afternoon", "Monday evening",
                              "Tuesday morning", "Tuesday afternoon", "Tuesday evening",
                              "Wednesday morning", "Wednesday afternoon", "Wednesday evening",
                              "Thursday morning", "Thursday afternoon", "Thursday evening",
                              "Friday morning", "Friday afternoon", "Friday evening",
                              "Saturday morning", "Saturday afternoon", "Saturday evening",
                              "Sunday morning", "Sunday afternoon", "Sunday evening")
  return(time_period %in% staff_coverage_periods)
}
hcv_ab_pos_summary <- hcv_ab_pos_summary %>%
  mutate(has_coverage = has_staff_coverage(result_day_time))


hcv_ab_pos_total <- sum(hcv_ab_pos_summary$frequency)

hcv_ab_pos_with_coverage <- sum(hcv_ab_pos_summary$frequency[hcv_ab_pos_summary$has_coverage])
hcv_ab_pos_with_coverage
hcv_ab_pos_with_coverage_percent <- percent(hcv_ab_pos_with_coverage/hcv_ab_pos_total, accuracy = 0.1)
hcv_ab_pos_with_coverage_percent

hcv_ab_pos_without_coverage <- sum(hcv_ab_pos_summary$frequency[!hcv_ab_pos_summary$has_coverage])
hcv_ab_pos_without_coverage
hcv_ab_pos_without_coverage_percent <- percent(hcv_ab_pos_without_coverage/hcv_ab_pos_total, accuracy = 0.1)
hcv_ab_pos_without_coverage_percent

```

``` {r EIP Encounter Data, include=FALSE}

###############################################################################################################
#########################################  Creating Encounter Dataset  ########################################
###############################################################################################################

enc <- eip
summary(enc$enc_date)
enc$enc_date <- as.Date(enc$enc_date, format = '%m/%d/%Y')
summary(enc$enc_date)
eip_encounters <- nrow(enc)
eip_encounters


################################################################################

##########  HCV Linkage Data  ##########


# HCV Status

table(enc$ltc_services___2, enc$diagnosis_hcv)
enc$hcv_status[enc$ltc_services___2 == 1 & enc$diagnosis_hcv == 1] <- 'New HCV Diagnosis'
enc$hcv_status[enc$ltc_services___2 == 1 & enc$diagnosis_hcv == 2] <- 'Previous HCV Diagnosis'
enc$hcv_status[enc$ltc_services___2 == 1 & is.na(enc$diagnosis_hcv)] <- 'Unknown HCV Status'
table(enc$hcv_status)


# HCV Linkage Data

table(enc$ltc_services___2)
enc$hcv_ltc[enc$ltc_services___2 == 1] <- 1
table(enc$hcv_ltc)

table(enc$hcv_ltc)
hcv_ltc <- enc[which(enc$hcv_ltc == 1), ]
dim(hcv_ltc)
hcv_ltc <- nrow(hcv_ltc)
hcv_ltc



# Ineligible HCV Linkage - Already Linked

table(enc$ltc_hcv_declined_rsn___23)
table(enc$ltc_hcv_prevented_rsn___16)
enc$hcv_already_linked[enc$hcv_ltc == 1 &
                         (enc$ltc_hcv_declined_rsn___23 == 1 |
                            enc$ltc_hcv_prevented_rsn___16 == 1)] <- 1
table(enc$hcv_already_linked)

table(enc$hcv_already_linked)
hcv_already_linked <- enc[which(enc$hcv_already_linked == 1), ]
dim(hcv_already_linked)
hcv_already_linked <- nrow(hcv_already_linked)
hcv_already_linked



# Ineligible HCV Linkage - Deceased

table(enc$ltc_hcv_declined_rsn___35)
table(enc$ltc_hcv_prevented_rsn___17)
enc$hcv_deceased[enc$hcv_ltc == 1 &
                   (enc$ltc_hcv_declined_rsn___35 == 1 |
                      enc$ltc_hcv_prevented_rsn___17 == 1)] <- 1
table(enc$hcv_deceased)

table(enc$hcv_deceased)
hcv_deceased <- enc[which(enc$hcv_deceased == 1), ]
dim(hcv_deceased)
hcv_deceased <- nrow(hcv_deceased)
hcv_deceased



# Ineligible HCV Linkage - Incarcerated

table(enc$ltc_hcv_prevented_rsn___12)
enc$hcv_incarcerated[enc$hcv_ltc == 1 &
                       enc$ltc_hcv_prevented_rsn___12 == 1] <- 1
table(enc$hcv_incarcerated)

table(enc$hcv_incarcerated)
hcv_incarcerated <- enc[which(enc$hcv_incarcerated == 1), ]
dim(hcv_incarcerated)
hcv_incarcerated <- nrow(hcv_incarcerated)
hcv_incarcerated



# Ineligible HCV Linkage - Inability to Contact

table(enc$ltc_hcv_final_ltc_status)
enc$hcv_inability_to_contact[enc$hcv_ltc == 1 &
                               enc$ltc_hiv_prevented_rsn___19 == 1] <- 1
table(enc$hcv_inability_to_contact)

table(enc$hcv_inability_to_contact)
hcv_inability_to_contact <- enc[which(enc$hcv_inability_to_contact == 1), ]
dim(hcv_inability_to_contact)
hcv_inability_to_contact <- nrow(hcv_inability_to_contact)
hcv_inability_to_contact



# Ineligible HCV Linkage - Declined Linkage Service

table(enc$ltc_hcv_final_ltc_status)
enc$hcv_linkage_declined[(enc$hcv_ltc == 1 &
                            enc$ltc_hcv_final_ltc_status == 2) &
                           (is.na(enc$hcv_already_linked) &
                              is.na(enc$hcv_deceased) &
                              is.na(enc$hcv_incarcerated))] <- 1
table(enc$hcv_linkage_declined)

table(enc$hcv_linkage_declined)
hcv_linkage_declined <- enc[which(enc$hcv_linkage_declined == 1), ]
dim(hcv_linkage_declined)
hcv_linkage_declined <- nrow(hcv_linkage_declined)
hcv_linkage_declined




# Ineligible HCV Linkage - Linkage in Progress

table(enc$ltc_hcv_prevented_rsn___18)
enc$hcv_ongoing_linkage[enc$hcv_ltc == 1 &
                          enc$ltc_hcv_prevented_rsn___18 == 1] <- 1
table(enc$hcv_ongoing_linkage)

table(enc$hcv_ongoing_linkage)
hcv_ongoing_linkage <- enc[which(enc$hcv_ongoing_linkage == 1), ]
dim(hcv_ongoing_linkage)
hcv_ongoing_linkage <- nrow(hcv_ongoing_linkage)
hcv_ongoing_linkage




# HCV Ineligible Cases

enc$hcv_ineligible_ltc[enc$hcv_already_linked == 1 |
                         enc$hcv_deceased == 1 |
                         enc$hcv_incarcerated == 1 |
                         enc$hcv_inability_to_contact == 1 |
                         enc$hcv_linkage_declined == 1 |
                         enc$hcv_ongoing_linkage == 1] <- 1
table(enc$hcv_ineligible_ltc)

table(enc$hcv_ineligible_ltc)
hcv_ineligible_ltc <- enc[which(enc$hcv_ineligible_ltc == 1), ]
dim(hcv_ineligible_ltc)
hcv_ineligible_ltc <- nrow(hcv_ineligible_ltc)
hcv_ineligible_ltc

hcv_ineligible_ltc_percent <- percent(hcv_ineligible_ltc/hcv_ltc, accuracy = 0.1)
hcv_ineligible_ltc_percent

hcv_already_linked_percent <- percent(hcv_already_linked/hcv_ineligible_ltc, accuracy = 0.1)
hcv_already_linked_percent

hcv_deceased_percent <- percent(hcv_deceased/hcv_ineligible_ltc, accuracy = 0.1)
hcv_deceased_percent

hcv_incarcerated_percent <- percent(hcv_incarcerated/hcv_ineligible_ltc, accuracy = 0.1)
hcv_incarcerated_percent

hcv_inability_to_contact_percent <- percent(hcv_inability_to_contact/hcv_ineligible_ltc, accuracy = 0.1)
hcv_inability_to_contact_percent

hcv_linkage_declined_percent <- percent(hcv_linkage_declined/hcv_ineligible_ltc, accuracy = 0.1)
hcv_linkage_declined_percent

hcv_ongoing_linkage_percent <- percent(hcv_ongoing_linkage/hcv_ineligible_ltc, accuracy = 0.1)
hcv_ongoing_linkage_percent




# HCV Eligibility to be Linked

enc$hcv_eligible_ltc[enc$hcv_ltc == 1 &
                       (is.na(enc$hcv_already_linked) &
                          is.na(enc$hcv_deceased) &
                          is.na(enc$hcv_incarcerated) &
                          is.na(enc$hcv_linkage_declined) &
                          is.na(enc$hcv_ongoing_linkage))] <- 1
table(enc$hcv_eligible_ltc)

table(enc$hcv_eligible_ltc)
hcv_eligible_ltc <- enc[which(enc$hcv_eligible_ltc == 1), ]
dim(hcv_eligible_ltc)
hcv_eligible_ltc <- nrow(hcv_eligible_ltc)
hcv_eligible_ltc

hcv_eligible_ltc_percent <- percent(hcv_eligible_ltc/hcv_ltc, accuracy = 0.1)
hcv_eligible_ltc_percent



table(enc$hcv_eligible_ltc, enc$hcv_status)
enc$hcv_new_eligible_ltc[enc$hcv_eligible_ltc == 1 &
                           enc$hcv_status == 'New HCV Diagnosis'] <- 1
table(enc$hcv_new_eligible_ltc)

table(enc$hcv_new_eligible_ltc)
hcv_new_eligible_ltc <- enc[which(enc$hcv_new_eligible_ltc == 1), ]
dim(hcv_new_eligible_ltc)
hcv_new_eligible_ltc <- nrow(hcv_new_eligible_ltc)
hcv_new_eligible_ltc

hcv_new_eligible_ltc_percent <- percent(hcv_new_eligible_ltc/hcv_eligible_ltc, accuracy = 0.1)
hcv_new_eligible_ltc_percent




table(enc$hcv_eligible_ltc, enc$hcv_status)
enc$hcv_prev_eligible_ltc[enc$hcv_eligible_ltc == 1 &
                            enc$hcv_status == 'Previous HCV Diagnosis'] <- 1
table(enc$hcv_prev_eligible_ltc)

table(enc$hcv_prev_eligible_ltc)
hcv_prev_eligible_ltc <- enc[which(enc$hcv_prev_eligible_ltc == 1), ]
dim(hcv_prev_eligible_ltc)
hcv_prev_eligible_ltc <- nrow(hcv_prev_eligible_ltc)
hcv_prev_eligible_ltc

hcv_prev_eligible_ltc_percent <- percent(hcv_prev_eligible_ltc/hcv_eligible_ltc, accuracy = 0.1)
hcv_prev_eligible_ltc_percent



table(enc$hcv_eligible_ltc, enc$hcv_status)
enc$hcv_unk_eligible_ltc[(enc$hcv_eligible_ltc == 1 &
                            (enc$hcv_status == 'Unknown HCV Status' |
                               is.na(enc$hcv_status)))] <- 1
table(enc$hcv_unk_eligible_ltc)

table(enc$hcv_unk_eligible_ltc)
hcv_unk_eligible_ltc <- enc[which(enc$hcv_unk_eligible_ltc == 1), ]
dim(hcv_unk_eligible_ltc)
hcv_unk_eligible_ltc <- nrow(hcv_unk_eligible_ltc)
hcv_unk_eligible_ltc

hcv_unk_eligible_ltc_percent <- percent(hcv_unk_eligible_ltc/hcv_eligible_ltc, accuracy = 0.1)
hcv_unk_eligible_ltc_percent




# hcv Open/Closed Cases

table(enc$ltc_hcv_open_case_calc)
enc$hcv_in_progress[enc$hcv_eligible_ltc == 1 &
                      enc$ltc_hcv_open_case_calc == 1] <- 1
table(enc$hcv_in_progress)

table(enc$hcv_in_progress)
hcv_in_progress <- enc[which(enc$hcv_in_progress == 1), ]
dim(hcv_in_progress)
hcv_in_progress <- nrow(hcv_in_progress)
hcv_in_progress

hcv_in_progress_percent <- percent(hcv_in_progress/hcv_eligible_ltc, accuracy = 0.1)
hcv_in_progress_percent



table(enc$hcv_in_progress, enc$hcv_status)
enc$hcv_new_in_progress[enc$hcv_in_progress == 1 &
                          enc$hcv_status == 'New HCV Diagnosis'] <- 1
table(enc$hcv_new_in_progress)

table(enc$hcv_new_in_progress)
hcv_new_in_progress <- enc[which(enc$hcv_new_in_progress == 1), ]
dim(hcv_new_in_progress)
hcv_new_in_progress <- nrow(hcv_new_in_progress)
hcv_new_in_progress

hcv_new_in_progress_percent <- percent(hcv_new_in_progress/hcv_new_eligible_ltc, accuracy = 0.1)
hcv_new_in_progress_percent



table(enc$hcv_in_progress, enc$hcv_status)
enc$hcv_prev_in_progress[enc$hcv_in_progress == 1 &
                           enc$hcv_status == 'Previous HCV Diagnosis'] <- 1
table(enc$hcv_prev_in_progress)

table(enc$hcv_prev_in_progress)
hcv_prev_in_progress <- enc[which(enc$hcv_prev_in_progress == 1), ]
dim(hcv_prev_in_progress)
hcv_prev_in_progress <- nrow(hcv_prev_in_progress)
hcv_prev_in_progress

hcv_prev_in_progress_percent <- percent(hcv_prev_in_progress/hcv_prev_eligible_ltc, accuracy = 0.1)
hcv_prev_in_progress_percent



table(enc$hcv_in_progress, enc$hcv_status)
enc$hcv_unk_in_progress[enc$hcv_in_progress == 1 &
                          (enc$hcv_status == 'Unknown HCV Status' |
                             is.na(enc$hcv_status))] <- 1
table(enc$hcv_unk_in_progress)

table(enc$hcv_unk_in_progress)
hcv_unk_in_progress <- enc[which(enc$hcv_unk_in_progress == 1), ]
dim(hcv_unk_in_progress)
hcv_unk_in_progress <- nrow(hcv_unk_in_progress)
hcv_unk_in_progress

hcv_unk_in_progress_percent <- percent(hcv_unk_in_progress/hcv_unk_eligible_ltc, accuracy = 0.1)
hcv_unk_in_progress_percent



table(enc$hcv_eligible_ltc, enc$hcv_in_progress)
enc$hcv_closed_case[enc$hcv_eligible_ltc == 1 &
                      is.na(enc$hcv_in_progress)] <- 1
table(enc$hcv_closed_case)

table(enc$hcv_closed_case)
hcv_closed_case <- enc[which(enc$hcv_closed_case == 1), ]
dim(hcv_closed_case)
hcv_closed_case <- nrow(hcv_closed_case)
hcv_closed_case

hcv_closed_case_percent <- percent(hcv_closed_case/hcv_eligible_ltc, accuracy = 0.1)
hcv_closed_case_percent



table(enc$hcv_in_progress)
enc$hcv_ltc_days_open <- difftime(Sys.Date(), enc$enc_date, units="days")
table(enc$hcv_ltc_days_open)
enc$hcv_in_progress_90days[enc$hcv_in_progress == 1 &
                             (enc$hcv_ltc_days_open > 90)] <- 1
table(enc$hcv_in_progress_90days)

table(enc$hcv_in_progress_90days)
hcv_in_progress_90days <- enc[which(enc$hcv_in_progress_90days == 1), ]
dim(hcv_in_progress_90days)
hcv_in_progress_90days <- nrow(hcv_in_progress_90days)
hcv_in_progress_90days

hcv_in_progress_90days_percent <- percent(hcv_in_progress_90days/hcv_in_progress, accuracy = 0.1)
hcv_in_progress_90days_percent




# HCV Cases Linked to Care

table(enc$hcv_closed_case, enc$ltc_hcv_final_ltc_status)
enc$hcv_linked[enc$hcv_closed_case == 1 &
                 enc$ltc_hcv_final_ltc_status == 1] <- 1
table(enc$hcv_linked)

table(enc$hcv_linked)
hcv_linked <- enc[which(enc$hcv_linked == 1), ]
dim(hcv_linked)
hcv_linked <- nrow(hcv_linked)
hcv_linked

hcv_linked_gauge <- (hcv_linked/hcv_closed_case)*100
hcv_linked_gauge
hcv_linked_percent <- percent(hcv_linked/hcv_closed_case, accuracy = 0.1)
hcv_linked_percent



table(enc$hcv_status, enc$hcv_eligible_ltc)
table(enc$hcv_linked, enc$hcv_status)
enc$hcv_new_linked[enc$hcv_linked == 1 &
                     enc$hcv_status == 'New HCV Diagnosis'] <- 1
table(enc$hcv_new_linked)

table(enc$hcv_new_linked)
hcv_new_linked <- enc[which(enc$hcv_new_linked == 1), ]
dim(hcv_new_linked)
hcv_new_linked <- nrow(hcv_new_linked)
hcv_new_linked

hcv_new_linked_percent <- percent(hcv_new_linked/hcv_new_eligible_ltc, accuracy = 0.1)
hcv_new_linked_percent



table(enc$hcv_status, enc$hcv_eligible_ltc)
table(enc$hcv_linked, enc$hcv_status)
enc$hcv_prev_linked[enc$hcv_linked == 1 &
                      enc$hcv_status == 'Previous HCV Diagnosis'] <- 1
table(enc$hcv_prev_linked)

table(enc$hcv_prev_linked)
hcv_prev_linked <- enc[which(enc$hcv_prev_linked == 1), ]
dim(hcv_prev_linked)
hcv_prev_linked <- nrow(hcv_prev_linked)
hcv_prev_linked

hcv_prev_linked_percent <- percent(hcv_prev_linked/hcv_prev_eligible_ltc, accuracy = 0.1)
hcv_prev_linked_percent




enc$hcv_not_linked[enc$hcv_eligible_ltc == 1 & is.na(enc$hcv_in_progress) & is.na(enc$hcv_linked)] <- 1
table(enc$hcv_not_linked)

table(enc$hcv_not_linked)
hcv_not_linked <- enc[which(enc$hcv_not_linked == 1), ]
dim(hcv_not_linked)
hcv_not_linked <- nrow(hcv_not_linked)
hcv_not_linked

hcv_not_linked_percent <- percent(hcv_not_linked/hcv_closed_case, accuracy = 0.1)
hcv_not_linked_percent



table(enc$hcv_not_linked, enc$hcv_status)
enc$hcv_new_not_linked[enc$hcv_not_linked == 1 &
                         enc$hcv_status == 'New HCV Diagnosis'] <- 1
table(enc$hcv_new_not_linked)

table(enc$hcv_new_not_linked)
hcv_new_not_linked <- enc[which(enc$hcv_new_not_linked == 1), ]
dim(hcv_new_not_linked)
hcv_new_not_linked <- nrow(hcv_new_not_linked)
hcv_new_not_linked

hcv_new_not_linked_percent <- percent(hcv_new_not_linked/hcv_new_eligible_ltc, accuracy = 0.1)
hcv_new_not_linked_percent



table(enc$hcv_not_linked, enc$hcv_status)
enc$hcv_prev_not_linked[enc$hcv_not_linked == 1 &
                          enc$hcv_status == 'Previous HCV Diagnosis'] <- 1
table(enc$hcv_prev_not_linked)

table(enc$hcv_prev_not_linked)
hcv_prev_not_linked <- enc[which(enc$hcv_prev_not_linked == 1), ]
dim(hcv_prev_not_linked)
hcv_prev_not_linked <- nrow(hcv_prev_not_linked)
hcv_prev_not_linked

hcv_prev_not_linked_percent <- percent(hcv_prev_not_linked/hcv_prev_eligible_ltc, accuracy = 0.1)
hcv_prev_not_linked_percent




# HCV Reasons Not Linked to Care

enc$hcv_not_linked_med_staff[(enc$hcv_closed_case == 1 & is.na(enc$hcv_linked)) &
                               (enc$ltc_hcv_prevented_rsn___1 == 1 |
                                  enc$ltc_hcv_prevented_rsn___2 == 1 |
                                  enc$ltc_hcv_prevented_rsn___11 == 1)] <- 1
table(enc$hcv_not_linked_med_staff)

table(enc$hcv_not_linked_med_staff)
hcv_not_linked_med_staff <- enc[which(enc$hcv_not_linked_med_staff == 1), ]
dim(hcv_not_linked_med_staff)
hcv_not_linked_med_staff <- nrow(hcv_not_linked_med_staff)
hcv_not_linked_med_staff

hcv_not_linked_med_staff_percent <- percent(hcv_not_linked_med_staff/hcv_not_linked, accuracy = 0.1)
hcv_not_linked_med_staff_percent



enc$hcv_not_linked_family[(enc$hcv_closed_case == 1 & is.na(enc$hcv_linked)) &
                            (enc$ltc_hcv_prevented_rsn___3 == 1)] <- 1
table(enc$hcv_not_linked_family)

table(enc$hcv_not_linked_family)
hcv_not_linked_family <- enc[which(enc$hcv_not_linked_family == 1), ]
dim(hcv_not_linked_family)
hcv_not_linked_family <- nrow(hcv_not_linked_family)
hcv_not_linked_family

hcv_not_linked_family_percent <- percent(hcv_not_linked_family/hcv_not_linked, accuracy = 0.1)
hcv_not_linked_family_percent



enc$hcv_not_linked_not_talking[(enc$hcv_closed_case == 1 & is.na(enc$hcv_linked)) &
                                 (enc$ltc_hcv_prevented_rsn___4 == 1)] <- 1
table(enc$hcv_not_linked_not_talking)

table(enc$hcv_not_linked_not_talking)
hcv_not_linked_not_talking <- enc[which(enc$hcv_not_linked_not_talking == 1), ]
dim(hcv_not_linked_not_talking)
hcv_not_linked_not_talking <- nrow(hcv_not_linked_not_talking)
hcv_not_linked_not_talking

hcv_not_linked_not_talking_percent <- percent(hcv_not_linked_not_talking/hcv_not_linked, accuracy = 0.1)
hcv_not_linked_not_talking_percent



enc$hcv_not_linked_safety[(enc$hcv_closed_case == 1 & is.na(enc$hcv_linked)) &
                            (enc$ltc_hcv_prevented_rsn___5 == 1)] <- 1
table(enc$hcv_not_linked_safety)

table(enc$hcv_not_linked_safety)
hcv_not_linked_safety <- enc[which(enc$hcv_not_linked_safety == 1), ]
dim(hcv_not_linked_safety)
hcv_not_linked_safety <- nrow(hcv_not_linked_safety)
hcv_not_linked_safety

hcv_not_linked_safety_percent <- percent(hcv_not_linked_safety/hcv_not_linked, accuracy = 0.1)
hcv_not_linked_safety_percent



enc$hcv_not_linked_medical[(enc$hcv_closed_case == 1 & is.na(enc$hcv_linked)) &
                             (enc$ltc_hcv_prevented_rsn___6 == 1 |
                                enc$ltc_hcv_prevented_rsn___8)] <- 1
table(enc$hcv_not_linked_medical)

table(enc$hcv_not_linked_medical)
hcv_not_linked_medical <- enc[which(enc$hcv_not_linked_medical == 1), ]
dim(hcv_not_linked_medical)
hcv_not_linked_medical <- nrow(hcv_not_linked_medical)
hcv_not_linked_medical

hcv_not_linked_medical_percent <- percent(hcv_not_linked_medical/hcv_not_linked, accuracy = 0.1)
hcv_not_linked_medical_percent



enc$hcv_not_linked_contact[(enc$hcv_closed_case == 1 & is.na(enc$hcv_linked)) &
                             (enc$ltc_hcv_prevented_rsn___20 == 1)] <- 1
table(enc$hcv_not_linked_contact)

table(enc$hcv_not_linked_contact)
hcv_not_linked_contact <- enc[which(enc$hcv_not_linked_contact == 1), ]
dim(hcv_not_linked_contact)
hcv_not_linked_contact <- nrow(hcv_not_linked_contact)
hcv_not_linked_contact

hcv_not_linked_contact_percent <- percent(hcv_not_linked_contact/hcv_not_linked, accuracy = 0.1)
hcv_not_linked_contact_percent



enc$hcv_not_linked_language[(enc$hcv_closed_case == 1 & is.na(enc$hcv_linked)) &
                              (enc$ltc_hcv_prevented_rsn___9 == 1)] <- 1
table(enc$hcv_not_linked_language)

table(enc$hcv_not_linked_language)
hcv_not_linked_language <- enc[which(enc$hcv_not_linked_language == 1), ]
dim(hcv_not_linked_language)
hcv_not_linked_language <- nrow(hcv_not_linked_language)
hcv_not_linked_language

hcv_not_linked_language_percent <- percent(hcv_not_linked_language/hcv_not_linked, accuracy = 0.1)
hcv_not_linked_language_percent



enc$hcv_not_linked_other[(enc$hcv_closed_case == 1 & is.na(enc$hcv_linked)) &
                           (enc$ltc_hcv_prevented_rsn___0 == 1)] <- 1
table(enc$hcv_not_linked_other)

table(enc$hcv_not_linked_other)
hcv_not_linked_other <- enc[which(enc$hcv_not_linked_other == 1), ]
dim(hcv_not_linked_other)
hcv_not_linked_other <- nrow(hcv_not_linked_other)
hcv_not_linked_other

hcv_not_linked_other_percent <- percent(hcv_not_linked_other/hcv_not_linked, accuracy = 0.1)
hcv_not_linked_other_percent


```


## HCV Epic Dashboard

The Epic dashboard for HCV testing went live on **January 2nd, 2024**. This Epic dashboard lists all University of Cincinnati Medical Center Emergency Department (UCMC ED) based HCV testing ordered, showing the results in real time. EIP staff monitors the HCV dashboard for positive results and approaches patients directly while they are still in the ED, or the hospital, to provide results, education and information for additional testing (if required), as well as linkage to care through UC's Clinical Pharmacy when appropriate.

The total daily testing numbers for HCV Antibody tests (HCV Ab) are shown in the table below, as well as a plot showing the daily trend in testing numbers. The overall HCV Ab positivity rate for the tests included in the HCV Epic Dashboard is described below the plot. The unique number of tests is determined by the *Order ID* for the test. The test is only included if the *Order Status* is "Completed" and the *Lab Status* indicates that it is the "Final Result" and the lab result is provided. The data is manually exported from the Epic HCV Dashboard each week with the data from the prior week by the EIP Data Team, and merged into a single data file used in this analysis, excluding duplicate records.

::: {.panel-tabset}

## Daily

<div align="center">
```{r, echo = FALSE}

# Table of daily HCV testing
daily_hcv_tbl <- hcv %>%
  group_by(order_date) %>%
  summarise(total_tests = sum(hcv_ab_tested),
            total_positive = sum(hcv_ab_positive),
            percent_positive = round((total_positive / total_tests) * 100, 1)) %>%
  arrange(desc(order_date))

reactable(daily_hcv_tbl,
          columns = list(
            order_date = colDef(name = "Order Date", align = "center", width = 125),
            total_tests = colDef(name = "HCV Ab Tests", align = "center", width = 130),
            total_positive = colDef(name = "HCV Ab +", align = "center", width = 125),
            percent_positive = colDef(name = "Percent +", align = "center", width = 125)),
          bordered = TRUE,
          highlight = TRUE,
          searchable = TRUE,
          paginationType = "simple",
          defaultColDef = colDef(style = list(fontSize = "12px", maxWidth = 505)),
          style = list(width = "50%"))

```
</div>
<br>
<div align="center">
``` {r, echo = FALSE, fig.frame="black"}

# Line graph of daily HCV testing
daily_hcv_test_plot <- daily_hcv_tests %>%
  plot_ly(x = ~order_date, y = ~total_tests, name = "HCV Ab Tests", type = 'scatter', mode = 'lines', line = list(color = '#DC9540')) %>%
  add_trace(y = ~total_positive, name = "HCV Ab+", line = list(color = 'royalblue')) %>%
  layout(
    xaxis = list(title = "Order Date"),
    yaxis = list(title = "Total HCV Tests", range = c(0, max(daily_hcv_tests$total_tests) + 10)),
    title = list(text = "HCV Dashboard Daily Ab Tests", font = list(size = 20)),
    margin = list(l = 50, r = 50, b = 50, t = 50),
    template = "plotly_dark"
  ) %>%
  config(displayModeBar = FALSE)
daily_hcv_test_plot

```
</div>
<br>


## Monthly

<div align="center">
```{r, echo = FALSE}

# Table of monthly HCV testing
monthly_hcv_tbl <- hcv %>%
  group_by(monthly_date) %>%
  summarise(total_tests = sum(hcv_ab_tested),
            total_positive = sum(hcv_ab_positive),
            percent_positive = round((total_positive / total_tests) * 100, 1)) %>%
  arrange(desc(monthly_date))

reactable(monthly_hcv_tbl,
          columns = list(
            monthly_date = colDef(name = "Month", align = "center", width = 125),
            total_tests = colDef(name = "HCV Ab Tests", align = "center", width = 130),
            total_positive = colDef(name = "HCV Ab +", align = "center", width = 125),
            percent_positive = colDef(name = "Percent +", align = "center", width = 125)),
          bordered = TRUE,
          highlight = TRUE,
          searchable = TRUE,
          paginationType = "simple",
          defaultColDef = colDef(style = list(fontSize = "12px", maxWidth = 505)),
          style = list(width = "50%"))

```
</div>
<br>
<div align="center">
``` {r, echo = FALSE, fig.frame="black"}

tickvals <- monthly_hcv_tests$monthly_date
ticktext <- format(monthly_hcv_tests$monthly_date, "%b %Y")

# Line graph of monthly HCV testing
monthly_hcv_test_plot <- monthly_hcv_tests %>%
  plot_ly(x = ~monthly_date, y = ~total_tests, name = "HCV Ab Tests", type = 'scatter', mode = 'lines', line = list(color = '#DC9540')) %>%
  add_trace(y = ~total_positive, name = "HCV Ab+", line = list(color = 'royalblue')) %>%
  layout(
    xaxis = list(
      title = "Month",
      tickvals = tickvals,
      ticktext = ticktext,
      tickmode = "array"
    ),
    yaxis = list(title = "Total HCV Tests", range = c(0, max(monthly_hcv_tests$total_tests) + 10)),
    title = list(text = "HCV Dashboard Daily Ab Tests", font = list(size = 20)),
    margin = list(l = 50, r = 50, b = 50, t = 50),
    template = "plotly_dark"
  ) %>%
  config(displayModeBar = FALSE)
monthly_hcv_test_plot

```
</div>
<br>

:::

It is important to note that since the HCV Epic dashboard data is manually extracted from Epic at various times, the total number of tests for the most recent day/month may not all be counted. For example, if data is pulled in the afternoon, then the tests conducted in the morning are counted, but not tests conducted later in the evening for that day. The day that the data was pulled is noted by the date at the top of this report. Also, depending on when the data was pulled, not all test results are finalized, so the positivity rate and number of positive tests/patients may also be slightly different. However, this should only pertain to the day the data is pulled, and not prior days included in the analysis.

The total number of HCV Ab tests since the initiation of the HCV Dashboard is **`r hcv_ab_tested` tests**. The total number of positive HCV Ab results is **`r hcv_ab_positive` Ab positive tests**, which is [**`r hcv_ab_positivity_rate`**]{style="color: red;"} of all HCV Ab tests conducted (*`r hcv_ab_positive`/`r hcv_ab_tested`*).

Since EIP is meant to approach each individual that has a reactive HCV Ab test to provide education, the data provided in the remainder of this report will focus on the unique number of patients rather than number of tests, and those patients that were followed up with by our staff and referred to UC's Clinical Pharmacy. Since the start of the HCV Dashboard, there have been a total of **`r hcv_pts_ab_tested` unique patients** that have been tested for HCV Ab, with a total of **`r hcv_pts_ab_positive` unique patients** that were positive for HCV Ab (*`r hcv_pts_ab_positive_percent` of all patients tested, `r hcv_pts_ab_positive`/`r hcv_pts_ab_tested`*). The unique number of patients tested is determined by the medical record number (MRN) attached to the lab test. The MRN is the identifier used to match back with the EIP REDCap Database to link with the patient's record to determine follow-up efforts described in the next section.

<br>


### EIP Follow-up

As mentioned above, there were a total of `r hcv_ab_positive` HCV positive tests, with `r hcv_pts_ab_positive` unique individuals. For EIP follow-up, we will focus on the unique number of patients in in regards to education of results or additional testing needed, and linkage to care efforts. A summary flow diagram for EIP's follow-up efforts regarding those that are identified HCV Ab+ through the HCV Dashboard is provided below. You can zoom into this flow diagram by clicking on the image.

```{r, echo = FALSE, warning = FALSE}
#| label: HCV Epic Dashboard Follow-up Flow Diagram 
#| fig-cap: "** *Unable to match records means that we are unable to match the EIP follow-up data with the data pulled from the Epic HCV Dashboard. The reason(s) for why these records are unable to be matched are: Tested under different MRN than patient record (n = 7).*"


grid_data <- tibble(x= 1:100, y= 1:100)

grid_data %>% 
  ggplot(aes(x, y)) +
  scale_x_continuous(minor_breaks = seq(10, 100, 10)) +
  scale_y_continuous(minor_breaks = seq(10, 100, 10)) +
  theme_linedraw() ->
  grid


grid +
  # Total HCV Ab Positive
  geom_rect(xmin = 0, xmax = 22, ymin = 90, ymax = 100, color = 'black',
            fill = 'lightyellow', size = 0.25, size = 0.25) +
  annotate('text', x = 10.5, y = 97, label = 'Total HCV Ab+ Patients', size = 2) +
  geom_rect(xmin = 0, xmax = 22, ymin = 90, ymax = 100, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 10.5, y = 93, label = hcv_pts_ab_positive, size = 2, color = 'black') +
  annotate('text', x = 19, y = 93, label = hcv_pts_ab_positive_percent, size = 2, color = 'goldenrod4') +
  
  
  # Unable to match records
  geom_rect(xmin = 11, xmax = 33, ymin = 80, ymax = 88, color = NA,
            fill = 'white', size = 0.25) +
  annotate('text', x = 19, y = 83, label = 'Unable to match records**', size = 2) +
  geom_rect(xmin = 13, xmax = 33, ymin = 80, ymax = 88, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 29, y = 83, label = no_eip_record_hcv_ab_pos, size = 2, color = 'black') +
  annotate('text', x = 33, y = 83, label = no_eip_record_hcv_ab_pos_percent, size = 2, color = 'goldenrod4') +
  
  
  # Known HCV RNA Negative Patients
  geom_rect(xmin = 41, xmax = 63, ymin = 75, ymax = 85, color = 'gray',
            fill = 'white', size = 0.25) +
  annotate('text', x = 52, y = 82, label = 'Known HCV RNA Negative Patients', size = 2) +
  geom_rect(xmin = 41, xmax = 63, ymin = 75, ymax = 85, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 51.5, y = 78, label = hcv_pts_rna_neg, size = 2, color = 'black') +
  annotate('text', x = 60, y = 78, label = hcv_pts_rna_neg_percent, size = 2, color = 'goldenrod4') +
  
  
  # HCV RNA Follow-up in ED
  geom_rect(xmin = 83, xmax = 100, ymin = 75, ymax = 85, color = NA,
            fill = 'white', size = 0.25) +
  annotate('text', x = 86, y = 80.25, label = 'Follow-up in ED', size = 2) +
  geom_rect(xmin = 41, xmax = 63, ymin = 75, ymax = 85, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 92, y = 80.25, label = hcv_pts_rna_neg_fu, size = 2, color = 'black') +
  annotate('text', x = 96, y = 80.25, label = hcv_pts_rna_neg_fu_percent, size = 2, color = 'goldenrod4') +
  
  
  # EIP Follow-up Needed
  geom_rect(xmin = 0, xmax = 22, ymin = 60, ymax = 70, color = 'black',
            fill = 'lightyellow', size = 0.25, size = 0.25) +
  annotate('text', x = 10.5, y = 67, label = 'EIP Follow-Up Needed', size = 2) +
  geom_rect(xmin = 0, xmax = 22, ymin = 60, ymax = 70, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 10.5, y = 63, label = hcv_pts_fu_needed, size = 2, color = 'black') +
  annotate('text', x = 19, y = 63, label = hcv_pts_fu_needed_percent, size = 2, color = 'goldenrod4') +
  
  
  # Unable to Follow-up
  geom_rect(xmin = 41, xmax = 63, ymin = 45, ymax = 55, color = 'gray',
            fill = 'white', size = 0.25) +
  annotate('text', x = 52, y = 52, label = 'Unable to Follow-up', size = 2) +
  geom_rect(xmin = 41, xmax = 63, ymin = 45, ymax = 55, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 51.5, y = 48, label = hcv_pts_no_education, size = 2, color = 'black') +
  annotate('text', x = 60, y = 48, label = hcv_pts_no_education_percent, size = 2, color = 'goldenrod4') +


# In Progress
  geom_rect(xmin = 41, xmax = 44, ymin = 45, ymax = 55, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 50, y = 44, label = 'In Progress', size = 2) +
  geom_rect(xmin = 41, xmax = 44, ymin = 45, ymax = 55, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 55.5, y = 44, label = hcv_dash_in_progress, size = 2, color = 'black') +
  annotate('text', x = 60, y = 44, label = hcv_dash_in_progress_percent, size = 2, color = 'goldenrod4') +
  
  
  # Reasons for No Follow-up
  geom_rect(xmin = 83, xmax = 100, ymin = 45, ymax = 55, color = NA,
            fill = 'white', size = 0.25) +
  annotate('text', x = 86, y = 65.25, label = 'Already Linked   ', size = 2) +
annotate('text', x = 86, y = 62.25, label = 'Deceased    ', size = 2) +
annotate('text', x = 86, y = 59.25, label = 'Incarcerated    ', size = 2) +
annotate('text', x = 86, y = 56.25, label = 'Inability to contact ', size = 2) +
annotate('text', x = 86, y = 53.25, label = 'Declined     ', size = 2) +
annotate('text', x = 86, y = 50.25, label = 'Med staff interferes', size = 2) +
annotate('text', x = 86, y = 47.25, label = 'Family interferes', size = 2) +
annotate('text', x = 86, y = 44.25, label = 'Refuses to talk', size = 2) +
annotate('text', x = 86, y = 41.25, label = 'Personal safety', size = 2) +
annotate('text', x = 86, y = 38.25, label = 'Medical course', size = 2) +
annotate('text', x = 86, y = 35.25, label = 'Unable to contact', size = 2) +
annotate('text', x = 86, y = 32.25, label = 'Language barrier', size = 2) +
annotate('text', x = 86, y = 29.25, label = 'Other', size = 2) +
  geom_rect(xmin = 41, xmax = 63, ymin = 45, ymax = 55, color = NA,
            fill = NA, size = 0.25) +
annotate('text', x = 92, y = 65.25, label = hcv_dash_already_linked, size = 2, color = 'black') +
  annotate('text', x = 96, y = 65.25, label = hcv_dash_already_linked_percent, size = 2, color = 'goldenrod4') +
annotate('text', x = 92, y = 62.25, label = hcv_dash_deceased, size = 2, color = 'black') +
  annotate('text', x = 96, y = 62.25, label = hcv_dash_deceased_percent, size = 2, color = 'goldenrod4') +
annotate('text', x = 92, y = 59.25, label = hcv_dash_incarcerated, size = 2, color = 'black') +
  annotate('text', x = 96, y = 59.25, label = hcv_dash_incarcerated_percent, size = 2, color = 'goldenrod4') +
annotate('text', x = 92, y = 56.25, label = hcv_dash_inability_to_contact, size = 2, color = 'black') +
  annotate('text', x = 96, y = 56.25, label = hcv_dash_inability_to_contact_percent, size = 2, color = 'goldenrod4') +
annotate('text', x = 92, y = 53.25, label = hcv_dash_linkage_declined, size = 2, color = 'black') +
  annotate('text', x = 96, y = 53.25, label = hcv_dash_linkage_declined_percent, size = 2, color = 'goldenrod4') +
  annotate('text', x = 92, y = 50.25, label = hcv_dash_not_linked_med_staff, size = 2, color = 'black') +
  annotate('text', x = 96, y = 50.25, label = hcv_dash_not_linked_med_staff_percent, size = 2, color = 'goldenrod4') +
annotate('text', x = 92, y = 47.25, label = hcv_dash_not_linked_family, size = 2, color = 'black') +
  annotate('text', x = 96, y = 47.25, label = hcv_dash_not_linked_family_percent, size = 2, color = 'goldenrod4') +
annotate('text', x = 92, y = 44.25, label = hcv_dash_not_linked_not_talking, size = 2, color = 'black') +
  annotate('text', x = 96, y = 44.25, label = hcv_dash_not_linked_not_talking_percent, size = 2, color = 'goldenrod4') +
annotate('text', x = 92, y = 41.25, label = hcv_dash_not_linked_safety, size = 2, color = 'black') +
  annotate('text', x = 96, y = 41.25, label = hcv_dash_not_linked_safety_percent, size = 2, color = 'goldenrod4') +
annotate('text', x = 92, y = 38.25, label = hcv_dash_not_linked_medical, size = 2, color = 'black') +
  annotate('text', x = 96, y = 38.25, label = hcv_dash_not_linked_medical_percent, size = 2, color = 'goldenrod4') +
annotate('text', x = 92, y = 35.25, label = hcv_dash_not_linked_contact, size = 2, color = 'black') +
  annotate('text', x = 96, y = 35.25, label = hcv_dash_not_linked_contact_percent, size = 2, color = 'goldenrod4') +
annotate('text', x = 92, y = 32.25, label = hcv_dash_not_linked_language, size = 2, color = 'black') +
  annotate('text', x = 96, y = 32.25, label = hcv_dash_not_linked_language_percent, size = 2, color = 'goldenrod4') +
annotate('text', x = 92, y = 29.25, label = hcv_dash_not_linked_other, size = 2, color = 'black') +
  annotate('text', x = 96, y = 29.25, label = hcv_dash_not_linked_other_percent, size = 2, color = 'goldenrod4') +
  
  
  # Follow-up Success
  geom_rect(xmin = 0, xmax = 22, ymin = 30, ymax = 40, color = 'black',
            fill = 'lightyellow', size = 0.25, size = 0.25) +
  annotate('text', x = 10.5, y = 37, label = 'EIP Follow-up Success', size = 2) +
  geom_rect(xmin = 0, xmax = 22, ymin = 30, ymax = 40, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 10.5, y = 33, label = hcv_pts_educated, size = 2, color = 'black') +
  annotate('text', x = 19, y = 33, label = hcv_pts_educated_percent, size = 2, color = 'goldenrod4') +
  
  
  # Follow-up while in ED
  geom_rect(xmin = 23, xmax = 45, ymin = 30, ymax = 40, color = NA,
            fill = NA, size = 0.25, size = 0.25) +
  annotate('text', x = 30, y = 38.5, label = 'While in the ED/Hospital', size = 2) +
  geom_rect(xmin = 23, xmax = 45, ymin = 30, ymax = 40, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 39, y = 38.5, label = hcv_pts_educated_ed, size = 2, color = 'black') +
  annotate('text', x = 43, y = 38.5, label = hcv_pts_educated_ed_percent, size = 2, color = 'goldenrod4') +
  
  
  # Follow-up via Phone Call
  geom_rect(xmin = 23, xmax = 45, ymin = 30, ymax = 40, color = NA,
            fill = NA, size = 0.25, size = 0.25) +
  annotate('text', x = 30, y = 35.5, label = 'Phone call after discharge', size = 2) +
  geom_rect(xmin = 23, xmax = 45, ymin = 30, ymax = 40, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 39, y = 35.5, label = hcv_pts_educated_phone, size = 2, color = 'black') +
  annotate('text', x = 43, y = 35.5, label = hcv_pts_educated_phone_percent, size = 2, color = 'goldenrod4') +
  
  
  # Follow-up via Other Staff
  geom_rect(xmin = 23, xmax = 45, ymin = 30, ymax = 40, color = NA,
            fill = NA, size = 0.25, size = 0.25) +
  annotate('text', x = 30, y = 32.5, label = 'Notified by Other Staff', size = 2) +
  geom_rect(xmin = 23, xmax = 45, ymin = 30, ymax = 40, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 39, y = 32.5, label = hcv_pts_educated_other, size = 2, color = 'black') +
  annotate('text', x = 43, y = 32.5, label = hcv_pts_educated_other_percent, size = 2, color = 'goldenrod4') +
  
  
  # Linkage to Care
  geom_rect(xmin = 0, xmax = 22, ymin = 0, ymax = 10, color = 'black',
            fill = 'lightyellow', size = 0.25, size = 0.25) +
  annotate('text', x = 11, y = 7, label = 'Linked to Care for HCV', size = 2) +
  geom_rect(xmin = 0, xmax = 22, ymin = 0, ymax = 10, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 10.5, y = 3, label = hcv_pts_linkage_total, size = 2, color = 'black') +
  annotate('text', x = 19, y = 3, label = hcv_pts_linkage_total_percent, size = 2, color = 'goldenrod4') +
  
  
  # Linked to UC Clinical Pharmacy
  geom_rect(xmin = 31.5, xmax = 53.5, ymin = 0, ymax = 10, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 30, y = 7, label = 'UC Clinical Pharmacy', size = 2) +
  geom_rect(xmin = 23, xmax = 53.5, ymin = 0, ymax = 10, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 39, y = 7, label = hcv_pts_linked, size = 2, color = 'black') +
  annotate('text', x = 43, y = 7, label = hcv_pts_linked_percent, size = 2, color = 'goldenrod4') +
  
  
  # Linked to Other
  geom_rect(xmin = 31.5, xmax = 53.5, ymin = 0, ymax = 10, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 30, y = 3, label = 'Other Location', size = 2) +
  geom_rect(xmin = 23, xmax = 53.5, ymin = 0, ymax = 10, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 39, y = 3, label = hcv_pts_linked_other, size = 2, color = 'black') +
  annotate('text', x = 43, y = 3, label = hcv_pts_linked_other_percent, size = 2, color = 'goldenrod4') +
  
  
  # HCV RNA Positive
  geom_rect(xmin = 78, xmax = 100, ymin = 0, ymax = 10, color = 'black',
            fill = 'darkseagreen1', size = 0.25) +
  annotate('text', x = 89, y = 7, label = 'Known HCV RNA+ Patients', size = 2) +
  geom_rect(xmin = 78, xmax = 100, ymin = 0, ymax = 10, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 88.5, y = 3, label = hcv_pts_rna_pos, size = 2, color = 'black') +
  annotate('text', x = 97, y = 3, label = hcv_pts_rna_pos_percent, size = 2, color = 'goldenrod4') +
  
  
  # Down Arrow 1
  geom_segment(
    x = 10.5, xend = 10.5, y = 90, yend = 70, 
    size = 0.15, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(2,"mm"), type = "closed")) +
  
  # Down Arrow 2
  geom_segment(
    x = 10.5, xend = 10.5, y = 60, yend = 40, 
    size = 0.15, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(2,"mm"), type = "closed")) +
  
  # Down Arrow 3
  geom_segment(
    x = 10.5, xend = 10.5, y = 30, yend = 10, 
    size = 0.15, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(2,"mm"), type = "closed")) +
  
  # Right Arrow 1
  geom_segment(
    x = 10.5, xend = 41, y = 80, yend = 80, 
    size = 0.05, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(1,"mm"), type = "closed"), color = 'darkgray') +
  
  # Right Arrow 2
  geom_segment(
    x = 10.5, xend = 41, y = 50, yend = 50, 
    size = 0.05, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(1,"mm"), type = "closed"), color = 'darkgray') +
  
  # Right Line 1
  geom_segment(
    x = 63, xend = 81, y = 80, yend = 80, 
    size = 0.15, linejoin = "mitre", lineend = "butt", linetype = "dotted") +
  
  # Right Line 2
  geom_segment(
    x = 63, xend = 81, y = 50, yend = 50, 
    size = 0.15, linejoin = "mitre", lineend = "butt", linetype = "dotted") ->
  grid

grid + theme_void()

```
<br>

As already mentioned, there were a total of `r hcv_pts_ab_positive` HCV Ab+ patients from the Epic HCV Dashboard. There were a total of `r no_eip_record_hcv_ab_pos` patients (*`r no_eip_record_hcv_ab_pos_percent` of all HCV Ab+ patients, `r no_eip_record_hcv_ab_pos`/`r hcv_pts_ab_positive`*) that currently do not have an EIP record created for follow-up regarding their HCV Ab+ result, which are in the process of being added. Based on further HCH RNA testing or recent medical record review, it is known that **`r hcv_pts_rna_neg` patients** are currently HCV RNA negative (*`r hcv_pts_rna_neg_percent` of all those identified as HCV Ab+ through the HCV Dashboard, `r hcv_pts_rna_neg`/`r hcv_pts_ab_positive`*). While EIP is not calling all those identified as HCV RNA negative to discuss those results due to the additional effort that would be, we do try to notify these patients and provide additional education and interpretation of these results if we catch them while they are still in the ED/hospital. The total number of patients EIP has provided follow-up education after their HCV RNA results negative is **`r hcv_pts_rna_neg_fu` patients** (*`r hcv_pts_rna_neg_fu_percent` of all those identified as HCV RNA negative, `r hcv_pts_rna_neg_fu`/`r hcv_pts_rna_neg`*).

Therefore, the number of patients who were identified as HCV Ab+ but either are HCV RNA positive or do not have a RNA lab resulted was **`r hcv_pts_fu_needed` patients** needing follow-up education and referral (*`r hcv_pts_fu_needed_percent` of all those HCV Ab+ from the Epic HCV Dashboard, `r hcv_pts_fu_needed`/`r hcv_pts_ab_positive`*). This means that EIP has been unable to follow-up with **`r hcv_pts_no_education` patients** who were HCV Ab+ and need follow-up results/education (*`r hcv_pts_no_education_percent` of all those HCV Ab+ from the Epic HCV Dashboard needing follow-up, `r hcv_pts_no_education`/`r hcv_pts_fu_needed`*)

Out of those patients that needed follow-up, EIP staff were able to approach and provide results/education to **`r hcv_pts_educated` patients** (*`r hcv_pts_educated_percent` of all those identified as HCV Ab+ through the HCV Dashboard needing follow-up, `r hcv_pts_educated`/`r hcv_pts_fu_needed`*). EIP makes every attempt to approach the patient while they are still located in the ED or admitted to the hospital. The number of patients where EIP was able to initiate face-to-face contact while they were still in the hospital (whether in the ED or roomed elsewhere) was **`r hcv_pts_educated_ed` patients** (*`r hcv_pts_educated_ed_percent` of all HCV Ab positive patients that were provided with education, `r hcv_pts_educated_ed`/`r hcv_pts_educated`*). If EIP is unable to approach patients while they were still in the ED/hospital, then attempts are made to follow-up with them using the contact information collected during ED intake. The number of patients where EIP was able to contact them after discharge was **`r hcv_pts_educated_phone` patients** (*`r hcv_pts_educated_phone_percent` of all HCV Ab positive patients that were provided with education, `r hcv_pts_educated_phone`/`r hcv_pts_educated`*). Additionally, if EIP is aware that an individual was provided with their results, education, and follow-up linkage referral by other staff through their typical ED treatment and care, then we monitor the case rather than direct involvement in order to decrease duplication of work in getting the patient linked to care. The number of patients where EIP was aware that the patient has been referred for HCV treatment by other staff was **`r hcv_pts_educated_other` patients** (*`r hcv_pts_educated_other_percent` of all HCV Ab positive patients that were provided with education, `r hcv_pts_educated_other`/`r hcv_pts_educated`*).

The EIP REDCap Database allows for documentation regarding referral to UC Clinical Pharmacy, as well as linkage to other locations that can manage/treat their HCV. The total number of patients that have been linked to care for HCV was **`r hcv_pts_linkage_total` patients** (*`r hcv_pts_linkage_total_percent` of all those EIP provided education to, `r hcv_pts_linkage_total`/`r hcv_pts_educated`*). The number of patients that were linked to care specifically to the UC Clinical Pharmacy was **`r hcv_pts_linked` patients** (*`r hcv_pts_linked_percent` of all those patients linked to care, `r hcv_pts_linked`/`r hcv_pts_linkage_total`*). Once EIP refers a patient to UC Clinical Pharmacy and gets them scheduled, they are documented as linked to care. It is our current process that UC Clinical Pharmacy will manage and follow-up with those individuals who do not successfully attend those appointments, re-linking them as needed. However, our documentation ends once the referral is made and the appointment is scheduled. The number of patients that were linked to care to a location other than the UC Clinical Pharmacy for HCV treatment is **`r hcv_pts_linked_other` patients** (*`r hcv_pts_linked_other_percent` of all those patients linked to care, `r hcv_pts_linked_other`/`r hcv_pts_linkage_total`*).

As part of EIP's follow-up efforts, we try to ensure anyone who is HCV Ab+ has the necessary lab testing to know if they are currently infected with HCV by facilitating RNA testing when appropriate. The total number of patients that had a follow-up RNA test documented within their EIP REDCap record was **`r hcv_pts_rna_known` patients** (*`r hcv_pts_rna_known_percent` of all those HCV Ab+, `r hcv_pts_rna_known`/`r hcv_pts_ab_positive`*). As mentioned above, there were a total of `r hcv_pts_rna_neg` patients that were negative for HCV RNA, which is `r hcv_pts_rna_neg_percent` of all those with a known HCV RNA result (*`r hcv_pts_rna_neg`/`r hcv_pts_rna_known`*). For those patients that were tested for RNA, the total number of those that were found to be true positives for HCV was **`r hcv_pts_rna_pos` patients** (*`r hcv_pts_rna_pos_percent` of all those tested for HCV RNA, `r hcv_pts_rna_pos`/`r hcv_pts_rna_known`*).



<br>

### Staff Coverage

In order to evaluate whether we have appropriate EIP staff coverage for this project, this section looks at the time that the HCV Ab test results are available and whether there is an EIP staff member dedicated for this project on staff. Therefore, we can know whether our staff is available to approach the patient in the ED/hospital when the lab results.

::: {.callout-warning collapse="true"}
## Lab Result times.
HCV Epic Dashboard dataset does not include Lab Result times. The result times for the labs are estimated using the Order Date/Time of the test and the average resulting time for HCV antibody tests based on CHI lab data.
:::

The HCV Dashboard does not include result times for the labs. Therefore, an average HCV Ab lab result time was calculated from CHI HCV Ab lab data and used here (*CHI HCV Ab lab result times average is about [3 hours and 53 minutes]{.underline}*). The HCV Ab dashboard lab result times were estimated by adding this average lab result time from the CHI lab data onto the Order Date/Time values for the dashboard labs. Since these are estimated lab result times, there is some variability in this data. Also, since these are estimates, EIP staff coverage times are estimated since those can vary slightly week to week.

Since these lab result times are estimates, they have been categorized into four categories to simplify the plot: [Overnight]{.underline} (12am-5:59am), [Morning]{.underline} (6am-11:59am), [Afternoon]{.underline} (12pm-5:59pm), and [Evening]{.underline} (6pm-11:59pm). Employee staff coverage is used an estimated based on these same parameters. Current staff coverage was used based on the staff shift schedule noted below:

- *RK: Monday-Thursday (7am-5pm; morning-afternoon) or Tuesday-Friday (7am-5pm; morning-afternoon), alternating weeks*

- *JF: Monday and Friday (10am-10pm; morning-evening) and Tuesday (9am-9pm; morning-evening)*

- *KA: Wednesday-Sunday (3pm-11pm; afternoon-evening)*


Therefore, it is estimated that EIP staff is available for this project during most day/times except for the overnight shifts for each day.

The plot below shows the days and time periods of the estimated HCV Ab+ lab result times, as well as the times that there is EIP coverage. The frequency shows the total number of HCV Ab+ results for each day/time since the start of the project. The colored bars indicates that there is EIP staff scheduled during this time to respond to the HCV Dashboard and approach those patients who are HCV Ab+.

<br>

```{r, echo = FALSE, fig.frame="black"}

hcv_staff_coverage <- ggplot(hcv_ab_pos_summary, aes(x = result_day_time, y = frequency, text = paste("Frequency:", frequency, "<br>Day and Time Period:", result_day_time))) +
  geom_bar(aes(fill = has_coverage), stat = "identity", color = "black", show.legend = FALSE) +
  labs(title = "Frequency of HCV Ab+ Results by Day/Time Period Estimates",
       x = "Day and Time Period Estimates",
       y = "Total Frequency") +
  scale_fill_manual(values = c("FALSE" = "white", "TRUE" = "lightskyblue"), guide = FALSE) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none") +
  geom_vline(xintercept = seq(4.5, length(unique(hcv_ab_pos_summary$result_day_time)), by = 4), color = "gray", linetype = "dashed")
hcv_staff_coverage <- ggplotly(hcv_staff_coverage, tooltip = "text") %>%
  plotly::config(displayModeBar = FALSE)
hcv_staff_coverage

```

<br>

The table below summarizes the total number of HCV Ab+ results where an EIP staff member assigned for this project was on shift, and the percentage of the total HCV Ab+ results. This table indicates that **EIP staff was available during `r hcv_ab_pos_with_coverage_percent` of the HCV Ab+ labs** when they were estimated to have resulted and appear in the HCV Dashboard (*`r hcv_ab_pos_with_coverage`/`r hcv_ab_pos_total`*). Also, this table shows that **EIP staff was not on shift for this project during `r hcv_ab_pos_without_coverage_percent` of the HCV Ab+ labs** when they were estimated to have resulted (*`r hcv_ab_pos_without_coverage`/`r hcv_ab_pos_total`*). *Reminder: this is looking at the total number of HCV Ab positive tests (n = `r hcv_ab_pos_total`), rather than the unique number of patients positive for HCV Ab (n = `r hcv_pts_ab_positive`) as used in the EIP follow-up flow diagram.*

<br>

```{r, echo = FALSE}

# Table of HCV Ab+ with EIP Coverage
hcv_ab_pos_coverage_tbl <- data.frame(matrix(ncol = 3, nrow = 0))
colnames(hcv_ab_pos_coverage_tbl) <- c('', 'Total Frequency', 'Percent')
hcv_ab_pos_coverage_tbl[nrow(hcv_ab_pos_coverage_tbl) + 1,] <- list('With EIP Coverage', hcv_ab_pos_with_coverage, hcv_ab_pos_with_coverage_percent)
hcv_ab_pos_coverage_tbl[nrow(hcv_ab_pos_coverage_tbl) + 1,] <- list('Without EIP Coverage', hcv_ab_pos_without_coverage, hcv_ab_pos_without_coverage_percent)
hcv_ab_pos_coverage_tbl %>%
  kbl(align = 'lcc') %>%
  kable_styling(full_width = F, font_size = 12)

```


<br>
<br>
<br>

## Additional Items still to add to this report.
Additional items still in development for this report include: Add reasons for no follow-up (rsns linkage declined/prevented)

<br>
<br>
<br>


## EIP HCV Testing & Linkage

The flow diagram below shows the total linkage to care efforts for EIP in regards to HCV.


```{r, echo=FALSE, warning=FALSE}

grid_data <- tibble(x= 1:100, y= 1:100)

grid_data %>% 
  ggplot(aes(x, y)) +
  scale_x_continuous(minor_breaks = seq(10, 100, 10)) +
  scale_y_continuous(minor_breaks = seq(10, 100, 10)) +
  theme_linedraw() ->
  grid


grid +
  # HCV Linkage Cases
  geom_rect(xmin = 0, xmax = 22, ymin = 90, ymax = 100, color = 'black',
            fill = 'khaki1', size = 0.25, size = 0.25) +
  annotate('text', x = 10.5, y = 97, label = 'HCV Linkage Cases', size = 2) +
  geom_rect(xmin = 0, xmax = 22, ymin = 90, ymax = 100, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 10.5, y = 93, label = hcv_ltc, size = 2, color = 'goldenrod3') +
  
  # Ineligible for Linkage
  geom_rect(xmin = 41, xmax = 63, ymin = 75, ymax = 85, color = 'gray',
            fill = 'white', size = 0.25) +
  annotate('text', x = 52.5, y = 82, label = 'Ineligible for Linkage', size = 2) +
  geom_rect(xmin = 41, xmax = 63, ymin = 75, ymax = 85, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 51.5, y = 78, label = hcv_ineligible_ltc, size = 2, color = 'goldenrod3') +
  annotate('text', x = 60, y = 78, label = hcv_ineligible_ltc_percent, size = 2, color = 'yellow4') +
  
  
  # Reasons Ineligible for Linkage
  geom_rect(xmin = 83, xmax = 100, ymin = 75, ymax = 85, color = NA,
            fill = 'white', size = 0.25) +
  annotate('text', x = 87, y = 85, label = 'Already Linked', size = 2) +
  annotate('text', x = 87, y = 82, label = '        Deceased', size = 2) +
  annotate('text', x = 87, y = 79, label = '    Incarcerated', size = 2) +
  annotate('text', x = 87, y = 76, label = 'Inability to Contact', size = 2) +
  annotate('text', x = 87, y = 73, label = '          Declined', size = 2) +
  annotate('text', x = 87, y = 70, label = 'Ongoing linkage ', size = 2) +
  geom_rect(xmin = 41, xmax = 63, ymin = 75, ymax = 85, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 94, y = 85, label = hcv_already_linked, size = 2, color = 'goldenrod3') +
  annotate('text', x = 98, y = 85, label = hcv_already_linked_percent, size = 2, color = 'yellow4') +
  annotate('text', x = 94, y = 82, label = hcv_deceased, size = 2, color = 'goldenrod3') +
  annotate('text', x = 98, y = 82, label = hcv_deceased_percent, size = 2, color = 'yellow4') +
  annotate('text', x = 94, y = 79, label = hcv_incarcerated, size = 2, color = 'goldenrod3') +
  annotate('text', x = 98, y = 79, label = hcv_incarcerated_percent, size = 2, color = 'yellow4') +
  annotate('text', x = 94, y = 76, label = hcv_inability_to_contact, size = 2, color = 'goldenrod3') +
  annotate('text', x = 98, y = 76, label = hcv_inability_to_contact_percent, size = 2, color = 'yellow4') +
  annotate('text', x = 94, y = 73, label = hcv_linkage_declined, size = 2, color = 'goldenrod3') +
  annotate('text', x = 98, y = 73, label = hcv_linkage_declined_percent, size = 2, color = 'yellow4') +
  annotate('text', x = 94, y = 70, label = hcv_ongoing_linkage, size = 2, color = 'goldenrod3') +
  annotate('text', x = 98, y = 70, label = hcv_ongoing_linkage_percent, size = 2, color = 'yellow4') +
  
  
  # Eligible for Linkage
  geom_rect(xmin = 0, xmax = 22, ymin = 60, ymax = 70, color = 'black',
            fill = 'khaki1', size = 0.25, size = 0.25) +
  annotate('text', x = 10.5, y = 67, label = 'Eligible for Linkage', size = 2) +
  geom_rect(xmin = 0, xmax = 22, ymin = 60, ymax = 70, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 10.5, y = 63, label = hcv_eligible_ltc, size = 2, color = 'goldenrod3') +
  annotate('text', x = 19, y = 63, label = hcv_eligible_ltc_percent, size = 2, color = 'yellow4') +
  
  
  # New vs. Prev vs. Unk Eligibility
  geom_rect(xmin = 25, xmax = 35, ymin = 60, ymax = 70, color = NA,
            fill = 'white', size = 0.25, size = 0.25) +
  annotate('text', x = 26, y = 69, label = 'New Dx:', size = 2) +
  annotate('text', x = 26, y = 65, label = 'Prev Dx:', size = 2) +
  annotate('text', x = 26, y = 61, label = 'Unk Dx:', size = 2) +
  geom_rect(xmin = 0, xmax = 22, ymin = 60, ymax = 70, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 30, y = 69, label = hcv_new_eligible_ltc, size = 2, color = 'goldenrod3') +
  annotate('text', x = 34, y = 69, label = hcv_new_eligible_ltc_percent, size = 2, color = 'yellow4') +
  annotate('text', x = 30, y = 65, label = hcv_prev_eligible_ltc, size = 2, color = 'goldenrod3') +
  annotate('text', x = 34, y = 65, label = hcv_prev_eligible_ltc_percent, size = 2, color = 'yellow4') +
  annotate('text', x = 30, y = 61, label = hcv_unk_eligible_ltc, size = 2, color = 'goldenrod3') +
  annotate('text', x = 34, y = 61, label = hcv_unk_eligible_ltc_percent, size = 2, color = 'yellow4') +
  
  
  # In Progress
  geom_rect(xmin = 41, xmax = 63, ymin = 45, ymax = 55, color = 'gray',
            fill = 'white', size = 0.25) +
  annotate('text', x = 50.5, y = 52, label = 'In Progress', size = 2) +
  geom_rect(xmin = 41, xmax = 63, ymin = 45, ymax = 55, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 51.5, y = 48, label = hcv_in_progress, size = 2, color = 'goldenrod3') +
  annotate('text', x = 60, y = 48, label = hcv_in_progress_percent, size = 2, color = 'yellow4') +
  
  
  # In Progress over 90 days
  geom_rect(xmin = 41, xmax = 63, ymin = 37, ymax = 44, color = NA,
            fill = 'white', size = 0.25, size = 0.25) +
  annotate('text', x = 52, y = 42, label = '>90 days:', size = 2) +
  geom_rect(xmin = 41, xmax = 63, ymin = 37, ymax = 44, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 56, y = 42, label = hcv_in_progress_90days, size = 2, color = 'goldenrod3') +
  annotate('text', x = 60, y = 42, label = hcv_in_progress_90days_percent, size = 2, color = 'yellow4') +
  
  
  # New vs. Prev vs. Unk In Progress
  geom_rect(xmin = 66, xmax = 88, ymin = 45, ymax = 55, color = NA,
            fill = 'white', size = 0.25, size = 0.25) +
  annotate('text', x = 67, y = 54, label = 'New Dx:', size = 2) +
  annotate('text', x = 67, y = 50, label = 'Prev Dx:', size = 2) +
  annotate('text', x = 67, y = 46, label = 'Unk Dx:', size = 2) +
  geom_rect(xmin = 66, xmax = 88, ymin = 45, ymax = 55, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 71, y = 54, label = hcv_new_in_progress, size = 2, color = 'goldenrod3') +
  annotate('text', x = 75, y = 54, label = hcv_new_in_progress_percent, size = 2, color = 'yellow4') +
  annotate('text', x = 71, y = 50, label = hcv_prev_in_progress, size = 2, color = 'goldenrod3') +
  annotate('text', x = 75, y = 50, label = hcv_prev_in_progress_percent, size = 2, color = 'yellow4') +
  annotate('text', x = 71, y = 46, label = hcv_unk_in_progress, size = 2, color = 'goldenrod3') +
  annotate('text', x = 75, y = 46, label = hcv_unk_in_progress_percent, size = 2, color = 'yellow4') +
  
  
  # Closed Cases
  geom_rect(xmin = 0, xmax = 22, ymin = 30, ymax = 40, color = 'black',
            fill = 'khaki1', size = 0.25, size = 0.25) +
  annotate('text', x = 10.5, y = 37, label = 'Closed Cases', size = 2) +
  geom_rect(xmin = 0, xmax = 22, ymin = 30, ymax = 40, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 10.5, y = 33, label = hcv_closed_case, size = 2, color = 'goldenrod3') +
  annotate('text', x = 19, y = 33, label = hcv_closed_case_percent, size = 2, color = 'yellow4') +
  
  
  # Not Linked
  geom_rect(xmin = 41, xmax = 63, ymin = 15, ymax = 25, color = 'gray',
            fill = 'white', size = 0.25) +
  annotate('text', x = 50.5, y = 22, label = 'Not Linked', size = 2) +
  geom_rect(xmin = 41, xmax = 63, ymin = 15, ymax = 25, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 51.5, y = 18, label = hcv_not_linked, size = 2, color = 'goldenrod3') +
  annotate('text', x = 60, y = 18, label = hcv_not_linked_percent, size = 2, color = 'yellow4') +
  
  
  # New vs. Prev Not Linked
  geom_rect(xmin = 41, xmax = 63, ymin = 7, ymax = 14, color = NA,
            fill = 'white', size = 0.25, size = 0.25) +
  annotate('text', x = 52, y = 12, label = 'New Dx:', size = 2) +
  annotate('text', x = 52, y = 8, label = 'Prev Dx:', size = 2) +
  geom_rect(xmin = 41, xmax = 63, ymin = 7, ymax = 14, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 56, y = 12, label = hcv_new_not_linked, size = 2, color = 'goldenrod3') +
  annotate('text', x = 60, y = 12, label = hcv_new_not_linked_percent, size = 2, color = 'yellow4') +
  annotate('text', x = 56, y = 8, label = hcv_prev_not_linked, size = 2, color = 'goldenrod3') +
  annotate('text', x = 60, y = 8, label = hcv_prev_not_linked_percent, size = 2, color = 'yellow4') +
  
  
  # Reasons Not Linked
  geom_rect(xmin = 83, xmax = 100, ymin = 0, ymax = 30, color = NA,
            fill = 'white', size = 0.25) +
  annotate('text', x = 87, y = 26, label = 'Med Staff interferes    ', size = 2) +
  annotate('text', x = 87, y = 23, label = '  Family interferes', size = 2) +
  annotate('text', x = 87, y = 20, label = '    Refuses to talk', size = 2) +
  annotate('text', x = 87, y = 17, label = '    Personal safety', size = 2) +
  annotate('text', x = 87, y = 14, label = '    Medical course', size = 2) +
  annotate('text', x = 87, y = 11, label = 'Inability to contact', size = 2) +
  annotate('text', x = 87, y = 8, label = ' Language barrier', size = 2) +
  annotate('text', x = 87, y = 5, label = '                   Other', size = 2) +
  geom_rect(xmin = 41, xmax = 63, ymin = 0, ymax = 30, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 94, y = 26, label = hcv_not_linked_med_staff, size = 2, color = 'goldenrod3') +
  annotate('text', x = 98, y = 26, label = hcv_not_linked_med_staff_percent, size = 2, color = 'yellow4') +
  annotate('text', x = 94, y = 23, label = hcv_not_linked_family, size = 2, color = 'goldenrod3') +
  annotate('text', x = 98, y = 23, label = hcv_not_linked_family_percent, size = 2, color = 'yellow4') +
  annotate('text', x = 94, y = 20, label = hcv_not_linked_not_talking, size = 2, color = 'goldenrod3') +
  annotate('text', x = 98, y = 20, label = hcv_not_linked_not_talking_percent, size = 2, color = 'yellow4') +
  annotate('text', x = 94, y = 17, label = hcv_not_linked_safety, size = 2, color = 'goldenrod3') +
  annotate('text', x = 98, y = 17, label = hcv_not_linked_safety_percent, size = 2, color = 'yellow4') +
  annotate('text', x = 94, y = 14, label = hcv_not_linked_medical, size = 2, color = 'goldenrod3') +
  annotate('text', x = 98, y = 14, label = hcv_not_linked_medical_percent, size = 2, color = 'yellow4') +
  annotate('text', x = 94, y = 11, label = hcv_not_linked_contact, size = 2, color = 'goldenrod3') +
  annotate('text', x = 98, y = 11, label = hcv_not_linked_contact_percent, size = 2, color = 'yellow4') +
  annotate('text', x = 94, y = 8, label = hcv_not_linked_language, size = 2, color = 'goldenrod3') +
  annotate('text', x = 98, y = 8, label = hcv_not_linked_language_percent, size = 2, color = 'yellow4') +
  annotate('text', x = 94, y = 5, label = hcv_not_linked_other, size = 2, color = 'goldenrod3') +
  annotate('text', x = 98, y = 5, label = hcv_not_linked_other_percent, size = 2, color = 'yellow4') +
  
  
  # Linked to Care
  geom_rect(xmin = 0, xmax = 22, ymin = 0, ymax = 10, color = 'black',
            fill = 'khaki1', size = 0.25, size = 0.25) +
  annotate('text', x = 10.5, y = 7, label = 'Linked to Care', size = 2) +
  geom_rect(xmin = 0, xmax = 22, ymin = 0, ymax = 10, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 10.5, y = 3, label = hcv_linked, size = 2, color = 'goldenrod3') +
  annotate('text', x = 19, y = 3, label = hcv_linked_percent, size = 2, color = 'yellow4') +
  
  
  # New vs. Prev Linked to Care
  geom_rect(xmin = 25, xmax = 35, ymin = 0, ymax = 10, color = NA,
            fill = 'white', size = 0.25, size = 0.25) +
  annotate('text', x = 26, y = 7, label = 'New Dx:', size = 2) +
  annotate('text', x = 26, y = 3, label = 'Prev Dx:', size = 2) +
  geom_rect(xmin = 0, xmax = 22, ymin = 0, ymax = 10, color = NA,
            fill = NA, size = 0.25) +
  annotate('text', x = 30, y = 7, label = hcv_new_linked, size = 2, color = 'goldenrod3') +
  annotate('text', x = 34, y = 7, label = hcv_new_linked_percent, size = 2, color = 'yellow4') +
  annotate('text', x = 30, y = 3, label = hcv_prev_linked, size = 2, color = 'goldenrod3') +
  annotate('text', x = 34, y = 3, label = hcv_prev_linked_percent, size = 2, color = 'yellow4') +
  
  
  # Down Arrow 1
  geom_segment(
    x = 10.5, xend = 10.5, y = 90, yend = 70, 
    size = 0.15, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(2,"mm"), type = "closed")) +
  
  # Down Arrow 2
  geom_segment(
    x = 10.5, xend = 10.5, y = 60, yend = 40, 
    size = 0.15, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(2,"mm"), type = "closed")) +
  
  # Down Arrow 3
  geom_segment(
    x = 10.5, xend = 10.5, y = 30, yend = 10, 
    size = 0.15, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(2,"mm"), type = "closed")) +
  
  # Right Arrow 1
  geom_segment(
    x = 10.5, xend = 41, y = 80, yend = 80, 
    size = 0.05, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(1,"mm"), type = "closed"), color = 'darkgray') +
  
  # Right Arrow 2
  geom_segment(
    x = 10.5, xend = 41, y = 50, yend = 50, 
    size = 0.05, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(1,"mm"), type = "closed"), color = 'darkgray') +
  
  # Right Arrow 3
  geom_segment(
    x = 10.5, xend = 41, y = 20, yend = 20, 
    size = 0.05, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(1,"mm"), type = "closed"), color = 'darkgray') +
  
  # Right Line 1
  geom_segment(
    x = 63, xend = 81, y = 80, yend = 80, 
    size = 0.15, linejoin = "mitre", lineend = "butt", linetype = "dotted") +
  
  # Right Line 2
  geom_segment(
    x = 63, xend = 80, y = 20, yend = 20, 
    size = 0.15, linejoin = "mitre", lineend = "butt", linetype = "dotted")->
  grid

grid + theme_void()


```

