---
title: "HIV Testing"
description: |
  This will pull together all of the different HIV testing methods (CTR, EHE, NACHO, Lab) showing independent testing programs as well as total testing through EIP.
date: "`r Sys.Date()`"
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}



```

## HIV Testing - Overview


Testing for Human Immunodeficiency Virus (HIV) is a major focus for EIP, and there are several methods for testing and funding streams that are a part of the program. The various programs that involve HIV testing are covered on this page. In parallel with lab-based testing conducted within the hospital and/or clinical settings, rapid-based testing conducted by EIP has been around since the start of the program in 1998 in some form or another.


**Show table of total testing for each program and positivity rates**

**Show graph of monthly testing**


# CTR Testing 


The Counseling, Testing, and Referral to treatment (CTR) testing program...


# EHE Testing


The Ending the HIV Epidemic (EHE) testing program...


# NACHO Testing


Spot holder for NACHO definition and data.




