---
title: "HIV Testing"
description: |
  This will pull together all of the different HIV testing methods (CTR, EHE, NACCHO, Lab) showing independent testing programs as well as total testing through EIP.
date: "`r Sys.Date()`"
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}

rm(list=ls(all=T))

library(dplyr)
library(tidyverse)
library(lubridate)
library(plotly)
library(ggplot2)
library(reactable)
library(htmltools)
library(lubridate)
library(hrbrthemes)
library(gt)
library(janitor)
library(scales)
library(apyramid)


eip <- read.csv('M:/EIP Data/EIP Database/REDCap Ver 5.0/EIP Database Data 20230627_0807.csv')
dim(eip)

```

```{r, include=FALSE}

# Person-level data is only visit_001_arm_1, use to match to encounters

table(eip$redcap_event_name)
person <- eip[which(eip$redcap_event_name == 'visit_001_arm_1'), ]
dim(person)

person <- select(person, record_id, mrn, dob, 
                 race___1, race___2, race___3, race___4, race___5, race___6, ethnicity,
                 sex_raised, sex_selfdefined, insurance, address_county,
                 address_zip_code)
dim(person)

eip <- select(eip, -mrn, -dob, 
              -race___1, -race___2, -race___3, -race___4, -race___5, 
              -race___6, -ethnicity,
              -sex_raised, -sex_selfdefined, -insurance, -address_county,
              -address_zip_code)

# Merge person dataset with full eip dataset

dim(eip)
dim(person)
eip <- merge(eip, person, by='record_id', all.x=T)
dim(eip)
eip <- distinct(eip)
dim(eip)


# Formatting variables

summary(eip$enc_date)
eip$enc_date <- as.Date(eip$enc_date, format='%m/%d/%Y')
summary(eip$enc_date)

summary(eip$dob)
eip$dob <- as.Date(eip$dob, format='%m/%d/%Y')
summary(eip$dob)


table(eip$race___1)
White <- eip[which(eip$race___1 == '1'), ]
dim(White)
White <- select(White, record_id)
White$White <- 1
table(White$White)
White <- distinct(White)
dim(White)
head(White)

table(eip$race___2)
Black <- eip[which(eip$race___2 == '1'), ]
dim(Black)
Black <- select(Black, record_id)
Black$Black <- 1
table(Black$Black)
Black <- distinct(Black)
dim(Black)
head(Black)

table(eip$race___3)
Asian <- eip[which(eip$race___3 == '1'), ]
dim(Asian)
Asian <- select(Asian, record_id)
Asian$Asian <- 1
table(Asian$Asian)
Asian <- distinct(Asian)
dim(Asian)
head(Asian)

table(eip$race___4)
AmIn <- eip[which(eip$race___4 == '1'), ]
dim(AmIn)
AmIn <- select(AmIn, record_id)
AmIn$AmIn <- 1
table(AmIn$AmIn)
AmIn <- distinct(AmIn)
dim(AmIn)
head(AmIn)

table(eip$race___5)
RaceOther <- eip[which(eip$race___5 == '1'), ]
dim(RaceOther)
RaceOther <- select(RaceOther, record_id)
RaceOther$RaceOther <- 1
table(RaceOther$RaceOther)
RaceOther <- distinct(RaceOther)
dim(RaceOther)
head(RaceOther)

table(eip$race___6)
RaceUnk <- eip[which(eip$race___6 == '1'), ]
dim(RaceUnk)
RaceUnk <- select(RaceUnk, record_id)
RaceUnk$RaceUnk <- 1
table(RaceUnk$RaceUnk)
RaceUnk <- distinct(RaceUnk)
dim(RaceUnk)
head(RaceUnk)

table(eip$ethnicity)
RaceHisp <- eip[which(eip$ethnicity == 1), ]
dim(RaceHisp)
RaceHisp <- select(RaceHisp, record_id)
RaceHisp$RaceHisp <- 1
table(RaceHisp$RaceHisp)
RaceHisp <- distinct(RaceHisp)
dim(RaceHisp)
head(RaceHisp)


race <- select(eip, record_id)
race <- distinct(race)
dim(race)


dim(race)
race <- merge(race, White, by = 'record_id', all.x = T)
race <- merge(race, Black, by = 'record_id', all.x = T)
race <- merge(race, Asian, by = 'record_id', all.x = T)
race <- merge(race, AmIn, by = 'record_id', all.x = T)
race <- merge(race, RaceOther, by = 'record_id', all.x = T)
race <- merge(race, RaceUnk, by = 'record_id', all.x = T)
race <- merge(race, RaceHisp, by = 'record_id', all.x = T)
dim(race)
head(race)

race$White[is.na(race$White)] <- 0
race$Black[is.na(race$Black)] <- 0
race$Asian[is.na(race$Asian)] <- 0
race$AmIn[is.na(race$AmIn)] <- 0
race$RaceOther[is.na(race$RaceOther)] <- 0
race$RaceUnk[is.na(race$RaceUnk)] <- 0
race$RaceHisp[is.na(race$RaceHisp)] <- 0

race$RaceNumber <- race$White + race$Black + race$Asian + race$AmIn + race$RaceOther + race$RaceUnk + race$RaceHisp
table(race$RaceNumber)
head(race)

race$race[race$RaceNumber == 1 & race$Black == 1] <- 'Black/African American'
race$race[race$RaceNumber == 1 & race$White == 1] <- 'White'
race$race[race$RaceNumber == 1 & race$Asian == 1] <- 'Asian/Pacific Islander'
race$race[race$RaceNumber == 1 & race$AmIn == 1] <- 'American Indian/Alaska native'
race$race[race$RaceNumber == 1 & race$RaceOther == 1] <- 'Other'
race$race[(race$RaceNumber == 1 & race$RaceHisp == 1) |
            (race$RaceNumber > 1 & race$RaceHisp == 1)] <- 'Hispanic/Latinx'
race$race[race$RaceNumber > 1 & race$RaceHisp != 1] <- 'Biracial/Multiracial'
race$race[race$RaceNumber == 0 | is.na(race$RaceNumber) | race$RaceUnk == 1] <- 'Unknown'
table(race$race)

dim(eip)
dim(race)
eip <- merge(eip, race, by = 'record_id', all.x = T)
dim(eip)
table(eip$race)




table(eip$sex_raised)
eip$sex[eip$sex_raised == 1] <- 'Male'
eip$sex[eip$sex_raised == 2] <- 'Female'
eip$sex[eip$sex_raised == 3 | is.na(eip$sex_raised) | eip$sex_raised == ''] <- 'Unknown/Unassigned'
table(eip$sex)



table(eip$sex_raised, eip$sex_selfdefined)
eip$gender[eip$sex_raised == 1 & eip$sex_selfdefined == 1] <- 'Male'
eip$gender[eip$sex_raised == 2 & eip$sex_selfdefined == 2] <- 'Female'
eip$gender[(eip$sex_raised == 1 & eip$sex_selfdefined == 2) |
             (eip$sex_raised == 2 & eip$sex_selfdefined == 1) |
             (eip$sex_raised == 1 & eip$sex_selfdefined == 3) |
             (eip$sex_raised == 2 & eip$sex_selfdefined == 3)] <- 'Transgender/Nonbinary'
eip$gender[(eip$sex_raised == 3 & eip$sex_selfdefined == 3) |
             is.na(eip$sex_raised) | is.na(eip$sex_selfdefined)] <- 'Unknown'
table(eip$gender)


table(eip$insurance)
eip$insurance[eip$insurance == 1] <- 'None'
eip$insurance[eip$insurance == 2] <- 'UC Health (Levy)'
eip$insurance[eip$insurance == 3] <- 'Medicaid'
eip$insurance[eip$insurance == 4] <- 'Medicare'
eip$insurance[eip$insurance == 5] <- 'Military/VA'
eip$insurance[eip$insurance == 6] <- 'Private'
eip$insurance[eip$insurance == 7] <- 'Dual Medicaid/Medicare'
eip$insurance[is.na(eip$insurance)] <- 'Unknown'
table(eip$insurance)



# Populations of Interest
### WOC, Youth (18-24), MSM, IDU, HRHS, PLWHA

table(eip$race, eip$gender)
eip$WOC[(eip$race != 'White' & eip$race != 'Unknown') & eip$gender == 'Female'] <- 1
table(eip$WOC)


table(eip$age)
eip$Youth[eip$age >= 13 & eip$age <= 29] <- 1
table(eip$Youth)


eip$MSM[eip$gender == 'Male' & ((eip$sex_orientation == '2' | eip$sex_orientation == '4') |
                                  (eip$sex_w_man___1 == '1' | eip$sex_w_man___2 == '1' |
                                     eip$sex_w_man___3 == '1') |
                                  (eip$sex_w_ftm___1 == '1' | eip$sex_w_ftm___2 == '1' |
                                     eip$sex_w_ftm___3 == '1') |
                                  (eip$sex_msm___1 == '1' | eip$sex_msm___2 == '1' |
                                     eip$sex_msm___3 == '1') |
                                  (eip$hiv_dx_risks___2 == '1'))] <- 1
table(eip$MSM)


eip$IDU[eip$idu_calc == 1 | eip$hiv_dx_risks___3 == '1'] <- 1
table(eip$IDU)


# For HRHS, all sexual behavior is within the previous 12 months
### Heterosexual males that have unprotected sex with women
### Heterosexual women that have unprotected sex with men
### Heterosexual women that have sex with MSM
### Heterosexual men/women that have sex with IDU
### Heterosexual men/women that have sex with HIV+ partner
### Heterosexual men/women that exchange money/drugs for sex
### Heterosexual men/women that have sex with STD+ partner
### Heterosexual men/women that have more than 3 partners

eip$Hetero[(eip$gender == 'Male' & (eip$sex_w_woman___1 == '1' |
                                      eip$sex_w_woman___2 == '1' | eip$sex_w_woman___3 == '1')) |
             (eip$gender == 'Female' & (eip$sex_w_man___1 == '1' | eip$sex_w_man___2 == '1' |
                                          eip$sex_w_man___3 == '1'))] <- 1
table(eip$Hetero)


eip$HRHS[(eip$Hetero == 1) & ((((eip$sex_w_woman___6 == '1' | eip$sex_w_woman___7 == '1') |
                                  (is.na(eip$sex_w_woman___6) & is.na(eip$sex_w_woman___7) &
                                     is.na(eip$sex_w_woman___8)))) | (((eip$sex_w_man___6 == '1' |
                                                                          eip$sex_w_man___7 == '1') |
                                                                         (is.na(eip$sex_w_man___6) &
                                                                            is.na(eip$sex_w_man___7) &
                                                                            is.na(eip$sex_w_man___8)))) |
                                (eip$sex_msm___1 == '1' | eip$sex_msm___2 == '1' | eip$sex_msm___3 == '1') |
                                (eip$sex_idu___1 == '1' | eip$sex_idu___2 == '1' | eip$sex_idu___3 == '1') |
                                (eip$sex_hiv_pos___1 == '1' | eip$sex_hiv_pos___2 == '1' |
                                   eip$sex_hiv_pos___3 == '1') | (eip$sex_receivemoney___1 == '1' |
                                                                    eip$sex_receivemoney___2 == '1' |
                                                                    eip$sex_receivemoney___3 == '1' |
                                                                    eip$sex_receivedrugs___1 == '1' |
                                                                    eip$sex_receivedrugs___2 == '1' |
                                                                    eip$sex_receivedrugs___3 == '1' |
                                                                    eip$sex_paymoney___1 == '1' |
                                                                    eip$sex_paymoney___2 == '1' |
                                                                    eip$sex_paymoney___3 == '1' |
                                                                    eip$sex_paydrugs___1 == '1' |
                                                                    eip$sex_paydrugs___2 == '1' |
                                                                    eip$sex_paydrugs___3 == '1')  |
                                (eip$sex_sti_pos___1 == '1' | eip$sex_sti_pos___2 == '1' |
                                   eip$sex_sti_pos___3 == '1') | (eip$sex_partners_past_year >= 3))] <- 1
table(eip$HRHS)




# Appalachian

eip$appalachian_pt[eip$address_zip_code == 43006 | eip$address_zip_code == 43056 |
                     eip$address_zip_code == 43076 | eip$address_zip_code == 43101 |
                     eip$address_zip_code == 43102 | eip$address_zip_code == 43107 |
                     eip$address_zip_code == 43111 | eip$address_zip_code == 43115 |
                     eip$address_zip_code == 43127 | eip$address_zip_code == 43135 |
                     eip$address_zip_code == 43138 | eip$address_zip_code == 43144 |
                     eip$address_zip_code == 43148 | eip$address_zip_code == 43149 |
                     eip$address_zip_code == 43150 | eip$address_zip_code == 43152 |
                     eip$address_zip_code == 43155 | eip$address_zip_code == 43158 |
                     eip$address_zip_code == 43160 | eip$address_zip_code == 43164 |
                     eip$address_zip_code == 43701 | eip$address_zip_code == 43702 |
                     eip$address_zip_code == 43711 | eip$address_zip_code == 43713 |
                     eip$address_zip_code == 43716 | eip$address_zip_code == 43717 |
                     eip$address_zip_code == 43718 | eip$address_zip_code == 43719 |
                     eip$address_zip_code == 43720 | eip$address_zip_code == 43722 |
                     eip$address_zip_code == 43723 | eip$address_zip_code == 43724 |
                     eip$address_zip_code == 43725 | eip$address_zip_code == 43727 |
                     eip$address_zip_code == 43728 | eip$address_zip_code == 43730 |
                     eip$address_zip_code == 43731 | eip$address_zip_code == 43732 |
                     eip$address_zip_code == 43733 | eip$address_zip_code == 43734 |
                     eip$address_zip_code == 43735 | eip$address_zip_code == 43736 |
                     eip$address_zip_code == 43738 | eip$address_zip_code == 43739 |
                     eip$address_zip_code == 43746 | eip$address_zip_code == 43747 |
                     eip$address_zip_code == 43748 | eip$address_zip_code == 43749 |
                     eip$address_zip_code == 43750 | eip$address_zip_code == 43752 |
                     eip$address_zip_code == 43754 | eip$address_zip_code == 43755 |
                     eip$address_zip_code == 43756 | eip$address_zip_code == 43757 |
                     eip$address_zip_code == 43758 | eip$address_zip_code == 43759 |
                     eip$address_zip_code == 43760 | eip$address_zip_code == 43761 |
                     eip$address_zip_code == 43762 | eip$address_zip_code == 43764 |
                     eip$address_zip_code == 43766 | eip$address_zip_code == 43767 |
                     eip$address_zip_code == 43768 | eip$address_zip_code == 43771 |
                     eip$address_zip_code == 43772 | eip$address_zip_code == 43773 |
                     eip$address_zip_code == 43777 | eip$address_zip_code == 43778 |
                     eip$address_zip_code == 43779 | eip$address_zip_code == 43780 |
                     eip$address_zip_code == 43782 | eip$address_zip_code == 43783 |
                     eip$address_zip_code == 43786 | eip$address_zip_code == 43787 |
                     eip$address_zip_code == 43788 | eip$address_zip_code == 43791 |
                     eip$address_zip_code == 43793 | eip$address_zip_code == 43802 |
                     eip$address_zip_code == 43803 | eip$address_zip_code == 43804 |
                     eip$address_zip_code == 43805 | eip$address_zip_code == 43811 |
                     eip$address_zip_code == 43812 | eip$address_zip_code == 43821 |
                     eip$address_zip_code == 43822 | eip$address_zip_code == 43824 |
                     eip$address_zip_code == 43828 | eip$address_zip_code == 43830 |
                     eip$address_zip_code == 43832 | eip$address_zip_code == 43836 |
                     eip$address_zip_code == 43837 | eip$address_zip_code == 43840 |
                     eip$address_zip_code == 43842 | eip$address_zip_code == 43843 |
                     eip$address_zip_code == 43844 | eip$address_zip_code == 43845 |
                     eip$address_zip_code == 43901 | eip$address_zip_code == 43902 |
                     eip$address_zip_code == 43903 | eip$address_zip_code == 43905 |
                     eip$address_zip_code == 43906 | eip$address_zip_code == 43907 |
                     eip$address_zip_code == 43908 | eip$address_zip_code == 43909 |
                     eip$address_zip_code == 43910 | eip$address_zip_code == 43912 |
                     eip$address_zip_code == 43913 | eip$address_zip_code == 43914 |
                     eip$address_zip_code == 43915 | eip$address_zip_code == 43916 |
                     eip$address_zip_code == 43917 | eip$address_zip_code == 43920 |
                     eip$address_zip_code == 43925 | eip$address_zip_code == 43926 |
                     eip$address_zip_code == 43927 | eip$address_zip_code == 43928 |
                     eip$address_zip_code == 43930 | eip$address_zip_code == 43931 |
                     eip$address_zip_code == 43932 | eip$address_zip_code == 43933 |
                     eip$address_zip_code == 43934 | eip$address_zip_code == 43935 |
                     eip$address_zip_code == 43937 | eip$address_zip_code == 43938 |
                     eip$address_zip_code == 43939 | eip$address_zip_code == 43940 |
                     eip$address_zip_code == 43941 | eip$address_zip_code == 43942 |
                     eip$address_zip_code == 43943 | eip$address_zip_code == 43944 |
                     eip$address_zip_code == 43945 | eip$address_zip_code == 43946 |
                     eip$address_zip_code == 43947 | eip$address_zip_code == 43948 |
                     eip$address_zip_code == 43950 | eip$address_zip_code == 43951 |
                     eip$address_zip_code == 43952 | eip$address_zip_code == 43953 |
                     eip$address_zip_code == 43961 | eip$address_zip_code == 43962 |
                     eip$address_zip_code == 43963 | eip$address_zip_code == 43964 |
                     eip$address_zip_code == 43967 | eip$address_zip_code == 43968 |
                     eip$address_zip_code == 43970 | eip$address_zip_code == 43971 |
                     eip$address_zip_code == 43972 | eip$address_zip_code == 43973 |
                     eip$address_zip_code == 43974 | eip$address_zip_code == 43976 |
                     eip$address_zip_code == 43977 | eip$address_zip_code == 43981 |
                     eip$address_zip_code == 43983 | eip$address_zip_code == 43984 |
                     eip$address_zip_code == 43985 | eip$address_zip_code == 43986 |
                     eip$address_zip_code == 43988 | eip$address_zip_code == 44003 |
                     eip$address_zip_code == 44004 | eip$address_zip_code == 44005 |
                     eip$address_zip_code == 44010 | eip$address_zip_code == 44030 |
                     eip$address_zip_code == 44032 | eip$address_zip_code == 44041 |
                     eip$address_zip_code == 44046 | eip$address_zip_code == 44047 |
                     eip$address_zip_code == 44048 | eip$address_zip_code == 44057 |
                     eip$address_zip_code == 44062 | eip$address_zip_code == 44064 |
                     eip$address_zip_code == 44068 | eip$address_zip_code == 44076 |
                     eip$address_zip_code == 44082 | eip$address_zip_code == 44084 |
                     eip$address_zip_code == 44085 | eip$address_zip_code == 44086 |
                     eip$address_zip_code == 44088 | eip$address_zip_code == 44093 |
                     eip$address_zip_code == 44099 | eip$address_zip_code == 44231 |
                     eip$address_zip_code == 44288 | eip$address_zip_code == 44401 |
                     eip$address_zip_code == 44402 | eip$address_zip_code == 44403 |
                     eip$address_zip_code == 44404 | eip$address_zip_code == 44405 |
                     eip$address_zip_code == 44406 | eip$address_zip_code == 44408 |
                     eip$address_zip_code == 44410 | eip$address_zip_code == 44411 |
                     eip$address_zip_code == 44412 | eip$address_zip_code == 44413 |
                     eip$address_zip_code == 44415 | eip$address_zip_code == 44416 |
                     eip$address_zip_code == 44417 | eip$address_zip_code == 44418 |
                     eip$address_zip_code == 44420 | eip$address_zip_code == 44422 |
                     eip$address_zip_code == 44423 | eip$address_zip_code == 44424 |
                     eip$address_zip_code == 44425 | eip$address_zip_code == 44427 |
                     eip$address_zip_code == 44428 | eip$address_zip_code == 44429 |
                     eip$address_zip_code == 44430 | eip$address_zip_code == 44431 |
                     eip$address_zip_code == 44432 | eip$address_zip_code == 44436 |
                     eip$address_zip_code == 44437 | eip$address_zip_code == 44438 |
                     eip$address_zip_code == 44439 | eip$address_zip_code == 44440 |
                     eip$address_zip_code == 44441 | eip$address_zip_code == 44442 |
                     eip$address_zip_code == 44443 | eip$address_zip_code == 44444 |
                     eip$address_zip_code == 44445 | eip$address_zip_code == 44446 |
                     eip$address_zip_code == 44449 | eip$address_zip_code == 44450 |
                     eip$address_zip_code == 44451 | eip$address_zip_code == 44452 |
                     eip$address_zip_code == 44453 | eip$address_zip_code == 44454 |
                     eip$address_zip_code == 44455 | eip$address_zip_code == 44460 |
                     eip$address_zip_code == 44470 | eip$address_zip_code == 44471 |
                     eip$address_zip_code == 44473 | eip$address_zip_code == 44481 |
                     eip$address_zip_code == 44482 | eip$address_zip_code == 44483 |
                     eip$address_zip_code == 44484 | eip$address_zip_code == 44485 |
                     eip$address_zip_code == 44486 | eip$address_zip_code == 44490 |
                     eip$address_zip_code == 44491 | eip$address_zip_code == 44492 |
                     eip$address_zip_code == 44493 | eip$address_zip_code == 44501 |
                     eip$address_zip_code == 44502 | eip$address_zip_code == 44503 |
                     eip$address_zip_code == 44504 | eip$address_zip_code == 44505 |
                     eip$address_zip_code == 44506 | eip$address_zip_code == 44507 |
                     eip$address_zip_code == 44509 | eip$address_zip_code == 44510 |
                     eip$address_zip_code == 44511 | eip$address_zip_code == 44512 |
                     eip$address_zip_code == 44513 | eip$address_zip_code == 44514 |
                     eip$address_zip_code == 44515 | eip$address_zip_code == 44555 |
                     eip$address_zip_code == 44601 | eip$address_zip_code == 44607 |
                     eip$address_zip_code == 44608 | eip$address_zip_code == 44609 |
                     eip$address_zip_code == 44610 | eip$address_zip_code == 44611 |
                     eip$address_zip_code == 44612 | eip$address_zip_code == 44615 |
                     eip$address_zip_code == 44617 | eip$address_zip_code == 44619 |
                     eip$address_zip_code == 44620 | eip$address_zip_code == 44621 |
                     eip$address_zip_code == 44622 | eip$address_zip_code == 44624 |
                     eip$address_zip_code == 44625 | eip$address_zip_code == 44626 |
                     eip$address_zip_code == 44627 | eip$address_zip_code == 44628 |
                     eip$address_zip_code == 44629 | eip$address_zip_code == 44633 |
                     eip$address_zip_code == 44634 | eip$address_zip_code == 44637 |
                     eip$address_zip_code == 44638 | eip$address_zip_code == 44639 |
                     eip$address_zip_code == 44643 | eip$address_zip_code == 44644 |
                     eip$address_zip_code == 44651 | eip$address_zip_code == 44653 |
                     eip$address_zip_code == 44654 | eip$address_zip_code == 44656 |
                     eip$address_zip_code == 44657 | eip$address_zip_code == 44660 |
                     eip$address_zip_code == 44661 | eip$address_zip_code == 44663 |
                     eip$address_zip_code == 44665 | eip$address_zip_code == 44671 |
                     eip$address_zip_code == 44672 | eip$address_zip_code == 44675 |
                     eip$address_zip_code == 44676 | eip$address_zip_code == 44678 |
                     eip$address_zip_code == 44679 | eip$address_zip_code == 44680 |
                     eip$address_zip_code == 44681 | eip$address_zip_code == 44682 |
                     eip$address_zip_code == 44683 | eip$address_zip_code == 44687 |
                     eip$address_zip_code == 44688 | eip$address_zip_code == 44689 |
                     eip$address_zip_code == 44690 | eip$address_zip_code == 44693 |
                     eip$address_zip_code == 44695 | eip$address_zip_code == 44697 |
                     eip$address_zip_code == 44699 | eip$address_zip_code == 44730 |
                     eip$address_zip_code == 44842 | eip$address_zip_code == 45101 |
                     eip$address_zip_code == 45102 | eip$address_zip_code == 45103 |
                     eip$address_zip_code == 45105 | eip$address_zip_code == 45106 |
                     eip$address_zip_code == 45107 | eip$address_zip_code == 45112 |
                     eip$address_zip_code == 45115 | eip$address_zip_code == 45118 |
                     eip$address_zip_code == 45119 | eip$address_zip_code == 45120 |
                     eip$address_zip_code == 45121 | eip$address_zip_code == 45122 |
                     eip$address_zip_code == 45123 | eip$address_zip_code == 45130 |
                     eip$address_zip_code == 45131 | eip$address_zip_code == 45132 |
                     eip$address_zip_code == 45133 | eip$address_zip_code == 45135 |
                     eip$address_zip_code == 45140 | eip$address_zip_code == 45142 |
                     eip$address_zip_code == 45144 | eip$address_zip_code == 45147 |
                     eip$address_zip_code == 45148 | eip$address_zip_code == 45150 |
                     eip$address_zip_code == 45153 | eip$address_zip_code == 45154 |
                     eip$address_zip_code == 45155 | eip$address_zip_code == 45156 |
                     eip$address_zip_code == 45157 | eip$address_zip_code == 45158 |
                     eip$address_zip_code == 45159 | eip$address_zip_code == 45160 |
                     eip$address_zip_code == 45162 | eip$address_zip_code == 45167 |
                     eip$address_zip_code == 45168 | eip$address_zip_code == 45171 |
                     eip$address_zip_code == 45172 | eip$address_zip_code == 45176 |
                     eip$address_zip_code == 45244 | eip$address_zip_code == 45245 |
                     eip$address_zip_code == 45255 | eip$address_zip_code == 45601 |
                     eip$address_zip_code == 45612 | eip$address_zip_code == 45613 |
                     eip$address_zip_code == 45614 | eip$address_zip_code == 45616 |
                     eip$address_zip_code == 45617 | eip$address_zip_code == 45618 |
                     eip$address_zip_code == 45619 | eip$address_zip_code == 45620 |
                     eip$address_zip_code == 45621 | eip$address_zip_code == 45622 |
                     eip$address_zip_code == 45623 | eip$address_zip_code == 45624 |
                     eip$address_zip_code == 45628 | eip$address_zip_code == 45629 |
                     eip$address_zip_code == 45630 | eip$address_zip_code == 45631 |
                     eip$address_zip_code == 45633 | eip$address_zip_code == 45634 |
                     eip$address_zip_code == 45636 | eip$address_zip_code == 45638 |
                     eip$address_zip_code == 45640 | eip$address_zip_code == 45642 |
                     eip$address_zip_code == 45643 | eip$address_zip_code == 45644 |
                     eip$address_zip_code == 45645 | eip$address_zip_code == 45646 |
                     eip$address_zip_code == 45647 | eip$address_zip_code == 45648 |
                     eip$address_zip_code == 45650 | eip$address_zip_code == 45651 |
                     eip$address_zip_code == 45652 | eip$address_zip_code == 45653 |
                     eip$address_zip_code == 45654 | eip$address_zip_code == 45656 |
                     eip$address_zip_code == 45657 | eip$address_zip_code == 45658 |
                     eip$address_zip_code == 45659 | eip$address_zip_code == 45660 |
                     eip$address_zip_code == 45661 | eip$address_zip_code == 45662 |
                     eip$address_zip_code == 45663 | eip$address_zip_code == 45669 |
                     eip$address_zip_code == 45671 | eip$address_zip_code == 45672 |
                     eip$address_zip_code == 45673 | eip$address_zip_code == 45674 |
                     eip$address_zip_code == 45675 | eip$address_zip_code == 45677 |
                     eip$address_zip_code == 45678 | eip$address_zip_code == 45679 |
                     eip$address_zip_code == 45680 | eip$address_zip_code == 45681 |
                     eip$address_zip_code == 45682 | eip$address_zip_code == 45683 |
                     eip$address_zip_code == 45684 | eip$address_zip_code == 45685 |
                     eip$address_zip_code == 45686 | eip$address_zip_code == 45687 |
                     eip$address_zip_code == 45688 | eip$address_zip_code == 45690 |
                     eip$address_zip_code == 45692 | eip$address_zip_code == 45693 |
                     eip$address_zip_code == 45694 | eip$address_zip_code == 45695 |
                     eip$address_zip_code == 45696 | eip$address_zip_code == 45697 |
                     eip$address_zip_code == 45698 | eip$address_zip_code == 45699 |
                     eip$address_zip_code == 45701 | eip$address_zip_code == 45710 |
                     eip$address_zip_code == 45711 | eip$address_zip_code == 45712 |
                     eip$address_zip_code == 45713 | eip$address_zip_code == 45714 |
                     eip$address_zip_code == 45715 | eip$address_zip_code == 45716 |
                     eip$address_zip_code == 45717 | eip$address_zip_code == 45719 |
                     eip$address_zip_code == 45720 | eip$address_zip_code == 45721 |
                     eip$address_zip_code == 45723 | eip$address_zip_code == 45724 |
                     eip$address_zip_code == 45727 | eip$address_zip_code == 45729 |
                     eip$address_zip_code == 45732 | eip$address_zip_code == 45734 |
                     eip$address_zip_code == 45735 | eip$address_zip_code == 45739 |
                     eip$address_zip_code == 45740 | eip$address_zip_code == 45741 |
                     eip$address_zip_code == 45742 | eip$address_zip_code == 45743 |
                     eip$address_zip_code == 45744 | eip$address_zip_code == 45745 |
                     eip$address_zip_code == 45746 | eip$address_zip_code == 45750 |
                     eip$address_zip_code == 45760 | eip$address_zip_code == 45761 |
                     eip$address_zip_code == 45764 | eip$address_zip_code == 45766 |
                     eip$address_zip_code == 45767 | eip$address_zip_code == 45768 |
                     eip$address_zip_code == 45769 | eip$address_zip_code == 45770 |
                     eip$address_zip_code == 45771 | eip$address_zip_code == 45772 |
                     eip$address_zip_code == 45773 | eip$address_zip_code == 45775 |
                     eip$address_zip_code == 45776 | eip$address_zip_code == 45777 |
                     eip$address_zip_code == 45778 | eip$address_zip_code == 45779 |
                     eip$address_zip_code == 45780 | eip$address_zip_code == 45782 |
                     eip$address_zip_code == 45783 | eip$address_zip_code == 45784 |
                     eip$address_zip_code == 45786 | eip$address_zip_code == 45787 |
                     eip$address_zip_code == 45788 | eip$address_zip_code == 45789 |
                     (eip$appalachian == 1 | eip$appalachian_family == 1)] <- 1
table(eip$appalachian_pt)




###############################################################################################################
#########################################  Creating Encounter Dataset  ########################################
###############################################################################################################

summary(eip$enc_date)
enc <- eip[which(eip$enc_date >= '2023-01-01' & eip$enc_date <= '2023-12-31'), ]
summary(enc$enc_date)






# CTR Testing

table(enc$ctr_calc)
ctr_tests <- enc[which(enc$ctr_calc == 1), ]
ctr_tests <- nrow(ctr_tests)
ctr_tests

table(enc$ctr_calc, enc$final_test_status_hiv)
ctr_positive <- enc[which(enc$ctr_calc == 1 & enc$final_test_status_hiv == 1), ]
ctr_positive <- nrow(ctr_positive)
ctr_positive

table(enc$ctr_calc, enc$final_test_status_hiv, enc$diagnosis_hiv)
ctr_new_positive <- enc[which(enc$ctr_calc == 1 & enc$final_test_status_hiv == 1 & enc$diagnosis_hiv == 1), ]
ctr_new_positive <- nrow(ctr_new_positive)
ctr_new_positive

ctr_positivity_rate <- percent(ctr_new_positive/ctr_tests, accuracy = 0.01)
ctr_positivity_rate





# EHE Testing

table(enc$ehe_calc)
ehe_tests <- enc[which(enc$ehe_calc == 1), ]
ehe_tests <- nrow(ehe_tests)
ehe_tests

table(enc$ehe_calc, enc$final_test_status_hiv)
ehe_positive <- enc[which(enc$ehe_calc == 1 & enc$final_test_status_hiv == 1), ]
ehe_positive <- nrow(ehe_positive)
ehe_positive

table(enc$ehe_calc, enc$final_test_status_hiv, enc$diagnosis_hiv)
ehe_new_positive <- enc[which(enc$ehe_calc == 1 & enc$final_test_status_hiv == 1 & enc$diagnosis_hiv == 1), ]
ehe_new_positive <- nrow(ehe_new_positive)
ehe_new_positive

ehe_positivity_rate <- percent(ehe_new_positive/ehe_tests, accuracy = 0.01)
ehe_positivity_rate






# Overall Positivity Rate for Rapid-testing

eip_total_hiv_tests <- ctr_tests + ehe_tests
eip_total_hiv_tests
eip_total_pos_hiv_tests <- ctr_new_positive + ehe_new_positive
eip_total_pos_hiv_tests
eip_positivity_rate <- percent(eip_total_pos_hiv_tests/eip_total_hiv_tests, accuracy = 0.01)
eip_positivity_rate




# Daily Testing NUmbers

daily_hiv_testing <- select(enc, enc_date, record_id, ctr_calc, ehe_calc)
daily_hiv_testing <- daily_hiv_testing[which(daily_hiv_testing$ctr_calc == 1 | daily_hiv_testing$ehe_calc == 1), ]
head(daily_hiv_testing)
daily_hiv_testing <- select(daily_hiv_testing, -record_id)
head(daily_hiv_testing)
colnames(daily_hiv_testing)[2] <- 'ctr_tests'
colnames(daily_hiv_testing)[3] <- 'ehe_tests'
head(daily_hiv_testing)

daily_hiv_tests <- aggregate(x = daily_hiv_testing[c("ctr_tests","ehe_tests")],
                             FUN = sum,
                             by = list(Date = daily_hiv_testing$enc_date))
daily_hiv_tests$ctr_tests[is.na(daily_hiv_tests$ctr_tests)] <- 0
daily_hiv_tests$ehe_tests[is.na(daily_hiv_tests$ehe_tests)] <- 0
head(daily_hiv_tests)
daily_hiv_tests







# Monthly Testing NUmbers

monthly_hiv_testing <- select(enc, enc_date, record_id, ctr_calc, ehe_calc)
monthly_hiv_testing <- monthly_hiv_testing[which(monthly_hiv_testing$ctr_calc == 1 | monthly_hiv_testing$ehe_calc == 1), ]
head(monthly_hiv_testing)
monthly_hiv_testing <- select(monthly_hiv_testing, -record_id)
head(monthly_hiv_testing)
colnames(monthly_hiv_testing)[2] <- 'ctr_tests'
colnames(monthly_hiv_testing)[3] <- 'ehe_tests'
monthly_hiv_testing$ctr_tests[is.na(monthly_hiv_testing$ctr_tests)] <- 0
monthly_hiv_testing$ehe_tests[is.na(monthly_hiv_testing$ehe_tests)] <- 0
head(monthly_hiv_testing)

monthly_hiv_testing$Date <- format(as.Date(monthly_hiv_testing$enc_date, format="%d/%m/%Y"),"%m/%Y")
head(monthly_hiv_testing)


monthly_hiv_tests <- aggregate(cbind(ctr_tests, ehe_tests) ~ Date,
                               monthly_hiv_testing,
                                  FUN = sum)
head(monthly_hiv_tests)
monthly_hiv_tests


```

## HIV Testing - Overview


Testing for Human Immunodeficiency Virus (HIV) is a major focus for EIP, and there are several methods for testing and funding streams that are a part of the program. The various programs that involve HIV testing are covered on this page. In parallel with lab-based testing conducted within the hospital and/or clinical settings, rapid-based testing conducted by EIP has been around since the start of the program in 1998 in some form or another.


The following table shows an overview of the total number of tests within each testing program, the total number of positives as well as the number of newly identified positive cases, and the positivity rate for each program. The overall positivity rate for the combined rapid-based testing methods within EIP is [**`r eip_positivity_rate`**]{style="color: red;"} (`r eip_total_pos_hiv_tests` total new positives out of `r eip_total_hiv_tests` total rapid-HIV tests).


```{r}

hiv_testing_tbl <- data.frame(matrix(ncol = 3, nrow = 0))
colnames(hiv_testing_tbl) <- c('.', 'CTR', 'EHE')
hiv_testing_tbl[nrow(hiv_testing_tbl) + 1,] <- list('Number of Tests', ctr_tests, ehe_tests)
hiv_testing_tbl[nrow(hiv_testing_tbl) + 1,] <- list('Positives', ctr_positive, ehe_positive)
hiv_testing_tbl[nrow(hiv_testing_tbl) + 1,] <- list('New Positives', ctr_new_positive, ehe_new_positive)
hiv_testing_tbl[nrow(hiv_testing_tbl) + 1,] <- list('Positivity Rate', ctr_positivity_rate, ehe_positivity_rate)
reactable(hiv_testing_tbl)


```


Daily HIV testing is tracked for each independent program and is shown in the chart below. The subsequent table also shows the number of tests for each HIV testing method on a daily basis.


```{r}

daily_hiv_testing_plot <- ggplot(daily_hiv_tests, aes(x = Date)) +
  geom_line(aes(y = ctr_tests), color = "salmon") +
  geom_line(aes(y = ehe_tests), color = "darkgreen") +
  ylab("Count") +
  ggtitle("Daily HIV Testing")

ggplotly(daily_hiv_testing_plot)


daily_hiv_testing_table <- select(daily_hiv_tests, Date, ctr_tests, ehe_tests)
colnames(daily_hiv_testing_table)[2] <- 'CTR Tests'
colnames(daily_hiv_testing_table)[3] <- 'EHE Tests'
reactable(daily_hiv_testing_table,
          showPageSizeOptions = TRUE,
          pageSizeOptions = c(10, 15, 31),
          defaultPageSize = 10)

```


However, since the reporting for each of these programs is done on a monthly basis, it is easier to look at the total number of tests that are conducted for each program within a monthly structure. The figure below shows the monthly testing numbers for each of the programs, as well as in the subsequent table.


```{r}

monthly_hiv_testing_plot <- plot_ly(data = monthly_hiv_tests, x = ~Date, y = ~ctr_tests, type = 'bar', name = 'CTR Tests',
             text = ~ctr_tests, textposition = 'auto',
             marker = list(color = 'salmon')) %>%
  add_trace(y = ~ehe_tests, name = 'EHE Tests',
            text = ~ehe_tests, textposition = 'auto',
            marker = list(color = 'darkgreen')) %>%
  layout(yaxis = list(title = 'Total HIV Tests'), barmode = 'stack')
monthly_hiv_testing_plot



monthly_hiv_testing_table <- select(monthly_hiv_tests, Date, ctr_tests, ehe_tests)
colnames(monthly_hiv_testing_table)[2] <- 'CTR Tests'
colnames(monthly_hiv_testing_table)[3] <- 'EHE Tests'
reactable(monthly_hiv_testing_table,
          showPageSizeOptions = TRUE,
          pageSizeOptions = c(12, 24),
          defaultPageSize = 12)

```


# CTR Testing 


The Counseling, Testing, and Referral to treatment (CTR) testing program...


# EHE Testing


The Ending the HIV Epidemic (EHE) testing program...


# NACCHO Testing


Spot holder for NACCHO definition and data.




