---
title: "Human Trafficking"
description: |
  The purpose of this form will be to document more detailed information regarding EIP efforts around screening and linkage for human trafficking.
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}

rm(list=ls(all=T))

library(dplyr)
library(tidyverse)
library(lubridate)
library(plotly)
library(ggplot2)
library(reactable)
library(htmltools)
library(lubridate)
library(hrbrthemes)
library(gt)
library(janitor)
library(scales)
library(apyramid)


eip <- read.csv('M:/EIP Data/EIP Database/REDCap Ver 5.0/EIP Database Data 20230627_0807.csv')
dim(eip)

```

```{r, include=FALSE}

# Person-level data is only visit_001_arm_1, use to match to encounters

table(eip$redcap_event_name)
person <- eip[which(eip$redcap_event_name == 'visit_001_arm_1'), ]
dim(person)

person <- select(person, record_id, mrn, dob, 
                 race___1, race___2, race___3, race___4, race___5, race___6, ethnicity,
                 sex_raised, sex_selfdefined, insurance, address_county,
                 address_zip_code)
dim(person)

eip <- select(eip, -mrn, -dob, 
              -race___1, -race___2, -race___3, -race___4, -race___5, 
              -race___6, -ethnicity,
              -sex_raised, -sex_selfdefined, -insurance, -address_county,
              -address_zip_code)

# Merge person dataset with full eip dataset

dim(eip)
dim(person)
eip <- merge(eip, person, by='record_id', all.x=T)
dim(eip)
eip <- distinct(eip)
dim(eip)


# Formatting variables

summary(eip$enc_date)
eip$enc_date <- as.Date(eip$enc_date, format='%m/%d/%Y')
summary(eip$enc_date)

summary(eip$dob)
eip$dob <- as.Date(eip$dob, format='%m/%d/%Y')
summary(eip$dob)


table(eip$race___1)
White <- eip[which(eip$race___1 == '1'), ]
dim(White)
White <- select(White, record_id)
White$White <- 1
table(White$White)
White <- distinct(White)
dim(White)
head(White)

table(eip$race___2)
Black <- eip[which(eip$race___2 == '1'), ]
dim(Black)
Black <- select(Black, record_id)
Black$Black <- 1
table(Black$Black)
Black <- distinct(Black)
dim(Black)
head(Black)

table(eip$race___3)
Asian <- eip[which(eip$race___3 == '1'), ]
dim(Asian)
Asian <- select(Asian, record_id)
Asian$Asian <- 1
table(Asian$Asian)
Asian <- distinct(Asian)
dim(Asian)
head(Asian)

table(eip$race___4)
AmIn <- eip[which(eip$race___4 == '1'), ]
dim(AmIn)
AmIn <- select(AmIn, record_id)
AmIn$AmIn <- 1
table(AmIn$AmIn)
AmIn <- distinct(AmIn)
dim(AmIn)
head(AmIn)

table(eip$race___5)
RaceOther <- eip[which(eip$race___5 == '1'), ]
dim(RaceOther)
RaceOther <- select(RaceOther, record_id)
RaceOther$RaceOther <- 1
table(RaceOther$RaceOther)
RaceOther <- distinct(RaceOther)
dim(RaceOther)
head(RaceOther)

table(eip$race___6)
RaceUnk <- eip[which(eip$race___6 == '1'), ]
dim(RaceUnk)
RaceUnk <- select(RaceUnk, record_id)
RaceUnk$RaceUnk <- 1
table(RaceUnk$RaceUnk)
RaceUnk <- distinct(RaceUnk)
dim(RaceUnk)
head(RaceUnk)

table(eip$ethnicity)
RaceHisp <- eip[which(eip$ethnicity == 1), ]
dim(RaceHisp)
RaceHisp <- select(RaceHisp, record_id)
RaceHisp$RaceHisp <- 1
table(RaceHisp$RaceHisp)
RaceHisp <- distinct(RaceHisp)
dim(RaceHisp)
head(RaceHisp)


race <- select(eip, record_id)
race <- distinct(race)
dim(race)


dim(race)
race <- merge(race, White, by = 'record_id', all.x = T)
race <- merge(race, Black, by = 'record_id', all.x = T)
race <- merge(race, Asian, by = 'record_id', all.x = T)
race <- merge(race, AmIn, by = 'record_id', all.x = T)
race <- merge(race, RaceOther, by = 'record_id', all.x = T)
race <- merge(race, RaceUnk, by = 'record_id', all.x = T)
race <- merge(race, RaceHisp, by = 'record_id', all.x = T)
dim(race)
head(race)

race$White[is.na(race$White)] <- 0
race$Black[is.na(race$Black)] <- 0
race$Asian[is.na(race$Asian)] <- 0
race$AmIn[is.na(race$AmIn)] <- 0
race$RaceOther[is.na(race$RaceOther)] <- 0
race$RaceUnk[is.na(race$RaceUnk)] <- 0
race$RaceHisp[is.na(race$RaceHisp)] <- 0

race$RaceNumber <- race$White + race$Black + race$Asian + race$AmIn + race$RaceOther + race$RaceUnk + race$RaceHisp
table(race$RaceNumber)
head(race)

race$race[race$RaceNumber == 1 & race$Black == 1] <- 'Black/African American'
race$race[race$RaceNumber == 1 & race$White == 1] <- 'White'
race$race[race$RaceNumber == 1 & race$Asian == 1] <- 'Asian/Pacific Islander'
race$race[race$RaceNumber == 1 & race$AmIn == 1] <- 'American Indian/Alaska native'
race$race[race$RaceNumber == 1 & race$RaceOther == 1] <- 'Other'
race$race[(race$RaceNumber == 1 & race$RaceHisp == 1) |
            (race$RaceNumber > 1 & race$RaceHisp == 1)] <- 'Hispanic/Latinx'
race$race[race$RaceNumber > 1 & race$RaceHisp != 1] <- 'Biracial/Multiracial'
race$race[race$RaceNumber == 0 | is.na(race$RaceNumber) | race$RaceUnk == 1] <- 'Unknown'
table(race$race)

dim(eip)
dim(race)
eip <- merge(eip, race, by = 'record_id', all.x = T)
dim(eip)
table(eip$race)




table(eip$sex_raised)
eip$sex[eip$sex_raised == 1] <- 'Male'
eip$sex[eip$sex_raised == 2] <- 'Female'
eip$sex[eip$sex_raised == 3 | is.na(eip$sex_raised) | eip$sex_raised == ''] <- 'Unknown/Unassigned'
table(eip$sex)



table(eip$sex_raised, eip$sex_selfdefined)
eip$gender[eip$sex_raised == 1 & eip$sex_selfdefined == 1] <- 'Male'
eip$gender[eip$sex_raised == 2 & eip$sex_selfdefined == 2] <- 'Female'
eip$gender[(eip$sex_raised == 1 & eip$sex_selfdefined == 2) |
             (eip$sex_raised == 2 & eip$sex_selfdefined == 1) |
             (eip$sex_raised == 1 & eip$sex_selfdefined == 3) |
             (eip$sex_raised == 2 & eip$sex_selfdefined == 3)] <- 'Transgender/Nonbinary'
eip$gender[(eip$sex_raised == 3 & eip$sex_selfdefined == 3) |
             is.na(eip$sex_raised) | is.na(eip$sex_selfdefined)] <- 'Unknown'
table(eip$gender)


table(eip$insurance)
eip$insurance[eip$insurance == 1] <- 'None'
eip$insurance[eip$insurance == 2] <- 'UC Health (Levy)'
eip$insurance[eip$insurance == 3] <- 'Medicaid'
eip$insurance[eip$insurance == 4] <- 'Medicare'
eip$insurance[eip$insurance == 5] <- 'Military/VA'
eip$insurance[eip$insurance == 6] <- 'Private'
eip$insurance[eip$insurance == 7] <- 'Dual Medicaid/Medicare'
eip$insurance[is.na(eip$insurance)] <- 'Unknown'
table(eip$insurance)



# Populations of Interest
### WOC, Youth (18-24), MSM, IDU, HRHS, PLWHA

table(eip$race, eip$gender)
eip$WOC[(eip$race != 'White' & eip$race != 'Unknown') & eip$gender == 'Female'] <- 1
table(eip$WOC)


table(eip$age)
eip$Youth[eip$age >= 13 & eip$age <= 29] <- 1
table(eip$Youth)


eip$MSM[eip$gender == 'Male' & ((eip$sex_orientation == '2' | eip$sex_orientation == '4') |
                                  (eip$sex_w_man___1 == '1' | eip$sex_w_man___2 == '1' |
                                     eip$sex_w_man___3 == '1') |
                                  (eip$sex_w_ftm___1 == '1' | eip$sex_w_ftm___2 == '1' |
                                     eip$sex_w_ftm___3 == '1') |
                                  (eip$sex_msm___1 == '1' | eip$sex_msm___2 == '1' |
                                     eip$sex_msm___3 == '1') |
                                  (eip$hiv_dx_risks___2 == '1'))] <- 1
table(eip$MSM)


eip$IDU[eip$idu_calc == 1 | eip$hiv_dx_risks___3 == '1'] <- 1
table(eip$IDU)


# For HRHS, all sexual behavior is within the previous 12 months
### Heterosexual males that have unprotected sex with women
### Heterosexual women that have unprotected sex with men
### Heterosexual women that have sex with MSM
### Heterosexual men/women that have sex with IDU
### Heterosexual men/women that have sex with HIV+ partner
### Heterosexual men/women that exchange money/drugs for sex
### Heterosexual men/women that have sex with STD+ partner
### Heterosexual men/women that have more than 3 partners

eip$Hetero[(eip$gender == 'Male' & (eip$sex_w_woman___1 == '1' |
                                      eip$sex_w_woman___2 == '1' | eip$sex_w_woman___3 == '1')) |
             (eip$gender == 'Female' & (eip$sex_w_man___1 == '1' | eip$sex_w_man___2 == '1' |
                                          eip$sex_w_man___3 == '1'))] <- 1
table(eip$Hetero)


eip$HRHS[(eip$Hetero == 1) & ((((eip$sex_w_woman___6 == '1' | eip$sex_w_woman___7 == '1') |
                                  (is.na(eip$sex_w_woman___6) & is.na(eip$sex_w_woman___7) &
                                     is.na(eip$sex_w_woman___8)))) | (((eip$sex_w_man___6 == '1' |
                                                                          eip$sex_w_man___7 == '1') |
                                                                         (is.na(eip$sex_w_man___6) &
                                                                            is.na(eip$sex_w_man___7) &
                                                                            is.na(eip$sex_w_man___8)))) |
                                (eip$sex_msm___1 == '1' | eip$sex_msm___2 == '1' | eip$sex_msm___3 == '1') |
                                (eip$sex_idu___1 == '1' | eip$sex_idu___2 == '1' | eip$sex_idu___3 == '1') |
                                (eip$sex_hiv_pos___1 == '1' | eip$sex_hiv_pos___2 == '1' |
                                   eip$sex_hiv_pos___3 == '1') | (eip$sex_receivemoney___1 == '1' |
                                                                    eip$sex_receivemoney___2 == '1' |
                                                                    eip$sex_receivemoney___3 == '1' |
                                                                    eip$sex_receivedrugs___1 == '1' |
                                                                    eip$sex_receivedrugs___2 == '1' |
                                                                    eip$sex_receivedrugs___3 == '1' |
                                                                    eip$sex_paymoney___1 == '1' |
                                                                    eip$sex_paymoney___2 == '1' |
                                                                    eip$sex_paymoney___3 == '1' |
                                                                    eip$sex_paydrugs___1 == '1' |
                                                                    eip$sex_paydrugs___2 == '1' |
                                                                    eip$sex_paydrugs___3 == '1')  |
                                (eip$sex_sti_pos___1 == '1' | eip$sex_sti_pos___2 == '1' |
                                   eip$sex_sti_pos___3 == '1') | (eip$sex_partners_past_year >= 3))] <- 1
table(eip$HRHS)




# Appalachian

eip$appalachian_pt[eip$address_zip_code == 43006 | eip$address_zip_code == 43056 |
                     eip$address_zip_code == 43076 | eip$address_zip_code == 43101 |
                     eip$address_zip_code == 43102 | eip$address_zip_code == 43107 |
                     eip$address_zip_code == 43111 | eip$address_zip_code == 43115 |
                     eip$address_zip_code == 43127 | eip$address_zip_code == 43135 |
                     eip$address_zip_code == 43138 | eip$address_zip_code == 43144 |
                     eip$address_zip_code == 43148 | eip$address_zip_code == 43149 |
                     eip$address_zip_code == 43150 | eip$address_zip_code == 43152 |
                     eip$address_zip_code == 43155 | eip$address_zip_code == 43158 |
                     eip$address_zip_code == 43160 | eip$address_zip_code == 43164 |
                     eip$address_zip_code == 43701 | eip$address_zip_code == 43702 |
                     eip$address_zip_code == 43711 | eip$address_zip_code == 43713 |
                     eip$address_zip_code == 43716 | eip$address_zip_code == 43717 |
                     eip$address_zip_code == 43718 | eip$address_zip_code == 43719 |
                     eip$address_zip_code == 43720 | eip$address_zip_code == 43722 |
                     eip$address_zip_code == 43723 | eip$address_zip_code == 43724 |
                     eip$address_zip_code == 43725 | eip$address_zip_code == 43727 |
                     eip$address_zip_code == 43728 | eip$address_zip_code == 43730 |
                     eip$address_zip_code == 43731 | eip$address_zip_code == 43732 |
                     eip$address_zip_code == 43733 | eip$address_zip_code == 43734 |
                     eip$address_zip_code == 43735 | eip$address_zip_code == 43736 |
                     eip$address_zip_code == 43738 | eip$address_zip_code == 43739 |
                     eip$address_zip_code == 43746 | eip$address_zip_code == 43747 |
                     eip$address_zip_code == 43748 | eip$address_zip_code == 43749 |
                     eip$address_zip_code == 43750 | eip$address_zip_code == 43752 |
                     eip$address_zip_code == 43754 | eip$address_zip_code == 43755 |
                     eip$address_zip_code == 43756 | eip$address_zip_code == 43757 |
                     eip$address_zip_code == 43758 | eip$address_zip_code == 43759 |
                     eip$address_zip_code == 43760 | eip$address_zip_code == 43761 |
                     eip$address_zip_code == 43762 | eip$address_zip_code == 43764 |
                     eip$address_zip_code == 43766 | eip$address_zip_code == 43767 |
                     eip$address_zip_code == 43768 | eip$address_zip_code == 43771 |
                     eip$address_zip_code == 43772 | eip$address_zip_code == 43773 |
                     eip$address_zip_code == 43777 | eip$address_zip_code == 43778 |
                     eip$address_zip_code == 43779 | eip$address_zip_code == 43780 |
                     eip$address_zip_code == 43782 | eip$address_zip_code == 43783 |
                     eip$address_zip_code == 43786 | eip$address_zip_code == 43787 |
                     eip$address_zip_code == 43788 | eip$address_zip_code == 43791 |
                     eip$address_zip_code == 43793 | eip$address_zip_code == 43802 |
                     eip$address_zip_code == 43803 | eip$address_zip_code == 43804 |
                     eip$address_zip_code == 43805 | eip$address_zip_code == 43811 |
                     eip$address_zip_code == 43812 | eip$address_zip_code == 43821 |
                     eip$address_zip_code == 43822 | eip$address_zip_code == 43824 |
                     eip$address_zip_code == 43828 | eip$address_zip_code == 43830 |
                     eip$address_zip_code == 43832 | eip$address_zip_code == 43836 |
                     eip$address_zip_code == 43837 | eip$address_zip_code == 43840 |
                     eip$address_zip_code == 43842 | eip$address_zip_code == 43843 |
                     eip$address_zip_code == 43844 | eip$address_zip_code == 43845 |
                     eip$address_zip_code == 43901 | eip$address_zip_code == 43902 |
                     eip$address_zip_code == 43903 | eip$address_zip_code == 43905 |
                     eip$address_zip_code == 43906 | eip$address_zip_code == 43907 |
                     eip$address_zip_code == 43908 | eip$address_zip_code == 43909 |
                     eip$address_zip_code == 43910 | eip$address_zip_code == 43912 |
                     eip$address_zip_code == 43913 | eip$address_zip_code == 43914 |
                     eip$address_zip_code == 43915 | eip$address_zip_code == 43916 |
                     eip$address_zip_code == 43917 | eip$address_zip_code == 43920 |
                     eip$address_zip_code == 43925 | eip$address_zip_code == 43926 |
                     eip$address_zip_code == 43927 | eip$address_zip_code == 43928 |
                     eip$address_zip_code == 43930 | eip$address_zip_code == 43931 |
                     eip$address_zip_code == 43932 | eip$address_zip_code == 43933 |
                     eip$address_zip_code == 43934 | eip$address_zip_code == 43935 |
                     eip$address_zip_code == 43937 | eip$address_zip_code == 43938 |
                     eip$address_zip_code == 43939 | eip$address_zip_code == 43940 |
                     eip$address_zip_code == 43941 | eip$address_zip_code == 43942 |
                     eip$address_zip_code == 43943 | eip$address_zip_code == 43944 |
                     eip$address_zip_code == 43945 | eip$address_zip_code == 43946 |
                     eip$address_zip_code == 43947 | eip$address_zip_code == 43948 |
                     eip$address_zip_code == 43950 | eip$address_zip_code == 43951 |
                     eip$address_zip_code == 43952 | eip$address_zip_code == 43953 |
                     eip$address_zip_code == 43961 | eip$address_zip_code == 43962 |
                     eip$address_zip_code == 43963 | eip$address_zip_code == 43964 |
                     eip$address_zip_code == 43967 | eip$address_zip_code == 43968 |
                     eip$address_zip_code == 43970 | eip$address_zip_code == 43971 |
                     eip$address_zip_code == 43972 | eip$address_zip_code == 43973 |
                     eip$address_zip_code == 43974 | eip$address_zip_code == 43976 |
                     eip$address_zip_code == 43977 | eip$address_zip_code == 43981 |
                     eip$address_zip_code == 43983 | eip$address_zip_code == 43984 |
                     eip$address_zip_code == 43985 | eip$address_zip_code == 43986 |
                     eip$address_zip_code == 43988 | eip$address_zip_code == 44003 |
                     eip$address_zip_code == 44004 | eip$address_zip_code == 44005 |
                     eip$address_zip_code == 44010 | eip$address_zip_code == 44030 |
                     eip$address_zip_code == 44032 | eip$address_zip_code == 44041 |
                     eip$address_zip_code == 44046 | eip$address_zip_code == 44047 |
                     eip$address_zip_code == 44048 | eip$address_zip_code == 44057 |
                     eip$address_zip_code == 44062 | eip$address_zip_code == 44064 |
                     eip$address_zip_code == 44068 | eip$address_zip_code == 44076 |
                     eip$address_zip_code == 44082 | eip$address_zip_code == 44084 |
                     eip$address_zip_code == 44085 | eip$address_zip_code == 44086 |
                     eip$address_zip_code == 44088 | eip$address_zip_code == 44093 |
                     eip$address_zip_code == 44099 | eip$address_zip_code == 44231 |
                     eip$address_zip_code == 44288 | eip$address_zip_code == 44401 |
                     eip$address_zip_code == 44402 | eip$address_zip_code == 44403 |
                     eip$address_zip_code == 44404 | eip$address_zip_code == 44405 |
                     eip$address_zip_code == 44406 | eip$address_zip_code == 44408 |
                     eip$address_zip_code == 44410 | eip$address_zip_code == 44411 |
                     eip$address_zip_code == 44412 | eip$address_zip_code == 44413 |
                     eip$address_zip_code == 44415 | eip$address_zip_code == 44416 |
                     eip$address_zip_code == 44417 | eip$address_zip_code == 44418 |
                     eip$address_zip_code == 44420 | eip$address_zip_code == 44422 |
                     eip$address_zip_code == 44423 | eip$address_zip_code == 44424 |
                     eip$address_zip_code == 44425 | eip$address_zip_code == 44427 |
                     eip$address_zip_code == 44428 | eip$address_zip_code == 44429 |
                     eip$address_zip_code == 44430 | eip$address_zip_code == 44431 |
                     eip$address_zip_code == 44432 | eip$address_zip_code == 44436 |
                     eip$address_zip_code == 44437 | eip$address_zip_code == 44438 |
                     eip$address_zip_code == 44439 | eip$address_zip_code == 44440 |
                     eip$address_zip_code == 44441 | eip$address_zip_code == 44442 |
                     eip$address_zip_code == 44443 | eip$address_zip_code == 44444 |
                     eip$address_zip_code == 44445 | eip$address_zip_code == 44446 |
                     eip$address_zip_code == 44449 | eip$address_zip_code == 44450 |
                     eip$address_zip_code == 44451 | eip$address_zip_code == 44452 |
                     eip$address_zip_code == 44453 | eip$address_zip_code == 44454 |
                     eip$address_zip_code == 44455 | eip$address_zip_code == 44460 |
                     eip$address_zip_code == 44470 | eip$address_zip_code == 44471 |
                     eip$address_zip_code == 44473 | eip$address_zip_code == 44481 |
                     eip$address_zip_code == 44482 | eip$address_zip_code == 44483 |
                     eip$address_zip_code == 44484 | eip$address_zip_code == 44485 |
                     eip$address_zip_code == 44486 | eip$address_zip_code == 44490 |
                     eip$address_zip_code == 44491 | eip$address_zip_code == 44492 |
                     eip$address_zip_code == 44493 | eip$address_zip_code == 44501 |
                     eip$address_zip_code == 44502 | eip$address_zip_code == 44503 |
                     eip$address_zip_code == 44504 | eip$address_zip_code == 44505 |
                     eip$address_zip_code == 44506 | eip$address_zip_code == 44507 |
                     eip$address_zip_code == 44509 | eip$address_zip_code == 44510 |
                     eip$address_zip_code == 44511 | eip$address_zip_code == 44512 |
                     eip$address_zip_code == 44513 | eip$address_zip_code == 44514 |
                     eip$address_zip_code == 44515 | eip$address_zip_code == 44555 |
                     eip$address_zip_code == 44601 | eip$address_zip_code == 44607 |
                     eip$address_zip_code == 44608 | eip$address_zip_code == 44609 |
                     eip$address_zip_code == 44610 | eip$address_zip_code == 44611 |
                     eip$address_zip_code == 44612 | eip$address_zip_code == 44615 |
                     eip$address_zip_code == 44617 | eip$address_zip_code == 44619 |
                     eip$address_zip_code == 44620 | eip$address_zip_code == 44621 |
                     eip$address_zip_code == 44622 | eip$address_zip_code == 44624 |
                     eip$address_zip_code == 44625 | eip$address_zip_code == 44626 |
                     eip$address_zip_code == 44627 | eip$address_zip_code == 44628 |
                     eip$address_zip_code == 44629 | eip$address_zip_code == 44633 |
                     eip$address_zip_code == 44634 | eip$address_zip_code == 44637 |
                     eip$address_zip_code == 44638 | eip$address_zip_code == 44639 |
                     eip$address_zip_code == 44643 | eip$address_zip_code == 44644 |
                     eip$address_zip_code == 44651 | eip$address_zip_code == 44653 |
                     eip$address_zip_code == 44654 | eip$address_zip_code == 44656 |
                     eip$address_zip_code == 44657 | eip$address_zip_code == 44660 |
                     eip$address_zip_code == 44661 | eip$address_zip_code == 44663 |
                     eip$address_zip_code == 44665 | eip$address_zip_code == 44671 |
                     eip$address_zip_code == 44672 | eip$address_zip_code == 44675 |
                     eip$address_zip_code == 44676 | eip$address_zip_code == 44678 |
                     eip$address_zip_code == 44679 | eip$address_zip_code == 44680 |
                     eip$address_zip_code == 44681 | eip$address_zip_code == 44682 |
                     eip$address_zip_code == 44683 | eip$address_zip_code == 44687 |
                     eip$address_zip_code == 44688 | eip$address_zip_code == 44689 |
                     eip$address_zip_code == 44690 | eip$address_zip_code == 44693 |
                     eip$address_zip_code == 44695 | eip$address_zip_code == 44697 |
                     eip$address_zip_code == 44699 | eip$address_zip_code == 44730 |
                     eip$address_zip_code == 44842 | eip$address_zip_code == 45101 |
                     eip$address_zip_code == 45102 | eip$address_zip_code == 45103 |
                     eip$address_zip_code == 45105 | eip$address_zip_code == 45106 |
                     eip$address_zip_code == 45107 | eip$address_zip_code == 45112 |
                     eip$address_zip_code == 45115 | eip$address_zip_code == 45118 |
                     eip$address_zip_code == 45119 | eip$address_zip_code == 45120 |
                     eip$address_zip_code == 45121 | eip$address_zip_code == 45122 |
                     eip$address_zip_code == 45123 | eip$address_zip_code == 45130 |
                     eip$address_zip_code == 45131 | eip$address_zip_code == 45132 |
                     eip$address_zip_code == 45133 | eip$address_zip_code == 45135 |
                     eip$address_zip_code == 45140 | eip$address_zip_code == 45142 |
                     eip$address_zip_code == 45144 | eip$address_zip_code == 45147 |
                     eip$address_zip_code == 45148 | eip$address_zip_code == 45150 |
                     eip$address_zip_code == 45153 | eip$address_zip_code == 45154 |
                     eip$address_zip_code == 45155 | eip$address_zip_code == 45156 |
                     eip$address_zip_code == 45157 | eip$address_zip_code == 45158 |
                     eip$address_zip_code == 45159 | eip$address_zip_code == 45160 |
                     eip$address_zip_code == 45162 | eip$address_zip_code == 45167 |
                     eip$address_zip_code == 45168 | eip$address_zip_code == 45171 |
                     eip$address_zip_code == 45172 | eip$address_zip_code == 45176 |
                     eip$address_zip_code == 45244 | eip$address_zip_code == 45245 |
                     eip$address_zip_code == 45255 | eip$address_zip_code == 45601 |
                     eip$address_zip_code == 45612 | eip$address_zip_code == 45613 |
                     eip$address_zip_code == 45614 | eip$address_zip_code == 45616 |
                     eip$address_zip_code == 45617 | eip$address_zip_code == 45618 |
                     eip$address_zip_code == 45619 | eip$address_zip_code == 45620 |
                     eip$address_zip_code == 45621 | eip$address_zip_code == 45622 |
                     eip$address_zip_code == 45623 | eip$address_zip_code == 45624 |
                     eip$address_zip_code == 45628 | eip$address_zip_code == 45629 |
                     eip$address_zip_code == 45630 | eip$address_zip_code == 45631 |
                     eip$address_zip_code == 45633 | eip$address_zip_code == 45634 |
                     eip$address_zip_code == 45636 | eip$address_zip_code == 45638 |
                     eip$address_zip_code == 45640 | eip$address_zip_code == 45642 |
                     eip$address_zip_code == 45643 | eip$address_zip_code == 45644 |
                     eip$address_zip_code == 45645 | eip$address_zip_code == 45646 |
                     eip$address_zip_code == 45647 | eip$address_zip_code == 45648 |
                     eip$address_zip_code == 45650 | eip$address_zip_code == 45651 |
                     eip$address_zip_code == 45652 | eip$address_zip_code == 45653 |
                     eip$address_zip_code == 45654 | eip$address_zip_code == 45656 |
                     eip$address_zip_code == 45657 | eip$address_zip_code == 45658 |
                     eip$address_zip_code == 45659 | eip$address_zip_code == 45660 |
                     eip$address_zip_code == 45661 | eip$address_zip_code == 45662 |
                     eip$address_zip_code == 45663 | eip$address_zip_code == 45669 |
                     eip$address_zip_code == 45671 | eip$address_zip_code == 45672 |
                     eip$address_zip_code == 45673 | eip$address_zip_code == 45674 |
                     eip$address_zip_code == 45675 | eip$address_zip_code == 45677 |
                     eip$address_zip_code == 45678 | eip$address_zip_code == 45679 |
                     eip$address_zip_code == 45680 | eip$address_zip_code == 45681 |
                     eip$address_zip_code == 45682 | eip$address_zip_code == 45683 |
                     eip$address_zip_code == 45684 | eip$address_zip_code == 45685 |
                     eip$address_zip_code == 45686 | eip$address_zip_code == 45687 |
                     eip$address_zip_code == 45688 | eip$address_zip_code == 45690 |
                     eip$address_zip_code == 45692 | eip$address_zip_code == 45693 |
                     eip$address_zip_code == 45694 | eip$address_zip_code == 45695 |
                     eip$address_zip_code == 45696 | eip$address_zip_code == 45697 |
                     eip$address_zip_code == 45698 | eip$address_zip_code == 45699 |
                     eip$address_zip_code == 45701 | eip$address_zip_code == 45710 |
                     eip$address_zip_code == 45711 | eip$address_zip_code == 45712 |
                     eip$address_zip_code == 45713 | eip$address_zip_code == 45714 |
                     eip$address_zip_code == 45715 | eip$address_zip_code == 45716 |
                     eip$address_zip_code == 45717 | eip$address_zip_code == 45719 |
                     eip$address_zip_code == 45720 | eip$address_zip_code == 45721 |
                     eip$address_zip_code == 45723 | eip$address_zip_code == 45724 |
                     eip$address_zip_code == 45727 | eip$address_zip_code == 45729 |
                     eip$address_zip_code == 45732 | eip$address_zip_code == 45734 |
                     eip$address_zip_code == 45735 | eip$address_zip_code == 45739 |
                     eip$address_zip_code == 45740 | eip$address_zip_code == 45741 |
                     eip$address_zip_code == 45742 | eip$address_zip_code == 45743 |
                     eip$address_zip_code == 45744 | eip$address_zip_code == 45745 |
                     eip$address_zip_code == 45746 | eip$address_zip_code == 45750 |
                     eip$address_zip_code == 45760 | eip$address_zip_code == 45761 |
                     eip$address_zip_code == 45764 | eip$address_zip_code == 45766 |
                     eip$address_zip_code == 45767 | eip$address_zip_code == 45768 |
                     eip$address_zip_code == 45769 | eip$address_zip_code == 45770 |
                     eip$address_zip_code == 45771 | eip$address_zip_code == 45772 |
                     eip$address_zip_code == 45773 | eip$address_zip_code == 45775 |
                     eip$address_zip_code == 45776 | eip$address_zip_code == 45777 |
                     eip$address_zip_code == 45778 | eip$address_zip_code == 45779 |
                     eip$address_zip_code == 45780 | eip$address_zip_code == 45782 |
                     eip$address_zip_code == 45783 | eip$address_zip_code == 45784 |
                     eip$address_zip_code == 45786 | eip$address_zip_code == 45787 |
                     eip$address_zip_code == 45788 | eip$address_zip_code == 45789 |
                     (eip$appalachian == 1 | eip$appalachian_family == 1)] <- 1
table(eip$appalachian_pt)




###############################################################################################################
#########################################  Creating Encounter Dataset  ########################################
###############################################################################################################

summary(eip$enc_date)
enc <- eip[which(eip$enc_date >= '2023-01-01' & eip$enc_date <= '2023-12-31'), ]
summary(enc$enc_date)


eip_encounters <- nrow(enc)
eip_encounters


table(enc$offer_outcome_risks)
assessments <- enc[which(enc$offer_outcome_risks == 1), ]
dim(assessments)
eip_assessments <- nrow(assessments)
eip_assessments


eip_assessments_percent <- percent(eip_assessments/eip_encounters, accuracy = 0.1)
eip_assessments_percent


enc$ht_assessed[(enc$unsafe_work == 0 | enc$unsafe_work == 1 | enc$unsafe_work == 3) |
                  (enc$forced_work == 0 | enc$forced_work == 1 | enc$forced_work == 3) |
                  (enc$fear_leave_work == 0 | enc$fear_leave_work == 1 | enc$fear_leave_work == 3) |
                  (enc$exchange_for_sex == 0 | enc$exchange_for_sex == 1 | enc$exchange_for_sex == 3) |
                  (enc$sex_receivemoney___0 == 1 |
                     enc$sex_receivemoney___1 == 1 |
                     enc$sex_receivemoney___2 == 1 |
                     enc$sex_receivemoney___3 == 1 |
                     enc$sex_receivemoney___4 == 1 |
                     enc$sex_receivemoney___5 == 1 |
                     enc$sex_receivedrugs___0 == 1 |
                     enc$sex_receivedrugs___1 == 1 |
                     enc$sex_receivedrugs___2 == 1 |
                     enc$sex_receivedrugs___3 == 1 |
                     enc$sex_receivedrugs___4 == 1 |
                     enc$sex_receivedrugs___5 == 1) |
                  (enc$safe_in_relationship == 0 | enc$safe_in_relationship == 1) |
                  (enc$pressure_sex == 0 | enc$pressure_sex == 1)] <- 1
table(enc$ht_assessed)
ht_assessed <- enc[which(enc$ht_assessed == 1), ]
dim(ht_assessed)
ht_assessed <- nrow(ht_assessed)
ht_assessed


ht_assessed_percent <- percent(ht_assessed/eip_assessments, accuracy = 0.1)
ht_assessed_percent


enc$ht_assessed_pulvino[(enc$unsafe_work == 0 | enc$unsafe_work == 1) |
                          (enc$forced_work == 0 | enc$forced_work == 1) |
                          (enc$fear_leave_work == 0 | enc$fear_leave_work == 1) |
                          (enc$exchange_for_sex == 0 | enc$exchange_for_sex == 1)] <- 1
table(enc$ht_assessed_pulvino)
ht_assessed_pulvino <- enc[which(enc$ht_assessed_pulvino == 1), ]
dim(ht_assessed_pulvino)
ht_assessed_pulvino <- nrow(ht_assessed_pulvino)
ht_assessed_pulvino


ht_assessed_pulvino_percent <- percent(ht_assessed_pulvino/eip_assessments, accuracy = 0.1)
ht_assessed_pulvino_percent


enc$ht_pos_pulvino[enc$unsafe_work == 1 |
                     enc$forced_work == 1 |
                     enc$fear_leave_work == 1 |
                     enc$exchange_for_sex == 1] <- 1
table(enc$ht_pos_pulvino)
ht_pos_pulvino <- enc[which(enc$ht_pos_pulvino == 1), ]
dim(ht_pos_pulvino)
ht_pos_pulvino <- nrow(ht_pos_pulvino)
ht_pos_pulvino


ht_pos_pulvino_percent <- percent(ht_pos_pulvino/ht_assessed_pulvino, accuracy = 0.1)
ht_pos_pulvino_percent



table(enc$unsafe_work)
ht_unsafe_work_assessed <- enc[which(!is.na(enc$unsafe_work)), ]
ht_unsafe_work_assessed <- nrow(ht_unsafe_work_assessed)
ht_unsafe_work_assessed

ht_unsafe_work_yes <- enc[which(enc$unsafe_work == 1), ]
ht_unsafe_work_yes <- nrow(ht_unsafe_work_yes)
ht_unsafe_work_yes
ht_unsafe_work_ypercent <- percent(ht_unsafe_work_yes/ht_unsafe_work_assessed, accurracy = 0.1)
ht_unsafe_work_ypercent

ht_unsafe_work_no <- enc[which(enc$unsafe_work == 0), ]
ht_unsafe_work_no <- nrow(ht_unsafe_work_no)
ht_unsafe_work_no

ht_unsafe_work_na <- enc[which(enc$unsafe_work == 2), ]
ht_unsafe_work_na <- nrow(ht_unsafe_work_na)
ht_unsafe_work_na

ht_unsafe_work_declined <- enc[which(enc$unsafe_work == 3), ]
ht_unsafe_work_declined <- nrow(ht_unsafe_work_declined)
ht_unsafe_work_declined



table(enc$forced_work)
ht_forced_work_assessed <- enc[which(!is.na(enc$forced_work)), ]
ht_forced_work_assessed <- nrow(ht_forced_work_assessed)
ht_forced_work_assessed

ht_forced_work_yes <- enc[which(enc$forced_work == 1), ]
ht_forced_work_yes <- nrow(ht_forced_work_yes)
ht_forced_work_yes
ht_forced_work_ypercent <- percent(ht_forced_work_yes/ht_forced_work_assessed, accurracy = 0.1)
ht_forced_work_ypercent

ht_forced_work_no <- enc[which(enc$forced_work == 0), ]
ht_forced_work_no <- nrow(ht_forced_work_no)
ht_forced_work_no

ht_forced_work_na <- enc[which(enc$forced_work == 2), ]
ht_forced_work_na <- nrow(ht_forced_work_na)
ht_forced_work_na

ht_forced_work_declined <- enc[which(enc$forced_work == 3), ]
ht_forced_work_declined <- nrow(ht_forced_work_declined)
ht_forced_work_declined



table(enc$fear_leave_work)
ht_fear_work_assessed <- enc[which(!is.na(enc$fear_leave_work)), ]
ht_fear_work_assessed <- nrow(ht_fear_work_assessed)
ht_fear_work_assessed

ht_fear_work_yes <- enc[which(enc$fear_leave_work == 1), ]
ht_fear_work_yes <- nrow(ht_fear_work_yes)
ht_fear_work_yes
ht_fear_work_ypercent <- percent(ht_fear_work_yes/ht_fear_work_assessed, accurracy = 0.1)
ht_fear_work_ypercent

ht_fear_work_no <- enc[which(enc$fear_leave_work == 0), ]
ht_fear_work_no <- nrow(ht_fear_work_no)
ht_fear_work_no

ht_fear_work_na <- enc[which(enc$fear_leave_work == 2), ]
ht_fear_work_na <- nrow(ht_fear_work_na)
ht_fear_work_na

ht_fear_work_declined <- enc[which(enc$fear_leave_work == 3), ]
ht_fear_work_declined <- nrow(ht_fear_work_declined)
ht_fear_work_declined



table(enc$exchange_for_sex)
ht_exchange_sex_assessed <- enc[which(!is.na(enc$exchange_for_sex)), ]
ht_exchange_sex_assessed <- nrow(ht_exchange_sex_assessed)
ht_exchange_sex_assessed

ht_exchange_sex_yes <- enc[which(enc$exchange_for_sex == 1), ]
ht_exchange_sex_yes <- nrow(ht_exchange_sex_yes)
ht_exchange_sex_yes
ht_exchange_sex_ypercent <- percent(ht_exchange_sex_yes/ht_exchange_sex_assessed, accurracy = 0.1)
ht_exchange_sex_ypercent

ht_exchange_sex_no <- enc[which(enc$exchange_for_sex == 0), ]
ht_exchange_sex_no <- nrow(ht_exchange_sex_no)
ht_exchange_sex_no

ht_exchange_sex_na <- enc[which(enc$exchange_for_sex == 2), ]
ht_exchange_sex_na <- nrow(ht_exchange_sex_na)
ht_exchange_sex_na

ht_exchange_sex_declined <- enc[which(enc$exchange_for_sex == 3), ]
ht_exchange_sex_declined <- nrow(ht_exchange_sex_declined)
ht_exchange_sex_declined


```


EIP officially began screening for human trafficking (HT) within the EIP Database as of **December 1st, 2022** with the introduction of Dr. Christa Pulvino's pilot grant. The EIP assessment has had some general questions that may indicate the risk of an individual being in a HT situation, but new assessment questions were added to indicate a risk for trafficking, as well as the HPA's general impression of whether the individual was at risk based on additional information. Additional resources for HT were included within the EIP list, and a new, electronic version of the EIP resource list was created that allowed the ability for patients to access the list of EIP resources using a QR code. The data captured for this project is provided on this page, along with additional data that pertains to the HT efforts within EIP.


There are a total of `r eip_encounters` encounters with EIP, with a total of `r eip_assessments` assessments completed (*`r eip_assessments_percent` of the total number of encounters*). As mentioned above, there are several questions within the EIP assessment that may indicate whether someone is in an at-risk situation for HT. The total number of assessments where *at least one* of these questions was asked and answered is `r ht_assessed` (*`r ht_assessed_percent` of the total number of assessments, `r ht_assessed`/`r eip_assessments`*). The questions that are included in the total assessed for HT (*in addition to the questions provided by Dr. Pulvino*) are noted below:

- *When did you last receive money and/or drugs for sex?*
- *Do you feel safe in your relationship?*
- *Does your partner pressure you into having sex?*


However, when we only consider those questions that were included with Dr. Pulvino's HT assessment, the number of assessments where this specific screening was done was `r ht_assessed_pulvino` (*`r ht_assessed_pulvino_percent` of the total number of assessments, `r ht_assessed_pulvino`/`r eip_assessments`*). Individuals are considered at risk for HT if they respond 'Yes' to any of the questions in this HT assessment. The total number of assessments where an individual screened positive for HT risk is `r ht_pos_pulvino` (*`r ht_pos_pulvino_percent` of the total assessed using Dr. Pulvino's assessment, `r ht_pos_pulvino`/`r ht_assessed_pulvino`*). The summary table for HT screening is provided below.


```{r, layout="l-page"}

ht_summary_tbl <- data.frame(matrix(ncol = 6, nrow = 0))
colnames(ht_summary_tbl) <- c('HT Assessed', '% Assessed', 'HT Assessed (Pulvino)', '% Assessed (Pulvino)', 'Screened HT+', '% HT+')
ht_summary_tbl[nrow(ht_summary_tbl) + 1,] <- list(ht_assessed, ht_assessed_percent, ht_assessed_pulvino, ht_assessed_pulvino_percent, ht_pos_pulvino, ht_pos_pulvino_percent)
reactable(ht_summary_tbl)

```


The breakdown of the responses for each question on Dr. Pulvino's HT assessment are provided in the table below.


```{r, layout="l-page"}

ht_pulvino_tbl <- data.frame(matrix(ncol = 7, nrow = 0))
colnames(ht_pulvino_tbl) <- c('Question', '# Assessed', 'Yes', '% Yes', 'No', 'Not Asked', 'Declined')
ht_pulvino_tbl[nrow(ht_pulvino_tbl) + 1,] <- list('Have you ever worked, or done other things, in a place that made you feel scared or unsafe?', ht_unsafe_work_assessed, ht_unsafe_work_yes, ht_unsafe_work_ypercent, ht_unsafe_work_no, ht_unsafe_work_na, ht_unsafe_work_declined)
ht_pulvino_tbl[nrow(ht_pulvino_tbl) + 1,] <- list('In thinking back over your past experience, have you ever been tricked or forced into doing any kind of work that you did not want to do?', ht_forced_work_assessed, ht_forced_work_yes, ht_forced_work_ypercent, ht_forced_work_no, ht_forced_work_na, ht_forced_work_declined)
ht_pulvino_tbl[nrow(ht_pulvino_tbl) + 1,] <- list('Have you ever been afraid to leave or quit a work situation due to fears of violence or threats of harm to yourself or your family?', ht_fear_work_assessed, ht_fear_work_yes, ht_fear_work_ypercent, ht_fear_work_no, ht_fear_work_na, ht_fear_work_declined)
ht_pulvino_tbl[nrow(ht_pulvino_tbl) + 1,] <- list('Have you ever received anything in exchange for sex (for example, a place to stay, gifts, or food)?', ht_exchange_sex_assessed, ht_exchange_sex_yes, ht_exchange_sex_ypercent, ht_exchange_sex_no, ht_exchange_sex_na, ht_exchange_sex_declined)
reactable(ht_pulvino_tbl,
          columns = list(
            Question = colDef(name = "",
                              minWidth = 300)))

```





# Things to include:

- Number referred for HT

- Number of encounters where the HPA suspects HT

- Number where they were suspected and referred for HT

- Number where they screened positive and were referred

- Number where they were suspected and screened positive

- Linkage flow data

- Number/percentage in an unsafe relationship

- Number/percentage that were pressured into sex












