---
title: "EIP Data Website"
description: |
  This site is currently under construction. The plan for this page is a general introduction to EIP and the data/data sources, the EIP mission statement, and other general info.
date: "`r Sys.Date()`"
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

## **EIP Mission:**

*The UC Early Intervention Program is committed to identifying and intervening with populations most at risk for threats to health and well-being at the earliest opportunity, and helping these individuals connect with community resources to improve health outcomes.*

## Timeline of EIP

This is an example of the potential timeline that can be included to document the history of EIP, when things were introduced, when research projects were conducted, etc. You can scroll to zoom in and out of the timeline, as well as drag to focus on particular time points or projects. Hovering over the specific text will give you exact dates and/or date ranges of each item.

```{r}
library(timevis)

eip_timespan <- data.frame(
  id = 1:8,
  content = c("Start of EIP",
              "PGx Study",
              "Peer Volunteers",
              "NACCHO",
              "Test & Protect",
              "NIDA-CTN0069",
              "Brown Study",
              "ASPIRE"),
  start = c("1/1/1998",
            "6/17/2020",
            "10/1/2018",
            "7/1/2023",
            "10/1/2020",
            "7/1/2017",
            "4/1/2014",
            "9/30/2018"),
  end = c(NA,
          "11/1/2022",
          NA,
          NA,
          "12/1/2022",
          "7/1/2018",
          "12/30/2019",
          "9/29/2023"),
  type = c("box",
           "range",
           "point",
           "box",
           "range",
           "range",
           "range",
           "range"),
  title = c("1/1/1998",
            "PGx 6/17/2020 - 11/1/2022",
            "Peers 10/1/2018",
            "NACCHO 7/1/2023 - Present",
            "TaP 10/1/2020 - 12/1/2022",
            "NIDA-CTN 7/1/2017 - Unknown",
            "NINR-Brown 4/1/2014 - 12/30/2019",
            "SAMHSA ASPIRE 9/30/2018 - 9/29/2023"),
  style = c(NA,
            "color: steelblue;",
            NA,
            NA,
            "color: steelblue;",
            "color: steelblue;",
            "color: steelblue;",
            "color: steelblue;"))
timevis(eip_timespan, showZoom = FALSE)

```
